### 2015-09-19 paper.tex
Imported template

\documentclass[12pt]{amsart}
\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, enumitem, graphicx, mathtools, xfrac, tikz-cd, nameref, thmtools, hyperref}
\usepackage[utf8]{inputenc}
\usepackage[backend=biber, citestyle=numeric-comp, natbib=true, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
\usepackage[activate={true,nocompatibility}]{microtype}
\usepackage[capitalize]{cleveref}

\newlist{thmlist}{enumerate}{1} \setlist[thmlist]{label=(\roman{thmlisti}), ref=\thethm.(\roman{thmlisti}),noitemsep} \Crefname{thmlisti}{Theorem}{Theorems}
\newlist{lemlist}{enumerate}{1} \setlist[lemlist]{label=(\roman{lemlisti}), ref=\thelemma.(\roman{lemlisti}),noitemsep} \Crefname{lemlisti}{Lemma}{Lemmas}

\theoremstyle{plain} \declaretheorem[name=Theorem, Refname={Theorem,Theorems}]{thm} \Crefname{thm}{Theorem}{Theorems}
\numberwithin{equation}{section}

\newtheorem{lemma}{Lemma} \numberwithin{lemma}{section} \Crefname{lemma}{Lemma}{Lemmas}
\newtheorem{cor}[lemma]{Corollary} \Crefname{cor}{Corollary}{Corollaries}
\newtheorem{prop}[lemma]{Proposition} \Crefname{prop}{Proposition}{Propositions}
\newtheorem*{thm*}{Theorem}
\newtheorem*{lemma*}{Lemma}
\theoremstyle{definition} \newtheorem{dfn}[lemma]{Definition} \Crefname{dfn}{Definition}{Definitions}
\newtheorem{example}[lemma]{Example} \Crefname{example}{Example}{Examples}
\theoremstyle{remark} \newtheorem{rem}[lemma]{Remark} \Crefname{rem}{Remark}{Remarks}

%Page layout
\textwidth 16cm 
\textheight 22cm 
\headheight 0.5cm 
\evensidemargin 0.3cm 
\oddsidemargin 0.2cm

%Theorem counters
\numberwithin{equation}{section}
\newcounter{thmcounter} 
\newcounter{lemmacounter}
\newtheorem{thm}[thmcounter]{Theorem}
\newtheorem{prop}[thmcounter]{Proposition}
\newtheorem{cor}[thmcounter]{Corollary}
\newtheorem{lemma}[lemmacounter]{Lemma}
\theoremstyle{definition}
\newtheorem{rem}[equation]{Remark}
\newtheorem{example}[equation]{Example}
\newtheorem{dfn}[equation]{Definition}
\newtheorem{notation}[equation]{Notation}

\newcommand{\catname}[1]{{\normalfont\textbf{#1}}}
\newcommand{\Ker}{\operatorname{Ker}}
\newcommand{\Cent}{\operatorname{Cent}}
\newcommand{\Img}{\operatorname{Im}}
\newcommand{\Coker}{\operatorname{Coker}}
\newcommand{\coker}{\operatorname{coker}}
\newcommand{\K}{\operatorname{\mathrm{K}}}
\newcommand{\GG}{\operatorname{\mathrm{G}}}
\newcommand{\St}{\operatorname{\mathrm{St}}}
\newcommand{\StU}{\operatorname{\hat{\mathrm{U}}}}
\newcommand{\G}{\operatorname{\mathrm{G}}}
\newcommand{\E}{\operatorname{\mathrm{E}}}
\newcommand{\M}{\operatorname{\mathrm{M}}}
\newcommand{\sr}{\operatorname{\mathrm{sr}}}
\newcommand{\Um}{\operatorname{\mathrm{Um}}}
\newcommand{\rk}{\operatorname{\mathrm{rk}}}
\newcommand{\rA}{\mathsf{A}}
\newcommand{\rB}{\mathsf{B}}
\newcommand{\rC}{\mathsf{C}} 
\newcommand{\rD}{\mathsf{D}} 
\newcommand{\rE}{\mathsf{E}}
\newcommand{\HH}{\mathrm{H}}
\newcommand{\eval}[4]{ev \textstyle \left[\frac{#2[#1] \rightarrow #3}{#1 \mapsto #4}\right]}
\newcommand{\ev}[3]{\eval{t}{#1}{#2}{#3}}

\newcommand\restr[2]{{\left.\kern-\nulldelimiterspace #1 \vphantom{\big|}\right|_{#2}}}
\newcommand*\MapsTo{\xrightarrow[\raisebox{0.25 em}{\smash{\ensuremath{\sim}}}]{}}

\title{Local-global principle for $\K_2$ of Chevalley groups}
\keywords {Chevalley groups, Steinberg groups, $K_2$-functor. {\em Mathematical Subject Classification (2010):} 19C09; 20G35}
\author {Andrei Lavrenov, Sergey Sinchuk}
\email {avlavrenov{\it at}gmail.com, sinchukss {\it at} gmail.com}
\date {\today}

\begin{document}

\begin{abstract} To be written. \end{abstract}

\maketitle

\section {Introduction}\label{intro}

\subsection{Acknowledgements}
The authors of the present paper acknowledges financial support from Russian Science Foundation grant 14-11-00297.

\section {Preliminaries}\label{prelim}

\printbibliography

\end{document}

### 2015-09-27 paper.tex
Minor
Added notes from meeting

@@
 \oddsidemargin 0.2cm
-
-%Theorem counters
-\numberwithin{equation}{section}
-\newcounter{thmcounter} 
-\newcounter{lemmacounter}
-\newtheorem{thm}[thmcounter]{Theorem}
-\newtheorem{prop}[thmcounter]{Proposition}
-\newtheorem{cor}[thmcounter]{Corollary}
-\newtheorem{lemma}[lemmacounter]{Lemma}
-\theoremstyle{definition}
-\newtheorem{rem}[equation]{Remark}
-\newtheorem{example}[equation]{Example}
-\newtheorem{dfn}[equation]{Definition}
-\newtheorem{notation}[equation]{Notation}
 
@@
 \author {Andrei Lavrenov, Sergey Sinchuk}
-\email {avlavrenov{\it at}gmail.com, sinchukss {\it at} gmail.com}
+\email {avlavrenov {\it at} gmail.com, sinchukss {\it at} gmail.com}
 \date {\today}
@@
 
+\section {Main results}
+
+\begin{dfn}
+ Let $u$,$v$ be elements of $B^n$ such that $v^Tu = 0$ and there exists $w \in B^n$ such that $<w,u> = a^N$.
+ In this context we define elements $Z^1(u,v)$ and 
+\end{dfn}
+
+for each $(u,v) \in \E_n(R) (e_1, e_2)$ we can find $y$ such that $(u,v,y) = g (e_1, e_2, e_3)$.
+
+$w^tu = a^N$, $z^Tv = a^N$, $x^T y = a^N$ + 6 additional orthogonality relations
+
+Computing $g = [Z^{1, N}(u xba^{2N}), Z^{2, N}(ua^{2N},v)]$ 
+$$ g = Z^{2, N}(ya^{2N} + uba^{5N},v) {Z^{2, N}(ya^{2N}, v)}^{-1} = Z^{2, N}(uba^{5N},v) = Z^2(uc, v)$$
+$$ g = ... = Z^1(u, vc)$$
+
 \printbibliography

### 2015-09-27 paper.tex
Added definition of the relative Steinberg group

@@
 \usepackage[backend=biber, citestyle=numeric-comp, natbib=true, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
+\addbibresource{paper.bib}
 \usepackage[activate={true,nocompatibility}]{microtype}
@@
 
+\subsection{Relative Steinberg group in rank $3$ and Tulenbaev's section map} 
+The main goal of this subsection is to construct Tulenbaev's section map from~\cite[\S~2]{T} for
+the linear Steinberg group of rank $3$. Combining this result with the amalgamation theorem
+of the the second named author (see~\cite[Theorem~9]{S15}) we deduce centrality for the orthogonal
+$\K_2$ in the next subsection.
+
+First of all, we will need to give yet another definition of the relative linear Steinberg group 
+(cf. \cite[Definitions~3.3 and 3.7]{S15}).
+
+\begin{dfn}
+ The relative Steinberg group $\St^*(n,R, I)$ is the group defined by the following two
+ families generators and four families of relations.
+ \begin{itemize}
+  \item Generators:
+  \begin{enumerate}
+  \item $X^1(u, v)$, where $u \in \E(n,R) \cdot e_1$, $v\ \in I^n$ such that $v^t \cdot u = 0$;
+  \item $X^2(u, v)$, where $u \in I^n$, $v \in \E(n,R) \cdot e_1$ such that $v^t \cdot u = 0$.
+ \end{enumerate}
+  Notice that the canonical image in $\E(n, R)$ of both $X^1(u, v)$ and $X^2(u, v)$ equals $T(u, v) = e_n + u \cdot v^T$.
+  \item Relations:
+  \begin{enumerate}
+  \item $X^1(u, v) \cdot X^1(u, w) = X^1(u, v+w)$, $u \in \E(n,R) \cdot e_1$, $v, w \in I^n$;
+  \item $X^2(u, v) \cdot X^2(w, v) = X^2(u+w, v)$, $u, w \in I^n$, $v \in \E(n,R) \cdot e_1$;
+  \item ${}^{X^\sigma(u^2, v^2)} \! X^\tau(u^1, v^1) = X^\tau(T(u^2, v^2) \cdot u^1, T(v^2, u^2)^{-1} \cdot v^1)$, $\sigma, \tau = 1..2$;
+  \item $X^1(u, vb) = X^2(ub, v)$ for $(u,v) \in E(n,R) \cdot (e_1, e_2)$, $b\in I$.
+ \end{enumerate}
+ \end{itemize}
+\end{dfn}
+It is easy to check correctness of the above definition.
+
+\begin{lemma}
+ The groups $\St^*(n, R, I)$ and $\St(n, R, I)$ are isomorphic.
+\end{lemma}
+\begin{proof}
+ TODO: 
+\end{proof}
+
+The next step is construct
+
 \begin{dfn}
@@
 
+\subsection{Centrality of orthogonal $K_2$.}
+
 \printbibliography

### 2015-09-27 paper.tex
Writing down construction of Tulenbaev elements

@@
 \end{dfn}
-It is easy to check correctness of the above definition.
+It is easy to check the correctness of the above definition.
 
@@
 
-The next step is construct
+The next step of the proof is to is construct certain elements in $\St(n, R)$ which are similar to Tulenbaev's elements $X_{u,v}(a)$ see~\cite[\S~1]{T}.
 
-\begin{dfn}
- Let $u$,$v$ be elements of $B^n$ such that $v^Tu = 0$ and there exists $w \in B^n$ such that $<w,u> = a^N$.
- In this context we define elements $Z^1(u,v)$ and 
-\end{dfn}
+Assume that $n \geq 4$. For the rest of this section $a$ denotes a nonnilpotent element of $R$.
+\begin{lemma}
+ Let $u, v \in R^n$ be columns such that $v^t \cdot u = 0$ and there exists $w = w(u) \in R^n$ satisfying $w^t \cdot u = a^N$ for some natural number $N$.
+ In this context one can define certain elements $Z^{1}(u,v), Z^{2}(v, u)$ of $\St(n, R)$. These elements satisfy the following relations:
+ \begin{itemize}
+  \item $Z^{1}(u, v_1 + v_2) = Z^{1}(u, v_1) \cdot Z^{1}(u, v_2)$;
+  \item $Z^{2}(v_1 + v_2, u) = Z^{2}(v_1, u) \cdot Z^{2}(v_2, u)$;
+  \item ${}^{g}\! Z^{\tau}(u, v) = Z^{\tau}(g \cdot u, g^* \cdot v)$, $\tau = 1..2$, $g \in \St(n, R)$ where $g^* = {g^t}^{-1}$ is the contragradient matrix.
+ \end{itemize}
+\end{lemma}
+\begin{proof} Both the construction of $Z^i$ and the relations for $Z^i$ are, in essence, just~\cite[Lemma~1.3]{T} applied twice. \end{proof}
+
+%TODO: Why we can assume u_1^t \cdot u_2 = 0$?
+Now let $g \in \E(n, R_a)$ be such that $g(e_1, e_2) = (\overline{u_1}, \overline{u_2})$ for some $u_1, u_2\in R^n$, $u_1^t \cdot u_2 = 0$.
+It is easy to find $w_1, w_2 \in R^n$ such that $w_1^t \cdot u_1 = a^{N_1}$, $w_2^t \cdot u_2 = a^{N_2}$.
+
+$Z^1(u, v) = Z^2(v, u)$.
 

### 2015-09-28 paper.tex
Fixed bug in the notation

@@
   \item ${}^{X^\sigma(u^2, v^2)} \! X^\tau(u^1, v^1) = X^\tau(T(u^2, v^2) \cdot u^1, T(v^2, u^2)^{-1} \cdot v^1)$, $\sigma, \tau = 1..2$;
-  \item $X^1(u, vb) = X^2(ub, v)$ for $(u,v) \in E(n,R) \cdot (e_1, e_2)$, $b\in I$.
+  \item $X^1(g \cdot e_1, g^* \cdot be_2) = X^2(g \cdot be_1, g^* \cdot e_2)$ where $g^* = {g^t}^{-1}$ is the contragradient matrix and $b\in I$.
  \end{enumerate}
@@
   \item $Z^{2}(v_1 + v_2, u) = Z^{2}(v_1, u) \cdot Z^{2}(v_2, u)$;
-  \item ${}^{g}\! Z^{\tau}(u, v) = Z^{\tau}(g \cdot u, g^* \cdot v)$, $\tau = 1..2$, $g \in \St(n, R)$ where $g^* = {g^t}^{-1}$ is the contragradient matrix.
+  \item ${}^{g}\! Z^{\tau}(u, v) = Z^{\tau}(g \cdot u, g^* \cdot v)$, $\tau = 1..2$, $g \in \St(n, R)$.
  \end{itemize}
@@
 \begin{proof} Both the construction of $Z^i$ and the relations for $Z^i$ are, in essence, just~\cite[Lemma~1.3]{T} applied twice. \end{proof}
+
+\begin{lemma}
+ For $u_1, u_2 \in R^n$ be columns such that $\overline{u_1} = g \cdot e_1$, $\overline{u_2} = g^* \cdot e_2$ for some $g \in \E(n, R_a)$.
+ Then for any $b\in I$ and $g',g'' \in M(n, R)$ such that $\overline{g'} = g$, $\overline{g''} = g^*$ one has 
+ $$Z^1(g' \cdot e_1, g'' \cdot be_2) = Z^2(g' \cdot be_1, g'' \cdot e_2).$$
+\end{lemma}
 

### 2015-09-30 paper.tex
Added a passage removed from JPAA article

@@
 
-The next step of the proof is to is construct certain elements in $\St(n, R)$ which are similar to Tulenbaev's elements $X_{u,v}(a)$ see~\cite[\S~1]{T}.
+The next step of the proof is to is construct certain elements in $\St(n, R)$ similar to Tulenbaev's elements $X_{u,v}(a)$ see~\cite[\S~1]{T}.
 
 Assume that $n \geq 4$. For the rest of this section $a$ denotes a nonnilpotent element of $R$.
+
+Let $v\in R^n$ be a column.
+A column $w\in R^n$ is called \emph{$v$-decomposable} if it can be presented as a finite sum $w = \sum\limits_{i=1}^n w^i$ of columns such that each $w^i$ 
+has at least two zero entries. 
+Denote by $D(v)$ the submodule of $R^n$ consisting of all $v$-decomposable columns.
+%For a column $v\in R^n$ denote by $I(v)$ the ideal of $R$ spanned by coordinates $v_1,\ldots, v_n$.
+
+Let $u,v,w\in R^n$ be columns such that $w^tv=0$.
+It is easy to check that $(uv)\cdot w = \sum_{i<j}w_{ij}$, where $w_{ij} = (w_iu_j - w_ju_i)(v_je_i - v_ie_j)\in{}\!A^n$ (cf.~\cite[Lemma~3.2]{Ka}).
+Such decomposition is called the {\it canonical} decomposition of $(uv)\cdot w$.
+In particular, this shows that row $a\cdot w$ is always $v$-decomposable for $a\in I(v)$, i.e. $I(v) \cdot O(v) \subseteq D(v)$.
+It is also obvious that $O(v)\subseteq O(bv)$, $D(v)\subseteq D(bv)$ for $b \in R$.
+
+Let $v$ be a (not neccessarily unimodular) column of height $n$, let $w$ be a $v$-decomposable row and $a$ be an element of $I(v)$.
+In this context Tulenbaev defines elements $X_{v,w}(a)$ of the Steinberg group $\St(n, A)$, $n\geq 4$ (see~\cite[\S~1]{T}).
+Tulenbaev requires $a \in I(v)$ in order to prove correctness of his definition.
+
+Let us list certain useful properties of these elements.
+\begin{lemma}\label{T13} Let $n\geq 4$. Elements $X_{v,w}(a)$ satisfy the following relations:
+\begin{enumerate}
+ \item $X_{v, w}(ab) = X_{v, bw}(a)$ for $w\in D(v)$, $b\in R$, $a\in I(v)$. If moreover $a\in b \cdot I(v)$ then $X_{v, w}(ab) = X_{bv, w}(a)$.
+ \item $X_{v,w_1 + w_2}(a) = X_{v, w_1}(a) X_{v, w_2}(a)$, $w_1, w_2 \in D(v)$, $a\in I(v)$.
+ \item \label{T133} For $g\in\St(n, A)$,  $w\in O(v)$, $a,b\in I(v)$  one has  $g^{-1}\cdot X_{v, bw}(a)\cdot g = X_{g^{-1}v, bwg}(a)$
+ \item Let $a$ be a nonnilpotent element of $A$.
+       For $n\geq 5$ let $(v_1,v_2)\in M_{n\times 2}(A)$ be a matrix such that its image in $M_{n\times 2}(A_a)$ is unimodular.
+       Let $w \in {}^n\!A$ be a row such that $wv_1=wv_2=0$. Then for sufficiently large natural numbers $k, m$ one has
+       $$X_{v_1 + bv_2, a^kw}(a^m) = X_{v_1,a^kw}(a^m)\cdot X_{v_2,ba^kw}(a^m),\ b\in A.$$
+\end{enumerate}\end{lemma}
+
 \begin{lemma}

### 2015-09-30 paper.tex
Written down Lavrenov's computation

--- 2015-09-27 paper.tex
@@
  \end{enumerate}
-  Notice that the canonical image in $\E(n, R)$ of both $X^1(u, v)$ and $X^2(u, v)$ equals $T(u, v) = e_n + u \cdot v^T$.
+  Notice that $\phi$ maps both $X^1(u, v)$ and $X^2(u, v)$ to $T(u, v) = e_n + u \cdot v^T$.
   \item Relations:
@@
   \item ${}^{X^\sigma(u^2, v^2)} \! X^\tau(u^1, v^1) = X^\tau(T(u^2, v^2) \cdot u^1, T(v^2, u^2)^{-1} \cdot v^1)$, $\sigma, \tau = 1..2$;
-  \item $X^1(u, vb) = X^2(ub, v)$ for $(u,v) \in E(n,R) \cdot (e_1, e_2)$, $b\in I$.
+  \item $X^1(g \cdot e_1, g^* \cdot be_2) = X^2(g \cdot be_1, g^* \cdot e_2)$ where $b\in I$ and $g^* = {g^t}^{-1}$ denotes the contragradient matrix.
  \end{enumerate}
@@
 
-The next step of the proof is to is construct certain elements in $\St(n, R)$ which are similar to Tulenbaev's elements $X_{u,v}(a)$ see~\cite[\S~1]{T}.
+The next step of the proof is to is construct certain elements in $\St(n, R)$ similar to Tulenbaev's elements $X_{u,v}(a)$ see~\cite[\S~1]{T}.
 
-Assume that $n \geq 4$. For the rest of this section $a$ denotes a nonnilpotent element of $R$.
+Let $v\in R^n$ be a column.
+A column $w\in R^n$ is called \emph{$v$-decomposable} if it can be presented as a finite sum $w = \sum\limits_{i=1}^n w^i$ such that each $w^i$ has at least two zero entries. 
+Denote by $D(v)$ the submodule of $R^n$ consisting of all $v$-decomposable columns.
+For a column $v\in R^n$ denote by $I(v)$ the ideal of $R$ spanned by coordinates $v_1,\ldots, v_n$.
+
+Let $u,v,w\in R^n$ be columns such that $w^tv=0$.
+It is easy to check (cf.~\cite[Lemma~3.2]{Ka}) that 
+$$(uv)\cdot w = \sum_{i<j}w_{ij},\ \text{where}\ w_{ij} = (w_iu_j - w_ju_i)(v_je_i - v_ie_j)\in{}\!A^n.$$
+The above decomposition is called the \emph{canonical} decomposition of $(uv)\cdot w$.
+In particular, the above argument shows that row $a\cdot w$ is always $v$-decomposable for $a\in I(v)$, i.e. $I(v) \cdot O(v) \subseteq D(v)$.
+It is also obvious that $O(v)\subseteq O(bv)$, $D(v)\subseteq D(bv)$ for $b \in R$.
+%\end{enumerate}\end{lemma}
+
+Denote by $B^1$ the subset of $R^n \times R^n \times R$ consisting of triples $(u, v, a)$ such that $v^t \cdot u = 0$, $v \in D(u)$, $a \in I(u)$.
+Denote by $B^2$ the set consisting of triples $(v, u, a)$ such that $(u, v, a) \in B^1$.
+
+\begin{lemma} \label{lem:Zproperties}
+Assume that $n \geq 4$.
+One can define two families of elements $Z^\tau(u, v, a) \in \St(n, R)$, $\tau=1,2$ parametrized by $(u, v, a) \in B^\tau$ satisfying the following properties
+ \begin{lemlist}
+  \item \label{rel:proj} $\phi(Z^\tau(u, v, a)) = e + uav^t \in \E(n, R)$, $(u,v,a) \in B^\tau$;
+  \item \label{rel:add1} $Z^{1}(u, v_1 + v_2, a) = Z^{1}(u, v_1, a) \cdot Z^{1}(u, v_2, a)$;
+  \item \label{rel:add2} $Z^{2}(v_1 + v_2, u, a) = Z^{2}(v_1, u, a) \cdot Z^{2}(v_2, u, a)$;
+  \item \label{rel:conj} ${}^{g}\! Z^{\tau}(u, v, a) = Z^{\tau}(\phi(g) \cdot u, \phi(g)^* \cdot v, a)$, $\tau = 1,2$, $g \in \St(n, R)$.
+ \end{lemlist}
+\end{lemma}
+\begin{proof}
+One constructs the elements $Z^1(u,v,a)$ in exactly the same way as Tulenbaev constructs his elements $X_{u,v}(a)$ (see definitions preceding~\cite[Lemma~1.2]{T}).
+Next, the elements $Z^2(u,v,a)$ are constructed by ``transposing'' Tulenbaev's construction.
+
+All the properties (with the exception of the last one in the case $n=4$) can be proved in exactly the same fashion as in~\cite[Lemma~1.3]{T}.
+To check the last property in the case $n=4$ one has to use the argument of W. van~der~Kallen (cf.~\cite{Ka}).
+%TODO: Write more details
+\end{proof}
+
+For the rest of this section $a$ denotes a nonnilpotent element of $R$.
 \begin{lemma}
- Let $u, v \in R^n$ be columns such that $v^t \cdot u = 0$ and there exists $w = w(u) \in R^n$ satisfying $w^t \cdot u = a^N$ for some natural number $N$.
- In this context one can define certain elements $Z^{1}(u,v), Z^{2}(v, u)$ of $\St(n, R)$. These elements satisfy the following relations:
- \begin{itemize}
-  \item $Z^{1}(u, v_1 + v_2) = Z^{1}(u, v_1) \cdot Z^{1}(u, v_2)$;
-  \item $Z^{2}(v_1 + v_2, u) = Z^{2}(v_1, u) \cdot Z^{2}(v_2, u)$;
-  \item ${}^{g}\! Z^{\tau}(u, v) = Z^{\tau}(g \cdot u, g^* \cdot v)$, $\tau = 1..2$, $g \in \St(n, R)$ where $g^* = {g^t}^{-1}$ is the contragradient matrix.
- \end{itemize}
+Let $u,v,w,z \in R^n$ be columns such that 
+\begin{equation*} u^t \cdot v = 0,\ w^t \cdot v = c \in R,\ u^t \cdot z = 0,\ w^t \cdot z = 0. \end{equation*}
+Assume, moreover, that $(u, v, a) \in B^1$, $(w, z, a) \in B^2$, then one has $$Z^1(u, ac \cdot z, a) = Z^2(ac \cdot u, z, a).$$
 \end{lemma}
-\begin{proof} Both the construction of $Z^i$ and the relations for $Z^i$ are, in essence, just~\cite[Lemma~1.3]{T} applied twice. \end{proof}
-
-%TODO: Why we can assume u_1^t \cdot u_2 = 0$?
-Now let $g \in \E(n, R_a)$ be such that $g(e_1, e_2) = (\overline{u_1}, \overline{u_2})$ for some $u_1, u_2\in R^n$, $u_1^t \cdot u_2 = 0$.
-It is easy to find $w_1, w_2 \in R^n$ such that $w_1^t \cdot u_1 = a^{N_1}$, $w_2^t \cdot u_2 = a^{N_2}$.
-
-$Z^1(u, v) = Z^2(v, u)$.
-
-for each $(u,v) \in \E_n(R) (e_1, e_2)$ we can find $y$ such that $(u,v,y) = g (e_1, e_2, e_3)$.
-
-$w^tu = a^N$, $z^Tv = a^N$, $x^T y = a^N$ + 6 additional orthogonality relations
-
-Computing $g = [Z^{1, N}(u xba^{2N}), Z^{2, N}(ua^{2N},v)]$ 
-$$ g = Z^{2, N}(ya^{2N} + uba^{5N},v) {Z^{2, N}(ya^{2N}, v)}^{-1} = Z^{2, N}(uba^{5N},v) = Z^2(uc, v)$$
-$$ g = ... = Z^1(u, vc)$$
+\begin{proof}
+Direct computation using \cref{lem:Zproperties} shows that
+ \begin{multline*}
+ Z^2(ac \cdot u, z, a) = Z^2((e+uav^t) w, (e-vau^t)z,a) \cdot Z^2(-w,z,a) = \\
+  {}^{Z^1(u,v,a)} \! Z^2(w,z,a) \cdot Z^2(-w,z,a) = [Z^1(u, v, a), Z^2(w, z, a)] = Z^1(u,v,a) \cdot {}^{Z^2(w,z,a)}\! Z^1(u,-v,a) = \\
+    = Z^1(u,v,a) \cdot Z^1((e+waz^t)u,-(e-zaw^t)v,a) = Z^1(u,ac \cdot z,a). \qedhere
+ \end{multline*}  
+\end{proof}
 

### 2015-10-01 paper.tex
Written down proof of relation 4

@@
 \usepackage[backend=biber, citestyle=numeric-comp, natbib=true, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
-\addbibresource{paper.bib}
 \usepackage[activate={true,nocompatibility}]{microtype}
 \usepackage[capitalize]{cleveref}
+
+%Bibliography
+\renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
+\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{http://dx.doi.org/\thefield{doi}}{#1}}}
+\DeclareFieldFormat{title}{\usebibmacro{string+doi}{\mkbibemph{#1}}}
+\DeclareFieldFormat[article, inproceedings, inbook, thesis]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
+\addbibresource{paper.bib}
 
@@
 
-\title{Local-global principle for $\K_2$ of Chevalley groups}
+\title{A local-global principle for $\K_2$ of Chevalley groups}
 \keywords {Chevalley groups, Steinberg groups, $K_2$-functor. {\em Mathematical Subject Classification (2010):} 19C09; 20G35}
@@
  \end{enumerate}
-  Notice that $\phi$ maps both $X^1(u, v)$ and $X^2(u, v)$ to $T(u, v) = e_n + u \cdot v^T$.
+  Notice that $\phi$ maps both $X^1(u, v)$ and $X^2(u, v)$ to $T(u, v) = e_n + u \cdot v^T \in \E(n, R, I)$.
   \item Relations:
@@
   \item $X^2(u, v) \cdot X^2(w, v) = X^2(u+w, v)$, $u, w \in I^n$, $v \in \E(n,R) \cdot e_1$;
-  \item ${}^{X^\sigma(u^2, v^2)} \! X^\tau(u^1, v^1) = X^\tau(T(u^2, v^2) \cdot u^1, T(v^2, u^2)^{-1} \cdot v^1)$, $\sigma, \tau = 1..2$;
+  \item ${}^{X^\sigma(u^2, v^2)} \! X^\tau(u^1, v^1) = X^\tau(T(u^2, v^2) \cdot u^1, T(v^2, u^2)^{-1} \cdot v^1)$, $\sigma, \tau = 1,2$;
   \item $X^1(g \cdot e_1, g^* \cdot be_2) = X^2(g \cdot be_1, g^* \cdot e_2)$ where $b\in I$ and $g^* = {g^t}^{-1}$ denotes the contragradient matrix.
@@
 Let $v\in R^n$ be a column.
-A column $w\in R^n$ is called \emph{$v$-decomposable} if it can be presented as a finite sum $w = \sum\limits_{i=1}^n w^i$ such that each $w^i$ has at least two zero entries. 
-Denote by $D(v)$ the submodule of $R^n$ consisting of all $v$-decomposable columns.
-For a column $v\in R^n$ denote by $I(v)$ the ideal of $R$ spanned by coordinates $v_1,\ldots, v_n$.
+Denote by $O(v)$ the submodule of $R^n$ consisting of all columns $w$ such that $w^t \cdot v = 0$.
+A column $w\in R^n$ is called \emph{$v$-decomposable} if it can be presented as a finite sum $w = \sum\limits_{i=1}^n w^i$ such that each $w^i$ has at least two zero entries and $v^t \cdot w^i = 0$. 
+Denote by $D(v)$ the submodule of $O(v)$ consisting of all $v$-decomposable columns.
+For a column $v\in R^n$ denote by $I(v)$ the ideal of $R$ spanned by its entries $v_1,\ldots, v_n$.
 
@@
 The above decomposition is called the \emph{canonical} decomposition of $(uv)\cdot w$.
-In particular, the above argument shows that row $a\cdot w$ is always $v$-decomposable for $a\in I(v)$, i.e. $I(v) \cdot O(v) \subseteq D(v)$.
-It is also obvious that $O(v)\subseteq O(bv)$, $D(v)\subseteq D(bv)$ for $b \in R$.
-%\end{enumerate}\end{lemma}
+In particular, this shows that the column $a\cdot w$ is always $v$-decomposable for $a\in I(v)$, $w \in O(v)$, i.\,e. $I(v) \cdot O(v) \subseteq D(v)$.
+It is also straightforward to check that $D(v)\subseteq D(bv)$, $b \cdot D(v) \subseteq D(v)$ for $b \in R$.
 
@@
 Assume that $n \geq 4$.
-One can define two families of elements $Z^\tau(u, v, a) \in \St(n, R)$, $\tau=1,2$ parametrized by $(u, v, a) \in B^\tau$ satisfying the following properties
+One can define two families of elements $Z^\tau(u, v, a)$, $\tau=1,2$ of the group $\St(n, R)$ parametrized by $(u, v, a) \in B^\tau$ satisfying the following properties:
  \begin{lemlist}
-  \item \label{rel:proj} $\phi(Z^\tau(u, v, a)) = e + uav^t \in \E(n, R)$, $(u,v,a) \in B^\tau$;
-  \item \label{rel:add1} $Z^{1}(u, v_1 + v_2, a) = Z^{1}(u, v_1, a) \cdot Z^{1}(u, v_2, a)$;
-  \item \label{rel:add2} $Z^{2}(v_1 + v_2, u, a) = Z^{2}(v_1, u, a) \cdot Z^{2}(v_2, u, a)$;
-  \item \label{rel:conj} ${}^{g}\! Z^{\tau}(u, v, a) = Z^{\tau}(\phi(g) \cdot u, \phi(g)^* \cdot v, a)$, $\tau = 1,2$, $g \in \St(n, R)$.
+  \item \label{item:proj} $\phi(Z^\tau(u, v, a)) = e + uav^t \in \E(n, R)$, $(u,v,a) \in B^\tau$;
+  \item \label{item:add1} $Z^{1}(u, v_1 + v_2, a) = Z^{1}(u, v_1, a) \cdot Z^{1}(u, v_2, a)$;
+  \item \label{item:add2} $Z^{2}(v_1 + v_2, u, a) = Z^{2}(v_1, u, a) \cdot Z^{2}(v_2, u, a)$;
+  \item \label{item:scalar} for $\tau=1,2$ and $b \in R$ if $(u,vb,a), (ub, v, a) \in B^\tau$ then one has
+   $$Z^\tau(u,vb, a) = Z^\tau(u, v, ab) = Z^\tau (ub, v, a);	$$
+  \item \label{item:conj} ${}^{g}\! Z^{\tau}(u, v, a) = Z^{\tau}(\phi(g) \cdot u, \phi(g)^* \cdot v, a)$, $\tau = 1,2$, $g \in \St(n, R)$.
  \end{lemlist}
@@
 One constructs the elements $Z^1(u,v,a)$ in exactly the same way as Tulenbaev constructs his elements $X_{u,v}(a)$ (see definitions preceding~\cite[Lemma~1.2]{T}).
-Next, the elements $Z^2(u,v,a)$ are constructed by ``transposing'' Tulenbaev's construction.
+Next, the elements $Z^2(u,v,a)$ are obtained by ``transposing'' Tulenbaev's construction.
 
-All the properties (with the exception of the last one in the case $n=4$) can be proved in exactly the same fashion as in~\cite[Lemma~1.3]{T}.
+All the properties (with the exception of the last one in the case $n=4$) can be proved by the same token as in~\cite[Lemma~1.3]{T}.
 To check the last property in the case $n=4$ one has to use the argument of W. van~der~Kallen (cf.~\cite{Ka}).
@@
 
-For the rest of this section $a$ denotes a nonnilpotent element of $R$.
-\begin{lemma}
-Let $u,v,w,z \in R^n$ be columns such that 
-\begin{equation*} u^t \cdot v = 0,\ w^t \cdot v = c \in R,\ u^t \cdot z = 0,\ w^t \cdot z = 0. \end{equation*}
-Assume, moreover, that $(u, v, a) \in B^1$, $(w, z, a) \in B^2$, then one has $$Z^1(u, ac \cdot z, a) = Z^2(ac \cdot u, z, a).$$
+For the rest of this section $a$ denotes a nonnilpotent element of $R$ and $\lambda_a \colon R \rightarrow R_a$ is the morphism of principal localization at $a$.
+\begin{lemma} For any $g \in \E(n, R_a)$ there exist $u, v \in R^n$ and sufficiently large natural numbers $k$, $m$ such that the following facts hold:
+\begin{lemlist}
+ \item \label{item:lifts} $\lambda_a(u) = g \cdot a^k e_1$, $\lambda_a(v) = g^* \cdot a^k e_2$ and $u^t \cdot v = 0$;
+ \item \label{item:correctness} $(u, v, a^m) \in B^1 \cap B^2$;
+ \item \label{item:relation4} for $b \in R$ divisible by some sufficiently large power of $a$ one has 
+             $$Z^1(u, b \cdot v, a^m) = Z^2(b \cdot u, v, a^m).$$
+\end{lemlist}
 \end{lemma}
 \begin{proof}
-Direct computation using \cref{lem:Zproperties} shows that
+It is straightforward to choose $u$ and $v$ satisfying the first requirement of the lemma.
+
+To satisfy the second requirement of the lemma we need to choose $u$, $v$ in such a way that $u \in D(v)$, $v \in D(u)$.
+This can also be accomplished if we choose large enough $k$ on the first step.
+Indeed, notice that $I(u) = a^{k_1}$, $I(v) = a^{k_2}$ for some natural $k_1$, $k_2$ hence for $u' = a^{k_2} \cdot u$ and $v' = a^{k_1} \cdot v$ one has
+$$u' \in I(v) \cdot O(v) \subseteq D(v) \subseteq D(v'),\quad v' \in I(u) \cdot O(u) \subseteq D(u) \subseteq D(u'),$$
+as required.
+
+In fact, we can also choose two extra columns $x, y \in R^n$ and a large natural $p$ in such a way that vectors $u,v,x,y$ additionally satisfy the following properties
+\begin{equation*} \lambda_a(x) = g^* \cdot a^k e_3,\ \lambda_a(y) = g \cdot a^k e_3,\ y^t \cdot x = a^p \in R, \end{equation*}
+\begin{equation*} u^t \cdot x = 0,\ u^t \cdot v = 0,\ y^t \cdot v = 0, \end{equation*}
+\begin{equation*} (u, x, a^m) \in B^1,\ (y, v, a^m) \in B^2. \end{equation*}
+
+Now direct computation using \cref{lem:Zproperties} shows that
  \begin{multline*}
- Z^2(ac \cdot u, z, a) = Z^2((e+uav^t) w, (e-vau^t)z,a) \cdot Z^2(-w,z,a) = \\
-  {}^{Z^1(u,v,a)} \! Z^2(w,z,a) \cdot Z^2(-w,z,a) = [Z^1(u, v, a), Z^2(w, z, a)] = Z^1(u,v,a) \cdot {}^{Z^2(w,z,a)}\! Z^1(u,-v,a) = \\
-    = Z^1(u,v,a) \cdot Z^1((e+waz^t)u,-(e-zaw^t)v,a) = Z^1(u,ac \cdot z,a). \qedhere
+ Z^2(a^{m+p}b \cdot u, v, a^m) = Z^2(b \cdot (e+a^m \cdot ux^t)y, (e-a^m \cdot xu^t)v,a^m) \cdot Z^2(-by,v,a^m) = \\
+  = [Z^1(u, x, a^m), Z^2(b \cdot y, v, a^m)] = \\
+    = Z^1(u,x,a^m) \cdot Z^1((e+a^mb \cdot yv^t)u,-(e- a^mb \cdot vy^t)x,a^m) = Z^1(u,a^{m+p}b \cdot v,a^m), \qedhere   
  \end{multline*}  
+hence the third assertion of the lemma follows. 
 \end{proof}

### 2015-10-02 paper.tex
Minor fixes

@@
 
-\subsection{Relative Steinberg group in rank $3$ and Tulenbaev's section map} 
+\subsection{Relative Steinberg group in rank $3$} 
 The main goal of this subsection is to construct Tulenbaev's section map from~\cite[\S~2]{T} for
@@
 
-First of all, we will need to give yet another definition of the relative linear Steinberg group 
+First of all, we will need to formulate yet another presentation of the relative linear Steinberg group 
 (cf. \cite[Definitions~3.3 and 3.7]{S15}).
@@
  \end{enumerate}
-  Notice that $\phi$ maps both $X^1(u, v)$ and $X^2(u, v)$ to $T(u, v) = e_n + u \cdot v^T \in \E(n, R, I)$.
+  Notice that $\phi$ maps both $X^1(u, v)$ and $X^2(u, v)$ to $T(u, v) = e + u \cdot v^t \in \E(n, R, I)$.
   \item Relations:
@@
 Denote by $O(v)$ the submodule of $R^n$ consisting of all columns $w$ such that $w^t \cdot v = 0$.
-A column $w\in R^n$ is called \emph{$v$-decomposable} if it can be presented as a finite sum $w = \sum\limits_{i=1}^n w^i$ such that each $w^i$ has at least two zero entries and $v^t \cdot w^i = 0$. 
+A column $w\in R^n$ is called \emph{$v$-decomposable} if it can be presented as a finite sum $w = \sum\limits_{i=1}^p w^i$ such that each $w^i$ has at least two zero entries and $v^t \cdot w^i = 0$. 
 Denote by $D(v)$ the submodule of $O(v)$ consisting of all $v$-decomposable columns.
@@
   \item \label{item:proj} $\phi(Z^\tau(u, v, a)) = e + uav^t \in \E(n, R)$, $(u,v,a) \in B^\tau$;
-  \item \label{item:add1} $Z^{1}(u, v_1 + v_2, a) = Z^{1}(u, v_1, a) \cdot Z^{1}(u, v_2, a)$;
-  \item \label{item:add2} $Z^{2}(v_1 + v_2, u, a) = Z^{2}(v_1, u, a) \cdot Z^{2}(v_2, u, a)$;
+  \item \label{item:add1} $Z^{1}(u, v + w, a) = Z^{1}(u, v, a) \cdot Z^{1}(u, w, a)$;
+  \item \label{item:add2} $Z^{2}(v + w, u, a) = Z^{2}(v, u, a) \cdot Z^{2}(w, u, a)$;
   \item \label{item:scalar} for $\tau=1,2$ and $b \in R$ if $(u,vb,a), (ub, v, a) \in B^\tau$ then one has
@@
 One constructs the elements $Z^1(u,v,a)$ in exactly the same way as Tulenbaev constructs his elements $X_{u,v}(a)$ (see definitions preceding~\cite[Lemma~1.2]{T}).
-Next, the elements $Z^2(u,v,a)$ are obtained by ``transposing'' Tulenbaev's construction.
+Indeed, set
+\begin{equation} Z^1(v, w, a) = \prod\limits_{k=1}^p X(v, a \cdot w^k), \quad Z^2(w, v, a) = \prod\limits_{k=1}^p X(a \cdot w^k, v). \end{equation}
+where $X(u, v)$ denotes the elements defined by Tulenbaev before~\cite[Lemma~1.1]{T}.
 
-All the properties (with the exception of the last one in the case $n=4$) can be proved by the same token as in~\cite[Lemma~1.3]{T}.
+The correctness of this definition and all the assertions of the lemma (with the exception of the last one in the case $n=4$) can be proved by the same token as in~\cite[Lemma~1.3]{T}.
 To check the last property in the case $n=4$ one has to use the argument of W. van~der~Kallen (cf.~\cite{Ka}).

### 2016-04-19 paper.tex
Imported Andrei's source

--- 2015-09-30 paper.tex
@@
-\documentclass[12pt]{amsart}
-\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, enumitem, graphicx, mathtools, xfrac, tikz-cd, nameref, thmtools, hyperref}
+\documentclass[11pt]{amsart}
+\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, enumitem, mathtools, xfrac, nameref, thmtools, hyperref}
 \usepackage[utf8]{inputenc}
 \usepackage[backend=biber, citestyle=numeric-comp, natbib=true, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
-\addbibresource{paper.bib}
 \usepackage[activate={true,nocompatibility}]{microtype}
 \usepackage[capitalize]{cleveref}
+\usepackage[english]{babel} 
+\usepackage{stmaryrd}
+\usepackage[matrix,arrow,curve]{xy}
+
+%Bibliography
+\renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
+\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{http://dx.doi.org/\thefield{doi}}{#1}}}
+\DeclareFieldFormat{title}{\usebibmacro{string+doi}{\mkbibemph{#1}}}
+\DeclareFieldFormat[article, inproceedings, inbook, thesis]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
+\addbibresource{paper.bib}
 
@@
 
-\theoremstyle{plain} \declaretheorem[name=Theorem, Refname={Theorem,Theorems}]{thm} \Crefname{thm}{Theorem}{Theorems}
+\theoremstyle{plain} \declaretheorem[name=Theorem, Refname={Theorem,Theorems}]{tm} \Crefname{tm}{Theorem}{Theorems}
 \numberwithin{equation}{section}
 
-\newtheorem{lemma}{Lemma} \numberwithin{lemma}{section} \Crefname{lemma}{Lemma}{Lemmas}
-\newtheorem{cor}[lemma]{Corollary} \Crefname{cor}{Corollary}{Corollaries}
-\newtheorem{prop}[lemma]{Proposition} \Crefname{prop}{Proposition}{Propositions}
-\newtheorem*{thm*}{Theorem}
-\newtheorem*{lemma*}{Lemma}
-\theoremstyle{definition} \newtheorem{dfn}[lemma]{Definition} \Crefname{dfn}{Definition}{Definitions}
-\newtheorem{example}[lemma]{Example} \Crefname{example}{Example}{Examples}
-\theoremstyle{remark} \newtheorem{rem}[lemma]{Remark} \Crefname{rem}{Remark}{Remarks}
+\newtheorem{lm}{Lemma} \numberwithin{lm}{section} \Crefname{lm}{Lemma}{Lemmas}
+\newtheorem{cl}[lm]{Corollary} \Crefname{cl}{Corollary}{Corollaries}
+\newtheorem{prop}[lm]{Proposition} \Crefname{prop}{Proposition}{Propositions}
+\newtheorem*{tm*}{Theorem}
+\newtheorem*{lm*}{Lemma}
+\theoremstyle{definition} \newtheorem{df}[lm]{Definition} \Crefname{df}{Definition}{Definitions}
+\newtheorem{example}[lm]{Example} \Crefname{example}{Example}{Examples}
+\theoremstyle{remark} \newtheorem{rk}[lm]{Remark} \Crefname{rk}{Remark}{Remarks}
+\newtheorem*{mtm}{Main Theorem}
+\newtheorem*{atm}{Another Presentation}
 
@@
 
-\newcommand{\catname}[1]{{\normalfont\textbf{#1}}}
-\newcommand{\Ker}{\operatorname{Ker}}
-\newcommand{\Cent}{\operatorname{Cent}}
-\newcommand{\Img}{\operatorname{Im}}
-\newcommand{\Coker}{\operatorname{Coker}}
-\newcommand{\coker}{\operatorname{coker}}
-\newcommand{\K}{\operatorname{\mathrm{K}}}
-\newcommand{\GG}{\operatorname{\mathrm{G}}}
-\newcommand{\St}{\operatorname{\mathrm{St}}}
-\newcommand{\StU}{\operatorname{\hat{\mathrm{U}}}}
-\newcommand{\G}{\operatorname{\mathrm{G}}}
-\newcommand{\E}{\operatorname{\mathrm{E}}}
-\newcommand{\M}{\operatorname{\mathrm{M}}}
-\newcommand{\sr}{\operatorname{\mathrm{sr}}}
-\newcommand{\Um}{\operatorname{\mathrm{Um}}}
-\newcommand{\rk}{\operatorname{\mathrm{rk}}}
-\newcommand{\rA}{\mathsf{A}}
-\newcommand{\rB}{\mathsf{B}}
-\newcommand{\rC}{\mathsf{C}} 
-\newcommand{\rD}{\mathsf{D}} 
-\newcommand{\rE}{\mathsf{E}}
-\newcommand{\HH}{\mathrm{H}}
-\newcommand{\eval}[4]{ev \textstyle \left[\frac{#2[#1] \rightarrow #3}{#1 \mapsto #4}\right]}
-\newcommand{\ev}[3]{\eval{t}{#1}{#2}{#3}}
+\newcommand{\Max}{\mathop{\mathrm{Max}}\nolimits}
+\newcommand{\proj}{\mathop{\mathrm{proj}}\nolimits}
+\newcommand{\Card}{\mathop{\mathrm{Card}}\nolimits}
+\newcommand{\Ker}{\mathop{\mathrm{Ker}}\nolimits}
+\newcommand{\Cent}{\mathop{\mathrm{Cent}}\nolimits}
+\newcommand{\E}{{\mathrm{E}}}
+\newcommand{\Um}{\mathop{\mathrm{Um}}\nolimits}
+\newcommand{\St}{\mathop{\mathrm{St}}\nolimits}
+\newcommand{\Sp}{\mathop{\mathrm{Sp}}\nolimits}
+\newcommand{\Ep}{\mathop{\mathrm{Ep}}\nolimits}
+\newcommand{\GL}{\mathop{\mathrm{GL}}\nolimits}
+\newcommand{\SL}{\mathop{\mathrm{SL}}\nolimits}
+\newcommand{\Kt}{\mathop{\mathrm{K_2}}\nolimits}
+\newcommand{\Ko}{\mathop{\mathrm{K_1}}\nolimits}
+\newcommand{\Ho}{\mathop{\mathrm{H_1}}\nolimits}
+\newcommand{\Ht}{\mathop{\mathrm{H_2}}\nolimits}
+\newcommand{\epi}{\twoheadrightarrow}
+\newcommand{\sgn}{\mathrm{sgn}}
+\newcommand{\eps}[1]{\varepsilon_{#1}}
+\newcommand{\sign}[1]{\mathrm{sign}(#1)}
+\newcommand{\lan}{\langle}
+\newcommand{\ran}{\rangle}
+\newcommand{\inv}{^{-1}}
+\newcommand{\ur}[1]{\!\,^{(#1)}U_1}
+\newcommand{\ps}[1]{\!\,^{(#1)}\!P_1}
+\newcommand{\ls}[1]{\!\,^{(#1)}\!L_1}
+
+\renewcommand{\labelenumi}{\theenumi{\rm)}}
+\renewcommand{\theenumi}{\alph{enumi}}
 
@@
 
-\title{Local-global principle for $\K_2$ of Chevalley groups}
-\keywords {Chevalley groups, Steinberg groups, $K_2$-functor. {\em Mathematical Subject Classification (2010):} 19C09; 20G35}
-\author {Andrei Lavrenov, Sergey Sinchuk}
-\email {avlavrenov {\it at} gmail.com, sinchukss {\it at} gmail.com}
+\title{A local-global principle for $K_2$ of $\GL_4$ and orthogonal groups}
+\keywords {Steinberg groups, $K_2$-functor. {\em Mathematical Subject Classification (2010):} 19C09}
+
+\author{Sergey Sinchuk}
+\email{sinchukss {\it at} gmail.com}
+
+\author {Andrei Lavrenov}
+\email {avlavrenov {\it at} gmail.com}
+
 \date {\today}
@@
 
-\section {Introduction}\label{intro}
+%\begin{thebibliography}{99}
+%\bibitem{Lav2} A.~Lavrenov, A local--global principle for symplectic $\mathrm K_2$, {\it to appear}.
+%\bibitem{Rao} *Statement of Ravi Rao's hypothesis
+%\bibitem{Swa1} *Swan's relative Steinberg group 1
+%\bibitem{Swa2} *Swan's relative Steinberg group 2
+%\bibitem{Swa3} *Swan's relative Steinberg group 3
+%\bibitem{Tul0} *Tulenbaev's paper on almost commutative rings (cite somewhere)
+%\end{thebibliography}
 
-\subsection{Acknowledgements}
-The authors of the present paper acknowledges financial support from Russian Science Foundation grant 14-11-00297.
+\section*{Inroduction}
 
-\section {Preliminaries}\label{prelim}
+The main goal of the present paper is to give a uniform proof of centrality of $\mathrm K_2$ for all simply-laced Chevalley groups of rank $\geq3$.\footnote{The authors acknowledge support of ER-EN-EF.}
 
-\section {Main results}
+The paper is organised as follows.
+In the first section we give yet another presentation for $\St(4,\,R,\,I)=\St(\mathrm A_3,\,R,\,I)$.
+It mimics the standart vector representation of $\SL(n,\,R)$, therefore in the first section we use representations and corresponding vector notation.
+Afterwards we can deduce a local--global principle for $\St(\mathrm\Phi,\,R)$ and centrality of $\Kt(\mathrm\Phi,\,R)$ for $\Phi=\mathrm A_3$.
+In the second section we use obtained results to prove the same theorems for any simply laced $\Phi$ of rank $\geq3$.
+There we switch to the root notation.
 
-\subsection{Relative Steinberg group in rank $3$ and Tulenbaev's section map} 
-The main goal of this subsection is to construct Tulenbaev's section map from~\cite[\S~2]{T} for
-the linear Steinberg group of rank $3$. Combining this result with the amalgamation theorem
-of the the second named author (see~\cite[Theorem~9]{S15}) we deduce centrality for the orthogonal
-$\K_2$ in the next subsection.
+\section{Case of $\mathrm A_3$}
 
-First of all, we will need to give yet another definition of the relative linear Steinberg group 
-(cf. \cite[Definitions~3.3 and 3.7]{S15}).
+Tulenbaev used {\it another presentation} for a relative Steinberg group to prove a local--global principle for a linear Steinberg group~\cite{Tul}.
+This relative another presentation was inspired by the {\it absolute} one of van der Kallen~\cite{vdK}.
+However, Tulenbaev's presentation can only be used for $\St(l+1,\,R)=\St(\mathrm A_l,\,R)$, $l\geq4$.
 
-\begin{dfn}
- The relative Steinberg group $\St^*(n,R, I)$ is the group defined by the following two
- families generators and four families of relations.
- \begin{itemize}
-  \item Generators:
+Tulenbaev's result can be applied to the subsystems of type $\mathrm A_4$ inside $\mathrm E_l$ and ``glued'' to get a local--global principle for Steinberg groups of type $\mathrm E_l$~\cite{SCh}.
+To use this glueing method for groups of type $\mathrm D_l$ as well one has to work with subsystems of type $\mathrm A_3$ instead, and thus extend Tulenbaev's result to the case of $\mathrm A_3$.
+
+Recently, the local--global principle was obtained for Steinberg groups of type $\mathrm C_l$ starting from rank 3~\cite{Lav2}.
+That is another motivation to consider the linear Steinberg group in rank 3.
+
+In the present paper $R$ denotes commutative (associative, unital) ring, $l\geq3$, and $n=l+1\geq4$, $R^n$ is a free (right) $R$-module with basis $e_1,\ldots,e_n$, $\GL(n,\,R)$ is a group of invertible $n\times n$ matrices over $R$, $\E(n,\,R)$ its elementary subgroup generated by elementary transvections
+$$\{t_{ij}(r)=1+e_{ij}r\mid1\leq i\neq j\leq n,\ r\in R\},$$
+where 1 stands for the identity matrix and $e_{ij}$ for the matrix unit. The Steinberg group is a group given by formal generators
+$$\{x_{ij}(r)\mid1\leq i\neq j\leq n,\ r\in R\}$$
+and Steinberg relations
+\setcounter{equation}{0}
+\renewcommand{\theequation}{S\arabic{equation}}
+\begin{align}
+&x_{ij}(r)x_{ij}(s)=x_{ij}(r+s),\\
+&[x_{ij}(r),\,x_{hk}(s)]=1,\text{ for }h\neq j,\ k\neq i,\\
+&[x_{ij}(r),\,x_{jk}(s)]=x_{ik}(rs).
+\end{align}
+All commutators in the present paper are left-normed, $[x,\,y]=xyx\inv y\inv$. Denote $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ a natural projection sending $x_{ij}(r)$ to $t_{ij}(r)$.
+
+Suslin showed that (already for $n\geq3$) the elementary group coincides with the subgroup of $\GL(n,\,R)$ generated by matrices
+$$
+\{t(u,\,v)=1+uv^t\mid u\in\Um(n,\,R),\ v\in R^n,\ u^tv=0\},
+$$
+where $\Um(n,\,R)$ is a set of unimodular coloumns of $R^n$, i.e., such that their entries generate the unit ideal of $R$, $u^t$ stands for $u$ {\it transposed}~\cite{Sus}.
+This result clearly implies that $\E(n,\,R)$ is normal inside $\GL(n,\,R)$.
+Then, van der Kallen developed Suslin's ideas and showed that the Steinberg group $\St(n,\,R)$ is isomorphic to a group defined by a set of generators
+$$
+\{X(u,\,v)\mid u\in\Um(n,\,R),\ v\in R^n,\ u^tv=0\}
+$$
+and relations
+\setcounter{equation}{0}
+\renewcommand{\theequation}{K\arabic{equation}}
+\begin{align}
+&X(u,\,v)X(u,\,w)=X(u,\,v+w),\\
+&X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(v,\,u)\inv v')
+\end{align}
+for $n\geq4$~\cite{vdK}.
+Then, it is also obvious that $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ is a central extension.
+Observe that van der Kallen uses pairs of a coloumn and a row $(i,\,j)$ to parametrise his generators, and we prefer two coloumns.
+
+The local--global principle for the elementary group proven by Suslin~\cite{Sus} is a statement that an elementary matrix over a polynomial ring $g\in\E(n,\,R[X])$ becomes trivial after the evaluation ``$X=0$''
+$$
+g\in\Ker\big(\E(n,\,R[X])\rightarrow\E(n,\,R)\big)
+$$
+and after localisations
+$$
+g_{\mathfrak m}=1\in\E(n,\,R_{\mathfrak m}[X])
+$$
+for all maximal ideals $\mathfrak m$ of a base ring $R$, if and only if it is trivial from the very begining
+$$
+g=1\in\E(n,\,R[X]).
+$$
+An analogous statement about Steinberg groups was proven by Tulenbaev for $n\geq5$~\cite[Th.~2.1]{Tul}. I.e., for $n\geq5$ and $g\in\St(n,\,R[X])$ such that 
+$$g(0)=1\in\St(n,\,R)\ \text{ and }\ g_{\mathfrak m}=1\in\St(n,\,R_{\mathfrak m}[X])$$
+ for all $\mathfrak m\in\Max R$ holds $g=1$.
+
+For $I\trianglelefteq R$ denote $\St(n,\,R,\,I)=\Ker\big(\St(n,\,R)\epi\St(n,\,R/I)\big)$ {\it a relative Steinberg group}. Clearly, $\St(n,\,R[X],\,XR[X])$ is the kernel of the evaluation ``$X=0$''.
+
+The key step in Tulenbaev's proof is constructing a homomorphism
+$$
+\mathrm T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X],\,XR_a[X])
+$$
+for any (non-nilpotent) element $a\in R$, $n\geq5$ ($R_a$ stands for a principle localisation of $R$ in $a$).
+This $\mathrm T$ is an inverse to a map induced by localisation, so that constructing $\mathrm T$ may be treated as a proof of excision property for Steinberg group in this very particular situation.
+
+To prove the local--global principle for Steinberg groups of type $\mathrm D_l$ and centrality of $\mathrm K_2(\mathrm D_l,\,R)$ we need such a map for $n=4$ (i.e., for the group of type $\mathrm A_3$).
+
+Tulenbaev uses the following presentaion for the relative Steinberg group, see~\cite[Prop.~1.6]{Tul}. Assume that $I\trianglelefteq R$ such that a short exact sequence
+\renewcommand{\theequation}{$\dagger$}
+\begin{align}
+\xymatrix{
+0\ar@<0.1ex>[r]^{}&I\ar@<0.1ex>[r]^{}&R\ar@<0.5ex>[r]^{\pi}&R/I\ar@<0.5ex>[l]^{\sigma}\ar@<0.1ex>[r]^{}&0
+}
+\end{align}
+splits, i.e., $\pi\sigma=1$. The $\St(n,\,R,\,I)$ is isomorphic to a group given by generators
+$$
+\{X(u,\,v)\mid u\in\E(n,\,R)e_1,\ v\in I^n,\ u^tv=0\}
+$$
+subject to relations
+\setcounter{equation}{0}
+\renewcommand{\theequation}{T\arabic{equation}}
+\begin{align}
+&X(u,\,v)X(u,\,w)=X(u,\,v+w),\\
+&X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(v,\,u)\inv v'),\\
+&X(ur+w,\,v)=X(u,\,vr)X(w,\,v)\,\text{ for }r\in R,\ (u,\,w)\in\Um_{n\times2}(R).
+\end{align}
+Here $\Um_{n\times2}(R)$ is a set of $n\times2$ matrices $M$ such that there exists a $2\times n$ matrix $N$ with $NM=\begin{pmatrix}1&0\\0&1\end{pmatrix}$.
+The ideal satisfying $\dagger$ is called the splitting ideal, $XR_a[X]\trianglelefteq R_a[X]$ is obviously the splitting one.
+
+Another presentations of van der Kallen and Tulenbaev are given in terms of generators parametrised by pairs of vectors, where the first one is ``good'' (unimodular or a coloumn of an elementary matrix) and the second one is arbitrary.
+This allows to formulate easily an additivity by the second argument, but one has to write something similar to T3 instead of additivity by the first one.
+
+Now, we need to construct a homomorphism
+$$
+\mathrm T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X],\,XR_a[X]),
+$$
+i.e., to find elements in the target group subject to Tulenbaev's relations, but because of T3 one can do it only for $n\geq5$, see~\cite[Lemmas~1.2 and~1.3\,c)]{Tul}.
+
+One can not parametrise generators by a pair of arbitrary vectors since it is not even known that $t(u,\,v)\in\E(n,\,R)$ for arbitrary orthogonal $u$ and $v$~\cite{Rao}.
+
+To generalise Tulenbaev's results for $n=4$ we use a presentation with two types of generators: $F(u,\,v)$ with $u$ good and $v$ arbitrary, which are additive by the second component, and $S(u,\,v)$ with $u$ arbitrary and $v$ good, which are additive by the first component.
+For $u$ and $v$ both good we require that these two types of generators coincide.
+More precisely,
+
+\begin{df}
+for $I\trianglelefteq R$, $n\geq4$ define $\St^*(n,\,R,\,I)$ to be a group given by the set of generators
+\begin{multline*}
+\{F(u,\,v)\mid u\in\E(n,\,R)e_1,\ v\in I^n,\ u^tv=0\}\,\cup\\
+\cup\{S(u,\,v)\mid u\in I^n,\ v\in\E(n,\,R)e_1,\ u^tv=0\}
+\end{multline*}
+subject to relations
+\setcounter{equation}{0}
+\renewcommand{\theequation}{R\arabic{equation}}
+\begin{align}
+&F(u,\,v)F(u,\,w)=F(u,\,v+w),\\
+&S(u,\,v)S(w,\,v)=S(u+w,\,v),\\
+&F(u,\,v)F(u',\,v')F(u,\,v)\inv=F(t(u,\,v)u',\,t(v,\,u)\inv v'),\\
+&F(u,\,va)=S(ua,\,v)\ \forall\,a\in I,\,(u,\,v^t)=(Me_1,\,e_2^tM\inv),\,M\!\in\E(n,\,R).
+\end{align}
+\end{df}
+
+One could probably wonder why we assumed only one relation on conjugated element, instead of four different relations on generators of each type conjugated by generators of each type.
+Three ``missing'' relations actualy hold automaticaly.
+
+\begin{lm}
+\label{allyouneedisf}
+Denote $\varphi\colon\St^*(n,\,R,\,I)\rightarrow\E(n,\,R)$ the natural map, sending $F(u,\,v)\mapsto t(u,\,v)$, $S(u,\,v)\mapsto t(u,\,v)$.
 \begin{enumerate}
-  \item $X^1(u, v)$, where $u \in \E(n,R) \cdot e_1$, $v\ \in I^n$ such that $v^t \cdot u = 0$;
-  \item $X^2(u, v)$, where $u \in I^n$, $v \in \E(n,R) \cdot e_1$ such that $v^t \cdot u = 0$.
+\item 
+$\St^*(n,\,R,\,I)$ is generated by the set of elements
+$$
+\{F(u,\,va)\mid a\in I,\ (u,\,v^t)=(Me_1,\,e_2^tM\inv),\,M\in\E(n,\,R)\};
+$$
+\item
+for any $g\in\St^*(n,\,R,\,I)$ holds
+\setcounter{equation}{2}
+\renewcommand{\theequation}{R\arabic{equation}'}
+\begin{align}
+&gF(u,\,v)g\inv=F(\varphi(g)u,\,\varphi(g\inv)^tv);
+\end{align}
+\item
+for any $g\in\St^*(n,\,R,\,I)$ holds
+\setcounter{equation}{2}
+\renewcommand{\theequation}{R\arabic{equation}''}
+\begin{align}
+&gS(u,\,v)g\inv=S(\varphi(g)u,\,\varphi(g\inv)^tv);
+\end{align}
+\item
+there exists a well-defined ``transpose automorphism''
+$$
+F(u,\,v)^t=S(v,\,u),\quad S(u,\,v)^t=F(v,\,u).
+$$
 \end{enumerate}
-  Notice that $\phi$ maps both $X^1(u, v)$ and $X^2(u, v)$ to $T(u, v) = e_n + u \cdot v^T$.
-  \item Relations:
-  \begin{enumerate}
-  \item $X^1(u, v) \cdot X^1(u, w) = X^1(u, v+w)$, $u \in \E(n,R) \cdot e_1$, $v, w \in I^n$;
-  \item $X^2(u, v) \cdot X^2(w, v) = X^2(u+w, v)$, $u, w \in I^n$, $v \in \E(n,R) \cdot e_1$;
-  \item ${}^{X^\sigma(u^2, v^2)} \! X^\tau(u^1, v^1) = X^\tau(T(u^2, v^2) \cdot u^1, T(v^2, u^2)^{-1} \cdot v^1)$, $\sigma, \tau = 1..2$;
-  \item $X^1(g \cdot e_1, g^* \cdot be_2) = X^2(g \cdot be_1, g^* \cdot e_2)$ where $b\in I$ and $g^* = {g^t}^{-1}$ denotes the contragradient matrix.
- \end{enumerate}
- \end{itemize}
-\end{dfn}
-It is easy to check the correctness of the above definition.
+\end{lm}
 
-\begin{lemma}
- The groups $\St^*(n, R, I)$ and $\St(n, R, I)$ are isomorphic.
-\end{lemma}
 \begin{proof}
- TODO: 
+Take an arbitrary generator of the first type $F(u,\,v)$ and take $M\in\E(n,\,R)$ such that $F(u,\,v)=F(Me_1,\,M^*\tilde v)$.
+Here $M^*$ stands for a contragradient matrix, $M^*=(M\inv)^t$.
+By R1 we have
+$$
+F(u,\,v)=\prod\limits_{k\neq1}F(Me_1,\,M^*e_k\tilde v_k)
+$$
+where $\tilde v_k$ stands for $k$-th coordinate of $\tilde v=\sum e_k\tilde v_k$. Similarly, with the use of R4 we get 
+$$
+S(u,\,v)=\prod\limits_{k\neq1}S(Ne_k\tilde u_k,\,N^*e_1)=\prod\limits_{k\neq1}F(Ne_k,\,N^*e_1\tilde u_k)
+$$
+and obtain a). Obviously, b) follows from a). For c) it is sufficient to show that
+$$
+F(u,\,v)S(u',\,v')F(u,\,v)\inv=S(t(u,\,v)u',\,t(u,\,v)^*v').
+$$
+Let $S(u',\,v')=\prod F(Ne_k,\,N^*e_1\tilde u_k)$, then
+\begin{multline*}
+F(u,\,v)S(u',\,v')F(u,\,v)\inv=F(u,\,v)\prod F(Ne_k,\,N^*e_1\tilde u_k)F(u,\,v)\inv=\\
+=\prod F(t(u,\,v)Ne_k,\,t(u,\,v)^*N^*e_1\tilde u_k)=\\
+=\prod S(t(u,\,v)Ne_k\tilde u_k,\,t(u,\,v)^*N^*e_1)=S(t(u,\,v)u',\,t(u,\,v)^*v').
+\end{multline*}
+Finally, d) follows from c).
 \end{proof}
 
-The next step of the proof is to is construct certain elements in $\St(n, R)$ similar to Tulenbaev's elements $X_{u,v}(a)$ see~\cite[\S~1]{T}.
+Next, we show that for a splitting ideal $I\trianglelefteq R$ the group $\St^*(n,\,R,\,I)$ is isomorphic to $\St(n,\,R,\,I)=\Ker\big(\St(n,\,R)\epi\St(n,\,R/I)\big)$.
+With this end we construct two inverse homomorphisms
+$$
+\xymatrix{
+\St^*(n,\,R,\,I)\ar@<0.5ex>[r]^{\iota}&\St(n,\,R,\,I)\ar@<0.5ex>[l]^{\kappa}.
+}
+$$
 
-Let $v\in R^n$ be a column.
-A column $w\in R^n$ is called \emph{$v$-decomposable} if it can be presented as a finite sum $w = \sum\limits_{i=1}^n w^i$ such that each $w^i$ has at least two zero entries. 
-Denote by $D(v)$ the submodule of $R^n$ consisting of all $v$-decomposable columns.
-For a column $v\in R^n$ denote by $I(v)$ the ideal of $R$ spanned by coordinates $v_1,\ldots, v_n$.
+Firstly, we define $\iota$ as a homomorhism to an absolute group
+$$
+\xymatrix{
+\St^*(n,\,R,\,I)\ar@<0.0ex>[r]^{\iota}&\St(n,\,R).
+}
+$$
+We do not need an assumption that $I$ is a splitting ideal for that.
 
-Let $u,v,w\in R^n$ be columns such that $w^tv=0$.
-It is easy to check (cf.~\cite[Lemma~3.2]{Ka}) that 
-$$(uv)\cdot w = \sum_{i<j}w_{ij},\ \text{where}\ w_{ij} = (w_iu_j - w_ju_i)(v_je_i - v_ie_j)\in{}\!A^n.$$
-The above decomposition is called the \emph{canonical} decomposition of $(uv)\cdot w$.
-In particular, the above argument shows that row $a\cdot w$ is always $v$-decomposable for $a\in I(v)$, i.e. $I(v) \cdot O(v) \subseteq D(v)$.
-It is also obvious that $O(v)\subseteq O(bv)$, $D(v)\subseteq D(bv)$ for $b \in R$.
-%\end{enumerate}\end{lemma}
+Clearly, we map elements $F(u,\,v)$ to van der Kallen's another generators $X(u,\,v)$.
+To find images for $S(u,\,v)$ as well we recall that van der Kallen in~\cite[3.8--3.10]{vdK} defines also elements
+$$
+x(u,\,v)\in\St(n,\,R),\ u^tv=0,\ u_i=0\,\text{ or }\,v_i=0\,\text{ for some }\,1\leq i\leq n.
+$$
+Now, ``transpose'' the definition~\cite[3.13]{vdK}.
 
-Denote by $B^1$ the subset of $R^n \times R^n \times R$ consisting of triples $(u, v, a)$ such that $v^t \cdot u = 0$, $v \in D(u)$, $a \in I(u)$.
-Denote by $B^2$ the set consisting of triples $(v, u, a)$ such that $(u, v, a) \in B^1$.
+\begin{df}
+For $u\in R^n$, $v\in\E(n,\,R)e_1$, $u^tv=0$, consider the set $\overline Y(u,\,v)\subseteq\St(n,\,R)$ consisiting of all elements $y\in\St(n,\,R)$ which could be decomposed as a product $\prod x(w^k,\,v)$, where $\sum w^k=u$ and $w^k=(e_pv_q-e_qv_p)c^k$ for some $c^k\in R$, $1\leq p\neq q\leq n$.
+\end{df}
 
-\begin{lemma} \label{lem:Zproperties}
-Assume that $n \geq 4$.
-One can define two families of elements $Z^\tau(u, v, a) \in \St(n, R)$, $\tau=1,2$ parametrized by $(u, v, a) \in B^\tau$ satisfying the following properties
- \begin{lemlist}
-  \item \label{rel:proj} $\phi(Z^\tau(u, v, a)) = e + uav^t \in \E(n, R)$, $(u,v,a) \in B^\tau$;
-  \item \label{rel:add1} $Z^{1}(u, v_1 + v_2, a) = Z^{1}(u, v_1, a) \cdot Z^{1}(u, v_2, a)$;
-  \item \label{rel:add2} $Z^{2}(v_1 + v_2, u, a) = Z^{2}(v_1, u, a) \cdot Z^{2}(v_2, u, a)$;
-  \item \label{rel:conj} ${}^{g}\! Z^{\tau}(u, v, a) = Z^{\tau}(\phi(g) \cdot u, \phi(g)^* \cdot v, a)$, $\tau = 1,2$, $g \in \St(n, R)$.
- \end{lemlist}
-\end{lemma}
+Since coloumns of elementary matrices are unimodular, $\overline Y(u,\,v)$ is not empty (see~\cite[3.1--3.2]{vdK}).
+Obviously, for $x\in\overline Y(u,\,v)$ and $y\in\overline Y(w,\,v)$ holds $xy\in\overline Y(u+w,\,v)$.
+
+Repeating~\cite[3.14--3.15]{vdK} verbatim one shows that
+
+\begin{lm}
+for $g\in\St(n,\,R)$ holds
+\begin{enumerate}
+\item
+$g\overline Y(u,\,v)g\inv\subseteq\overline Y(\phi(g)u,\,\phi(g)^*v)$;
+\item
+$\overline Y(u,\,v)$ consists of exactly one element.
+\end{enumerate}
+\end{lm}
+
+The only element of $\overline Y(u,\,v)$ we denote by $Y(u,\,v)$.
+We map elements $S(u,\,v)\in\St^*(n,\,R,\,I)$ to $Y(u,\,v)$.
+To show that such a homomorphism is well-defined we check that $X(u,\,v)$ and $Y(u,\,v)$ satisfy relations R1--R4, but R1--R3 are already checked.
+
+\begin{lm}
+Consider $(u,\,v^t)=(Me_1,\,e_2^tM\inv)$, $M\in\E(n,\,R)$, $a\in I$. Then $X(u,\,va)=Y(ua,\,v)$.
+\end{lm}
+
 \begin{proof}
-One constructs the elements $Z^1(u,v,a)$ in exactly the same way as Tulenbaev constructs his elements $X_{u,v}(a)$ (see definitions preceding~\cite[Lemma~1.2]{T}).
-Next, the elements $Z^2(u,v,a)$ are constructed by ``transposing'' Tulenbaev's construction.
-
-All the properties (with the exception of the last one in the case $n=4$) can be proved in exactly the same fashion as in~\cite[Lemma~1.3]{T}.
-To check the last property in the case $n=4$ one has to use the argument of W. van~der~Kallen (cf.~\cite{Ka}).
-%TODO: Write more details
+It suffices to show that $X(e_1,\,e_2a)=Y(e_1a,\,e_2)$. Compute the commutator $[Y(-e_3,\,e_2),\,X(e_1,\,e_3a)]$ in two ways:
+$$
+Y(-e_3,\,e_2)X(e_1,\,e_3a)Y(-e_3,\,e_2)\inv\cdot X(e_1,\,-e_3a)=X(e_1,\,e_2a),
+$$
+and
+$$
+Y(-e_3,\,e_2)\cdot\,X(e_1,\,e_3a)Y(e_3,\,e_2)X(e_1,\,e_3a)\inv=Y(e_1a,\,e_2).
+$$
 \end{proof}
 
-For the rest of this section $a$ denotes a nonnilpotent element of $R$.
-\begin{lemma}
-Let $u,v,w,z \in R^n$ be columns such that 
-\begin{equation*} u^t \cdot v = 0,\ w^t \cdot v = c \in R,\ u^t \cdot z = 0,\ w^t \cdot z = 0. \end{equation*}
-Assume, moreover, that $(u, v, a) \in B^1$, $(w, z, a) \in B^2$, then one has $$Z^1(u, ac \cdot z, a) = Z^2(ac \cdot u, z, a).$$
-\end{lemma}
+Therefore, the homomorphism $\iota\colon\St^*(n,\,R,\,I)\rightarrow\St(n,\,R)$ sending $F(u,\,v)$ to $X(u,\,v)$ and $S(u,\,v)$ to $Y(u,\,v)$ is well-defined.
+Denote $\rho_I\colon R\epi R/I$, then one can easily see that induced morphism on Steinberg groups
+$$\rho_I^*\colon\St(n,\,R)\rightarrow\St(n,\,R/I)$$
+ sends $X(u,\,v)$ to $X(\rho_I(u),\,\rho_I(v))$ and $Y(u,\,v)$ to $Y(\rho_I(u),\,\rho_I(v))$.
+Observe that $\E(n,\,R)\epi\E(n,\,R/I)$ is surjective so that for $x\in\E(n,\,R)e_1$ holds that $\rho_I(x)\in\E(n,\,R/I)e_1$.
+It follows from additivity relations that $X(u,\,0)=1=Y(0,\,v)$, thus $\mathrm{Im}(\iota)\subseteq\Ker(\rho_I^*)=\St(n,\,R,\,I)$.
+
+We constructed $\iota$ for an arbitrary $I\trianglelefteq R$. For $I$ a splitting ideal we construct an inverse homomorphism
+$$
+\kappa\colon\St(n,\,R,\,I)\rightarrow\St^*(n,\,R,\,I).
+$$
+With this end we recall a presentation of $\St(n,\,R,\,I)$ as a group with action of $\St(n,\,R)$.
+For a splitting ideal such a presentation was firstly obtained by Swan~\cite{Swa1,Swa2,Swa3}, and for an arbitrary $I$ by Keune~\cite{Keu} and Loday~\cite{Lod}.
+
+For a group $G$ acting on a group $H$ from the left denote by $\!\,^gh$ the image of $h\in H$ under homomorphism corresponding by $g\in G$.
+
+Let $I\trianglelefteq R$ be a splitting ideal then $\St(n,\,R,\,I)$ can be presented as a group with action of $\St(n,\,R)$ with the set of (relative) generators
+$$
+\{y_{ij}(a)\mid a\in I,\ 1\leq i\neq j\leq n\}
+$$
+subject to relations
+\setcounter{equation}{0}
+\renewcommand{\theequation}{KL\arabic{equation}}
+\begin{align}
+&y_{ij}(a)y_{ij}(b)=y_{ij}(a+b),\\
+&\!\,^{x_{ij}(r)}y_{hk}(b)=y_{hk}(b),\text{ for }h\neq j,\ k\neq i,\\
+&\!\,^{x_{ij}(r)}y_{jk}(b)\cdot y_{jk}(-b)=y_{ik}(rb),\\
+&y_{ij}(a)\cdot\,^{x_{jk}(s)}y_{ij}(-a)=y_{ik}(as),\\
+&\!\,^{x_{hk}(a)}\big(\!\,^gy_{ij}(b)\big)=y_{hk}(a)\cdot\,^gy_{ij}(b)\cdot y_{hk}(-a)\,\text{ for }a\in I,\ g\in\St(n,\,R).
+\end{align}
+
+In other words, $\St(n,\,R,\,I)$ is isomorphic to a quotient group of a free group $F$ on the set of generators 
+$$\St(n,\,R)\times\{y_{ij}(a)\mid a\in I,\ 1\leq i\neq j\leq n\}$$
+(the natural action of $\St(n,\,R)$ on $F$ is given by $\!\,^f(g,\,y)=(fg,\,y)$) modulo the normal equivariant subgroup generated by KL1--KL5 (where $y_{ij}(a)$ stands for $(1,\,y_{ij}(a))$.
+Keune in Loday consider only stable Steinberg group $\St(R)=\varinjlim\St(n,\,R)$.
+This presentation for unstable group firstly appeared in~\cite{SCh} in the context of Chevalley groups.
+Observe that the definition of the relative Steinberg group in~\cite[Def.~3.3]{SCh} differs from ours but remark after this definition and~\cite[Lem.~8]{SCh} immediantly imply that for a splitting ideal $I\trianglelefteq R$ it coincides with the one given in the present paper.
+The existance of the presentation is proven in~\cite[Prop.~6]{SCh}.
+Relation~5 in~\cite[Prop.~6]{SCh} joins relations KL3 and KL4, and relations~2 and 3 follow from KL4 and KL5 with the use of KL6.
+
+One could probably wonder why Tulenbaev needs his own presentation for $\St(n,\,R,\,I)$ and does not use the one of Keune--Loday.
+The reason is the following.
+To construct a map from Keune--Loday group one should firstly define an action of the absolute Steinberg group on the target group, in our context, the action of $\St(n,\,B_a)$ on $\St(n,\,B,\,I)$, what is probably possible, but seems to be much harder, then giving another presentation (in particular, one should define $\!\,^{x_{ij}(r/a^m)}y_{ji}(c)$).
+
+Now, to construct
+$
+\kappa\colon\St(n,\,R,\,I)\rightarrow\St^*(n,\,R,\,I)
+$
+we need to define an action of $\St(n,\,R)$ on $\St^*(n,\,R,\,I)$ and find elements $y^*_{ij}(a)\in\St^*(n,\,R,\,I)$ subject to KL1--KL5.
+To define a action of the absolute group we use van der Kallen's another presentaion for it.
+For $u\in\Um(n,\,R)$, $v\in R^n$, $u^tv=0$ define
+$
+\alpha(u,\,v)\colon\St^*(n,\,R,\,I)\rightarrow\St^*(n,\,R,\,I)
+$
+by $\alpha(u,\,v)\big(F(u',\,v')\big)=F(t(u,\,v)u',\,t(u,\,v)^*v')$, and $\alpha(u,\,v)\big(S(u',\,v')\big)=S(t(u,\,v)u',\,t(u,\,v)^*v')$.
+Obviously, the images of the generators satisfy R1--R4, so that $\alpha(u,\,v)$ is a well-defined automorphism.
+Also, $\alpha$'s themselves clearly satisfy K1--K2, thus $X(u,\,v)\mapsto\alpha(u,\,v)$ is a well-defined action of $\St(n,\,R)$ on $\St^*(n,\,R,\,I)$.
+
+Next, define $y_{ij}^*(a)=F(e_i,\,e_ja)$, $a\in I$. These elements obviously satisfy KL1, KL2 and KL5. Check KL3:
+\begin{multline*}
+\!\,^{x_{ij}(r)}y^*_{jk}(b)=F(t_{ij}(r)e_j,\,t_{ji}(-r)e_kb)=F(e_ir+e_j,\,e_kb)=\\
+=S(e_irb+e_jb,\,e_k)=S(e_irb,\,e_k)S(e_jb,\,e_k)=F(e_i,\,e_krb)F(e_j,\,e_kb).
+\end{multline*} 
+KL4 is similar. Finally, we have a well-defined map
+$$
+\kappa\colon\St(n,\,R,\,I)\rightarrow\St^*(n,\,R,\,I)
+$$
+sending $y_{ij}(a)$ to $y^*_{ij}(a)$.
+Obviously, $\iota\circ\kappa=\mathrm{id}$ (cf.~\cite[3.6\,d)]{vdK}), thus $\kappa$ is injective.
+Surjectivity of $\kappa$ follows from Lemma~\ref{allyouneedisf}\,a), thus it is an isomorphism and $\iota$ is inverse to it.
+
+At this point we obtained the presentation $\St^*(n,\,R,\,I)$ for the $\St(n,\,R,\,I)$ where $I\trianglelefteq R$ is a splitting ideal, $n\geq4$.
+
+Below we obtain the main result of this section, namely, construct a map 
+$$
+\mathrm T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X],\,XR_a[X]),
+$$
+for $n\geq4$. A local-global principle for Steinberg group and centrality of $\mathrm K_2$ formally follow from existance of this map~\cite[Lem.~15, Lem.~16, proof of Th.~2]{SCh}.
+
+We work in a more general situation.
+
+\begin{tm}
+\label{a3map}
+Let $B$ be a ring, $I\trianglelefteq B$, $a\in B$ such that $\forall\,x\in I$ there exists a unique $y\in I$ such that $ya=x$ {\rm(}we denote this $y$ by $\frac xa$, elements $\frac x{a^m}$ are also well defined{\rm)}.
+This requirement is equivalent to say that the principle localisation $\lambda_a\colon I\rightarrow I_a$ of ideal $I$ is an isomorphism.
+Then there exists a map
+$$
+\mathrm T\colon\St(n,\,B_a,\,I)\rightarrow\St(n,\,B)
+$$
+making the diagram
+$$
+\xymatrix{
+\St^*(2n,\,B,\,I)\ar@<-0.0ex>[rr]^{\iota}\ar@<-0.0ex>[d]_{\lambda_{a}^*}&&\St(2n,\,B)\ar@<-0.0ex>[d]^{\lambda_{a}^*}\\
+\St^*(2n,\,B_a,\,I)\ar@<-0.0ex>[rr]_{\iota}\ar@{-->}[rru]_{\mathrm T}&&\St(2n,\,B_a)
+}
+$$
+commutative.
+\end{tm}
+
+To prove this theorem we need to find some elements ``$X(u,\,v)$'' inside $\St(n,\,B)$ for $u\in\E(n,\,B_a)e_1$, $v\in I$.
+The idea is the following.
+Say $a$ is not a zero divisor, then $ua^m\in B$ for some $m$ and we will construct some element ``$X(ua^m,\,va^{-m})$''.
+One can not garantee that $ua^m\in\E(n,\,B)e_1a^k$, however, the ideal generated by entries of $ua^m$ contains some power of $a$ (this is equivalent to say that $ua^m$ becomes unimodular after the principle localisation in $a$).
+Denote $\mathrm I(u)$ the ideal generated by entries of $u\in R^n$, $\mathrm I(u)=\sum\limits_{k=1}^nu_kR$.
+Then, we need generators parametrised by pairs $(u,\,v)$ with $u^tv=0$, $v\in I$, $a^m\in\mathrm I(u)$ for some $m\in\mathbb N$.
+Such generators are defined in~\cite{Tul}.
+
+\begin{df}[Tulenbaev]
+For $u$, $v\in B^n$, $a\in\mathrm I(u)$ and $v_1,\ldots,v_N\in B^n$ such that $u^tv_k=0$ $\forall\,k$,  each $v_k$ has at least two zero coordinates and $\sum_{k=1}^Nv_k=v$ define $X_{u,v}(a)=\prod\limits_{k=1}^Nx(u,\,v_ka)$.
+Tulenbaev shows that factors $x(u,\,v_ka)$ commute~\cite[Lem.~1.1\,e)]{Tul} and that for any other decomposition of $v$ as a sum $v=\sum_{j=1}^Mv'_j$ of vectors orthogonal to $u$ and having two zero coordinates holds $\prod_{k=1}^Nx(u,\,v_ka)=\prod_{j=1}^Mx(u,\,v'_ja)$~\cite[p.~3]{Tul}, i.e., elements $X_{u,v}(a)$ are well-defined.
+Obviously, $\phi(X_{u,v}(a))=t(u,\,va)$.
+\end{df}
+
+Observe that Tulenbaev uses different notation for van der Kallen elements. He writes $X_{u,v}$ instead of $X(u,\,v)$ and $X(u,\,v)$ instead of $x(u,\,v)$. We keep van der Kallen's notation.
+
+\begin{lm}
+\label{xproperties}
+For $u$, $v$, $v'$ and $w\in B^n$, such that $v$ and $v'$ have decomposition as in above definition, $u^tw=0$, $a$, $b\in\mathrm I(u)$, $c\in B$, $g\in\St(n,\,B)$ holds
+\begin{enumerate}
+\item
+$X_{u,vc}(a)=X_{u,v}(ca)$,
+\item
+$X_{uc,v}(ca)=X_{u,vc^2}(a)$,
+\item
+$X_{u,v}(a)X_{u,v'}(a)=X_{u,v+v'}(a)$,
+\item
+$g\,X_{u,wb}(a)g\inv=X_{\phi(g)u,\phi(g)^*wb}(a)$.
+\end{enumerate}
+\end{lm}
+
 \begin{proof}
-Direct computation using \cref{lem:Zproperties} shows that
+The statement of a) is obvious from the definition, b) follows from~\cite[Lem.~1.1\,d)]{Tul}, c) is~\cite[Lem.~1.3\,a)]{Tul}, d) is proven for $n\geq5$ in~\cite[Lem.~1.3\,b)]{Tul} and afterwards Tulenbaev makes a remark that for $n=4$ the statement is also true.
+Indeed, take $z\in B^n$ such that $z^tu=b$ and decompose
+$$
+(z^tu)w=\sum_{i<j}w_{ij},
+$$
+where $w_{ij}=(e_iu_j-e_ju_i)(w_iz_j-w_jz_i)=w_{ji}$.
+Each $w_{ij}$ is orthogonal to $u$ and has two zero coordinates ($n\geq4$).
+Thus, $X_{u,wb}(a)=\prod_{i<j}x(u,\,w_{ij}a)$.
+It is enough to prove the statement of d) for $g=x_{hk}(r)$.
+If $h\neq i,j$ or $\{h,k\}=\{i,j\}$, $\phi(g)^*w_{ij}a$ still has two zero coordinates.
+Consider the case $j=h$, $i\neq k$.
+With~\cite[3.12]{vdK} we get $g\,x(u,\,w_{ij}a)g\inv=x(\phi(g)u,\,\phi(g)^*w_{ij}a)$.
+Denote $u_{ij}=e_iu_j-e_ju_i$ and $c_{ij}=w_iz_j-w_jz_i$.
+Using
+$$
+\phi(g)^*u_{ij}=(\phi(g)u)_{ij}+(\phi(g)u)_{ki}\,r
+$$
+and~\cite[3.11]{vdK} one obtains
+$$
+x(\phi(g)u,\,\phi(g)^*w_{ij}a)=x(\phi(g)u,\,(\phi(g)u)_{ij}c_{ij}a)\cdot x(\phi(g)u,\,(\phi(g)u)_{ki}\,rc_{ij}a).
+$$
+Decomposing in such a way each $\phi(g)^*w_{ij}a$ which does not have two zero coordinates we finally get a product from the definition of $X_{\phi(g)u,\phi(g)^*wb}(a)$.
+\end{proof}
+
+Siilarly, one can define ``transposed'' version of Tulenbaev's elements $X_{u,v}(a)$.
+
+\begin{df}
+For $u$, $v\in B^n$, $a\in\mathrm I(v)$, and $u_1,\ldots,u_N\in B^n$ such that $u_k^tv=0$, each $u_k$ has at least two zero coordinates and $u=\sum_{k=1}^Nu_k$ define $Y_{u,v}(a)=\prod\limits_{k=1}^Nx(u_ka,\,v)$.
+Repeating Tulenbaev's argumentation~\cite[p.~3]{Tul} one can show that the definition does not depend on the order of factors and on choice of decomposition of $u$.
+\end{df}
+
+Now, one can repeat van der Kallen's and Tulenbaev's argumentation to prove transposed version of Lemma~\ref{xproperties}. We leave this to the reader.
+
+\begin{lm}
+\label{yproperties}
+For $u$, $u'$, $w$ and $v\in B^n$, such that $u$ and $u'$ have decomposition as in above definition, $w^tv=0$, $a$, $b\in\mathrm I(v)$, $c\in B$, $g\in\St(n,\,B)$ holds
+\begin{enumerate}
+\item
+$Y_{uc,v}(a)=Y_{u,v}(ca)$,
+\item
+$Y_{u,vc}(ca)=Y_{uc^2,v}(a)$,
+\item
+$Y_{u,v}(a)X_{u',v}(a)=Y_{u+u',v}(a)$,
+\item
+$g\,Y_{wb,v}(a)g\inv=Y_{\phi(g)wb,\phi(g)^*v}(a)$.
+\end{enumerate}
+\end{lm}
+
+Finally, it only remains to show that for a ``good'' pair $(u,\,v)$ elements $X$ and $Y$ coincide.
+
+\begin{lm}
+\label{x=y}
+Consider $w$, $u$, $z$, $v$, $x$, $y\in B^n$ $a$, $r\in B$ such that $w^tu=a$, $z^tv=a$, $x^ty=a$ and pairs $(w,\,u)$, $(z,\,v)$ and $(x,\,y)$ are mutually orthogonal. Then 
+$$
+X_{u,v}(ra^3)=Y_{u,v}(ra^3).
+$$
+\end{lm}
+
+\begin{proof}
+On one hand,
 \begin{multline*}
- Z^2(ac \cdot u, z, a) = Z^2((e+uav^t) w, (e-vau^t)z,a) \cdot Z^2(-w,z,a) = \\
-  {}^{Z^1(u,v,a)} \! Z^2(w,z,a) \cdot Z^2(-w,z,a) = [Z^1(u, v, a), Z^2(w, z, a)] = Z^1(u,v,a) \cdot {}^{Z^2(w,z,a)}\! Z^1(u,-v,a) = \\
-    = Z^1(u,v,a) \cdot Z^1((e+waz^t)u,-(e-zaw^t)v,a) = Z^1(u,ac \cdot z,a). \qedhere
+[Y_{x,-v}(ra),\,X_{u,y}(a)]=X_{t(x,-vra)u,t(x,-vra)^*y}(a)X_{u,-y}(a)=\\
+=X_{u,y+vra^2}(a)X_{u,-y}(a)=X_{u,v}(ra^3).
+\end{multline*}
+On the other,
+\begin{multline*}
+[Y_{x,-v}(ra),\,X_{u,y}(a)]=Y_{x,-v}(ra)Y_{t(u,ya)x,t(u,ya)^*v}(ra)=\\
+=Y_{-x,v}(ra)Y_{x+ua^2,v}(ra)=Y_{u,v}(ra^3).
 \end{multline*}
@@
 
-\subsection{Centrality of orthogonal $K_2$.}
+Now, we are ready to construct a map 
+$
+\mathrm T\colon\St(n,\,B_a,\,I)\rightarrow\St(n,\,B).
+$
+
+\begin{proof}[Proof of Theorem~\ref{a3map}]
+For $u=Me_1$, $M\in\E(n,\,B_a)$, $v\in I^n$, $u^tv=0$ denote $w=M^*e_1$ (then $wu=1$) and choose $m\in\mathbb N$ such that some $\tilde w$, $\tilde u\in B^n$ localise to $wa^m$ and $ua^m$, $\tilde u^tv=0$ and $\tilde w^t\tilde u=a^{2m}$.
+Now set $\mathrm T(F(u,\,v))=X_{\tilde u,v/a^{3m}}(a^{2m})$.
+Lemma~\ref{xproperties}\,a) and b) garantees that this definition does not depend on the choice of $m$ and the lifts $\tilde u$ and $\tilde w$.
+Similarly, set $\mathrm T(S(u,\,v))=Y_{u/a^{3m},\tilde v}(a^{2m})$.
+These elements satisfy R1--R3 by Lemmas~\ref{xproperties} and~\ref{yproperties}.
+For $u=Me_1$, $v=M^*e_2$, $M\in\E(n,\,B_a)$ consider $w=M^*e_1$, $z=Me_2$, $x=Me_3$ and $y=M^*e_3$.
+Then, multiply these element on appropriate power of $a$, take their lifts to $B$ and apply Lemma~\ref{x=y} to get R4.
+So that, the map $\mathrm T$ is well-defined.
+
+Commutativity of the diagram follows directly from the definitions of elements $X(u,\,v)$, $Y(u,\,v)$ and $X_{u,v}(a)$, $Y_{u,v}(a)$ and the possibility to redistribute the powers of $a$ after localisation.
+\end{proof}
+
+The next section is devoted to the proof of Theorem~\ref{a3map} for Steinberg groups corresponding to an arbitrary simply-laced root system of rank $l\geq3$.
+To do so, we will ``glue'' maps $T$ constructed in the present section for systems of type $\mathrm A_3$.
+All main results of the present paper follow from the existence of such a map.
 

### 2016-04-20 paper.tex
Minor

@@
 
-\title{A local-global principle for $K_2$ of $\GL_4$ and orthogonal groups}
+\title{On centrality of orthogonal $\Kt$}
 \keywords {Steinberg groups, $K_2$-functor. {\em Mathematical Subject Classification (2010):} 19C09}
@@
 \date {\today}
+\thanks{Authors of the present paper acknowledge the financial support from Russian Science Foundation grant 14-11-00297}
 
@@
 
-\begin{abstract} To be written. \end{abstract}
+\begin{abstract} We give a short uniform proof of centrality of $\mathrm K_2(\Phi, R)$ for all simply-laced root systems $\Phi$ of rank $\geq 3$.
+\end{abstract}
 
@@
 
-The main goal of the present paper is to give a uniform proof of centrality of $\mathrm K_2$ for all simply-laced Chevalley groups of rank $\geq3$.\footnote{The authors acknowledge support of ER-EN-EF.}
-
-The paper is organised as follows.
-In the first section we give yet another presentation for $\St(4,\,R,\,I)=\St(\mathrm A_3,\,R,\,I)$.
+The paper is organised as follows. In the first section we give yet another presentation for $\St(4,\,R,\,I)=\St(\mathrm A_3,\,R,\,I)$.
 It mimics the standart vector representation of $\SL(n,\,R)$, therefore in the first section we use representations and corresponding vector notation. 
 Afterwards we can deduce a local--global principle for $\St(\mathrm\Phi,\,R)$ and centrality of $\Kt(\mathrm\Phi,\,R)$ for $\Phi=\mathrm A_3$. 
-In the second section we use obtained results to prove the same theorems for any simply laced $\Phi$ of rank $\geq3$.
-There we switch to the root notation.
+In the second section we use obtained results to prove the same theorems for any simply laced $\Phi$ of rank $\geq3$. There we switch to the root notation.
 
-\section{Case of $\mathrm A_3$}
+\section{Principal notation}
 
@@
 
-In the present paper $R$ denotes commutative (associative, unital) ring, $l\geq3$, and $n=l+1\geq4$, $R^n$ is a free (right) $R$-module with basis $e_1,\ldots,e_n$, $\GL(n,\,R)$ is a group of invertible $n\times n$ matrices over $R$, $\E(n,\,R)$ its elementary subgroup generated by elementary transvections
+In the present paper $R$ denotes commutative (associative, unital) ring, $l\geq3$, and $n=l+1\geq4$, $R^n$ is a free (right) $R$-module with basis $e_1,\ldots,e_n$, 
+$\GL(n,\,R)$ is a group of invertible $n\times n$ matrices over $R$, $\E(n,\,R)$ its elementary subgroup generated by elementary transvections 
 $$\{t_{ij}(r)=1+e_{ij}r\mid1\leq i\neq j\leq n,\ r\in R\},$$
@@
 \end{align}
-All commutators in the present paper are left-normed, $[x,\,y]=xyx\inv y\inv$. Denote $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ a natural projection sending $x_{ij}(r)$ to $t_{ij}(r)$.
+All commutators in the present paper are left-normed, $[x,\,y]=xyx\inv y\inv$. 
+Denote $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ a natural projection sending $x_{ij}(r)$ to $t_{ij}(r)$.
 
 Suslin showed that (already for $n\geq3$) the elementary group coincides with the subgroup of $\GL(n,\,R)$ generated by matrices
-$$
-\{t(u,\,v)=1+uv^t\mid u\in\Um(n,\,R),\ v\in R^n,\ u^tv=0\},
-$$
+$$\{t(u,\,v)=1+uv^t\mid u\in\Um(n,\,R),\ v\in R^n,\ u^tv=0\},$$
 where $\Um(n,\,R)$ is a set of unimodular coloumns of $R^n$, i.e., such that their entries generate the unit ideal of $R$, $u^t$ stands for $u$ {\it transposed}~\cite{Sus}.
@@
 Then, van der Kallen developed Suslin's ideas and showed that the Steinberg group $\St(n,\,R)$ is isomorphic to a group defined by a set of generators
-$$
-\{X(u,\,v)\mid u\in\Um(n,\,R),\ v\in R^n,\ u^tv=0\}
-$$
-and relations
-\setcounter{equation}{0}
-\renewcommand{\theequation}{K\arabic{equation}}
+$$\{X(u,\,v)\mid u\in\Um(n,\,R),\ v\in R^n,\ u^tv=0\}$$ and relations
+\setcounter{equation}{0} \renewcommand{\theequation}{K\arabic{equation}}
 \begin{align}

### 2016-04-21 paper.tex
Writing introduction

@@
 \newcommand{\ls}[1]{\!\,^{(#1)}\!L_1}
+\newcommand{\rA}{\mathsf{A}}
+\newcommand{\rB}{\mathsf{B}}
+\newcommand{\rC}{\mathsf{C}} 
+\newcommand{\rD}{\mathsf{D}} 
+\newcommand{\rE}{\mathsf{E}}
+\newcommand{\rF}{\mathsf{F}}
+\newcommand{\rG}{\mathsf{G}}
 
@@
 \section*{Inroduction}
+The main goal of the present paper is to obtain a uniform proof of the local-global principle for $\Kt$ and centrality of $\Kt$ for Chevalley groups of type $ADE$.
+
+Recall that for each reduced root system $\Phi$ and a commutative ring $R$ one can construct a split simple group $G(\Phi, R)$ called \emph{Chevalley group}.
+For $\Phi$ of rank $\geq 2$ the abstract group $G(\Phi, R)$ contains a large normal subgroup $\E(\Phi, R)$ generated by the elementary root unipotents $t_\alpha(\xi)$, $\xi\in R$, $\alpha\in \Phi$.
+The quotient group $\Ko(\Phi, R)=G(\Phi, R)/\E(\Phi, R)$ is called the \emph{unstable $\Ko$-functor}.
+This functor shares many properties with its stable counterpart $\mathrm{SK}_1(R) = \lim\limits_{l\to\infty}\Ko(\rA_\ell, R)$ which, in turn, is an essential direct summand of $\Ko(R)$.
+
+Similarly to the definition of the algebraic $\Kt$-functor, one can define $\Kt(\Phi, R)$ as the kernel of the canonical projection $\varphi\colon\St(\Phi, R)\twoheadrightarrow \E(\Phi, R)$.
+Here $\St(\Phi, R)$ stands for the \emph{Steinberg group} of type $\Phi$, i.\,e. the group defined by formal generators $x_\alpha(\xi)$ modeling root unipotents $t_\alpha(\xi)$
+and the explicit list of relations called Steinberg relations. The projection $\varphi$ is defined by the identity $\varphi(x_\alpha(\xi))=t_\alpha(\xi)$.
+
+It is classically known that $\Kt(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$ if $R$ is commutative local ring and $\Phi$ has rank $\geq 2$ (see \cite{Stein}).
+However, to prove that centrality of $\Kt$ holds for \emph{arbitrary} $R$ is much harder.
+The first result in this direction was obtained in 1977 by W. van~der~Kallen for $\Phi=\rA_\ell$, $\ell\geq 3$.
+Using a similar method the first-named author established centrality of $\Kt(\rC_\ell, R)$, see \cite{Lav}.
+On the other hand, the second-named author has obtained centrality of $\Kt(\rE_\ell, R)$ using a different method, see \cite{SCh}.
+In turn, our main result is the following theorem.
+\begin{tm}\label{tm:main} Let $R$ be an arbitrary commutative ring.
+ If $\Phi$ is an irreducible root system of type $\Phi=\rA_\ell, \rD_\ell, \rE_\ell$, $\ell\geq 3$ then the following statements are true:
+ \begin{enumerate}
+  \item The group $\St(\Phi, R)$ satisfies local-global principle for $\Kt$, i.\,e. an element $g\in\St(n,\,R[X])$ such that $g(0)=1\in\St(n,\,R)$
+  is trivial if and only if $g_M=1\in\St(n,\,R_M[X])$ for all maximal ideals $M\triangleleft R$.
+  \item The group $\Kt(\Phi, R)$ is contained in the centre of $\St(\Phi, R)$.  
+ \end{enumerate}
+\end{tm}
+The special case $\Phi=\rA_\ell$, $\ell\geq 3$ of the first statement of the above theorem was proven for the first time by Tulenbaev~\cite[Th.~2.1]{Tul}, while the case $\Phi=\rE_\ell$ was studied in~\cite{SCh}.
+Thus, the new cases in \cref{tm:main} are $\Phi=\rA_3$ and $\Phi=\rD_\ell$, $\ell\geq 4$.
 
@@
 $$
-An analogous statement about Steinberg groups was proven by Tulenbaev for $n\geq5$~\cite[Th.~2.1]{Tul}. I.e., for $n\geq5$ and $g\in\St(n,\,R[X])$ such that 
-$$g(0)=1\in\St(n,\,R)\ \text{ and }\ g_{\mathfrak m}=1\in\St(n,\,R_{\mathfrak m}[X])$$
- for all $\mathfrak m\in\Max R$ holds $g=1$.
 
 For $I\trianglelefteq R$ denote $\St(n,\,R,\,I)=\Ker\big(\St(n,\,R)\epi\St(n,\,R/I)\big)$ {\it a relative Steinberg group}. Clearly, $\St(n,\,R[X],\,XR[X])$ is the kernel of the evaluation ``$X=0$''.
+
+\section{Yet another presentation for $\St(4, R)$.}
 

### 2016-04-22 paper.tex
Further expanded the introduction

--- 2016-04-20 paper.tex
@@
 \newcommand{\E}{{\mathrm{E}}}
+\newcommand{\GG}{{\mathrm{G}}}
 \newcommand{\Um}{\mathop{\mathrm{Um}}\nolimits}
@@
 \section*{Inroduction}
+The main goal of this paper is to establish the local-global principle and centrality of orthogonal $\Kt$ for arbitrary commutative ring $R$.
 
-The paper is organised as follows. In the first section we give yet another presentation for $\St(4,\,R,\,I)=\St(\mathrm A_3,\,R,\,I)$.
-It mimics the standart vector representation of $\SL(n,\,R)$, therefore in the first section we use representations and corresponding vector notation. 
-Afterwards we can deduce a local--global principle for $\St(\mathrm\Phi,\,R)$ and centrality of $\Kt(\mathrm\Phi,\,R)$ for $\Phi=\mathrm A_3$. 
-In the second section we use obtained results to prove the same theorems for any simply laced $\Phi$ of rank $\geq3$. There we switch to the root notation.
+Recall that for each reduced root system $\Phi$ and a commutative ring $R$ one can associate a split simple group $\GG(\Phi, R)$ called the \emph{Chevalley group}.
+For $\Phi$ of rank $\geq 2$ the abstract group $\GG(\Phi, R)$ contains a large normal subgroup $\E(\Phi, R)$ generated by the elementary root unipotents $t_\alpha(\xi)$, $\xi\in R$, $\alpha\in \Phi$.
+The quotient group functor $\Ko(\Phi, R)=\GG(\Phi, R)/\E(\Phi, R)$ is called the \emph{unstable $\Ko$-functor}.
+This functor shares many properties with its stable counterpart $\mathrm{SK}_1(R) = \lim\limits_{l\to\infty}\Ko(\rA_\ell, R)$ which, in turn, is an essential direct summand of $\Ko(R)$.
+
+Similarly to the definition of the algebraic $\Kt$-functor, one can define $\Kt(\Phi, R)$ as the kernel of the canonical projection $\varphi\colon\St(\Phi, R)\twoheadrightarrow \E(\Phi, R)$.
+Here $\St(\Phi, R)$ stands for the \emph{Steinberg group} of type $\Phi$, i.\,e. the group defined by formal generators $x_\alpha(\xi)$ modeling root unipotents $t_\alpha(\xi)$
+and the explicit list of relations called Steinberg relations. The projection $\varphi$ is defined by the identity $\varphi(x_\alpha(\xi))=t_\alpha(\xi)$.
+
+It is classically known that $\Kt(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$ if $R$ is commutative local ring and $\Phi$ has rank $\geq 2$ (see \cite{Stein}).
+However, to prove that centrality of $\Kt$ holds for \emph{arbitrary} $R$ is much harder.
+The first result in this direction was obtained in 1977 by W. van~der~Kallen for $\Phi=\rA_\ell$, $\ell\geq 3$ using the technique called ``another presentation''.
+Using a similar approach, in \cite{Lav} the first-named author has established centrality of $\Kt(\rC_\ell, R)$ for $\ell\geq 3$.
+In turn, the key result of this paper is the following theorem.
+\begin{tm}\label{tm:centrality}  Let $R$ be an arbitrary commutative ring and $\ell\geq 4$ then 
+the group $\Kt(\rD_\ell, R)$ is contained in the centre of $\St(\rD_\ell, R)$. \end{tm}
+Notice that the analogous assertion for $\Phi=\rE_\ell$, $\ell=6,7,8$ has been demonstrated by the second named author in \cite{SCh}.
+Our proof of \cref{tm:centrality} follows the same lines as in \cite[Theorem~1]{SCh} and, essentially, boils down to the proof of the following local-global principle.
+\begin{tm}\label{tm:lg-principle} Let $\Phi$ be an irreducible simply-laced root system of rank $\geq 3$ and $R$ be arbitrary commutative ring.
+Then an element $g\in\St(\Phi,\,R[X])$ satisfying $g(0)=1\in\St(\Phi,\,R)$ is trivial in $\St(\Phi,\,R[X])$
+if and only if the elements $g_M\in\St(\Phi,\,R_M[X])$ are trivial for all maximal ideals $M\triangleleft R$. \end{tm}
+
+The special case $\Phi=\rA_\ell$, $\ell\geq 4$ of \cref{tm:lg-principle} was demonstrated for the first time by Tulenbaev, see~\cite[Theorem~2.1]{Tul},
+while similar assertions for $\Phi=\rC_\ell$, $\ell\geq 3$ and $\Phi=\rE_\ell$, $\ell=6,7,8$ have been established in \cite{Lav2} and \cite{SCh}, respectively.
+The special cases $\Phi=\rA_3$ and $\Phi=\rD_\ell$, $\ell\geq 4$ of \cref{tm:lg-principle} are new and have not been known before.
+
+Compare \cref{tm:lg-principle} with the local-global principle for $\Ko$ which states that an element of the congruence subgroup $g\in \GG(\Phi,\,R[X], XR[X])$ is elementary
+(i.\,e. lies in $\E(\Phi, R[X])$) if and only if $g_M=1\in\E(\Phi,\,R_M)$ for all maximal ideals $M \triangleleft R$.
+
+The rest of the paper is organised as follows. 
+In \cref{sec:yap} we formulate ``yet another presentation'' for the rank $3$ linear Steinberg groups $\St(4,\,R)=\St(\mathrm A_3,\,R)$.
+This presentation allows us to reprove Tulenbaev's key lemma \cite[Lemma~2.3]{Tul} under a weaker assumption on the rank of $\Phi$.
+%It mimics the standart vector representation of $\SL(n,\,R)$, therefore in the first section we use representations and corresponding vector notation. 
+Finally, in \cref{sec:patching} we apply patching techniques from \cite{SCh} to deduce our main results.
+%There we switch to the root notation.
 
@@
 
-The local--global principle for the elementary group proven by Suslin~\cite{Sus} is a statement that an elementary matrix over a polynomial ring $g\in\E(n,\,R[X])$ becomes trivial after the evaluation ``$X=0$''
-$$
-g\in\Ker\big(\E(n,\,R[X])\rightarrow\E(n,\,R)\big)
-$$
-and after localisations
-$$
-g_{\mathfrak m}=1\in\E(n,\,R_{\mathfrak m}[X])
-$$
-for all maximal ideals $\mathfrak m$ of a base ring $R$, if and only if it is trivial from the very begining
-$$
-g=1\in\E(n,\,R[X]).
-$$
-An analogous statement about Steinberg groups was proven by Tulenbaev for $n\geq5$~\cite[Th.~2.1]{Tul}. I.e., for $n\geq5$ and $g\in\St(n,\,R[X])$ such that 
-$$g(0)=1\in\St(n,\,R)\ \text{ and }\ g_{\mathfrak m}=1\in\St(n,\,R_{\mathfrak m}[X])$$
- for all $\mathfrak m\in\Max R$ holds $g=1$.
+For $I\trianglelefteq R$ denote $\St(n,\,R,\,I)=\Ker\big(\St(n,\,R)\epi\St(n,\,R/I)\big)$ {\it a relative Steinberg group}. Clearly, $\St(n,\,R[X],\,XR[X])$ is the kernel of the evaluation ``$X=0$''.
 
-For $I\trianglelefteq R$ denote $\St(n,\,R,\,I)=\Ker\big(\St(n,\,R)\epi\St(n,\,R/I)\big)$ {\it a relative Steinberg group}. Clearly, $\St(n,\,R[X],\,XR[X])$ is the kernel of the evaluation ``$X=0$''.
+\section{Yet another presentation for $\St(4, R)$.} \label{sec:yap}
 
@@
 
+\section{Patching Tulenbaev maps}\label{sec:patching}
+
 The next section is devoted to the proof of Theorem~\ref{a3map} for Steinberg groups corresponding to an arbitrary simply-laced root system of rank $l\geq3$.

### 2016-04-22 paper.tex
Minor

@@
 \section{Principal notation}
+In the present paper $R$ denotes commutative (associative, unital) ring, $l\geq3$, and $n=l+1\geq4$, $R^n$ is a free (right) $R$-module with basis $e_1,\ldots,e_n$, 
+$\GL(n,\,R)$ is a group of invertible $n\times n$ matrices over $R$, $\E(n,\,R)$ its elementary subgroup generated by elementary transvections
 
@@
 
-In the present paper $R$ denotes commutative (associative, unital) ring, $l\geq3$, and $n=l+1\geq4$, $R^n$ is a free (right) $R$-module with basis $e_1,\ldots,e_n$, 
-$\GL(n,\,R)$ is a group of invertible $n\times n$ matrices over $R$, $\E(n,\,R)$ its elementary subgroup generated by elementary transvections 
 $$\{t_{ij}(r)=1+e_{ij}r\mid1\leq i\neq j\leq n,\ r\in R\},$$

### 2016-04-22 paper.tex
Fixed preliminaries

@@
 
+\author {Andrei Lavrenov}
+\email {avlavrenov {\it at} gmail.com}
+
 \author{Sergey Sinchuk}
 \email{sinchukss {\it at} gmail.com}
-
-\author {Andrei Lavrenov}
-\email {avlavrenov {\it at} gmail.com}
 
@@
 
-Similarly to the definition of the algebraic $\Kt$-functor, one can define $\Kt(\Phi, R)$ as the kernel of the canonical projection $\varphi\colon\St(\Phi, R)\twoheadrightarrow \E(\Phi, R)$.
+Similarly to the definition of the algebraic $\Kt$-functor, one can define $\Kt(\Phi, R)$ as the kernel of the canonical projection $\phi\colon\St(\Phi, R)\twoheadrightarrow \E(\Phi, R)$.
 Here $\St(\Phi, R)$ stands for the \emph{Steinberg group} of type $\Phi$, i.\,e. the group defined by formal generators $x_\alpha(\xi)$ modeling root unipotents $t_\alpha(\xi)$
-and the explicit list of relations called Steinberg relations. The projection $\varphi$ is defined by the identity $\varphi(x_\alpha(\xi))=t_\alpha(\xi)$.
+and the explicit list of relations called Steinberg relations (see~\cref{sec:prelim}).
 
-It is classically known that $\Kt(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$ if $R$ is commutative local ring and $\Phi$ has rank $\geq 2$ (see \cite{Stein}).
+It is classically known that $\Kt(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$ if $R$ is commutative local ring and $\Phi$ has rank $\geq 2$ (see \cite{St73}).
 However, to prove that centrality of $\Kt$ holds for \emph{arbitrary} $R$ is much harder.
 The first result in this direction was obtained in 1977 by W. van~der~Kallen for $\Phi=\rA_\ell$, $\ell\geq 3$ using the technique called ``another presentation''.
-Using a similar approach, in \cite{Lav} the first-named author has established centrality of $\Kt(\rC_\ell, R)$ for $\ell\geq 3$.
+Using a similar approach, the first-named author has established centrality of $\Kt(\rC_\ell, R)$ for $\ell\geq 3$, see \cite{Lav}.
 In turn, the key result of this paper is the following theorem.
@@
 the group $\Kt(\rD_\ell, R)$ is contained in the centre of $\St(\rD_\ell, R)$. \end{tm}
-Notice that the analogous assertion for $\Phi=\rE_\ell$, $\ell=6,7,8$ has been demonstrated by the second named author in \cite{SCh}.
-Our proof of \cref{tm:centrality} follows the same lines as in \cite[Theorem~1]{SCh} and, essentially, boils down to the proof of the following local-global principle.
+Notice that the analogous statement in the case $\Phi=\rE_\ell$, $\ell=6,7,8$ has been demonstrated by the second named author in \cite{SCh}.
+\cref{tm:centrality} is essentially a corollary of the following local-global principle.
 \begin{tm}\label{tm:lg-principle} Let $\Phi$ be an irreducible simply-laced root system of rank $\geq 3$ and $R$ be arbitrary commutative ring.
@@
 
+There are known counterexamples to centrality of $\Kt$ in the rank $2$ case (see~\cite{W}).
+This shows that the assumption on the rank of $\Phi$ in \cref{tm:lg-principle} is strict.
+
 Compare \cref{tm:lg-principle} with the local-global principle for $\Ko$ which states that an element of the congruence subgroup $g\in \GG(\Phi,\,R[X], XR[X])$ is elementary
@@
 
+Our proof of \cref{tm:lg-principle} follows the same lines as in \cite[Theorem~1]{SCh}.
+More concretely, using the same patching technique as in \cite{SCh} we reduce the problem to the case $\Phi=\rA_3$.
+Then, we formulate and prove a new presentation of the linear group $\St(4, R)$ and then utilize it to reprove 
+Tulenbaev's key lemma (cf. \cite[Lemma~2.3]{Tul}) in the rank $3$ case.
+
 The rest of the paper is organised as follows. 
-In \cref{sec:yap} we formulate ``yet another presentation'' for the rank $3$ linear Steinberg groups $\St(4,\,R)=\St(\mathrm A_3,\,R)$.
-This presentation allows us to reprove Tulenbaev's key lemma \cite[Lemma~2.3]{Tul} under a weaker assumption on the rank of $\Phi$.
+In \cref{sec:yap} we formulate ``yet another presentation'' for the rank $3$ Steinberg groups.
 %It mimics the standart vector representation of $\SL(n,\,R)$, therefore in the first section we use representations and corresponding vector notation. 
-Finally, in \cref{sec:patching} we apply patching techniques from \cite{SCh} to deduce our main results.
+Finally, in \cref{sec:patching} we prove our main results.
 %There we switch to the root notation.
 
-\section{Principal notation}
-In the present paper $R$ denotes commutative (associative, unital) ring, $l\geq3$, and $n=l+1\geq4$, $R^n$ is a free (right) $R$-module with basis $e_1,\ldots,e_n$, 
-$\GL(n,\,R)$ is a group of invertible $n\times n$ matrices over $R$, $\E(n,\,R)$ its elementary subgroup generated by elementary transvections
+\section{Preliminaries} \label{sec:prelim}
+Throughout this paper $R$ denotes an associative commutative ring with identity.
+All commutators are left-normed, i.\,e. $[x,\,y]=xyx\inv y\inv$.
 
-Tulenbaev used {\it another presentation} for a relative Steinberg group to prove a local--global principle for a linear Steinberg group~\cite{Tul}. 
-This relative another presentation was inspired by the {\it absolute} one of van der Kallen~\cite{vdK}. 
-However, Tulenbaev's presentation can only be used for $\St(l+1,\,R)=\St(\mathrm A_l,\,R)$, $l\geq4$.
+%Tulenbaev used {\it another presentation} for a relative Steinberg group to prove a local--global
+%principle for a linear Steinberg group~\cite{Tul}. 
+%This relative another presentation was inspired by the {\it absolute} one of van der Kallen~\cite{vdK}. 
+%However, Tulenbaev's presentation can only be used for $\St(l+1,\,R)=\St(\mathrm A_l,\,R)$, $l\geq4$.
 
-Tulenbaev's result can be applied to the subsystems of type $\mathrm A_4$ inside $\mathrm E_l$ and ``glued'' to get a local--global principle for Steinberg groups of type $\mathrm E_l$~\cite{SCh}. 
-To use this glueing method for groups of type $\mathrm D_l$ as well one has to work with subsystems of type $\mathrm A_3$ instead, and thus extend Tulenbaev's result to the case of $\mathrm A_3$.
+%Tulenbaev's result can be applied to the subsystems of type $\mathrm A_4$ inside $\mathrm E_l$ and ``glued'' 
+% to get a local--global principle for Steinberg groups of type $\mathrm E_l$~\cite{SCh}. 
+%To use this glueing method for groups of type $\mathrm D_l$ as well one has to work with subsystems 
+%of type $\mathrm A_3$ instead, and thus extend Tulenbaev's result to the case of $\mathrm A_3$.
 
-Recently, the local--global principle was obtained for Steinberg groups of type $\mathrm C_l$ starting from rank 3~\cite{Lav2}. 
-That is another motivation to consider the linear Steinberg group in rank 3.
+%Recently, the local--global principle was obtained for Steinberg groups of type $\mathrm C_l$ starting from rank 3~\cite{Lav2}. 
+%That is another motivation to consider the linear Steinberg group in rank 3.
 
-$$\{t_{ij}(r)=1+e_{ij}r\mid1\leq i\neq j\leq n,\ r\in R\},$$
-where 1 stands for the identity matrix and $e_{ij}$ for the matrix unit. The Steinberg group is a group given by formal generators
-$$\{x_{ij}(r)\mid1\leq i\neq j\leq n,\ r\in R\}$$
-and Steinberg relations
+We denote by $R^n$ the free $R$-module with basis $e_1,\ldots,e_n$ and by $\Um(n,\,R)$ the subset of unimodular columns $v\in R^n$ 
+whose entries generate $R$ as an ideal.
+
+As usual, $\E(n, R)=\E(\rA_{n-1}, R)$ denotes the elementary group, i.\,e. the subgroup of the general linear group $\GL(n, R)$ generated by transvections
+$t_{ij}(r)=1+r \cdot e_{ij}$, $1\leq i\neq j\leq n$, $r\in R$,
+where 1 stands for the identity matrix and $e_{ij}$ for the matrix unit.
+
+The Steinberg group $\St(n, R) = \St(\rA_{n-1}, R)$ is the group presented by generators
+$x_{ij}(r)$, $1\leq i\neq j\leq n$, $r\in R\}$ and relations
 \setcounter{equation}{0}
@@
 \end{align}
-All commutators in the present paper are left-normed, $[x,\,y]=xyx\inv y\inv$. 
-Denote $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ a natural projection sending $x_{ij}(r)$ to $t_{ij}(r)$.
+The natural projection $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ sends $x_{ij}(r)$ to $t_{ij}(r)$.
 
-Suslin showed that (already for $n\geq3$) the elementary group coincides with the subgroup of $\GL(n,\,R)$ generated by matrices
-$$\{t(u,\,v)=1+uv^t\mid u\in\Um(n,\,R),\ v\in R^n,\ u^tv=0\},$$
-where $\Um(n,\,R)$ is a set of unimodular coloumns of $R^n$, i.e., such that their entries generate the unit ideal of $R$, $u^t$ stands for $u$ {\it transposed}~\cite{Sus}.
+In \cite{Sus} Suslin showed for $n\geq 3$ that the elementary group $\E(n, R)$ coincides with the subgroup of $\GL(n,\,R)$ generated by matrices
+of the form $t(u,\,v)=1+uv^t$ where $u\in\Um(n,\,R)$, $v\in R^n$ and $u^tv=0$. Here $u^t$ stands for the transpose of $u$.
 This result clearly implies that $\E(n,\,R)$ is normal inside $\GL(n,\,R)$.
-Then, van der Kallen developed Suslin's ideas and showed that the Steinberg group $\St(n,\,R)$ is isomorphic to a group defined by a set of generators
-$$\{X(u,\,v)\mid u\in\Um(n,\,R),\ v\in R^n,\ u^tv=0\}$$ and relations
+Afterwards, W.~van~der~Kallen developed Suslin's ideas and showed for $n\geq4$ that the Steinberg group $\St(n,\,R)$ is isomorphic to the group presented by generators
+$$\{X(u,\,v)\mid u\in\Um(n,\,R),\ v\in R^n,\ u^tv=0\}$$ and the following list of relations (see~\cite{vdK}):
 \setcounter{equation}{0} \renewcommand{\theequation}{K\arabic{equation}}
@@
 &X(u,\,v)X(u,\,w)=X(u,\,v+w),\\
-&X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(v,\,u)\inv v')
+&X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(v,\,u)\inv v').
 \end{align}
-for $n\geq4$~\cite{vdK}.
-Then, it is also obvious that $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ is a central extension.
-Observe that van der Kallen uses pairs of a coloumn and a row $(i,\,j)$ to parametrise his generators, and we prefer two coloumns.
+This presentation clearly implies that $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ is a central extension.
+Notice that our notation for the generators slightly differs from that of~\cite{vdK}, e.\,g. our elements $X(u, v)$ correspond to van der Kallen's $(u, v^t)$.
 
-For $I\trianglelefteq R$ denote $\St(n,\,R,\,I)=\Ker\big(\St(n,\,R)\epi\St(n,\,R/I)\big)$ {\it a relative Steinberg group}. Clearly, $\St(n,\,R[X],\,XR[X])$ is the kernel of the evaluation ``$X=0$''.
+For a splitting ideal $I\trianglelefteq R$ the \emph{relative Steinberg group} $\St(n,\,R,\,I)$ can be defined as the kernel $\Ker\big(\St(n,\,R)\epi\St(n,\,R/I)\big)$.
+%Clearly, $\St(n,\,R[X],\,XR[X])$ is the kernel of the evaluation ``$X=0$''.
 

### 2016-04-24 paper.tex
Rewriting 2

@@
 \begin{align}
-&X(u,\,v)X(u,\,w)=X(u,\,v+w),\\
+&X(u,\,v)X(u,\,w)=X(u,\,v+w), \label{add1} \\
 &X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(v,\,u)\inv v').
@@
 
+Recall that an ideal $I\trianglelefteq R$ is called a \emph{splitting ideal} if the canonical projection $R \twoheadrightarrow R/I$ splits as a unital ring morphism.
 For a splitting ideal $I\trianglelefteq R$ the \emph{relative Steinberg group} $\St(n,\,R,\,I)$ can be defined as the kernel $\Ker\big(\St(n,\,R)\epi\St(n,\,R/I)\big)$.
-%Clearly, $\St(n,\,R[X],\,XR[X])$ is the kernel of the evaluation ``$X=0$''.
+
+For general $I$ the relative Steinberg group is no more a subgroup of $\St(n, R)$ but rather is its central extension.
+For the purposes of the present text it suffices to consider only relative Steinberg groups corresponding to splitting ideals $I$.
+For more information regarding general relative Steinberg groups we refer the reader to \cite[Section~3]{SCh}.
 
 \section{Yet another presentation for $\St(4, R)$.} \label{sec:yap}
+The key ingredient in Tulenbaev's proof of the local-global principle is the construction of the homomorphism $T$ which fits into the following commutative diagram.
+$$\xymatrix{\St(n,\,R\ltimes XR_a[X],\,XR_a[X]) \ar@{^{(}->}[r] \ar[d] & \St(n, R \ltimes XR_a[X]) \ar[d]_-{\lambda_a^*} \\
+             \St(n,\,R_a[X],\,XR_a[X]) \ar@{-->}[ru]_-{T} \ar@{^{(}->}[r] & \St(n, R_a[X])}$$
+Here $a$ is arbitrary nonnilpotent element of $R$, $n\geq5$ and $\lambda_a^*$ is the morphism induced by the morphism $\lambda_a\colon R \to R_a$ of principal localisation at $a$.
+Notice that $XR_a[X]$ is a splitting ideal for both $R_a[X]$ and $R \ltimes XR_a[X]$.
+It is clear that the image of $T$ is contained in the image of the top arrow, therefore this implies the relative Steinberg groups in the left-hand side of the diagram are isomoprhic.
+%This $T$ is an inverse to a map induced by localisation, so that constructing $\mathrm T$ may be treated
+%as a proof of excision property for Steinberg group in this very particular situation.
 
-The key step in Tulenbaev's proof is constructing a homomorphism
-$$
-\mathrm T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X],\,XR_a[X])
-$$
-for any (non-nilpotent) element $a\in R$, $n\geq5$ ($R_a$ stands for a principle localisation of $R$ in $a$).
-This $\mathrm T$ is an inverse to a map induced by localisation, so that constructing $\mathrm T$ may be treated as a proof of excision property for Steinberg group in this very particular situation.
+%To prove the local--global principle for Steinberg groups of type $\mathrm D_l$ and centrality 
+%of $\mathrm K_2(\mathrm D_l,\,R)$ we need such a map for $n=4$ (i.e., for the group of type $\mathrm A_3$).
 
-To prove the local--global principle for Steinberg groups of type $\mathrm D_l$ and centrality of $\mathrm K_2(\mathrm D_l,\,R)$ we need such a map for $n=4$ (i.e., for the group of type $\mathrm A_3$).
-
-Tulenbaev uses the following presentaion for the relative Steinberg group, see~\cite[Prop.~1.6]{Tul}. Assume that $I\trianglelefteq R$ such that a short exact sequence
-\renewcommand{\theequation}{$\dagger$}
-\begin{align}
-\xymatrix{
-0\ar@<0.1ex>[r]^{}&I\ar@<0.1ex>[r]^{}&R\ar@<0.5ex>[r]^{\pi}&R/I\ar@<0.5ex>[l]^{\sigma}\ar@<0.1ex>[r]^{}&0
-}
-\end{align}
-splits, i.e., $\pi\sigma=1$. The $\St(n,\,R,\,I)$ is isomorphic to a group given by generators
-$$
-\{X(u,\,v)\mid u\in\E(n,\,R)e_1,\ v\in I^n,\ u^tv=0\}
-$$
-subject to relations
+In order to construct the arrow $T$ Tulenbaev uses the following presentation for the relative Steinberg group, see~\cite[Proposition~1.6]{Tul}. 
+%Assume that $I\trianglelefteq R$ such that a short exact sequence
+%\renewcommand{\theequation}{$\dagger$}
+%\begin{align} \xymatrix{0\ar@<0.1ex>[r]^{}&I\ar@<0.1ex>[r]^{}&R\ar@<0.5ex>[r]^{\pi}&R/I\ar@<0.5ex>[l]^{\sigma}\ar@<0.1ex>[r]^{}&0} \end{align} splits, i.e., $\pi\sigma=1$.
+\begin{prop}\label{prop:TulPres}
+For a splitting ideal $I$ the group $\St(n,\,R,\,I)$ is isomorphic to the group given by generators
+$$\{X(u,\,v)\mid u\in\E(n,\,R)e_1,\ v\in I^n,\ u^tv=0\}$$ subject to relations
 \setcounter{equation}{0}
@@
 &X(u,\,v)X(u,\,w)=X(u,\,v+w),\\
-&X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(v,\,u)\inv v'),\\
-&X(ur+w,\,v)=X(u,\,vr)X(w,\,v)\,\text{ for }r\in R,\ (u,\,w)\in\Um_{n\times2}(R).
+&X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(v,\,u)\inv v'), \label{add2} \\
+&X(ur+w,\,v)=X(u,\,vr)X(w,\,v)\,\text{ for }r\in R,\ (u,\,w)\in\Um_{n\times2}(R) \label{add3}.
 \end{align}
-Here $\Um_{n\times2}(R)$ is a set of $n\times2$ matrices $M$ such that there exists a $2\times n$ matrix $N$ with $NM=\begin{pmatrix}1&0\\0&1\end{pmatrix}$.
-The ideal satisfying $\dagger$ is called the splitting ideal, $XR_a[X]\trianglelefteq R_a[X]$ is obviously the splitting one.
+\end{prop}
+Here $\Um_{n\times2}(R)$ denotes the set of $n\times2$ \emph{unimodular matrices}, i.\,e.
+matrices $M$ such that there exists a $2\times n$ matrix $N$ satisfying $NM=\begin{pmatrix}1&0\\0&1\end{pmatrix}$.
 
-Another presentations of van der Kallen and Tulenbaev are given in terms of generators parametrised by pairs of vectors, where the first one is ``good'' (unimodular or a coloumn of an elementary matrix) and the second one is arbitrary.
-This allows to formulate easily an additivity by the second argument, but one has to write something similar to T3 instead of additivity by the first one.
+Both ``another presentations'' of van der Kallen and Tulenbaev are given in terms of generators parametrised by pairs of vectors,
+ where the first one is in some sense ``good'' (i.\,e. unimodular or a column of an elementary matrix) and the second one is arbitrary.
+It is easy to formulate the additivity property in the second argument for these generators (cf. \eqref{add1}, \eqref{add2}),
+while it is not so easy when it comes for the additivity in the first argument (cf. \eqref{add3}).
+%Such presentations allowed them to formulate easily an additivity by the second argument, but one has to write something similar to T3 instead of additivity by the first one.
 
 Now, we need to construct a homomorphism
-$$
-\mathrm T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X],\,XR_a[X]),
-$$
+$$\mathrm T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X],\,XR_a[X]),$$
 i.e., to find elements in the target group subject to Tulenbaev's relations, but because of T3 one can do it only for $n\geq5$, see~\cite[Lemmas~1.2 and~1.3\,c)]{Tul}.

### 2016-04-24 paper.tex
Finished first 4 pages

@@
 \newtheorem*{atm}{Another Presentation}
+\newlist{lmlist}{enumerate}{1} \setlist[lmlist]{label={\rm(\roman{lmlisti})}, ref=\thelm.(\roman{lmlisti}),noitemsep} \Crefname{lmlisti}{Lemma}{Lemmas}
 
@@
 &X(u,\,v)X(u,\,w)=X(u,\,v+w), \label{add1} \\
-&X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(v,\,u)\inv v').
+&X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(v,\,u)\inv v'). \label{conj1}
 \end{align}
@@
 Recall that an ideal $I\trianglelefteq R$ is called a \emph{splitting ideal} if the canonical projection $R \twoheadrightarrow R/I$ splits as a unital ring morphism.
-For a splitting ideal $I\trianglelefteq R$ the \emph{relative Steinberg group} $\St(n,\,R,\,I)$ can be defined as the kernel $\Ker\big(\St(n,\,R)\epi\St(n,\,R/I)\big)$.
+For a splitting ideal $I\trianglelefteq R$ the \emph{relative Steinberg group} $\St(n,\,R,\,I) = \St(\rA_{n-1}, R, I)$ can be defined as the kernel $\Ker\big(\St(n,\,R)\epi\St(n,\,R/I)\big)$.
 
-For general $I$ the relative Steinberg group is no more a subgroup of $\St(n, R)$ but rather is its central extension.
+For a general $I$ the relative Steinberg group $\St(\Phi, R, I)$ is no more a subgroup of $\St(\Phi, R)$ but rather is its central extension.
 For the purposes of the present text it suffices to consider only relative Steinberg groups corresponding to splitting ideals $I$.
@@
              \St(n,\,R_a[X],\,XR_a[X]) \ar@{-->}[ru]_-{T} \ar@{^{(}->}[r] & \St(n, R_a[X])}$$
-Here $a$ is arbitrary nonnilpotent element of $R$, $n\geq5$ and $\lambda_a^*$ is the morphism induced by the morphism $\lambda_a\colon R \to R_a$ of principal localisation at $a$.
+Here $n\geq5$, $a$ is arbitrary nonnilpotent element of $R$ and $\lambda_a^*$ is the morphism induced by the morphism $\lambda_a\colon R \to R_a$ of principal localisation at $a$.
 Notice that $XR_a[X]$ is a splitting ideal for both $R_a[X]$ and $R \ltimes XR_a[X]$.
-It is clear that the image of $T$ is contained in the image of the top arrow, therefore this implies the relative Steinberg groups in the left-hand side of the diagram are isomoprhic.
+It is clear that the image of $T$ is contained in the image of the top arrow, therefore this implies that the relative Steinberg groups in the left-hand side of the diagram are isomoprhic.
 %This $T$ is an inverse to a map induced by localisation, so that constructing $\mathrm T$ may be treated
@@
 \begin{align}
-&X(u,\,v)X(u,\,w)=X(u,\,v+w),\\
-&X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(v,\,u)\inv v'), \label{add2} \\
+&X(u,\,v)X(u,\,w)=X(u,\,v+w), \label{add2}\\
+&X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(v,\,u)\inv v'), \label{conj2}  \\
 &X(ur+w,\,v)=X(u,\,vr)X(w,\,v)\,\text{ for }r\in R,\ (u,\,w)\in\Um_{n\times2}(R) \label{add3}.
@@
 
-Now, we need to construct a homomorphism
-$$\mathrm T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X],\,XR_a[X]),$$
-i.e., to find elements in the target group subject to Tulenbaev's relations, but because of T3 one can do it only for $n\geq5$, see~\cite[Lemmas~1.2 and~1.3\,c)]{Tul}.
+The construction of the homomorphism $T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X]])$
+amounts to choosing certain elements in the target group $\St(n,\,R\ltimes XR_a[X]])$ and proving that these elements satisfy the relations \eqref{add2}--\eqref{add3}, see~\cite[Lemmas~1.2 and~1.3\,c)]{Tul}.
+The main problem with this recipe is that the assumption $n\geq5$ is essential to check that the relation~\eqref{add3} holds.
 
-One can not parametrise generators by a pair of arbitrary vectors since it is not even known that $t(u,\,v)\in\E(n,\,R)$ for arbitrary orthogonal $u$ and $v$~\cite{Rao}.
+It is not possible to choose arbitrary orthogonal vectors $u$, $v$ as parameters for the generators because in this situation it is not even known that $t(u,\,v)\in\E(n,\,R)$, see~\cite{Rao}.
 
-To generalise Tulenbaev's results for $n=4$ we use a presentation with two types of generators: $F(u,\,v)$ with $u$ good and $v$ arbitrary, which are additive by the second component, and $S(u,\,v)$ with $u$ arbitrary and $v$ good, which are additive by the first component.
-For $u$ and $v$ both good we require that these two types of generators coincide.
-More precisely,
+To generalise Tulenbaev's results for $n=4$ we will use a more ``symmetric`` presentation with two types of generators: 
+$F(u,\,v)$ with $u$ ''good`` and $v$ arbitrary and $S(u,\,v)$ with $u$ arbitrary and $v$ ''good``.
+The generators $F(u,\,v)$ will be additive in the second component, while $S(u,\,v)$ will be additive in the first one.
+When $u$ and $v$ are both ''good`` we require these two generators to coincide.
+More formally, we have the following presentation.
 
 \begin{df}
-for $I\trianglelefteq R$, $n\geq4$ define $\St^*(n,\,R,\,I)$ to be a group given by the set of generators
+For $I\trianglelefteq R$ and $n\geq4$ define $\St^*(n,\,R,\,I)$ to be the group with the set of generators
 \begin{multline*}
-\{F(u,\,v)\mid u\in\E(n,\,R)e_1,\ v\in I^n,\ u^tv=0\}\,\cup\\
-\cup\{S(u,\,v)\mid u\in I^n,\ v\in\E(n,\,R)e_1,\ u^tv=0\}
+\{F(u,\,v)\mid u\in\E(n,\,R)e_1,\ v\in I^n,\ u^tv=0\}\,\cup\{S(u,\,v)\mid u\in I^n,\ v\in\E(n,\,R)e_1,\ u^tv=0\}
 \end{multline*}
@@
 \begin{align}
-&F(u,\,v)F(u,\,w)=F(u,\,v+w),\\
-&S(u,\,v)S(w,\,v)=S(u+w,\,v),\\
-&F(u,\,v)F(u',\,v')F(u,\,v)\inv=F(t(u,\,v)u',\,t(v,\,u)\inv v'),\\
-&F(u,\,va)=S(ua,\,v)\ \forall\,a\in I,\,(u,\,v^t)=(Me_1,\,e_2^tM\inv),\,M\!\in\E(n,\,R).
+&F(u,\,v)F(u,\,w)=F(u,\,v+w), \label{add4}\\
+&S(u,\,v)S(w,\,v)=S(u+w,\,v), \label{add5}\\
+&F(u,\,v)F(u',\,v')F(u,\,v)\inv=F(t(u,\,v)u',\,t(v,\,u)\inv v'), \label{conj3} \\
+&F(u,\,va)=S(ua,\,v)\ \forall\,a\in I,\,(u,\,v^t)=(M e_1,\,e_2^t M\inv),\,M\!\in\E(n,\,R) \label{coinc}.
 \end{align}
 \end{df}
-
-One could probably wonder why we assumed only one relation on conjugated element, instead of four different relations on generators of each type conjugated by generators of each type.
-Three ``missing'' relations actualy hold automaticaly.
-
+Notice that we only described how a generator $F(u, v)$ acts via conjugation on another generator $F(u',v')$ and omitted three similar relations involving generators $S(u,v)$ of the second type.
+The reason for this is the following lemma which asserts that the ``missing'' relations will follow automatically from \eqref{add4}--\eqref{coinc}.
 \begin{lm}
 \label{allyouneedisf}
-Denote $\varphi\colon\St^*(n,\,R,\,I)\rightarrow\E(n,\,R)$ the natural map, sending $F(u,\,v)\mapsto t(u,\,v)$, $S(u,\,v)\mapsto t(u,\,v)$.
-\begin{enumerate}
-\item 
-$\St^*(n,\,R,\,I)$ is generated by the set of elements
-$$
-\{F(u,\,va)\mid a\in I,\ (u,\,v^t)=(Me_1,\,e_2^tM\inv),\,M\in\E(n,\,R)\};
-$$
-\item
-for any $g\in\St^*(n,\,R,\,I)$ holds
-\setcounter{equation}{2}
-\renewcommand{\theequation}{R\arabic{equation}'}
-\begin{align}
-&gF(u,\,v)g\inv=F(\varphi(g)u,\,\varphi(g\inv)^tv);
-\end{align}
-\item
-for any $g\in\St^*(n,\,R,\,I)$ holds
-\setcounter{equation}{2}
-\renewcommand{\theequation}{R\arabic{equation}''}
-\begin{align}
-&gS(u,\,v)g\inv=S(\varphi(g)u,\,\varphi(g\inv)^tv);
-\end{align}
-\item
-there exists a well-defined ``transpose automorphism''
-$$
-F(u,\,v)^t=S(v,\,u),\quad S(u,\,v)^t=F(v,\,u).
-$$
-\end{enumerate}
-\end{lm}
+Denote by $\phi\colon\St^*(n,\,R,\,I)\rightarrow\E(n,\,R)$ the natural map sending $F(u,\,v)\mapsto t(u,\,v)$ and $S(u,\,v)\mapsto t(u,\,v)$.
+Then the following facts are true.
+\begin{lmlist}
+\item $\St^*(n,\,R,\,I)$ is generated as an abstract group by the set of elements 
+      $$\{F(u,\,va)\mid a\in I,\ (u,\,v^t)=(Me_1,\,e_2^tM\inv),\,M\in\E(n,\,R)\};$$
+\item for any $g\in\St^*(n,\,R,\,I)$ one has 
+      \setcounter{equation}{2} \renewcommand{\theequation}{R\arabic{equation}'}
+      \begin{equation} gF(u,\,v)g\inv=F(\phi(g)u,\,\phi(g\inv)^tv); \end{equation}
+\item for any $g\in\St^*(n,\,R,\,I)$ one has
+       \setcounter{equation}{2} \renewcommand{\theequation}{R\arabic{equation}''}
+      \begin{equation} gS(u,\,v)g\inv=S(\phi(g)u,\,\phi(g\inv)^tv); \end{equation}
+\item there is a ``transpose automorphism'' defined on $\St^*(n, R, I)$ satisfying
+      $$F(u,\,v)^t=S(v,\,u),\quad S(u,\,v)^t=F(v,\,u).$$
+\end{lmlist} \end{lm}
 
 \begin{proof}
-Take an arbitrary generator of the first type $F(u,\,v)$ and take $M\in\E(n,\,R)$ such that $F(u,\,v)=F(Me_1,\,M^*\tilde v)$.
-Here $M^*$ stands for a contragradient matrix, $M^*=(M\inv)^t$.
-By R1 we have
-$$
-F(u,\,v)=\prod\limits_{k\neq1}F(Me_1,\,M^*e_k\tilde v_k)
-$$
-where $\tilde v_k$ stands for $k$-th coordinate of $\tilde v=\sum e_k\tilde v_k$. Similarly, with the use of R4 we get 
-$$
-S(u,\,v)=\prod\limits_{k\neq1}S(Ne_k\tilde u_k,\,N^*e_1)=\prod\limits_{k\neq1}F(Ne_k,\,N^*e_1\tilde u_k)
-$$
-and obtain a). Obviously, b) follows from a). For c) it is sufficient to show that
-$$
-F(u,\,v)S(u',\,v')F(u,\,v)\inv=S(t(u,\,v)u',\,t(u,\,v)^*v').
-$$
-Let $S(u',\,v')=\prod F(Ne_k,\,N^*e_1\tilde u_k)$, then
+Let $F(u,\,v)$ be an arbitrary generator of the first type and let $M\in\E(n,\,R)$ be such that $F(u,\,v)=F(Me_1,\,M^*\tilde v)$. 
+Here we denote by $M^*$ the contragradient matrix, $M^*=(M\inv)^t$. 
+By \eqref{add4} we have $$F(u,\,v)=\prod\limits_{k\neq1}F(Me_1,\,M^*e_k\tilde v_k)$$
+where $\tilde v_k$ stands for $k$-th coordinate of $\tilde v=\sum e_i\tilde v_i$.
+Applying relations \eqref{add5}, \eqref{coinc} we get
+$$S(u,\,v)=\prod\limits_{k\neq1}S(Ne_k\tilde u_k,\,N^*e_1)=\prod\limits_{k\neq1}F(Ne_k,\,N^*e_1\tilde u_k)$$
+and, thus, obtain $(\mathrm{i})$. Obviously, $(\mathrm{ii})$ follows from $(\mathrm{i})$. 
+To prove $(\mathrm{iii})$ it suffices to show that
+$$F(u,\,v)S(u',\,v')F(u,\,v)\inv=S(t(u,\,v)u',\,t(u,\,v)^*v').$$
+For $S(u',\,v')=\prod_{k\neq 1} F(Ne_k,\,N^*e_1\tilde u_k)$ we have
 \begin{multline*}
@@
 \end{multline*}
-Finally, d) follows from c).
+Finally, $(\mathrm{iv})$ follows from $(\mathrm{iii})$.
 \end{proof}

### 2016-04-25 paper.tex
Proofread one more page

@@
 Afterwards, W.~van~der~Kallen developed Suslin's ideas and showed for $n\geq4$ that the Steinberg group $\St(n,\,R)$ is isomorphic to the group presented by generators
-$$\{X(u,\,v)\mid u\in\Um(n,\,R),\ v\in R^n,\ u^tv=0\}$$ and the following list of relations (see~\cite{vdK}):
+$$\{X(u,\,v)\mid u\in\Um(n,\,R),\ v\in R^n,\ u^tv=0\}$$ and the following list of relations (see~\cite[Theorem~1]{vdK}):
 \setcounter{equation}{0} \renewcommand{\theequation}{K\arabic{equation}}
@@
 This presentation clearly implies that $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ is a central extension.
-Notice that our notation for the generators slightly differs from that of~\cite{vdK}, e.\,g. our elements $X(u, v)$ correspond to van der Kallen's $(u, v^t)$.
+Notice that our notation for the generators of $\St(n, R)$ slightly differs from that of~\cite{vdK}, e.\,g. we parametrize elements $X(u, v)$ with two columns
+rather than with one column and one row. Our generator $X(u,v)$ corresponds to van der Kallen's generator $(u, v^t)$.
 
@@
 
-Next, we show that for a splitting ideal $I\trianglelefteq R$ the group $\St^*(n,\,R,\,I)$ is isomorphic to $\St(n,\,R,\,I)=\Ker\big(\St(n,\,R)\epi\St(n,\,R/I)\big)$.
-With this end we construct two inverse homomorphisms
-$$
-\xymatrix{
-\St^*(n,\,R,\,I)\ar@<0.5ex>[r]^{\iota}&\St(n,\,R,\,I)\ar@<0.5ex>[l]^{\kappa}.
-}
-$$
+Our next goal is to show for a splitting ideal $I\trianglelefteq R$ that the group $\St^*(n,\,R,\,I)$ is isomorphic to $\St(n,\,R,\,I)=\Ker\big(\St(n,\,R)\epi\St(n,\,R/I)\big)$.
+With this end we construct two mutually inverse homomorphisms
+$$\xymatrix{\St^*(n,\,R,\,I)\ar@<0.5ex>[r]^{\iota}&\St(n,\,R,\,I)\ar@<0.5ex>[l]^{\kappa}.}$$
 
-Firstly, we define $\iota$ as a homomorhism to an absolute group
-$$
-\xymatrix{
-\St^*(n,\,R,\,I)\ar@<0.0ex>[r]^{\iota}&\St(n,\,R).
-}
-$$
-We do not need an assumption that $I$ is a splitting ideal for that.
+Firstly, we define $\iota$ as a homomorphism to the absolute group (for which we de not need the assumption that $I$ is splitting).
+$$\xymatrix{\St^*(n,\,R,\,I)\ar@<0.0ex>[r]^{\iota}&\St(n,\,R).}$$
 
-Clearly, we map elements $F(u,\,v)$ to van der Kallen's another generators $X(u,\,v)$.
-To find images for $S(u,\,v)$ as well we recall that van der Kallen in~\cite[3.8--3.10]{vdK} defines also elements
-$$
-x(u,\,v)\in\St(n,\,R),\ u^tv=0,\ u_i=0\,\text{ or }\,v_i=0\,\text{ for some }\,1\leq i\leq n.
-$$
-Now, ``transpose'' the definition~\cite[3.13]{vdK}.
+Clearly, we must map the elements $F(u,\,v)$ to van der Kallen's generators $X(u,\,v)$.
+Now we should find the images for the elements $S(u,\,v)$ as well.
+First of all, recall that van der Kallen in~\cite[3.8--3.10]{vdK} constructs the following elements
+$$x(u,\,v)\in\St(n,\,R),\ u^tv=0,\ u_i=0\,\text{ or }\,v_i=0\,\text{ for some }\,1\leq i\leq n.$$
+The following definition is the ``transpose'' of \cite[3.13]{vdK}.
+\begin{df} For $u\in R^n$, $v\in\E(n,\,R)e_1$, $u^tv=0$, consider the set $\overline Y(u,\,v)\subseteq\St(n,\,R)$
+ consisiting of all elements $y\in\St(n,\,R)$ that admit the decomposition $y=\prod x(w^k,\,v)$, 
+ where $\sum u^k=u$ and $u^k=c^k \cdot (e_pv_q-e_qv_p)$ for some $c^k\in R$, $1\leq p\neq q\leq n$. \end{df}
 
-\begin{df}
-For $u\in R^n$, $v\in\E(n,\,R)e_1$, $u^tv=0$, consider the set $\overline Y(u,\,v)\subseteq\St(n,\,R)$ consisiting of all elements $y\in\St(n,\,R)$ which could be decomposed as a product $\prod x(w^k,\,v)$, where $\sum w^k=u$ and $w^k=(e_pv_q-e_qv_p)c^k$ for some $c^k\in R$, $1\leq p\neq q\leq n$.
-\end{df}
+Since columns of elementary matrices are unimodular, one can find $w\in R^t$ such that $w^tv=1$.
+It is not hard to check that $u = (w^t\cdot v)\cdot u = \sum_{p<q}u_{pq}$, where $u_{pq} = (u_pw_q - u_qw_p) \cdot (v_qe_p - v_pe_q)\in{}\!R^n$,
+therefore $\overline Y(u,\,v)$ is not empty (cf.~\cite[3.1--3.2]{vdK}).
+Obviously, for $x\in\overline Y(u,\,v)$ and $y\in\overline Y(w,\,v)$ one has $xy\in\overline Y(u+w,\,v)$.
 
-Since coloumns of elementary matrices are unimodular, $\overline Y(u,\,v)$ is not empty (see~\cite[3.1--3.2]{vdK}).
-Obviously, for $x\in\overline Y(u,\,v)$ and $y\in\overline Y(w,\,v)$ holds $xy\in\overline Y(u+w,\,v)$.
+Repeating~\cite[3.14--3.15]{vdK} verbatim one shows the following.
+\begin{lm} For $g\in\St(n,\,R)$ one has
+\begin{enumerate} \item $g\overline Y(u,\,v)g\inv\subseteq\overline Y(\phi(g)u,\,\phi(g)^*v)$;
+                  \item $\overline Y(u,\,v)$ consists of exactly one element. \end{enumerate} \end{lm}
 
-Repeating~\cite[3.14--3.15]{vdK} verbatim one shows that
-
-\begin{lm}
-for $g\in\St(n,\,R)$ holds
-\begin{enumerate}
-\item
-$g\overline Y(u,\,v)g\inv\subseteq\overline Y(\phi(g)u,\,\phi(g)^*v)$;
-\item
-$\overline Y(u,\,v)$ consists of exactly one element.
-\end{enumerate}
-\end{lm}
-
-The only element of $\overline Y(u,\,v)$ we denote by $Y(u,\,v)$.
-We map elements $S(u,\,v)\in\St^*(n,\,R,\,I)$ to $Y(u,\,v)$.
-To show that such a homomorphism is well-defined we check that $X(u,\,v)$ and $Y(u,\,v)$ satisfy relations R1--R4, but R1--R3 are already checked.
-
-\begin{lm}
-Consider $(u,\,v^t)=(Me_1,\,e_2^tM\inv)$, $M\in\E(n,\,R)$, $a\in I$. Then $X(u,\,va)=Y(ua,\,v)$.
-\end{lm}
-
+We denote the only element of $\overline Y(u,\,v)$ by $Y(u,\,v)$. 
+Now we can define $\iota$ by sending $S(u,\,v)\in\St^*(n,\,R,\,I)$ to $Y(u,\,v)$. 
+To show that the map $\iota$ is well-defined we should check that the elements $X(u,\,v)$ and $Y(u,\,v)$ satisfy the relations 
+\eqref{add4}--\eqref{coinc} (with $F$'s and $S$'s replaced with $X$'s and $Y$'s).
+Notice that the validity of relations \eqref{add4}--\eqref{conj3} has already been checked.
+\begin{lm} For $(u,\,v^t)=(Me_1,\,e_2^tM\inv)$, $M\in\E(n,\,R)$, $a\in I$ one has $X(u,\,va)=Y(ua,\,v)$. \end{lm}
 \begin{proof}
-It suffices to show that $X(e_1,\,e_2a)=Y(e_1a,\,e_2)$. Compute the commutator $[Y(-e_3,\,e_2),\,X(e_1,\,e_3a)]$ in two ways:
-$$
-Y(-e_3,\,e_2)X(e_1,\,e_3a)Y(-e_3,\,e_2)\inv\cdot X(e_1,\,-e_3a)=X(e_1,\,e_2a),
-$$
-and
-$$
-Y(-e_3,\,e_2)\cdot\,X(e_1,\,e_3a)Y(e_3,\,e_2)X(e_1,\,e_3a)\inv=Y(e_1a,\,e_2).
-$$
+In view of the above lemma we only need to show that $X(e_1,\,e_2a)=Y(e_1a,\,e_2)$.
+This equality can be obtained by computing the commutator $[Y(-e_3,\,e_2),\,X(e_1,\,e_3a)]$ in two ways:
+$$ Y(-e_3,\,e_2)X(e_1,\,e_3a)Y(-e_3,\,e_2)\inv\cdot X(e_1,\,-e_3a)=X(e_1,\,e_2a), \text{ and} $$
+$$ Y(-e_3,\,e_2)\cdot\,X(e_1,\,e_3a)Y(e_3,\,e_2)X(e_1,\,e_3a)\inv=Y(e_1a,\,e_2). \qedhere $$
 \end{proof}
 
-Therefore, the homomorphism $\iota\colon\St^*(n,\,R,\,I)\rightarrow\St(n,\,R)$ sending $F(u,\,v)$ to $X(u,\,v)$ and $S(u,\,v)$ to $Y(u,\,v)$ is well-defined.
-Denote $\rho_I\colon R\epi R/I$, then one can easily see that induced morphism on Steinberg groups
-$$\rho_I^*\colon\St(n,\,R)\rightarrow\St(n,\,R/I)$$
- sends $X(u,\,v)$ to $X(\rho_I(u),\,\rho_I(v))$ and $Y(u,\,v)$ to $Y(\rho_I(u),\,\rho_I(v))$.
-Observe that $\E(n,\,R)\epi\E(n,\,R/I)$ is surjective so that for $x\in\E(n,\,R)e_1$ holds that $\rho_I(x)\in\E(n,\,R/I)e_1$.
-It follows from additivity relations that $X(u,\,0)=1=Y(0,\,v)$, thus $\mathrm{Im}(\iota)\subseteq\Ker(\rho_I^*)=\St(n,\,R,\,I)$.
+We can sum up the above discussion into the following result.
+\begin{lm} \label{lm:map-iota}
+ For a splitting ideal $I\trianglelefteq R$ there exists a well-defined homomorphism 
+ $$\iota\colon\St^*(n,\,R,\,I)\rightarrow\St(n,\,R, I) \subseteq \St(n, R)$$ 
+ satisfying the equalities $\iota (F(u,\,v)) = X(u,\,v)$ and $\iota (S(u,\,v)) = Y(u,\,v)$. \end{lm}
+\begin{proof}
+We already know that $\iota$ is well-defined. It suffices to check that the image of $\iota$ is contained in $\St(n,\,R,I)$.
+Denote the canonical projection $R\epi R/I$ by $\rho$.
+Clearly, the induced group morphism $\rho^*\colon\St(n,\,R)\rightarrow\St(n,\,R/I)$ sends $X(u,\,v)$ to $X(\rho(u),\,\rho(v))$ and $Y(u,\,v)$ to $Y(\rho(u),\,\rho(v))$. 
+Observe that $\E(n,\,R)\epi\E(n,\,R/I)$ is surjective, therefore for $x\in\E(n,\,R)e_1$ one has $\rho(x)\in\E(n,\,R/I)e_1$. 
+From the additivity relations we get that $X(u,\,0)=1=Y(0,\,v)$, hence $\mathrm{Im}(\iota)\subseteq\Ker(\rho^*)=\St(n,\,R,\,I)$, as required. \end{proof}
 

### 2016-04-25 paper.tex
Minor fix

@@
 \begin{lm} \label{lm:map-iota}
- For a splitting ideal $I\trianglelefteq R$ there exists a well-defined homomorphism 
- $$\iota\colon\St^*(n,\,R,\,I)\rightarrow\St(n,\,R, I) \subseteq \St(n, R)$$ 
+ For any $I \trianglelefteq R$ there exists a well-defined homomorphism $$\iota\colon\St^*(n,\,R,\,I)\rightarrow\St(n,\,R, I) \subseteq \St(n, R)$$ 
  satisfying the equalities $\iota (F(u,\,v)) = X(u,\,v)$ and $\iota (S(u,\,v)) = Y(u,\,v)$. \end{lm}

### 2016-04-25 paper.tex
More fixes

@@
 \begin{prop}\label{prop:TulPres}
-For a splitting ideal $I$ the group $\St(n,\,R,\,I)$ is isomorphic to the group given by generators
-$$\{X(u,\,v)\mid u\in\E(n,\,R)e_1,\ v\in I^n,\ u^tv=0\}$$ subject to relations
+For a splitting ideal $I$ and $n\geq 4$ the group $\St(n,\,R,\,I)$ is isomorphic to the group defined by generators
+$$\{X(u,\,v)\mid u\in\E(n,\,R)e_1,\ v\in I^n,\ u^tv=0\}$$ and the following set of relations
 \setcounter{equation}{0}
@@
 \end{align}
+Moreover, the group $\St(n, R)$ decomposes into the semidirect product $\St(n,\,R, I)\rtimes \St(n,\,R/I)$.
 \end{prop}
@@
 Both ``another presentations'' of van der Kallen and Tulenbaev are given in terms of generators parametrised by pairs of vectors,
- where the first one is in some sense ``good'' (i.\,e. unimodular or a column of an elementary matrix) and the second one is arbitrary.
+ where the first one is ``good'' in some sense  (i.\,e. unimodular or a column of an elementary matrix) while the second one is arbitrary.
 It is easy to formulate the additivity property in the second argument for these generators (cf. \eqref{add1}, \eqref{add2}),
-while it is not so easy when it comes for the additivity in the first argument (cf. \eqref{add3}).
+while it is not so easy when it comes to the additivity in the first argument (cf. \eqref{add3}).
 %Such presentations allowed them to formulate easily an additivity by the second argument, but one has to write something similar to T3 instead of additivity by the first one.
 
-The construction of the homomorphism $T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X]])$
-amounts to choosing certain elements in the target group $\St(n,\,R\ltimes XR_a[X]])$ and proving that these elements satisfy the relations \eqref{add2}--\eqref{add3}, see~\cite[Lemmas~1.2 and~1.3\,c)]{Tul}.
+The construction of the homomorphism $T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X])$
+amounts to choosing certain elements in the group $\St(n,\,R\ltimes XR_a[X])$ and proving that these elements satisfy relations \eqref{add2}--\eqref{add3}, see~\cite[Lemmas~1.2 and~1.3\,c)]{Tul}.
 The main problem with this recipe is that the assumption $n\geq5$ is essential to check that the relation~\eqref{add3} holds.
@@
 Clearly, we must map the elements $F(u,\,v)$ to van der Kallen's generators $X(u,\,v)$.
-Now we should find the images for the elements $S(u,\,v)$ as well.
+Now we should find the images for elements $S(u,\,v)$ as well.
 First of all, recall that van der Kallen in~\cite[3.8--3.10]{vdK} constructs the following elements
@@
 We denote the only element of $\overline Y(u,\,v)$ by $Y(u,\,v)$. 
-Now we can define $\iota$ by sending $S(u,\,v)\in\St^*(n,\,R,\,I)$ to $Y(u,\,v)$. 
-To show that the map $\iota$ is well-defined we should check that the elements $X(u,\,v)$ and $Y(u,\,v)$ satisfy the relations 
+Now we can finish the definition of $\iota$ by requiring that $\iota(S(u,\,v)) = Y(u,\,v)$ for $S(u,\,v)\in\St^*(n,\,R,\,I)$. 
+To show that the map $\iota$ is well-defined we should check that elements $X(u,\,v)$ and $Y(u,\,v)$ satisfy the relations 
 \eqref{add4}--\eqref{coinc} (with $F$'s and $S$'s replaced with $X$'s and $Y$'s).
-Notice that the validity of relations \eqref{add4}--\eqref{conj3} has already been checked.
-\begin{lm} For $(u,\,v^t)=(Me_1,\,e_2^tM\inv)$, $M\in\E(n,\,R)$, $a\in I$ one has $X(u,\,va)=Y(ua,\,v)$. \end{lm}
+Only the validity of relation \eqref{coinc} is not immediately obvious.
+\begin{lm} \label{lm:XY} For $(u,\,v^t)=(Me_1,\,e_2^tM\inv)$, $M\in\E(n,\,R)$, $a\in I$ one has $X(u,\,va)=Y(ua,\,v)$. \end{lm}
 \begin{proof}
@@
 
-We can sum up the above discussion into the following result.
+The following result is a consequence of the above argument.
 \begin{lm} \label{lm:map-iota}
@@
 
+In order to construct the arrow $\kappa$ we use the presentation from \cref{prop:TulPres}.
+We set $$\kappa(X(u,v)) = F(u,v),\ u\in \E(n, R)e_1,\ v\in I^n.$$ 
+We have to check that $F(u,v)$ satisfy the relations \eqref{add2}--\eqref{add3}.
+The relations \eqref{add2} and \eqref{conj2} are immediately obvious.
+
+\begin{comment}
 We constructed $\iota$ for an arbitrary $I\trianglelefteq R$. For $I$ a splitting ideal we construct an inverse homomorphism
@@
 Surjectivity of $\kappa$ follows from Lemma~\ref{allyouneedisf}\,a), thus it is an isomorphism and $\iota$ is inverse to it.
+\end{comment}
 

### 2016-04-27 paper.tex
Improved proof of the isomorphism St*=St

@@
 \begin{align}
-&x_{ij}(r)x_{ij}(s)=x_{ij}(r+s),\\
-&[x_{ij}(r),\,x_{hk}(s)]=1,\text{ for }h\neq j,\ k\neq i,\\
-&[x_{ij}(r),\,x_{jk}(s)]=x_{ik}(rs).
+&x_{ij}(r)x_{ij}(s)=x_{ij}(r+s), \label{add0}\\
+&[x_{ij}(r),\,x_{hk}(s)]=1,\text{ for }h\neq j,\ k\neq i, \label{ccf1}\\
+&[x_{ij}(r),\,x_{jk}(s)]=x_{ik}(rs) \label{ccf2}.
 \end{align}
@@
 
-Recall that an ideal $I\trianglelefteq R$ is called a \emph{splitting ideal} if the canonical projection $R \twoheadrightarrow R/I$ splits as a unital ring morphism.
+Recall that an ideal $I\trianglelefteq R$ is called a \emph{splitting ideal} if the canonical projection $R \twoheadrightarrow R/I$ splits as a unital ring morphism, i.\,e. one has $\pi\sigma=1$.
+$$\xymatrix{0\ar@<0.1ex>[r]^{}&I\ar@<0.1ex>[r]^{}&R\ar@<0.5ex>[r]^{\pi}&R/I\ar@<0.5ex>[l]^{\sigma}\ar@<0.1ex>[r]^{}&0}$$
 For a splitting ideal $I\trianglelefteq R$ the \emph{relative Steinberg group} $\St(n,\,R,\,I) = \St(\rA_{n-1}, R, I)$ can be defined as the kernel $\Ker\big(\St(n,\,R)\epi\St(n,\,R/I)\big)$.
@@
 For the purposes of the present text it suffices to consider only relative Steinberg groups corresponding to splitting ideals $I$.
-For more information regarding general relative Steinberg groups we refer the reader to \cite[Section~3]{SCh}.
+For more information regarding the general case we refer the reader to \cite[Section~3]{SCh}.
 
@@
 %\renewcommand{\theequation}{$\dagger$}
-%\begin{align} \xymatrix{0\ar@<0.1ex>[r]^{}&I\ar@<0.1ex>[r]^{}&R\ar@<0.5ex>[r]^{\pi}&R/I\ar@<0.5ex>[l]^{\sigma}\ar@<0.1ex>[r]^{}&0} \end{align} splits, i.e., $\pi\sigma=1$.
 \begin{prop}\label{prop:TulPres}
@@
 matrices $M$ such that there exists a $2\times n$ matrix $N$ satisfying $NM=\begin{pmatrix}1&0\\0&1\end{pmatrix}$.
+In the definition of the semidirect product the group $\St(n, R/I)$ acts on $\St(n, R, I)$ by conjugation via the splitting map, i.\,e. $g \cdot X(u,\,v) = X(\phi(s(g))u, \phi(s(g))^*v)$.
+
+\begin{proof} For the sake of completeness we present below a more detailed version of Tulenbaev's proof.
+Tulenbaev constructs a pair of mutually inverse maps
+$$\xymatrix{ \St(n, R, I) \rtimes \St(n, R/I) \ar@<0.6ex>[r]^-\varphi &  \ar[l]^-\psi \St(n, R).}$$
+
+Define the map $\psi$ by $\psi(x_{ij}(\xi)) = (X(e_i, (\xi - \pi(\xi)e_j),\ x_{ij}(\pi(\xi)))$. 
+We have to check that $\psi$ preserves the relations \eqref{add0}--\eqref{ccf2}.
+For example, let us check \eqref{ccf1}. 
+First of all, recall that in any semidirect product of groups one can compute the commutator of two elements as follows:
+$$[(a, b), (c, d)] = (a \cdot {}^bc \cdot {}^{bdb^{-1}}a^{-1} \cdot {}^{[b, d]}c^{-1} , [b, d]).$$
+For $\xi\in R$ set $\xi' = \xi - \pi(\xi)$.
+Specializing $a = X(e_i, \xi' e_j)$, $b = x_{ij}(\pi(\xi))$, $c = X(e_j, \eta'e_k)$, $d = x_{jk}(\pi(\eta))$ and using the definition of the conjugation action 
+one computes the commutator $[\psi(x_{ij}(\xi), \psi(x_{jk}(\eta)]$ as follows:
+$$\left(X(e_i, \xi' e_j) \cdot X(e_j + \pi(\xi)e_i, \eta'e_k) \cdot X(e_i, \pi(\eta)\xi' e_k - \xi' e_j) \cdot X(e_j, -\eta'e_k),\ x_{ik}(\pi(\xi\eta))\right).$$
+After applying additivity relations \eqref{add2}, \eqref{add3} and moving the factor $X(e_i, -\xi' e_j)$ to the left hand side of the formula by means of relation \eqref{conj2}
+one gets the following expression
+$$(X(e_j, \eta'e_k) \cdot X(e_i, (\xi' \eta' + \pi(\xi)\eta' + \pi(\eta)\xi')e_k \cdot X(e_j, -\eta'e_k),\ x_{ik}(\pi(\xi\eta)).$$
+Since $\xi'\eta' + \pi(\xi)\eta' + \pi(\eta)\xi' = \xi\eta - \pi(\xi\eta)$ the above expression clearly simplifies to $\psi(x_{ik}(\xi\eta))$, as claimed.
+\end{proof}
+
+\begin{rk} \label{rk:T123'} Notice that from the proof of the above proposition it follows that one could replace the family of relations \eqref{add3}
+in the definition of $\St(n, R, I)$ with the following smaller family \eqref{add3'}.
+\setcounter{equation}{2} \renewcommand{\theequation}{T\arabic{equation}'}
+\begin{equation} X(e_ir+e_j,\,e_k)=X(e_i,\,rae_k)X(e_j,\,ae_k)\,\text{ for }r\in R,\ a\in I\text{ and } i,j,k\text{ distinct}. \label{add3'} \end{equation} \end{rk}
 
@@
 &F(u,\,v)F(u',\,v')F(u,\,v)\inv=F(t(u,\,v)u',\,t(v,\,u)\inv v'), \label{conj3} \\
-&F(u,\,va)=S(ua,\,v)\ \forall\,a\in I,\,(u,\,v^t)=(M e_1,\,e_2^t M\inv),\,M\!\in\E(n,\,R) \label{coinc}.
+&F(u,\,va)=S(ua,\,v),\ \text{for all}\ a\in I,\,(u,\,v^t)=(M e_1,\,e_2^t M\inv),\,M\!\in\E(n,\,R) \label{coinc}.
 \end{align}
 \end{df}
-Notice that we only described how a generator $F(u, v)$ acts via conjugation on another generator $F(u',v')$ and omitted three similar relations involving generators $S(u,v)$ of the second type.
+Notice that we only described how a generator $F(u, v)$ acts via conjugation on another generator $F(u',v')$ and have omitted three similar relations involving generators $S(u,v)$ of the second type.
 The reason for this is the following lemma which asserts that the ``missing'' relations will follow automatically from \eqref{add4}--\eqref{coinc}.
@@
 
-Firstly, we define $\iota$ as a homomorphism to the absolute group (for which we de not need the assumption that $I$ is splitting).
+In order to construct the arrow $\kappa$ we use the presentation from \cref{prop:TulPres}.
+We set $$\kappa(X(u,v)) = F(u,v),\ u\in \E(n, R)e_1,\ v\in I^n.$$ 
+In view of \cref{rk:T123'} it suffices to check that $F(u,v)$ satisfy the relations \eqref{add2}, \eqref{conj2}, \eqref{add3'}.
+The validity relations \eqref{add2}, \eqref{conj2} is obvious while \eqref{add3'} follows from the following computation:
+$$ F(e_i, rae_k) F(e_j, ae_k) = S(rae_i, e_k) S(ae_j, e_k) = S(a(re_i+e_j), e_k) = F(e_ir+e_j, ae_k). \qedhere $$
+
+As for the map $\iota$ we firstly define it as a homomorphism to the absolute group (for which we de not need the assumption that $I$ is splitting).
 $$\xymatrix{\St^*(n,\,R,\,I)\ar@<0.0ex>[r]^{\iota}&\St(n,\,R).}$$
@@
 Clearly, we must map the elements $F(u,\,v)$ to van der Kallen's generators $X(u,\,v)$.
-Now we should find the images for elements $S(u,\,v)$ as well.
+We should find the images for the elements $S(u,\,v)$ as well.
 First of all, recall that van der Kallen in~\cite[3.8--3.10]{vdK} constructs the following elements
@@
 From the additivity relations we get that $X(u,\,0)=1=Y(0,\,v)$, hence $\mathrm{Im}(\iota)\subseteq\Ker(\rho^*)=\St(n,\,R,\,I)$, as required. \end{proof}
-
-In order to construct the arrow $\kappa$ we use the presentation from \cref{prop:TulPres}.
-We set $$\kappa(X(u,v)) = F(u,v),\ u\in \E(n, R)e_1,\ v\in I^n.$$ 
-We have to check that $F(u,v)$ satisfy the relations \eqref{add2}--\eqref{add3}.
-The relations \eqref{add2} and \eqref{conj2} are immediately obvious.
 
@@
 
-At this point we obtained the presentation $\St^*(n,\,R,\,I)$ for the $\St(n,\,R,\,I)$ where $I\trianglelefteq R$ is a splitting ideal, $n\geq4$.
-
-Below we obtain the main result of this section, namely, construct a map 
-$$
-\mathrm T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X],\,XR_a[X]),
-$$
-for $n\geq4$. A local-global principle for Steinberg group and centrality of $\mathrm K_2$ formally follow from existance of this map~\cite[Lem.~15, Lem.~16, proof of Th.~2]{SCh}.
+At this point we have demonstrated for $n\geq4$ and a splitting ideal $I$ that $\St^*(n,\,R,\,I)$ and $\St(n,\,R,\,I)$ are isomorphic.
+Now we turn to the main result of this section, namely, we construct a map $$T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X],\,XR_a[X]),$$ for $n\geq4$. 
+A local-global principle for Steinberg group and centrality of $\mathrm K_2$ formally follow from existance of this map~\cite[Lem.~15, Lem.~16, proof of Th.~2]{SCh}.
 

### 2016-04-27 paper.tex
Fixed statement of Theorem 3

@@
 
-\title{On centrality of orthogonal $\Kt$}
+\title{On centrality of even orthogonal $\Kt$}
 \keywords {Steinberg groups, $K_2$-functor. {\em Mathematical Subject Classification (2010):} 19C09}
@@
 
-\section{Yet another presentation for $\St(4, R)$.} \label{sec:yap}
+\section{Yet another presentation for the relative Steinberg group.} \label{sec:yap}
 The key ingredient in Tulenbaev's proof of the local-global principle is the construction of the homomorphism $T$ which fits into the following commutative diagram.
-$$\xymatrix{\St(n,\,R\ltimes XR_a[X],\,XR_a[X]) \ar@{^{(}->}[r] \ar[d] & \St(n, R \ltimes XR_a[X]) \ar[d]_-{\lambda_a^*} \\
-             \St(n,\,R_a[X],\,XR_a[X]) \ar@{-->}[ru]_-{T} \ar@{^{(}->}[r] & \St(n, R_a[X])}$$
+\numberwithin{equation}{section}
+\begin{equation} \xymatrix{\St(n,\,R\ltimes XR_a[X],\,XR_a[X]) \ar@{^{(}->}[r] \ar[d] & \St(n, R \ltimes XR_a[X]) \ar[d]_-{\lambda_a^*} \\
+             \St(n,\,R_a[X],\,XR_a[X]) \ar@{-->}[ru]_-{T} \ar@{^{(}->}[r] & \St(n, R_a[X])} \label{eq:diagram} \end{equation}
 Here $n\geq5$, $a$ is arbitrary nonnilpotent element of $R$ and $\lambda_a^*$ is the morphism induced by the morphism $\lambda_a\colon R \to R_a$ of principal localisation at $a$.
@@
 matrices $M$ such that there exists a $2\times n$ matrix $N$ satisfying $NM=\begin{pmatrix}1&0\\0&1\end{pmatrix}$.
-In the definition of the semidirect product the group $\St(n, R/I)$ acts on $\St(n, R, I)$ by conjugation via the splitting map, i.\,e. $g \cdot X(u,\,v) = X(\phi(s(g))u, \phi(s(g))^*v)$.
+In the definition of the semidirect product the group $\St(n, R/I)$ acts on $\St(n, R, I)$ by conjugation via the splitting map, i.\,e.
+${}^g X(u,\,v) = X(\phi(s(g))u, \phi(s(g))^*v)$ for $g \in \St(n, R/I)$.
 
@@
 Since $\xi'\eta' + \pi(\xi)\eta' + \pi(\eta)\xi' = \xi\eta - \pi(\xi\eta)$ the above expression clearly simplifies to $\psi(x_{ik}(\xi\eta))$, as claimed.
+
+It remains to check that the map $\varphi$ given by $\varphi\left((X(u, v), 1)\right) = X(u, v),$ $\varphi\left((1, x_{ij}(\xi))\right) = X(e_i, \sigma(\xi)e_j)$
+is well-defined and inverse to $\psi$.
 \end{proof}
@@
 In view of \cref{rk:T123'} it suffices to check that $F(u,v)$ satisfy the relations \eqref{add2}, \eqref{conj2}, \eqref{add3'}.
-The validity relations \eqref{add2}, \eqref{conj2} is obvious while \eqref{add3'} follows from the following computation:
+The validity of relations \eqref{add2}, \eqref{conj2} is obvious while \eqref{add3'} follows from \eqref{add5} and \eqref{coinc}, indeed:
 $$ F(e_i, rae_k) F(e_j, ae_k) = S(rae_i, e_k) S(ae_j, e_k) = S(a(re_i+e_j), e_k) = F(e_ir+e_j, ae_k). \qedhere $$
@@
 
-The following result is a consequence of the above argument.
-\begin{lm} \label{lm:map-iota}
- For any $I \trianglelefteq R$ there exists a well-defined homomorphism $$\iota\colon\St^*(n,\,R,\,I)\rightarrow\St(n,\,R, I) \subseteq \St(n, R)$$ 
- satisfying the equalities $\iota (F(u,\,v)) = X(u,\,v)$ and $\iota (S(u,\,v)) = Y(u,\,v)$. \end{lm}
-\begin{proof}
-We already know that $\iota$ is well-defined. It suffices to check that the image of $\iota$ is contained in $\St(n,\,R,I)$.
-Denote the canonical projection $R\epi R/I$ by $\rho$.
-Clearly, the induced group morphism $\rho^*\colon\St(n,\,R)\rightarrow\St(n,\,R/I)$ sends $X(u,\,v)$ to $X(\rho(u),\,\rho(v))$ and $Y(u,\,v)$ to $Y(\rho(u),\,\rho(v))$. 
-Observe that $\E(n,\,R)\epi\E(n,\,R/I)$ is surjective, therefore for $x\in\E(n,\,R)e_1$ one has $\rho(x)\in\E(n,\,R/I)e_1$. 
-From the additivity relations we get that $X(u,\,0)=1=Y(0,\,v)$, hence $\mathrm{Im}(\iota)\subseteq\Ker(\rho^*)=\St(n,\,R,\,I)$, as required. \end{proof}
+Since $\pi^*(\iota(F(u, v))) = X(\pi(u),\,0)=1$ and $\pi^*(\iota(S(u,v)) = Y(0,\,\pi(v)) = 1$ we get that $\mathrm{Im}(\iota)\subseteq\Ker(\pi^*)=\St(n,\,R,\,I)$. 
+Thus, we have demonstrated the following result.
+
+\begin{prop} \label{lm:map-iota}
+ For a splitting ideal $I \trianglelefteq R$ and $n\geq 4$ the groups $\St^*(n,\,R,\,I)$ and $\St(n,\,R, I)$ are isomorphic.
+% there exists a well-defined homomorphism $$\iota\colon\St^*(n,\,R,\,I)\rightarrow\St(n,\,R, I) \subseteq \St(n, R)$$ 
+% satisfying the equalities $\iota (F(u,\,v)) = X(u,\,v)$ and $\iota (S(u,\,v)) = Y(u,\,v)$. 
+\end{prop}
+%\begin{proof}
+%We already know that $\iota$ is well-defined. It suffices to check that the image of $\iota$ is contained in $\St(n,\,R,I)$.
+%Denote the canonical projection $R\epi R/I$ by $\rho$.
+%Clearly, the induced group morphism $\rho^*\colon\St(n,\,R)\rightarrow\St(n,\,R/I)$ sends $X(u,\,v)$ to $X(\rho(u),\,\rho(v))$ and $Y(u,\,v)$ to $Y(\rho(u),\,\rho(v))$. 
+%Observe that $\E(n,\,R)\epi\E(n,\,R/I)$ is surjective, therefore for $x\in\E(n,\,R)e_1$ one has $\rho(x)\in\E(n,\,R/I)e_1$. 
+%, as required. \end{proof}
 
@@
 
-At this point we have demonstrated for $n\geq4$ and a splitting ideal $I$ that $\St^*(n,\,R,\,I)$ and $\St(n,\,R,\,I)$ are isomorphic.
-Now we turn to the main result of this section, namely, we construct a map $$T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X],\,XR_a[X]),$$ for $n\geq4$. 
-A local-global principle for Steinberg group and centrality of $\mathrm K_2$ formally follow from existance of this map~\cite[Lem.~15, Lem.~16, proof of Th.~2]{SCh}.
+\section{The local-global principle for $\Kt$.} \label{sec:lgp}
+%At this point we have demonstrated for $n\geq4$ and a splitting ideal $I$ that $\St^*(n,\,R,\,I)$ and $\St(n,\,R,\,I)$ are isomorphic.
+Now we turn to the main result of this paper, namely, we construct the map $$T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X]),\ \text{ for} n\geq4.$$ 
+The local-global principle for the Steinberg group and centrality of $\mathrm K_2$ will formally follow from the existence of this map, see~\cite[Lemmas~15--16, and the proof of Theorem~2]{SCh}.
 
-We work in a more general situation.
+We will prove a somewhat more general result. Let $B$ be a commutative unital ring.
+A $B$-module $M$ is called \emph{$r$-divisible} if for every $m\in M$ there exists $m'\in M$ such that $rm' = m$ (we denote such $m'$ by $\frac{m}{a}$).
+Clearly, $M$ is $a$-divisible if and only if the morphism of principal localization $\lambda_a\colon M \to M_a$ is an isomorphism.
 
-\begin{tm}
-\label{a3map}
-Let $B$ be a ring, $I\trianglelefteq B$, $a\in B$ such that $\forall\,x\in I$ there exists a unique $y\in I$ such that $ya=x$ {\rm(}we denote this $y$ by $\frac xa$, elements $\frac x{a^m}$ are also well defined{\rm)}.
-This requirement is equivalent to say that the principle localisation $\lambda_a\colon I\rightarrow I_a$ of ideal $I$ is an isomorphism.
-Then there exists a map
-$$
-\mathrm T\colon\St(n,\,B_a,\,I)\rightarrow\St(n,\,B)
-$$
-making the diagram
-$$
-\xymatrix{
-\St^*(2n,\,B,\,I)\ar@<-0.0ex>[rr]^{\iota}\ar@<-0.0ex>[d]_{\lambda_{a}^*}&&\St(2n,\,B)\ar@<-0.0ex>[d]^{\lambda_{a}^*}\\
-\St^*(2n,\,B_a,\,I)\ar@<-0.0ex>[rr]_{\iota}\ar@{-->}[rru]_{\mathrm T}&&\St(2n,\,B_a)
-}
-$$
-commutative.
-\end{tm}
+\begin{tm} \label{a3map} Let $B$ be a ring, $a\in B$ and let $I$ be an ideal $B$ that is $a$-divisible.
+Then there exists a map $T\colon\St(n,\,B_a,\,I)\rightarrow\St(n,\,B)$ which makes the following diagram commute.
+$$\xymatrix{ \St^*(2n,\,B,\,I)\ar@<-0.0ex>[rr]^{\iota}\ar@<-0.0ex>[d]_{\lambda_{a}^*}&&\St(2n,\,B)\ar@<-0.0ex>[d]^{\lambda_{a}^*}\\
+             \St^*(2n,\,B_a,\,I)\ar@<-0.0ex>[rr]_{\iota}\ar@{-->}[rru]_{T}&&\St(2n,\,B_a)}$$ \end{tm}
 

### 2016-04-27 paper.tex
Fixed page 7

@@
 \begin{rk} \label{rk:T123'} Notice that from the proof of the above proposition it follows that one could replace the family of relations \eqref{add3}
-in the definition of $\St(n, R, I)$ with the following smaller family \eqref{add3'}.
+in the definition of $\St(n, R, I)$ with the following smaller family:
 \setcounter{equation}{2} \renewcommand{\theequation}{T\arabic{equation}'}
@@
 %At this point we have demonstrated for $n\geq4$ and a splitting ideal $I$ that $\St^*(n,\,R,\,I)$ and $\St(n,\,R,\,I)$ are isomorphic.
-Now we turn to the main result of this paper, namely, we construct the map $$T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X]),\ \text{ for} n\geq4.$$ 
+Now we turn to the main result of this paper, namely, we construct for $n\geq 4$ the map $$T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X]),$$ that fits into the diagram \eqref{eq:diagram}.
 The local-global principle for the Steinberg group and centrality of $\mathrm K_2$ will formally follow from the existence of this map, see~\cite[Lemmas~15--16, and the proof of Theorem~2]{SCh}.
@@
 A $B$-module $M$ is called \emph{$r$-divisible} if for every $m\in M$ there exists $m'\in M$ such that $rm' = m$ (we denote such $m'$ by $\frac{m}{a}$).
-Clearly, $M$ is $a$-divisible if and only if the morphism of principal localization $\lambda_a\colon M \to M_a$ is an isomorphism.
+Clearly, $M$ is $r$-divisible if and only if the morphism of principal localisation $\lambda_r\colon M \to M_r$ is an isomorphism.
 
 \begin{tm} \label{a3map} Let $B$ be a ring, $a\in B$ and let $I$ be an ideal $B$ that is $a$-divisible.
-Then there exists a map $T\colon\St(n,\,B_a,\,I)\rightarrow\St(n,\,B)$ which makes the following diagram commute.
-$$\xymatrix{ \St^*(2n,\,B,\,I)\ar@<-0.0ex>[rr]^{\iota}\ar@<-0.0ex>[d]_{\lambda_{a}^*}&&\St(2n,\,B)\ar@<-0.0ex>[d]^{\lambda_{a}^*}\\
-             \St^*(2n,\,B_a,\,I)\ar@<-0.0ex>[rr]_{\iota}\ar@{-->}[rru]_{T}&&\St(2n,\,B_a)}$$ \end{tm}
+Then for $n\geq 4$ there exists a map $T\colon\St(n,\,B_a,\,I)\rightarrow\St(n,\,B)$ which makes the following diagram commute.
+$$\xymatrix{ \St^*(n,\,B,\,I)\ar@<-0.0ex>[rr]^{\iota}\ar@<-0.0ex>[d]_{\lambda_{a}^*} && \St(n,\,B)\ar@<-0.0ex>[d]^{\lambda_{a}^*}\\
+             \St^*(n,\,B_a,\,I)\ar@<-0.0ex>[rr]_{\iota}\ar@{-->}[rru]_{T}            && \St(n,\,B_a)}$$ \end{tm}
 
-To prove this theorem we need to find some elements ``$X(u,\,v)$'' inside $\St(n,\,B)$ for $u\in\E(n,\,B_a)e_1$, $v\in I$.
-The idea is the following.
-Say $a$ is not a zero divisor, then $ua^m\in B$ for some $m$ and we will construct some element ``$X(ua^m,\,va^{-m})$''.
-One can not garantee that $ua^m\in\E(n,\,B)e_1a^k$, however, the ideal generated by entries of $ua^m$ contains some power of $a$ (this is equivalent to say that $ua^m$ becomes unimodular after the principle localisation in $a$).
-Denote $\mathrm I(u)$ the ideal generated by entries of $u\in R^n$, $\mathrm I(u)=\sum\limits_{k=1}^nu_kR$.
-Then, we need generators parametrised by pairs $(u,\,v)$ with $u^tv=0$, $v\in I$, $a^m\in\mathrm I(u)$ for some $m\in\mathbb N$.
-Such generators are defined in~\cite{Tul}.
+For a vector $u\in R^n$ we denote by $I(u)$ the ideal generated by the entries of $u\in R^n$, i.\,e. $I(u)=\sum\limits_{k=1}^nu_kR$.
+To prove \cref{a3map} we follow the approach of Tulenbaev and construct yet another family of elements $X_{u,v}(a)\in \St(n,\,B)$, $a\in B$ which contains van der Kallen's generators $X(u, v)$ as a subfamily (i.\,e.
+$X_{u,v}(1) = X(u, v)$).
+The key feature of this new family is that the assumption $u \in\Um(n, B)$ is replaced with a weaker condition $a \in I(u)$ (this is equivalent to saying that $u$ becomes unimodular after localisation in $a$).
+%The idea is the following. Say $a$ is not a zero divisor, then $ua^m\in B$ for some $m$ and we will construct some element ``$X(ua^m,\,va^{-m})$''.
+%One can not garantee that $ua^m\in\E(n,\,B)e_1a^k$, however, the ideal generated by entries of $ua^m$ contains some power of $a$ .
+More formally, we have the following definition.
+%Then, we need generators parametrised by pairs $(u,\,v)$ with $u^tv=0$, $v\in I$, $a^m\in\mathrm I(u)$ for some $m\in\mathbb N$. Such generators are defined in~\cite{Tul}.
 
 \begin{df}[Tulenbaev]
-For $u$, $v\in B^n$, $a\in\mathrm I(u)$ and $v_1,\ldots,v_N\in B^n$ such that $u^tv_k=0$ $\forall\,k$,  each $v_k$ has at least two zero coordinates and $\sum_{k=1}^Nv_k=v$ define $X_{u,v}(a)=\prod\limits_{k=1}^Nx(u,\,v_ka)$.
-Tulenbaev shows that factors $x(u,\,v_ka)$ commute~\cite[Lem.~1.1\,e)]{Tul} and that for any other decomposition of $v$ as a sum $v=\sum_{j=1}^Mv'_j$ of vectors orthogonal to $u$ and having two zero coordinates holds $\prod_{k=1}^Nx(u,\,v_ka)=\prod_{j=1}^Mx(u,\,v'_ja)$~\cite[p.~3]{Tul}, i.e., elements $X_{u,v}(a)$ are well-defined.
-Obviously, $\phi(X_{u,v}(a))=t(u,\,va)$.
+Let $u$, $v\in B^n$ be such that $v=\sum_{k=1}^Nv_k$ for some $v_1,\ldots,v_N\in B^n$ such that $u^tv_k=0$ and $v_k$ has at least two zero coordinates for all $k$.
+We call such a decomposition of $v$ a \emph{canonical decomposition}.
+Now for $a\in I(u)$ define $X_{u,v}(a) = \prod\limits_{k=1}^Nx(u,\,v_ka)$. 
 \end{df}
+Tulenbaev shows that the factors $x(u,\,v_ka)$ commute~\cite[Lemma~1.1\,e)]{Tul} and that for any other canonical decomposition $v=\sum_{j=1}^Mv'_j$ one has
+$\prod_{k=1}^Nx(u,\,v_ka)=\prod_{j=1}^Mx(u,\,v'_ja)$, see the discussion after \cite[Lemma~1.1]{Tul}.
+Thus, the elements $X_{u,v}(a)$ are well-defined. Obviously, $\phi(X_{u,v}(a))=t(u,\,va)$.
 
-Observe that Tulenbaev uses different notation for van der Kallen elements. He writes $X_{u,v}$ instead of $X(u,\,v)$ and $X(u,\,v)$ instead of $x(u,\,v)$. We keep van der Kallen's notation.
+Notice that Tulenbaev uses different notation for van der Kallen elements, e.\,g. he writes $X_{u,v}$ instead of $X(u,\,v)$ and $X(u,\,v)$ instead of $x(u,\,v)$. 
+We stick to van der Kallen's notation. \textbf{TODO: I thought we use our own notation?}
 
@@
 \label{xproperties}
-For $u$, $v$, $v'$ and $w\in B^n$, such that $v$ and $v'$ have decomposition as in above definition, $u^tw=0$, $a$, $b\in\mathrm I(u)$, $c\in B$, $g\in\St(n,\,B)$ holds
+For $u$, $v$, $v'$ and $w\in B^n$, such that $v$ and $v'$ possess a canonical decomposition, $u^tw=0$, $a$, $b\in I(u)$, $c\in B$, $g\in\St(n,\,B)$ the following facts are true.
 \begin{enumerate}
-\item
-$X_{u,vc}(a)=X_{u,v}(ca)$,
-\item
-$X_{uc,v}(ca)=X_{u,vc^2}(a)$,
-\item
-$X_{u,v}(a)X_{u,v'}(a)=X_{u,v+v'}(a)$,
-\item
-$g\,X_{u,wb}(a)g\inv=X_{\phi(g)u,\phi(g)^*wb}(a)$.
+\item $X_{u,vc}(a)=X_{u,v}(ca)$,
+\item $X_{uc,v}(ca)=X_{u,vc^2}(a)$,
+\item $X_{u,v}(a)X_{u,v'}(a)=X_{u,v+v'}(a)$,
+\item $g\,X_{u,wb}(a)g\inv=X_{\phi(g)u,\phi(g)^*wb}(a)$.
 \end{enumerate}

### 2016-04-27 paper.tex
Proofread one more page

@@
 %\renewcommand{\theequation}{$\dagger$}
+\setcounter{lm}{1}
 \begin{prop}\label{prop:TulPres}
@@
 Then the following facts are true.
-\begin{lmlist}
+\begin{enumerate}
 \item $\St^*(n,\,R,\,I)$ is generated as an abstract group by the set of elements 
@@
       $$F(u,\,v)^t=S(v,\,u),\quad S(u,\,v)^t=F(v,\,u).$$
-\end{lmlist} \end{lm}
+\end{enumerate} \end{lm}
 
@@
 $$S(u,\,v)=\prod\limits_{k\neq1}S(Ne_k\tilde u_k,\,N^*e_1)=\prod\limits_{k\neq1}F(Ne_k,\,N^*e_1\tilde u_k)$$
-and, thus, obtain $(\mathrm{i})$. Obviously, $(\mathrm{ii})$ follows from $(\mathrm{i})$. 
-To prove $(\mathrm{iii})$ it suffices to show that
+and, thus, obtain $(\mathrm{a})$. Obviously, $(\mathrm{b})$ follows from $(\mathrm{a})$. 
+To prove $(\mathrm{c})$ it suffices to show that
 $$F(u,\,v)S(u',\,v')F(u,\,v)\inv=S(t(u,\,v)u',\,t(u,\,v)^*v').$$
@@
 \end{multline*}
-Finally, $(\mathrm{iv})$ follows from $(\mathrm{iii})$.
+Finally, $(\mathrm{d})$ follows from $(\mathrm{c})$.
 \end{proof}
@@
 Since columns of elementary matrices are unimodular, one can find $w\in R^t$ such that $w^tv=1$.
-It is not hard to check that $u = (w^t\cdot v)\cdot u = \sum_{p<q}u_{pq}$, where $u_{pq} = (u_pw_q - u_qw_p) \cdot (v_qe_p - v_pe_q)\in{}\!R^n$,
+It is not hard to check that \setcounter{equation}{6} \setcounter{lm}{7}
+\begin{equation} u = (w^t\cdot v)\cdot u = \sum_{p<q}u_{pq},\text{ where }u_{pq} = (u_pw_q - u_qw_p) \cdot (v_qe_p - v_pe_q)\in{}\!R^n, \label{eq:canonical}\end{equation}
 therefore $\overline Y(u,\,v)$ is not empty (cf.~\cite[3.1--3.2]{vdK}).
@@
 
-\begin{df}[Tulenbaev]
-Let $u$, $v\in B^n$ be such that $v=\sum_{k=1}^Nv_k$ for some $v_1,\ldots,v_N\in B^n$ such that $u^tv_k=0$ and $v_k$ has at least two zero coordinates for all $k$.
-We call such a decomposition of $v$ a \emph{canonical decomposition}.
-Now for $a\in I(u)$ define $X_{u,v}(a) = \prod\limits_{k=1}^Nx(u,\,v_ka)$. 
+\begin{df}[Tulenbaev] \label{df:TulX}
+For $u \in R^n$ we denote by $D(u)$ the set consisting of all $v\in B^n$ such that $v=\sum_{k=1}^Nv_k$ for some $v_1,\ldots,v_N\in B^n$ and that $u^tv_k=0$ and $v_k$ has at least two zero coordinates for all $k$.
+Now for $a\in I(u)$ and $v \in D(u)$ set $X_{u,v}(a) = \prod\limits_{k=1}^Nx(u,\,v_ka)$. 
 \end{df}
-Tulenbaev shows that the factors $x(u,\,v_ka)$ commute~\cite[Lemma~1.1\,e)]{Tul} and that for any other canonical decomposition $v=\sum_{j=1}^Mv'_j$ one has
-$\prod_{k=1}^Nx(u,\,v_ka)=\prod_{j=1}^Mx(u,\,v'_ja)$, see the discussion after \cite[Lemma~1.1]{Tul}.
+Tulenbaev shows that factors $x(u,\,v_ka)$, $1\leq k\leq N$ commute~\cite[Lemma~1.1\,e)]{Tul} and that for any other decomposition $v=\sum_{j=1}^Mv'_j$ one has
+$\prod_{k=1}^Nx(u,\,v_ka)=\prod_{j=1}^Mx(u,\,v'_ja)$, see the discussion following \cite[Lemma~1.1]{Tul}.
 Thus, the elements $X_{u,v}(a)$ are well-defined. Obviously, $\phi(X_{u,v}(a))=t(u,\,va)$.
@@
 Notice that Tulenbaev uses different notation for van der Kallen elements, e.\,g. he writes $X_{u,v}$ instead of $X(u,\,v)$ and $X(u,\,v)$ instead of $x(u,\,v)$. 
-We stick to van der Kallen's notation. \textbf{TODO: I thought we use our own notation?}
+We stick to van der Kallen's notation.
 
-\begin{lm}
-\label{xproperties}
-For $u$, $v$, $v'$ and $w\in B^n$, such that $v$ and $v'$ possess a canonical decomposition, $u^tw=0$, $a$, $b\in I(u)$, $c\in B$, $g\in\St(n,\,B)$ the following facts are true.
+\begin{lm} \label{xproperties}
+For $u$, $w\in B^n$, $v, v' \in D(u)$ such that $u^tw=0$, for $a$, $b\in I(u)$, $c\in B$, $g\in\St(n,\,B)$ the following facts are true.
 \begin{enumerate}
@@
 \begin{proof}
-The statement of a) is obvious from the definition, b) follows from~\cite[Lem.~1.1\,d)]{Tul}, c) is~\cite[Lem.~1.3\,a)]{Tul}, d) is proven for $n\geq5$ in~\cite[Lem.~1.3\,b)]{Tul} and afterwards Tulenbaev makes a remark that for $n=4$ the statement is also true.
-Indeed, take $z\in B^n$ such that $z^tu=b$ and decompose
-$$
-(z^tu)w=\sum_{i<j}w_{ij},
-$$
-where $w_{ij}=(e_iu_j-e_ju_i)(w_iz_j-w_jz_i)=w_{ji}$.
-Each $w_{ij}$ is orthogonal to $u$ and has two zero coordinates ($n\geq4$).
-Thus, $X_{u,wb}(a)=\prod_{i<j}x(u,\,w_{ij}a)$.
-It is enough to prove the statement of d) for $g=x_{hk}(r)$.
-If $h\neq i,j$ or $\{h,k\}=\{i,j\}$, $\phi(g)^*w_{ij}a$ still has two zero coordinates.
-Consider the case $j=h$, $i\neq k$.
-With~\cite[3.12]{vdK} we get $g\,x(u,\,w_{ij}a)g\inv=x(\phi(g)u,\,\phi(g)^*w_{ij}a)$.
-Denote $u_{ij}=e_iu_j-e_ju_i$ and $c_{ij}=w_iz_j-w_jz_i$.
-Using
-$$
-\phi(g)^*u_{ij}=(\phi(g)u)_{ij}+(\phi(g)u)_{ki}\,r
-$$
-and~\cite[3.11]{vdK} one obtains
-$$
-x(\phi(g)u,\,\phi(g)^*w_{ij}a)=x(\phi(g)u,\,(\phi(g)u)_{ij}c_{ij}a)\cdot x(\phi(g)u,\,(\phi(g)u)_{ki}\,rc_{ij}a).
-$$
-Decomposing in such a way each $\phi(g)^*w_{ij}a$ which does not have two zero coordinates we finally get a product from the definition of $X_{\phi(g)u,\phi(g)^*wb}(a)$.
-\end{proof}
+The statement of $(\mathrm a)$ is obvious from the definition, $(\mathrm b)$ follows from~\cite[Lemma~1.1\,d)]{Tul}, $(\mathrm c)$ is exactly the statement of~\cite[Lemma~1.3\,a)]{Tul}.
 
-Siilarly, one can define ``transposed'' version of Tulenbaev's elements $X_{u,v}(a)$.
+The assertion of $(\mathrm d)$ is proven in~\cite[Lemma~1.3\,b)]{Tul} under the assumption $n\geq5$. 
+Afterwards Tulenbaev remarks that the assertion remains true for $n=4$. % We will give a detailed proof of this fact.
+Indeed, take $z\in B^n$ such that $z^tu=b$ and write the canonical decomposition, cf. \eqref{eq:canonical}:
+$$(z^tu)w=\sum_{i<j}c_{ij} u_{ij}, \text{ where } u_{ij}=u_je_i-u_ie_j,\text{ and }c_{ij}=w_iz_j-w_jz_i.$$
+Each $c_{ij}u_{ij}$ is orthogonal to $u$ and because of the assumption $n\geq4$ has at least two zero coordinates.
+Thus, $X_{u,wb}(a)=\prod_{i<j}x(u,\,a c_{ij} u_{ij})$. 
+It is enough to prove the assertion of $(\mathrm d)$ in the special case $g=x_{hk}(r)$.
+If $h\neq i,j$ or $\{h,k\}=\{i,j\}$ the vector $\phi(g)^*ac_{ij}u_{ij}$ still has two zero coordinates.
 
-\begin{df}
-For $u$, $v\in B^n$, $a\in\mathrm I(v)$, and $u_1,\ldots,u_N\in B^n$ such that $u_k^tv=0$, each $u_k$ has at least two zero coordinates and $u=\sum_{k=1}^Nu_k$ define $Y_{u,v}(a)=\prod\limits_{k=1}^Nx(u_ka,\,v)$.
-Repeating Tulenbaev's argumentation~\cite[p.~3]{Tul} one can show that the definition does not depend on the order of factors and on choice of decomposition of $u$.
+Now consider the case $j=h$, $i\neq k$. 
+By~\cite[3.12]{vdK} one has $$g\,x(u,\,ac_{ij}u_{ij})g\inv=x(\phi(g)u,\,ac_{ij}\,\phi(g)^*u_{ij}).$$
+Set $u' = \phi(g)u$, since
+$\phi(g)^*u_{ij} = t_{kj}(-r) \cdot u_{ij} = u_je_i - u_ie_j + ru_i e_k =u'_{ij}+r\,u'_{ki},$ 
+we obtain from~\cite[3.11]{vdK} that
+$$x(\phi(g)u,\,ac_{ij}\,\phi(g)^* u_{ij})=x\left(u',\,c_{ij}a\,u'_{ij}\right)\cdot x\left(u',\,rc_{ij}a\,u'_{ki}\right).$$
+Decomposing in this fashion each factor $g\,x(u,\,ac_{ij}u_{ij})g$ for which $\phi(g)^*ac_{ij}\, u_{ij}$ does not have two zero coordinates, 
+ we arrive at a product satisfying the requirements of the definition of $X_{\phi(g)u,\phi(g)^*wb}(a)$. \end{proof}
+
+We will also need the ``transposed'' analogue of Tulenbaev's elements $X_{u,v}(a)$.
+\begin{df} \label{df:TulY}
+Let $v\in B^n$, $a\in I(v)$, and $u \in D(v)$, i.\,e. $u = \sum\limits_{i=1}^M u_i$ for some $u_k$ having two zero components such that $v^tu_k=0$.
+Set $Y_{u,v}(a)=\prod_{k=1}^Mx(u_ka,\,v)$. 
+Similarly to \cref{df:TulX} this definition is correct and does not depend neither on the order of factors nor on the choice of decomposition for $u$.
 \end{df}
 
-Now, one can repeat van der Kallen's and Tulenbaev's argumentation to prove transposed version of Lemma~\ref{xproperties}. We leave this to the reader.
-
+One can repeat van der Kallen's and Tulenbaev's arguments and prove the following transposed version of Lemma~\ref{xproperties}.
+We leave the proof of this lemma to the reader.
 \begin{lm}
@@
 \begin{enumerate}
-\item
-$Y_{uc,v}(a)=Y_{u,v}(ca)$,
-\item
-$Y_{u,vc}(ca)=Y_{uc^2,v}(a)$,
-\item
-$Y_{u,v}(a)X_{u',v}(a)=Y_{u+u',v}(a)$,
-\item
-$g\,Y_{wb,v}(a)g\inv=Y_{\phi(g)wb,\phi(g)^*v}(a)$.
+\item $Y_{uc,v}(a)=Y_{u,v}(ca)$,
+\item $Y_{u,vc}(ca)=Y_{uc^2,v}(a)$,
+\item $Y_{u,v}(a)X_{u',v}(a)=Y_{u+u',v}(a)$,
+\item $g\,Y_{wb,v}(a)g\inv=Y_{\phi(g)wb,\phi(g)^*v}(a)$.
 \end{enumerate}
@@
 
-Finally, it only remains to show that for a ``good'' pair $(u,\,v)$ elements $X$ and $Y$ coincide.
+Finally, it remains to show that for a ``good'' pair $(u,\,v)$ the elements $X$ and $Y$ coincide.
 
@@
 \label{x=y}
-Consider $w$, $u$, $z$, $v$, $x$, $y\in B^n$ $a$, $r\in B$ such that $w^tu=a$, $z^tv=a$, $x^ty=a$ and pairs $(w,\,u)$, $(z,\,v)$ and $(x,\,y)$ are mutually orthogonal. Then 
-$$
-X_{u,v}(ra^3)=Y_{u,v}(ra^3).
-$$
+Let $w$, $u$, $z$, $v$, $x$, $y\in B^n$ be vectors and $a$, $r\in B$ be scalars such that $w^tu=a$, $z^tv=a$, $x^ty=a$.
+Suppose that the pairs $(w,\,u)$, $(z,\,v)$ and $(x,\,y)$ are mutually orthogonal. Then $$ X_{u,v}(ra^3)=Y_{u,v}(ra^3).$$
 \end{lm}
-
 \begin{proof}
-On one hand,
 \begin{multline*}
-[Y_{x,-v}(ra),\,X_{u,y}(a)]=X_{t(x,-vra)u,t(x,-vra)^*y}(a)X_{u,-y}(a)=\\
-=X_{u,y+vra^2}(a)X_{u,-y}(a)=X_{u,v}(ra^3).
-\end{multline*}
-On the other,
-\begin{multline*}
-[Y_{x,-v}(ra),\,X_{u,y}(a)]=Y_{x,-v}(ra)Y_{t(u,ya)x,t(u,ya)^*v}(ra)=\\
-=Y_{-x,v}(ra)Y_{x+ua^2,v}(ra)=Y_{u,v}(ra^3).
+ X_{u,v}(ra^3) = X_{u,y+vra^2}(a)\, X_{u,-y}(a) = X_{t(x,-vra)u,t(x,-vra)^*y}(a)X_{u,-y}(a) = [Y_{x,-v}(ra),\,X_{u,y}(a)] = \\
+ = Y_{x,-v}(ra)\, Y_{t(u,ya)x,t(u,ya)^*v}(ra)= Y_{-x,v}(ra)\, Y_{x+ua^2,v}(ra)=Y_{u,v}(ra^3).\qedhere
 \end{multline*}
@@
 
-Now, we are ready to construct a map 
-$
-\mathrm T\colon\St(n,\,B_a,\,I)\rightarrow\St(n,\,B).
-$
+Now, we are ready to construct the desired map $T\colon\St(n,\,B_a,\,I)\rightarrow\St(n,\,B).$
 

### 2016-04-29 paper.tex
Finished proofreading

@@
 In the definition of the semidirect product the group $\St(n, R/I)$ acts on $\St(n, R, I)$ by conjugation via the splitting map, i.\,e.
-${}^g X(u,\,v) = X(\phi(s(g))u, \phi(s(g))^*v)$ for $g \in \St(n, R/I)$.
+${}^g X(u,\,v) = X(\phi(\sigma(g))u, \phi(\sigma(g))^*v)$ for $g \in \St(n, R/I)$.
 
@@
 It is not hard to check that \setcounter{equation}{6} \setcounter{lm}{7}
-\begin{equation} u = (w^t\cdot v)\cdot u = \sum_{p<q}u_{pq},\text{ where }u_{pq} = (u_pw_q - u_qw_p) \cdot (v_qe_p - v_pe_q)\in{}\!R^n, \label{eq:canonical}\end{equation}
+\begin{equation} (w^t\cdot v)\cdot u = \sum_{p<q}u_{pq},\text{ where }u_{pq} = (u_pw_q - u_qw_p) \cdot (v_qe_p - v_pe_q)\in{}\!R^n, \label{eq:canonical}\end{equation}
 therefore $\overline Y(u,\,v)$ is not empty (cf.~\cite[3.1--3.2]{vdK}).
@@
 We will prove a somewhat more general result. Let $B$ be a commutative unital ring.
-A $B$-module $M$ is called \emph{$r$-divisible} if for every $m\in M$ there exists $m'\in M$ such that $rm' = m$ (we denote such $m'$ by $\frac{m}{a}$).
-Clearly, $M$ is $r$-divisible if and only if the morphism of principal localisation $\lambda_r\colon M \to M_r$ is an isomorphism.
+A $B$-module $M$ is called \emph{uniquely $r$-divisible} if for every $m\in M$ there exists a sole $m'\in M$ such that $rm' = m$ (we denote such $m'$ by $\frac{m}{a}$).
+Clearly, $M$ is uniquely $r$-divisible if and only if the morphism of principal localisation $\lambda_r\colon M \to M_r$ is an isomorphism.
 
-\begin{tm} \label{a3map} Let $B$ be a ring, $a\in B$ and let $I$ be an ideal $B$ that is $a$-divisible.
+\begin{tm} \label{a3map} Let $B$ be a ring, $a\in B$ and let $I$ be an ideal $B$ that is uniquely $a$-divisible.
 Then for $n\geq 4$ there exists a map $T\colon\St(n,\,B_a,\,I)\rightarrow\St(n,\,B)$ which makes the following diagram commute.
-$$\xymatrix{ \St^*(n,\,B,\,I)\ar@<-0.0ex>[rr]^{\iota}\ar@<-0.0ex>[d]_{\lambda_{a}^*} && \St(n,\,B)\ar@<-0.0ex>[d]^{\lambda_{a}^*}\\
-             \St^*(n,\,B_a,\,I)\ar@<-0.0ex>[rr]_{\iota}\ar@{-->}[rru]_{T}            && \St(n,\,B_a)}$$ \end{tm}
+\begin{equation} \xymatrix{ \St^*(n,\,B,\,I)\ar@<-0.0ex>[rr]^{\iota}\ar@<-0.0ex>[d]_{\lambda_{a}^*} && \St(n,\,B)\ar@<-0.0ex>[d]^{\lambda_{a}^*}\\
+                            \St^*(n,\,B_a,\,I)\ar@<-0.0ex>[rr]_{\iota}\ar@{-->}[rru]_{T}            && \St(n,\,B_a)} \label{eq:a3diag} \end{equation} \end{tm}
 
@@
 $X_{u,v}(1) = X(u, v)$).
-The key feature of this new family is that the assumption $u \in\Um(n, B)$ is replaced with a weaker condition $a \in I(u)$ (this is equivalent to saying that $u$ becomes unimodular after localisation in $a$).
+The key feature of this definition is that the assumption $u \in\Um(n, B)$ is replaced with a weaker condition $a \in I(u)$ (this is equivalent to saying that $u$ becomes unimodular after localisation in $a$).
 %The idea is the following. Say $a$ is not a zero divisor, then $ua^m\in B$ for some $m$ and we will construct some element ``$X(ua^m,\,va^{-m})$''.
 %One can not garantee that $ua^m\in\E(n,\,B)e_1a^k$, however, the ideal generated by entries of $ua^m$ contains some power of $a$ .
-More formally, we have the following definition.
+%More formally, we have the following definition.
 %Then, we need generators parametrised by pairs $(u,\,v)$ with $u^tv=0$, $v\in I$, $a^m\in\mathrm I(u)$ for some $m\in\mathbb N$. Such generators are defined in~\cite{Tul}.
 
-\begin{df}[Tulenbaev] \label{df:TulX}
-For $u \in R^n$ we denote by $D(u)$ the set consisting of all $v\in B^n$ such that $v=\sum_{k=1}^Nv_k$ for some $v_1,\ldots,v_N\in B^n$ and that $u^tv_k=0$ and $v_k$ has at least two zero coordinates for all $k$.
+\setcounter{df}{1}
+\begin{df} \label{df:TulX}
+For $u \in R^n$ we denote by $D(u)$ the set consisting of all $v\in B^n$ decomposing into a sum $v=\sum_{k=1}^Nv_k$ where $v_1,\ldots,v_N\in B^n$ are such that $u^tv_k=0$ and each $v_k$ has at least two zero coordinates.
 Now for $a\in I(u)$ and $v \in D(u)$ set $X_{u,v}(a) = \prod\limits_{k=1}^Nx(u,\,v_ka)$.
@@
 
+\begin{rk} \label{rk:ID}
+From the canonical decomposition~\eqref{eq:canonical} it follows that $bv\in D(u)$ for any $b\in I(u)$ and $v$ such that $v^tu=0$.
+In particular, if $I$ is uniquely $a$-divisible and $a^k\in I(u)$, then every $v\in I^n$ satisfying $v^tu=0$ is contained in $D(u)$.
+\end{rk}
+
 Notice that Tulenbaev uses different notation for van der Kallen elements, e.\,g. he writes $X_{u,v}$ instead of $X(u,\,v)$ and $X(u,\,v)$ instead of $x(u,\,v)$. 
@@
 \begin{lm} \label{xproperties}
-For $u$, $w\in B^n$, $v, v' \in D(u)$ such that $u^tw=0$, for $a$, $b\in I(u)$, $c\in B$, $g\in\St(n,\,B)$ the following facts are true.
+For $u$, $w\in B^n$, $v, v' \in D(u)$ such that $u^tw=0$, for $a$, $b\in I(u)$, $c\in B$, $g\in\St(n,\,B)$ the following are true:
 \begin{enumerate}
@@
 The assertion of $(\mathrm d)$ is proven in~\cite[Lemma~1.3\,b)]{Tul} under the assumption $n\geq5$. 
-Afterwards Tulenbaev remarks that the assertion remains true for $n=4$. % We will give a detailed proof of this fact.
-Indeed, take $z\in B^n$ such that $z^tu=b$ and write the canonical decomposition, cf. \eqref{eq:canonical}:
+Afterwards Tulenbaev remarks that the assertion remains true for $n=4$. We will give a detailed proof of this fact.
+Indeed, take $z\in B^n$ such that $z^tu=b$ and write the canonical decomposition \eqref{eq:canonical}:
 $$(z^tu)w=\sum_{i<j}c_{ij} u_{ij}, \text{ where } u_{ij}=u_je_i-u_ie_j,\text{ and }c_{ij}=w_iz_j-w_jz_i.$$
-Each $c_{ij}u_{ij}$ is orthogonal to $u$ and because of the assumption $n\geq4$ has at least two zero coordinates.
+Each $c_{ij}u_{ij}$ is orthogonal to $u$ and, because of the assumption $n\geq4$, has at least two zero coordinates.
 Thus, $X_{u,wb}(a)=\prod_{i<j}x(u,\,a c_{ij} u_{ij})$. 
@@
 $$x(\phi(g)u,\,ac_{ij}\,\phi(g)^* u_{ij})=x\left(u',\,c_{ij}a\,u'_{ij}\right)\cdot x\left(u',\,rc_{ij}a\,u'_{ki}\right).$$
-Decomposing in this fashion each factor $g\,x(u,\,ac_{ij}u_{ij})g$ for which $\phi(g)^*ac_{ij}\, u_{ij}$ does not have two zero coordinates, 
+Decomposing in this fashion each factor $g\,x(u,\,ac_{ij}u_{ij})g^{-1}$ for which $\phi(g)^*ac_{ij}\, u_{ij}$ does not have two zero coordinates, 
  we arrive at a product satisfying the requirements of the definition of $X_{\phi(g)u,\phi(g)^*wb}(a)$. \end{proof}
@@
 Set $Y_{u,v}(a)=\prod_{k=1}^Mx(u_ka,\,v)$. 
-Similarly to \cref{df:TulX} this definition is correct and does not depend neither on the order of factors nor on the choice of decomposition for $u$.
+Similarly to \cref{df:TulX} this definition does not depend neither on the order of factors nor on the choice of decomposition for $u$.
 \end{df}
@@
 \label{yproperties}
-For $u$, $u'$, $w$ and $v\in B^n$, such that $u$ and $u'$ have decomposition as in above definition, $w^tv=0$, $a$, $b\in\mathrm I(v)$, $c\in B$, $g\in\St(n,\,B)$ holds
+For $u$, $u'$, $w$ and $v\in B^n$, such that $u$ and $u'$ have decomposition as in above definition, $w^tv=0$, $a$, $b\in I(v)$, $c\in B$, $g\in\St(n,\,B)$ holds
 \begin{enumerate}
@@
 Finally, it remains to show that for a ``good'' pair $(u,\,v)$ the elements $X$ and $Y$ coincide.
-
-\begin{lm}
-\label{x=y}
-Let $w$, $u$, $z$, $v$, $x$, $y\in B^n$ be vectors and $a$, $r\in B$ be scalars such that $w^tu=a$, $z^tv=a$, $x^ty=a$.
-Suppose that the pairs $(w,\,u)$, $(z,\,v)$ and $(x,\,y)$ are mutually orthogonal. Then $$ X_{u,v}(ra^3)=Y_{u,v}(ra^3).$$
+\begin{lm}\label{x=y}
+Let $u$, $v$, $x$, $y$ be elements of $B^n$ and $b,r\in B$ be such that $u^t v = 0$, $x^ty=b$, $x^tv=0$, $u^ty=0$ and $b\in I(u)\cap I(v)$.
+Then one has $X_{u,b^4rv}(b)=Y_{b^4ru,v}(b).$
 \end{lm}
 \begin{proof}
-\begin{multline*}
- X_{u,v}(ra^3) = X_{u,y+vra^2}(a)\, X_{u,-y}(a) = X_{t(x,-vra)u,t(x,-vra)^*y}(a)X_{u,-y}(a) = [Y_{x,-v}(ra),\,X_{u,y}(a)] = \\
- = Y_{x,-v}(ra)\, Y_{t(u,ya)x,t(u,ya)^*v}(ra)= Y_{-x,v}(ra)\, Y_{x+ua^2,v}(ra)=Y_{u,v}(ra^3).\qedhere
-\end{multline*}
+Compute $g=[Y_{-arx,v}(b),\,X_{u,ay}(b)]$ in two different ways using Lemmas~\ref{xproperties}~and~\ref{yproperties}:
+$$ g = X_{t(b^2rx,-v)u,\,t(b^2rx,-v)^*yb}(b)X_{u,-yb}(b) = X_{u,\,by+b^4rv}(b)\, X_{u,-by}(b) = X_{u,b^4rv}(b),$$
+$$ g = Y_{-brx,v}(b) Y_{t(u,b^2y)arx,\,t(u,b^2y)^*v}(b)= Y_{-brx,v}(b)\, Y_{brx+b^4ru,\,v}(b)=Y_{b^4ru,v}(b).\qedhere$$
 \end{proof}
@@
 \begin{proof}[Proof of Theorem~\ref{a3map}]
-For $u=Me_1$, $M\in\E(n,\,B_a)$, $v\in I^n$, $u^tv=0$ denote $w=M^*e_1$ (then $wu=1$) and choose $m\in\mathbb N$ such that some $\tilde w$, $\tilde u\in B^n$ localise to $wa^m$ and $ua^m$, $\tilde u^tv=0$ and $\tilde w^t\tilde u=a^{2m}$.
-Now set $\mathrm T(F(u,\,v))=X_{\tilde u,v/a^{3m}}(a^{2m})$.
-Lemma~\ref{xproperties}\,a) and b) garantees that this definition does not depend on the choice of $m$ and the lifts $\tilde u$ and $\tilde w$.
-Similarly, set $\mathrm T(S(u,\,v))=Y_{u/a^{3m},\tilde v}(a^{2m})$.
-These elements satisfy R1--R3 by Lemmas~\ref{xproperties} and~\ref{yproperties}.
-For $u=Me_1$, $v=M^*e_2$, $M\in\E(n,\,B_a)$ consider $w=M^*e_1$, $z=Me_2$, $x=Me_3$ and $y=M^*e_3$.
-Then, multiply these element on appropriate power of $a$, take their lifts to $B$ and apply Lemma~\ref{x=y} to get R4.
-So that, the map $\mathrm T$ is well-defined.
+Consider $u=Me_1$, $M\in\E(n,\,B_a)$ and $v\in I^n$ such that $u^tv=0$.
+Set $w=M^*e_1$. Since $w^tu=1$ there exist vectors $\tilde w$, $\tilde u\in B^n$ and a natural number $m$ such that 
+$$ \lambda_a(\tilde{w})=wa^m,\ \lambda_a(\tilde{u})=ua^m\text{ and moreover }\tilde u^tv=0\text{ and }\tilde w^t\tilde u=a^{2m}.$$
+It is clear that $a^{2m}\in I(\tilde u)$, moreover by~\cref{rk:ID} we have $v/a^{3m} \in D(\tilde u)$, therefore we are allowed to set $T(F(u,\,v))=X_{\tilde u,v/a^{3m}}(a^{2m})$.
 
-Commutativity of the diagram follows directly from the definitions of elements $X(u,\,v)$, $Y(u,\,v)$ and $X_{u,v}(a)$, $Y_{u,v}(a)$ and the possibility to redistribute the powers of $a$ after localisation.
-\end{proof}
+The first two assertions of \cref{xproperties} guarantee that this definition does not depend on the choice of $m$ and the liftings $\tilde u$ and $\tilde w$.
+Similarly, we can define $T(S(u,\,v))=Y_{u/a^{3m},\tilde v}(a^{2m})$.
+In view of Lemmas~\ref{xproperties}~and~\ref{yproperties} the map $T$ preserves relations \eqref{add4}--\eqref{conj3}.
+
+It remains to check for $u = Me_1$, $v=M^*e_2$ and $c\in I$ that 
+\begin{equation}T(F(u, bv)) = X_{\tilde u,c/a^{4m}\,\tilde v}(a^{2m}) = Y_{c/a^{4m}\, \tilde u,\tilde v}(a^{2m}) = T(S(ub, v)). \label{eq:last}\end{equation}
+Here $\tilde u, \tilde v \in B^n$ are liftings of $u$ and $v$ such that $\lambda_a(\tilde u)=a^m u$, $\lambda_a(\tilde v)=a^m v$ and $\tilde u^t \tilde v = 0$.
+We can also assume that $m$ is so large that $a^{2m}\in I(\tilde{u})\cap I(\tilde{v})$ and there exist $\tilde{x}$, $\tilde{y}$ such that the following equations hold:
+$$\lambda_a(\tilde{x})=a^mMe_3,\ \lambda_a(\tilde{y})=a^mM^*e_3\text{ and }\tilde{x}^t\tilde{y}=a^{2m},\ \tilde{x}^t\tilde{v} = 0,\ \tilde{u}^t\tilde{y} =0.$$
+To obtain~\eqref{eq:last} it remains to apply \cref{x=y} taking $b=a^{2m}$, $r=c/a^{12m}$.
+Thus, the map $T$ is well-defined.
+
+Commutativity of the diagram~\eqref{eq:a3diag} follows directly from the definitions of elements $X(u,\,v)$, $Y(u,\,v)$ and $X_{u,v}(a)$, $Y_{u,v}(a)$. \end{proof}
 

### 2016-04-29 paper.tex
Minor tweaks in intro

@@
 
-\title{On centrality of even orthogonal $\Kt$}
+\title{On centrality of orthogonal $\Kt$}
 \keywords {Steinberg groups, $K_2$-functor. {\em Mathematical Subject Classification (2010):} 19C09}
@@
 
-Recall that for each reduced root system $\Phi$ and a commutative ring $R$ one can associate a split simple group $\GG(\Phi, R)$ called the \emph{Chevalley group}.
+Recall that to each reduced root system $\Phi$ and a commutative ring $R$ one can associate a split simple group $\GG(\Phi, R)$ called the \emph{Chevalley group}.
 For $\Phi$ of rank $\geq 2$ the abstract group $\GG(\Phi, R)$ contains a large normal subgroup $\E(\Phi, R)$ generated by the elementary root unipotents $t_\alpha(\xi)$, $\xi\in R$, $\alpha\in \Phi$.
-The quotient group functor $\Ko(\Phi, R)=\GG(\Phi, R)/\E(\Phi, R)$ is called the \emph{unstable $\Ko$-functor}.
-This functor shares many properties with its stable counterpart $\mathrm{SK}_1(R) = \lim\limits_{l\to\infty}\Ko(\rA_\ell, R)$ which, in turn, is an essential direct summand of $\Ko(R)$.
+The quotient group $\Ko(\Phi, R)=\GG(\Phi, R)/\E(\Phi, R)$ is called the \emph{unstable $\Ko$-group}.
+This group shares many properties with its stable counterpart $\mathrm{SK}_1(R) = \lim\limits_{l\to\infty}\Ko(\rA_\ell, R)$ which, in turn, is an essential direct summand of $\Ko(R)$.
 
@@
 The special case $\Phi=\rA_\ell$, $\ell\geq 4$ of \cref{tm:lg-principle} was demonstrated for the first time by Tulenbaev, see~\cite[Theorem~2.1]{Tul},
-while similar assertions for $\Phi=\rC_\ell$, $\ell\geq 3$ and $\Phi=\rE_\ell$, $\ell=6,7,8$ have been established in \cite{Lav2} and \cite{SCh}, respectively.
+while cases $\Phi=\rC_\ell$, $\ell\geq 3$ and $\Phi=\rE_\ell$, $\ell=6,7,8$ have been analyzed in \cite{Lav2} and \cite{SCh}, respectively.
 The special cases $\Phi=\rA_3$ and $\Phi=\rD_\ell$, $\ell\geq 4$ of \cref{tm:lg-principle} are new and have not been known before.
 
-There are known counterexamples to centrality of $\Kt$ in the rank $2$ case (see~\cite{W}).
-This shows that the assumption on the rank of $\Phi$ in \cref{tm:lg-principle} is strict.
+There are known counterexamples to centrality of $\Kt$ in rank $2$ (see~\cite{W}).
+This shows that our assumption on the rank of $\Phi$ in \cref{tm:lg-principle} is strict.
 
@@
 
-Our proof of \cref{tm:lg-principle} follows the same lines as in \cite[Theorem~1]{SCh}.
-More concretely, using the same patching technique as in \cite{SCh} we reduce the problem to the case $\Phi=\rA_3$.
-Then, we formulate and prove a new presentation of the linear group $\St(4, R)$ and then utilize it to reprove 
-Tulenbaev's key lemma (cf. \cite[Lemma~2.3]{Tul}) in the rank $3$ case.
+Our proof of \cref{tm:lg-principle} is similar to that of \cite[Theorem~1]{SCh}.
+Using the same patching technique we reduce the problem to the case $\Phi=\rA_3$.
+Then, using a new presentation of the relative Steinberg group $\St(4, R, I)$ we reprove Tulenbaev's key lemma (cf. \cite[Lemma~2.3]{Tul}) in the rank $3$ case.
 
 The rest of the paper is organised as follows. 
-In \cref{sec:yap} we formulate ``yet another presentation'' for the rank $3$ Steinberg groups.
+In \cref{sec:yap} we describe a new symmetric presentation for the relative Steinberg group of rank $3$.
+This presentation is then used in~\cref{sec:lgp} to establish the particular case $\Phi=\rA_3$ of \cref{tm:lg-principle}.
 %It mimics the standart vector representation of $\SL(n,\,R)$, therefore in the first section we use representations and corresponding vector notation. 
-Finally, in \cref{sec:patching} we prove our main results.
+Finally, in \cref{sec:patching} we derive our principal results from this special case and the amalgamation theorem for relative Steinberg groups from~\cite{SCh}.
 %There we switch to the root notation.
@@
 
-\section{Patching Tulenbaev maps}\label{sec:patching}
+\section{Patching Tulenbaev maps (to be written)}\label{sec:patching}
 
-The next section is devoted to the proof of Theorem~\ref{a3map} for Steinberg groups corresponding to an arbitrary simply-laced root system of rank $l\geq3$.
-To do so, we will ``glue'' maps $T$ constructed in the present section for systems of type $\mathrm A_3$.
-All main results of the present paper follow from the existence of such a map.
+The next section is devoted to the proof of Theorems~\ref{tm:centrality}--\ref{tm:lg-principle} for Steinberg groups corresponding to 
+arbitrary simply-laced root system of rank $l\geq3$.
+To do so, we glue maps $T$ constructed in the previous section following the approach of~\cite{SCh}.
 

### 2016-04-30 paper.tex
Minor fixes
Fixed many bugs found by Andrei

@@
 \section*{Inroduction}
-The main goal of this paper is to establish the local-global principle and centrality of orthogonal $\Kt$ for arbitrary commutative ring $R$.
+The main goal of the present paper is to establish a local-global principle and centrality of orthogonal $\Kt$ for arbitrary commutative ring $R$.
 
-Recall that to each reduced root system $\Phi$ and a commutative ring $R$ one can associate a split simple group $\GG(\Phi, R)$ called the \emph{Chevalley group}.
+Recall that to each reduced root system $\Phi$ and a commutative ring $R$ one can associate a split simple group $\GG(\Phi, R)$ called a \emph{Chevalley group}.
 For $\Phi$ of rank $\geq 2$ the abstract group $\GG(\Phi, R)$ contains a large normal subgroup $\E(\Phi, R)$ generated by the elementary root unipotents $t_\alpha(\xi)$, $\xi\in R$, $\alpha\in \Phi$.
-The quotient group $\Ko(\Phi, R)=\GG(\Phi, R)/\E(\Phi, R)$ is called the \emph{unstable $\Ko$-group}.
-This group shares many properties with its stable counterpart $\mathrm{SK}_1(R) = \lim\limits_{l\to\infty}\Ko(\rA_\ell, R)$ which, in turn, is an essential direct summand of $\Ko(R)$.
+The quotient group $\Ko(\Phi, R)=\GG(\Phi, R)/\E(\Phi, R)$ is called the \emph{unstable $\Ko$-group}
+This group shares many properties with its stable counterpart $\mathrm{SK}_1(R) = \lim\limits_{l\to\infty}\Ko(\rA_\ell, R)$, which, in turn,
+is a direct summand of the $\Ko$-group, i.\,e. $\Ko(R) = \mathrm{SK}_1(R) \oplus R^*$.
 
@@
 Then an element $g\in\St(\Phi,\,R[X])$ satisfying $g(0)=1\in\St(\Phi,\,R)$ is trivial in $\St(\Phi,\,R[X])$
-if and only if the elements $g_M\in\St(\Phi,\,R_M[X])$ are trivial for all maximal ideals $M\triangleleft R$. \end{tm}
+if and only if the images $g_M\in\St(\Phi,\,R_M[X])$ of $g$ under localisation morphisms $R\to R_M$ are trivial for all maximal ideals $M\trianglelefteq R$. \end{tm}
 
@@
 This presentation clearly implies that $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ is a central extension.
-Notice that our notation for the generators of $\St(n, R)$ slightly differs from that of~\cite{vdK}, e.\,g. we parametrize elements $X(u, v)$ with two columns
-rather than with one column and one row. Our generator $X(u,v)$ corresponds to van der Kallen's generator $(u, v^t)$.
+%Our notation for the generators of $\St(n, R)$ differs from van der Kallen's, e.\,g.
+Notice that we parametrize elements $X(u, v)$ with two columns rather than with one column and one row as it is done in~\cite{vdK}.
+Our generator $X(u,v)$ corresponds to van der Kallen's generator $(u, v^t)$.
 
@@
 
-For a general $I$ the relative Steinberg group $\St(\Phi, R, I)$ is no more a subgroup of $\St(\Phi, R)$ but rather is its central extension.
-For the purposes of the present text it suffices to consider only relative Steinberg groups corresponding to splitting ideals $I$.
+For a general $I$ the relative Steinberg group $\St(\Phi, R, I)$ is no more a subgroup of $\St(\Phi, R)$ and should be defined as a central extension of the above kernel.
+For the purposes of the present text it suffices to consider only relative Steinberg groups corresponding to splitting ideals.
 For more information regarding the general case we refer the reader to \cite[Section~3]{SCh}.
@@
 \numberwithin{equation}{section}
-\begin{equation} \xymatrix{\St(n,\,R\ltimes XR_a[X],\,XR_a[X]) \ar@{^{(}->}[r] \ar[d] & \St(n, R \ltimes XR_a[X]) \ar[d]_-{\lambda_a^*} \\
+\begin{equation} \xymatrix{\St(n,\,R\ltimes XR_a[X],\,XR_a[X]) \ar@{^{(}->}[r] \ar[d]_-{\lambda_a^*} & \St(n, R \ltimes XR_a[X]) \ar[d]_-{\lambda_a^*} \\
              \St(n,\,R_a[X],\,XR_a[X]) \ar@{-->}[ru]_-{T} \ar@{^{(}->}[r] & \St(n, R_a[X])} \label{eq:diagram} \end{equation}
-Here $n\geq5$, $a$ is arbitrary nonnilpotent element of $R$ and $\lambda_a^*$ is the morphism induced by the morphism $\lambda_a\colon R \to R_a$ of principal localisation at $a$.
+Here $n\geq5$, $a$ is arbitrary non-nilpotent element of $R$ and $\lambda_a^*$ is the morphism induced by the morphism $\lambda_a\colon R \to R_a$ of principal localisation (i.\,e.
+localisation by the powers of $a$).
 Notice that $XR_a[X]$ is a splitting ideal for both $R_a[X]$ and $R \ltimes XR_a[X]$.
@@
 
-To generalise Tulenbaev's results for $n=4$ we will use a more ``symmetric`` presentation with two types of generators: 
-$F(u,\,v)$ with $u$ ''good`` and $v$ arbitrary and $S(u,\,v)$ with $u$ arbitrary and $v$ ''good``.
+To generalise Tulenbaev's results for $n=4$ we use a more symmetric presentation with two types of generators: 
+$F(u,\,v)$ with $u$ good and $v$ arbitrary and $S(u,\,v)$ with $u$ arbitrary and $v$ good.
 The generators $F(u,\,v)$ will be additive in the second component, while $S(u,\,v)$ will be additive in the first one.
-When $u$ and $v$ are both ''good`` we require these two generators to coincide.
-More formally, we have the following presentation.
+When $u$ and $v$ are both good we require that these two generators coincide.
+More formally, we make the following definition.
 
@@
 
-As for the map $\iota$ we firstly define it as a homomorphism to the absolute group (for which we de not need the assumption that $I$ is splitting).
-$$\xymatrix{\St^*(n,\,R,\,I)\ar@<0.0ex>[r]^{\iota}&\St(n,\,R).}$$
-
-Clearly, we must map the elements $F(u,\,v)$ to van der Kallen's generators $X(u,\,v)$.
+As for the map $\iota$, we firsty define it as a homomorphism to the absolute group.
+Then we prove that the image of $\iota$ is contained in $\St(n, R, I)$.
+%$$\xymatrix{\St^*(n,\,R,\,I)\ar@<0.0ex>[r]^{\iota}&\St(n,\,R).}$$
+Clearly, $\iota$ should map the elements $F(u,\,v)$ to van der Kallen's generators $X(u,\,v)$.
 We should find the images for the elements $S(u,\,v)$ as well.
-First of all, recall that van der Kallen in~\cite[3.8--3.10]{vdK} constructs the following elements
+First of all, recall that van der Kallen in~\cite[3.8--3.10]{vdK} constructs the following elements:
 $$x(u,\,v)\in\St(n,\,R),\ u^tv=0,\ u_i=0\,\text{ or }\,v_i=0\,\text{ for some }\,1\leq i\leq n.$$
@@
 \begin{df} For $u\in R^n$, $v\in\E(n,\,R)e_1$, $u^tv=0$, consider the set $\overline Y(u,\,v)\subseteq\St(n,\,R)$
- consisiting of all elements $y\in\St(n,\,R)$ that admit the decomposition $y=\prod x(w^k,\,v)$, 
+ consisiting of all elements $y\in\St(n,\,R)$ that admit a decomposition $y=\prod x(w^k,\,v)$, 
  where $\sum u^k=u$ and $u^k=c^k \cdot (e_pv_q-e_qv_p)$ for some $c^k\in R$, $1\leq p\neq q\leq n$. \end{df}
@@
 Now we can finish the definition of $\iota$ by requiring that $\iota(S(u,\,v)) = Y(u,\,v)$ for $S(u,\,v)\in\St^*(n,\,R,\,I)$. 
-To show that the map $\iota$ is well-defined we should check that elements $X(u,\,v)$ and $Y(u,\,v)$ satisfy the relations 
-\eqref{add4}--\eqref{coinc} (with $F$'s and $S$'s replaced with $X$'s and $Y$'s).
-Only the validity of relation \eqref{coinc} is not immediately obvious.
+To show that the map $\iota$ is well-defined we should check that elements $X(u,\,v)$ and $Y(u,\,v)$ satisfy relations \eqref{add4}--\eqref{coinc} 
+(with $F$'s and $S$'s replaced with $X$'s and $Y$'s).
+Only the relation \eqref{coinc} is not immediately obvious.
 \begin{lm} \label{lm:XY} For $(u,\,v^t)=(Me_1,\,e_2^tM\inv)$, $M\in\E(n,\,R)$, $a\in I$ one has $X(u,\,va)=Y(ua,\,v)$. \end{lm}
@@
 Since $\pi^*(\iota(F(u, v))) = X(\pi(u),\,0)=1$ and $\pi^*(\iota(S(u,v)) = Y(0,\,\pi(v)) = 1$ we get that $\mathrm{Im}(\iota)\subseteq\Ker(\pi^*)=\St(n,\,R,\,I)$. 
-Thus, we have demonstrated the following result.
+It is clear that $\iota\kappa=\mathrm{id}$ hence $\kappa$ is injective.
+On the other hand, $\kappa$ is surjective by Lemma~\ref{allyouneedisf}\,$(\mathrm a)$.
+Thus, we have the following result.
 
@@
 sending $y_{ij}(a)$ to $y^*_{ij}(a)$. 
-Obviously, $\iota\circ\kappa=\mathrm{id}$ (cf.~\cite[3.6\,d)]{vdK}), thus $\kappa$ is injective.
-Surjectivity of $\kappa$ follows from Lemma~\ref{allyouneedisf}\,a), thus it is an isomorphism and $\iota$ is inverse to it.
 \end{comment}
@@
 We will prove a somewhat more general result. Let $B$ be a commutative unital ring.
-A $B$-module $M$ is called \emph{uniquely $r$-divisible} if for every $m\in M$ there exists a sole $m'\in M$ such that $rm' = m$ (we denote such $m'$ by $\frac{m}{a}$).
+A $B$-module $M$ is called \emph{uniquely $r$-divisible} if for every $m\in M$ there exists a sole $m'\in M$ such that $rm' = m$ (we denote such $m'$ by $\frac{m}{r}$).
 Clearly, $M$ is uniquely $r$-divisible if and only if the morphism of principal localisation $\lambda_r\colon M \to M_r$ is an isomorphism.
 
-\begin{tm} \label{a3map} Let $B$ be a ring, $a\in B$ and let $I$ be an ideal $B$ that is uniquely $a$-divisible.
-Then for $n\geq 4$ there exists a map $T\colon\St(n,\,B_a,\,I)\rightarrow\St(n,\,B)$ which makes the following diagram commute.
+\begin{tm} \label{a3map} Let $B$ be a ring, $a\in B$ and let $I$ be an ideal of $B$ that is uniquely $a$-divisible.
+Then for $n\geq 4$ there exists a map $T\colon\St^*(n,\,B_a,\,I)\rightarrow\St(n,\,B)$ which makes the following diagram commute.
 \begin{equation} \xymatrix{ \St^*(n,\,B,\,I)\ar@<-0.0ex>[rr]^{\iota}\ar@<-0.0ex>[d]_{\lambda_{a}^*} && \St(n,\,B)\ar@<-0.0ex>[d]^{\lambda_{a}^*}\\
@@
 \end{df}
-Tulenbaev shows that factors $x(u,\,v_ka)$, $1\leq k\leq N$ commute~\cite[Lemma~1.1\,e)]{Tul} and that for any other decomposition $v=\sum_{j=1}^Mv'_j$ one has
+Tulenbaev shows that the factors $x(u,\,v_ka)$, $1\leq k\leq N$ commute, see~\cite[Lemma~1.1\,e)]{Tul}.
+He also shows that if $v$ admits another decomposition $v=\sum_{j=1}^Mv'_j$ satisfying the assumptions of \cref{df:TulX} then one has
 $\prod_{k=1}^Nx(u,\,v_ka)=\prod_{j=1}^Mx(u,\,v'_ja)$, see the discussion following \cite[Lemma~1.1]{Tul}.
@@
 The assertion of $(\mathrm d)$ is proven in~\cite[Lemma~1.3\,b)]{Tul} under the assumption $n\geq5$. 
-Afterwards Tulenbaev remarks that the assertion remains true for $n=4$. We will give a detailed proof of this fact.
+Afterwards Tulenbaev remarks that the assertion remains true for $n=4$. % We will give a detailed proof of this fact.
 Indeed, take $z\in B^n$ such that $z^tu=b$ and write the canonical decomposition \eqref{eq:canonical}:
-$$(z^tu)w=\sum_{i<j}c_{ij} u_{ij}, \text{ where } u_{ij}=u_je_i-u_ie_j,\text{ and }c_{ij}=w_iz_j-w_jz_i.$$
-Each $c_{ij}u_{ij}$ is orthogonal to $u$ and, because of the assumption $n\geq4$, has at least two zero coordinates.
-Thus, $X_{u,wb}(a)=\prod_{i<j}x(u,\,a c_{ij} u_{ij})$. 
+$$(z^tu)w=\sum_{i<j}u_{ij} c_{ij}, \text{ where } u_{ij}=e_iu_j-e_ju_i,\text{ and }c_{ij}=w_iz_j-w_jz_i.$$
+Each $u_{ij} c_{ij}$ is orthogonal to $u$ and, because of the assumption $n\geq4$, has at least two zero coordinates.
+Thus, $X_{u,wb}(a)=\prod_{i<j}x(u,\, u_{ij} ac_{ij})$. 
 It is enough to prove the assertion of $(\mathrm d)$ in the special case $g=x_{hk}(r)$.
-If $h\neq i,j$ or $\{h,k\}=\{i,j\}$ the vector $\phi(g)^*ac_{ij}u_{ij}$ still has two zero coordinates.
+If $h\neq i,j$ or $\{h,k\}=\{i,j\}$ the vector $\phi(g)^*u_{ij}ac_{ij}$ still has two zero coordinates.
 
 Now consider the case $j=h$, $i\neq k$. 
-By~\cite[3.12]{vdK} one has $$g\,x(u,\,ac_{ij}u_{ij})g\inv=x(\phi(g)u,\,ac_{ij}\,\phi(g)^*u_{ij}).$$
+By~\cite[3.12]{vdK} one has $$g\,x(u,\,u_{ij}ac_{ij})g\inv=x(\phi(g)u,\,\phi(g)^*u_{ij}ac_{ij}).$$
 Set $u' = \phi(g)u$, since
-$\phi(g)^*u_{ij} = t_{kj}(-r) \cdot u_{ij} = u_je_i - u_ie_j + ru_i e_k =u'_{ij}+r\,u'_{ki},$ 
+$\phi(g)^*u_{ij} = t_{kj}(-r) \cdot u_{ij} = e_iu_j - e_ju_i + e_kru_i =u'_{ij}+u'_{ki}r,$ 
 we obtain from~\cite[3.11]{vdK} that
-$$x(\phi(g)u,\,ac_{ij}\,\phi(g)^* u_{ij})=x\left(u',\,c_{ij}a\,u'_{ij}\right)\cdot x\left(u',\,rc_{ij}a\,u'_{ki}\right).$$
-Decomposing in this fashion each factor $g\,x(u,\,ac_{ij}u_{ij})g^{-1}$ for which $\phi(g)^*ac_{ij}\, u_{ij}$ does not have two zero coordinates, 
+$$x(\phi(g)u,\,\phi(g)^* u_{ij} ac_{ij})=x\left(u',\,u'_{ij}c_{ij}a\right)\cdot x\left(u',\,u'_{ki} rc_{ij}a\right).$$
+Decomposing in this fashion each factor $g\,x(u,u_{ij}ac_{ij})g^{-1}$ for which $\phi(g)^*u_{ij}ac_{ij}$ does not have two zero coordinates, 
  we arrive at a product satisfying the requirements of the definition of $X_{\phi(g)u,\phi(g)^*wb}(a)$. \end{proof}
@@
 Let $u$, $v$, $x$, $y$ be elements of $B^n$ and $b,r\in B$ be such that $u^t v = 0$, $x^ty=b$, $x^tv=0$, $u^ty=0$ and $b\in I(u)\cap I(v)$.
-Then one has $X_{u,b^4rv}(b)=Y_{b^4ru,v}(b).$
+Then one has $X_{u,vb^4r}(b)=Y_{ub^4r,v}(b).$
 \end{lm}
 \begin{proof}
-Compute $g=[Y_{-arx,v}(b),\,X_{u,ay}(b)]$ in two different ways using Lemmas~\ref{xproperties}~and~\ref{yproperties}:
-$$ g = X_{t(b^2rx,-v)u,\,t(b^2rx,-v)^*yb}(b)X_{u,-yb}(b) = X_{u,\,by+b^4rv}(b)\, X_{u,-by}(b) = X_{u,b^4rv}(b),$$
-$$ g = Y_{-brx,v}(b) Y_{t(u,b^2y)arx,\,t(u,b^2y)^*v}(b)= Y_{-brx,v}(b)\, Y_{brx+b^4ru,\,v}(b)=Y_{b^4ru,v}(b).\qedhere$$
+Compute $g=[Y_{-xbr,v}(b),\,X_{u,yb}(b)]$ in two different ways using Lemmas~\ref{xproperties}~and~\ref{yproperties}:
+$$ g = X_{t(xb^2r,-v)u,\,t(xb^2r,-v)^*yb}(b)X_{u,-yb}(b) = X_{u,\,yb+vb^4r}(b)\, X_{u,-yb}(b) = X_{u,vb^4r}(b),$$
+$$ g = Y_{-xbr,v}(b) Y_{t(u,yb^2)xbr,\,t(u,yb^2)^*v}(b)= Y_{-xbr,v}(b)\, Y_{xbr+ub^4r,\,v}(b)=Y_{ub^4r,v}(b).\qedhere$$
 \end{proof}
@@
 It remains to check for $u = Me_1$, $v=M^*e_2$ and $c\in I$ that 
-\begin{equation}T(F(u, bv)) = X_{\tilde u,c/a^{4m}\,\tilde v}(a^{2m}) = Y_{c/a^{4m}\, \tilde u,\tilde v}(a^{2m}) = T(S(ub, v)). \label{eq:last}\end{equation}
-Here $\tilde u, \tilde v \in B^n$ are liftings of $u$ and $v$ such that $\lambda_a(\tilde u)=a^m u$, $\lambda_a(\tilde v)=a^m v$ and $\tilde u^t \tilde v = 0$.
+\begin{equation}T(F(u, cv)) = X_{\tilde u,\,\tilde v c/a^{4m}}(a^{2m}) = Y_{\tilde uc/a^{4m},\, \tilde v}(a^{2m}) = T(S(uc, v)). \label{eq:last}\end{equation}
+Here $\tilde u, \tilde v \in B^n$ are liftings of $u$ and $v$ such that $\lambda_a(\tilde u)= ua^m$, $\lambda_a(\tilde v)= va^m$ and $\tilde u^t \tilde v = 0$.
 We can also assume that $m$ is so large that $a^{2m}\in I(\tilde{u})\cap I(\tilde{v})$ and there exist $\tilde{x}$, $\tilde{y}$ such that the following equations hold:
-$$\lambda_a(\tilde{x})=a^mMe_3,\ \lambda_a(\tilde{y})=a^mM^*e_3\text{ and }\tilde{x}^t\tilde{y}=a^{2m},\ \tilde{x}^t\tilde{v} = 0,\ \tilde{u}^t\tilde{y} =0.$$
+$$\lambda_a(\tilde{x})=Me_3a^m,\ \lambda_a(\tilde{y})=M^*e_3a^m\text{ and }\tilde{x}^t\tilde{y}=a^{2m},\ \tilde{x}^t\tilde{v} = 0,\ \tilde{u}^t\tilde{y} =0.$$
 To obtain~\eqref{eq:last} it remains to apply \cref{x=y} taking $b=a^{2m}$, $r=c/a^{12m}$.

### 2016-04-30 paper.tex
Fixed problem with proposition 2.2

@@
 Since $\xi'\eta' + \pi(\xi)\eta' + \pi(\eta)\xi' = \xi\eta - \pi(\xi\eta)$ the above expression clearly simplifies to $\psi(x_{ik}(\xi\eta))$, as claimed.
+Verification of the fact that $\psi$ preserves relations \eqref{add0}, \eqref{ccf2} is similar to the above computation but is easier.
+In particular, one does not need to use relation~\eqref{add3}.
 
@@
 \setcounter{equation}{2} \renewcommand{\theequation}{T\arabic{equation}'}
-\begin{equation} X(e_ir+e_j,\,e_k)=X(e_i,\,rae_k)X(e_j,\,ae_k)\,\text{ for }r\in R,\ a\in I\text{ and } i,j,k\text{ distinct}. \label{add3'} \end{equation} \end{rk}
+\begin{equation} X(e_ir+e_j,\,e_k)=X(e_i,\,rae_k)X(e_j,\,ae_k)\,\text{ for }r\in R,\ a\in I\text{ and } i,j,k\text{ distinct}. \label{add3'} \end{equation} 
+This is because only this smaller family of relations is actually used during the construction of $\psi$. \end{rk}
 

### 2016-05-01 paper.tex
Fixes during the talk

--- 2016-04-30 paper.tex
@@
 \section*{Inroduction}
-The main goal of the present paper is to establish a local-global principle and centrality of orthogonal $\Kt$ for arbitrary commutative ring $R$.
+The main goal of the present paper is to establish Quillen's local-global principle and the centrality of orthogonal $\Kt$ for arbitrary commutative ring $R$.
 
@@
 This group shares many properties with its stable counterpart $\mathrm{SK}_1(R) = \lim\limits_{l\to\infty}\Ko(\rA_\ell, R)$, which, in turn,
-is a direct summand of the $\Ko$-group, i.\,e. $\Ko(R) = \mathrm{SK}_1(R) \oplus R^*$.
+is an essential direct summand of the $\Ko$-group ($\Ko(R) = \mathrm{SK}_1(R) \oplus R^*$).
 
@@
 Compare \cref{tm:lg-principle} with the local-global principle for $\Ko$ which states that an element of the congruence subgroup $g\in \GG(\Phi,\,R[X], XR[X])$ is elementary
-(i.\,e. lies in $\E(\Phi, R[X])$) if and only if $g_M=1\in\E(\Phi,\,R_M)$ for all maximal ideals $M \triangleleft R$.
+(i.\,e. lies in $\E(\Phi, R[X])$) if and only if $g_M=1\in\E(\Phi,\,R_M)$ for all maximal ideals $M \trianglelefteq R$.
 
@@
 Notice that we parametrize elements $X(u, v)$ with two columns rather than with one column and one row as it is done in~\cite{vdK}.
-Our generator $X(u,v)$ corresponds to van der Kallen's generator $(u, v^t)$.
+Our generator $X(u,v)$ corresponds to van der Kallen's generator $X(u, v^t)$.
 
@@
 Define the map $\psi$ by $\psi(x_{ij}(\xi)) = (X(e_i, (\xi - \pi(\xi)e_j),\ x_{ij}(\pi(\xi)))$. 
-We have to check that $\psi$ preserves the relations \eqref{add0}--\eqref{ccf2}.
-For example, let us check \eqref{ccf1}. 
-First of all, recall that in any semidirect product of groups one can compute the commutator of two elements as follows:
+We have to check that $\psi$ preserves relations \eqref{add0}--\eqref{ccf2}.
+For example, let us check \eqref{ccf2}. 
+First of all, recall that in any semidirect product of groups one can compute the commutator of two elements in the following way:
 $$[(a, b), (c, d)] = (a \cdot {}^bc \cdot {}^{bdb^{-1}}a^{-1} \cdot {}^{[b, d]}c^{-1} , [b, d]).$$
@@
 Since $\xi'\eta' + \pi(\xi)\eta' + \pi(\eta)\xi' = \xi\eta - \pi(\xi\eta)$ the above expression clearly simplifies to $\psi(x_{ik}(\xi\eta))$, as claimed.
+Verification of the fact that $\psi$ preserves relations \eqref{add0}, \eqref{ccf1} is similar to the above computation but is easier.
+In particular, one does not need to use relation~\eqref{add3}.
 
@@
 \setcounter{equation}{2} \renewcommand{\theequation}{T\arabic{equation}'}
-\begin{equation} X(e_ir+e_j,\,e_k)=X(e_i,\,rae_k)X(e_j,\,ae_k)\,\text{ for }r\in R,\ a\in I\text{ and } i,j,k\text{ distinct}. \label{add3'} \end{equation} \end{rk}
+\begin{equation} X(e_ir+e_j,\,e_k)=X(e_i,\,rae_k)X(e_j,\,ae_k)\,\text{ for }r\in R,\ a\in I\text{ and } i,j,k\text{ distinct}. \label{add3'} \end{equation} 
+This is because only this smaller family of relations is actually used in the construction of $\psi$. \end{rk}
 
@@
 $F(u,\,v)$ with $u$ good and $v$ arbitrary and $S(u,\,v)$ with $u$ arbitrary and $v$ good.
-The generators $F(u,\,v)$ will be additive in the second component, while $S(u,\,v)$ will be additive in the first one.
+The generators $F(u,\,v)$ are additive in the second component, while $S(u,\,v)$ are additive in the first one.
 When $u$ and $v$ are both good we require that these two generators coincide.
@@
  consisiting of all elements $y\in\St(n,\,R)$ that admit a decomposition $y=\prod x(w^k,\,v)$, 
- where $\sum u^k=u$ and $u^k=c^k \cdot (e_pv_q-e_qv_p)$ for some $c^k\in R$, $1\leq p\neq q\leq n$. \end{df}
+ where $\sum u^k=u$ and $u^k= (e_pv_q-e_qv_p)c^k$ for some $c^k\in R$, $1\leq p\neq q\leq n$. \end{df}
 
@@
 It is not hard to check that \setcounter{equation}{6} \setcounter{lm}{7}
-\begin{equation} (w^t\cdot v)\cdot u = \sum_{p<q}u_{pq},\text{ where }u_{pq} = (u_pw_q - u_qw_p) \cdot (v_qe_p - v_pe_q)\in{}\!R^n, \label{eq:canonical}\end{equation}
+\begin{equation} (w^t\cdot v)\cdot u = \sum_{p<q}u_{pq},\text{ where }u_{pq} = (e_pv_q - e_qv_p)\cdot  (u_pw_q - u_qw_p)\in{}\!R^n, \label{eq:canonical}\end{equation}
 therefore $\overline Y(u,\,v)$ is not empty (cf.~\cite[3.1--3.2]{vdK}).
@@
 \begin{rk} \label{rk:ID}
-From the canonical decomposition~\eqref{eq:canonical} it follows that $bv\in D(u)$ for any $b\in I(u)$ and $v$ such that $v^tu=0$.
+From the canonical decomposition~\eqref{eq:canonical} it follows that $vb\in D(u)$ for any $b\in I(u)$ and $v$ such that $v^tu=0$.
 In particular, if $I$ is uniquely $a$-divisible and $a^k\in I(u)$, then every $v\in I^n$ satisfying $v^tu=0$ is contained in $D(u)$.
@@
 
-Now consider the case $j=h$, $i\neq k$. 
+Now consider the case $j=h$, $i\neq k$
 By~\cite[3.12]{vdK} one has $$g\,x(u,\,u_{ij}ac_{ij})g\inv=x(\phi(g)u,\,\phi(g)^*u_{ij}ac_{ij}).$$
@@
 Decomposing in this fashion each factor $g\,x(u,u_{ij}ac_{ij})g^{-1}$ for which $\phi(g)^*u_{ij}ac_{ij}$ does not have two zero coordinates, 
- we arrive at a product satisfying the requirements of the definition of $X_{\phi(g)u,\phi(g)^*wb}(a)$. \end{proof}
+ we arrive at a product satisfying the requirements of the definition of $X_{\phi(g)u,\phi(g)^*wb}(a)$.
+
+ Since $u_{ij} = - u_{ji}$, $c_{ij}= - c_{ji}$ the case $i=h$, $j\neq k$ formally follows from the one just considered. \end{proof}
 

### 2016-05-01 paper.tex
Fixed more comments

@@
 
-\section*{Inroduction}
+\section*{Introduction}
 The main goal of the present paper is to establish Quillen's local-global principle and the centrality of orthogonal $\Kt$ for arbitrary commutative ring $R$.
@@
 Recall that to each reduced root system $\Phi$ and a commutative ring $R$ one can associate a split simple group $\GG(\Phi, R)$ called a \emph{Chevalley group}.
-For $\Phi$ of rank $\geq 2$ the abstract group $\GG(\Phi, R)$ contains a large normal subgroup $\E(\Phi, R)$ generated by the elementary root unipotents $t_\alpha(\xi)$, $\xi\in R$, $\alpha\in \Phi$.
+For $\Phi$ of rank $\geq 2$ the abstract group $\GG(\Phi, R)$ contains a large normal subgroup $\E(\Phi, R)$ generated by the elementary root unipotents $t_\alpha(\xi)$, $\xi\in R$, $\alpha\in \Phi$, see~\cite{Ta}.
 The quotient group $\Ko(\Phi, R)=\GG(\Phi, R)/\E(\Phi, R)$ is called the \emph{unstable $\Ko$-group}
@@
 
-It is classically known that $\Kt(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$ if $R$ is commutative local ring and $\Phi$ has rank $\geq 2$ (see \cite{St73}).
-However, to prove that centrality of $\Kt$ holds for \emph{arbitrary} $R$ is much harder.
-The first result in this direction was obtained in 1977 by W. van~der~Kallen for $\Phi=\rA_\ell$, $\ell\geq 3$ using the technique called ``another presentation''.
-Using a similar approach, the first-named author has established centrality of $\Kt(\rC_\ell, R)$ for $\ell\geq 3$, see \cite{Lav}.
+It is classically known that $\Kt(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$ if $R$ is a commutative local ring and $\Phi$ has rank $\geq 2$, see \cite{St73}.
+We refer to the latter statement as the ``centrality of $\Kt$''.
+In~\cite{vdK} using the technique called ``another presentation'' W. van~der~Kallen has shown that the centrality of $\Kt$ holds for $\Phi=\rA_\ell$, $\ell\geq 3$ and arbitrary commutative ring $R$.
+Using similar ideas Tulenbaev in~\cite{Tul0} has further generalised van~der~Kallen's result to associative rings that are module-finite over their centres.
+
+Thus, it is natural to expect that the centrality of $\Kt$ holds for arbitrary commutative rings and different types of Chevalley groups, as well.
+In \cite{Lav}, \cite{SCh} the authors of the present paper have established the centrality of $\Kt(\rC_\ell, R)$ for $\ell\geq 3$ and $\Kt(\rE_\ell, R)$, $\ell=6,7,8$.
 In turn, the key result of this paper is the following theorem.
@@
 the group $\Kt(\rD_\ell, R)$ is contained in the centre of $\St(\rD_\ell, R)$. \end{tm}
-Notice that the analogous statement in the case $\Phi=\rE_\ell$, $\ell=6,7,8$ has been demonstrated by the second named author in \cite{SCh}.
+
 \cref{tm:centrality} is essentially a corollary of the following local-global principle.
@@
 one computes the commutator $[\psi(x_{ij}(\xi), \psi(x_{jk}(\eta)]$ as follows:
-$$\left(X(e_i, \xi' e_j) \cdot X(e_j + \pi(\xi)e_i, \eta'e_k) \cdot X(e_i, \pi(\eta)\xi' e_k - \xi' e_j) \cdot X(e_j, -\eta'e_k),\ x_{ik}(\pi(\xi\eta))\right).$$
+\setcounter{equation}{2}
+\begin{equation} \left(X(e_i, \xi' e_j) \cdot X(e_j + \pi(\xi)e_i, \eta'e_k) \cdot X(e_i, \pi(\eta)\xi' e_k - \xi' e_j) \cdot X(e_j, -\eta'e_k),\ x_{ik}(\pi(\xi\eta))\right).
+\label{eq:proofS3}\end{equation}
+\setcounter{lm}{3}
 After applying additivity relations \eqref{add2}, \eqref{add3} and moving the factor $X(e_i, -\xi' e_j)$ to the left hand side of the formula by means of relation \eqref{conj2}
@@
 \begin{equation} X(e_ir+e_j,\,e_k)=X(e_i,\,rae_k)X(e_j,\,ae_k)\,\text{ for }r\in R,\ a\in I\text{ and } i,j,k\text{ distinct}. \label{add3'} \end{equation} 
-This is because only this smaller family of relations is actually used in the construction of $\psi$. \end{rk}
+This follows from the fact that only this smaller family of relations was actually used in the construction of the map $\psi$
+(more precisely, it was used to simplify the second factor of~\eqref{eq:proofS3}). \end{rk}
 
@@
 We will prove a somewhat more general result. Let $B$ be a commutative unital ring.
-A $B$-module $M$ is called \emph{uniquely $r$-divisible} if for every $m\in M$ there exists a sole $m'\in M$ such that $rm' = m$ (we denote such $m'$ by $\frac{m}{r}$).
-Clearly, $M$ is uniquely $r$-divisible if and only if the morphism of principal localisation $\lambda_r\colon M \to M_r$ is an isomorphism.
+We call an ideal $I$ of $B$ \emph{uniquely $r$-divisible} if for every $m\in I$ there exists only one $m'\in I$ such that $rm' = m$ (we denote such $m'$ by $\frac{m}{r}$).
+Clearly, $I$ is uniquely $r$-divisible if and only if the restriction of the morphism of principal localisation $\lambda_r\colon R \to R_r$ to $I$ is an isomorphism.
 

### 2016-05-01 paper.tex
Minor

@@
 In~\cite{vdK} using the technique called ``another presentation'' W. van~der~Kallen has shown that the centrality of $\Kt$ holds for $\Phi=\rA_\ell$, $\ell\geq 3$ and arbitrary commutative ring $R$.
-Using similar ideas Tulenbaev in~\cite{Tul0} has further generalised van~der~Kallen's result to associative rings that are module-finite over their centres.
+Using similar ideas Tulenbaev in~\cite{Tul0} further generalised van~der~Kallen's result to associative rings that are module-finite over their centres.
 

### 2016-05-08 paper.tex
Rewritten the introduction

@@
 \section*{Introduction}
-The main goal of the present paper is to establish Quillen's local-global principle and the centrality of orthogonal $\Kt$ for arbitrary commutative ring $R$.
+The aim of this paper is to establish Quillen's local-global principle and the centrality of even orthogonal $\Kt$ for arbitrary commutative ring $R$.
 
-Recall that to each reduced root system $\Phi$ and a commutative ring $R$ one can associate a split simple group $\GG(\Phi, R)$ called a \emph{Chevalley group}.
-For $\Phi$ of rank $\geq 2$ the abstract group $\GG(\Phi, R)$ contains a large normal subgroup $\E(\Phi, R)$ generated by the elementary root unipotents $t_\alpha(\xi)$, $\xi\in R$, $\alpha\in \Phi$, see~\cite{Ta}.
-The quotient group $\Ko(\Phi, R)=\GG(\Phi, R)/\E(\Phi, R)$ is called the \emph{unstable $\Ko$-group}
-This group shares many properties with its stable counterpart $\mathrm{SK}_1(R) = \lim\limits_{l\to\infty}\Ko(\rA_\ell, R)$, which, in turn,
-is an essential direct summand of the $\Ko$-group ($\Ko(R) = \mathrm{SK}_1(R) \oplus R^*$).
+Recall that to each reduced irreducible root system $\Phi$ and a commutative ring $R$ one can associate a split simple group $\GG(\Phi, R)$ called a \emph{Chevalley group}.
+The {\it elementary group} $\E(\Phi, R)$ is defined as the subgroup of $\GG(\Phi, R)$ generated by elementary root unipotents $t_\alpha(\xi)$, $\xi\in R$, $\alpha\in \Phi$.
+By definition, the Steinberg group $\St(\Phi, R)$ is presented by generators $x_\alpha(\xi)$, which model the unipotents $t_\alpha(\xi)$, subjected to Steinberg relations (see~\cref{sec:prelim}). 
+There is a natural map $\phi\colon\St(\Phi, R)\twoheadrightarrow \GG(\Phi, R)$ sending $x_\alpha(\xi)$ to $t_\alpha(\xi)$ whose image equals $\E(\Phi, R)$.
 
-Similarly to the definition of the algebraic $\Kt$-functor, one can define $\Kt(\Phi, R)$ as the kernel of the canonical projection $\phi\colon\St(\Phi, R)\twoheadrightarrow \E(\Phi, R)$.
-Here $\St(\Phi, R)$ stands for the \emph{Steinberg group} of type $\Phi$, i.\,e. the group defined by formal generators $x_\alpha(\xi)$ modeling root unipotents $t_\alpha(\xi)$
-and the explicit list of relations called Steinberg relations (see~\cref{sec:prelim}).
+By a theorem of Taddei (see~\cite{Ta}) the elementary group $\E(\Phi, R)$ is a normal subgroup of $\GG(\Phi, R)$ if $\Phi$ has rank at least $2$.
+Thus, similarly to the definition of algebraic $\mathrm{SK}_1$ and $\Kt$-functors, one can define the groups $\Ko(\Phi, R)$, $\Kt(\Phi, R)$ as the cokernel and kernel of $\phi$:
+$$\xymatrix{1 \ar[r] & \Kt(\Phi, R) \ar[r] & \St(\Phi, R) \ar[r] & \GG(\Phi, R) \ar[r] & \Ko(\Phi, R) \ar[r] & 1.}$$
 
-It is classically known that $\Kt(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$ if $R$ is a commutative local ring and $\Phi$ has rank $\geq 2$, see \cite{St73}.
-We refer to the latter statement as the ``centrality of $\Kt$''.
-In~\cite{vdK} using the technique called ``another presentation'' W. van~der~Kallen has shown that the centrality of $\Kt$ holds for $\Phi=\rA_\ell$, $\ell\geq 3$ and arbitrary commutative ring $R$.
-Using similar ideas Tulenbaev in~\cite{Tul0} further generalised van~der~Kallen's result to associative rings that are module-finite over their centres.
+It is a classical theorem of M.~Kervaire and R.~Steinberg that the stable Steinberg group $\St(R)$ is the universal central extension of $\E(R)$ for arbitrary $R$, see \cite[Theorem~III.5.5]{Kbook}.
+The unstable analogue of the ``universality'' part of this theorem was obtained by M.~Stein and W.~van~der~Kallen in 1970's, see \cite{St1, KaS}.
+However, until recently, the analogue of the ``centrality'' part of the theorem was only known for $\Phi=\rA_\ell$, $\ell\geq 4$, see~\cite[Corollary~2]{vdK} and for other classical $\Phi$ ``in the stable range'',
+i.\,e. when the dimension of $R$ is suffiently small with respect to the rank of $\Phi$, see~\cite[Corollary~3.4]{St78}.
 
-Thus, it is natural to expect that the centrality of $\Kt$ holds for arbitrary commutative rings and different types of Chevalley groups, as well.
-In \cite{Lav}, \cite{SCh} the authors of the present paper have established the centrality of $\Kt(\rC_\ell, R)$ for $\ell\geq 3$ and $\Kt(\rE_\ell, R)$, $\ell=6,7,8$.
+Recently the authors of this paper have established the centrality of $\Kt(\rC_\ell, R)$ ($\ell\geq 3$) and $\Kt(\rE_\ell, R)$ ($\ell=6,7,8$) for arbitrary commutative ring $R$, see \cite{Lav, SCh}.
 In turn, the key result of this paper is the following theorem.
 \begin{tm}\label{tm:centrality}  Let $R$ be an arbitrary commutative ring and $\ell\geq 4$ then 
-the group $\Kt(\rD_\ell, R)$ is contained in the centre of $\St(\rD_\ell, R)$. \end{tm}
+the group $\Kt(\rD_\ell, R)$ is a central subgroup of $\St(\rD_\ell, R)$. \end{tm}
 
-\cref{tm:centrality} is essentially a corollary of the following local-global principle.
+\cref{tm:centrality} follows from the following local-global principle.
+We refer the reader to the proof ~\cite[Theorem~]{SCh}
 \begin{tm}\label{tm:lg-principle} Let $\Phi$ be an irreducible simply-laced root system of rank $\geq 3$ and $R$ be arbitrary commutative ring.
@@
 
-The Steinberg group $\St(n, R) = \St(\rA_{n-1}, R)$ is the group presented by generators
+The Steinberg group $\St(n, R) = \St(\rA_{n-1}, R)$ is the group defined by generators
 $x_{ij}(r)$, $1\leq i\neq j\leq n$, $r\in R\}$ and relations
@@
 
-\section{Patching Tulenbaev maps (to be written)}\label{sec:patching}
-
-The next section is devoted to the proof of Theorems~\ref{tm:centrality}--\ref{tm:lg-principle} for Steinberg groups corresponding to 
-arbitrary simply-laced root system of rank $l\geq3$.
-To do so, we glue maps $T$ constructed in the previous section following the approach of~\cite{SCh}.
-
-\printbibliography
+%\printbibliography
 

### 2016-05-08 paper.tex
Minor fixes

@@
 \newcommand{\rG}{\mathsf{G}}
+\DeclareRobustCommand{\VAN}[2]{#1}
 
@@
 It is a classical theorem of M.~Kervaire and R.~Steinberg that the stable Steinberg group $\St(R)$ is the universal central extension of $\E(R)$ for arbitrary $R$, see \cite[Theorem~III.5.5]{Kbook}.
-The unstable analogue of the ``universality'' part of this theorem was obtained by M.~Stein and W.~van~der~Kallen in 1970's, see \cite{St1, KaS}.
-However, until recently, the analogue of the ``centrality'' part of the theorem was only known for $\Phi=\rA_\ell$, $\ell\geq 4$, see~\cite[Corollary~2]{vdK} and for other classical $\Phi$ ``in the stable range'',
-i.\,e. when the dimension of $R$ is suffiently small with respect to the rank of $\Phi$, see~\cite[Corollary~3.4]{St78}.
+The unstable analogue of the ``universality'' part of this theorem was proved by M.~Stein and W.~van~der~Kallen for $\Phi$ of rank $\geq 5$ (or even $\geq 4$ for $\Phi$ of type $\rA_\ell, \rB_\ell, \rC_\ell$, see \cite{St1, KaS})
+However, until recently, the analogue of the ``centrality'' part was only known for $\Phi=\rA_\ell$, $\ell\geq 3$, see~\cite[Corollary~2]{vdK} and for other classical $\Phi$ ``in the stable range'',
+i.\,e. when the dimension of $R$ is suffiently small in comparison with the rank of $\Phi$, see~\cite[Corollary~3.4]{St78}.
 
@@
 
-\cref{tm:centrality} follows from the following local-global principle.
-We refer the reader to the proof ~\cite[Theorem~]{SCh}
+The above theorem is a corollary of the following local-global principle (cf. with the proof of~\cite[Theorem~1]{SCh}).
 \begin{tm}\label{tm:lg-principle} Let $\Phi$ be an irreducible simply-laced root system of rank $\geq 3$ and $R$ be arbitrary commutative ring.
@@
 
-The special case $\Phi=\rA_\ell$, $\ell\geq 4$ of \cref{tm:lg-principle} was demonstrated for the first time by Tulenbaev, see~\cite[Theorem~2.1]{Tul},
-while cases $\Phi=\rC_\ell$, $\ell\geq 3$ and $\Phi=\rE_\ell$, $\ell=6,7,8$ have been analyzed in \cite{Lav2} and \cite{SCh}, respectively.
+\cref{tm:lg-principle} includes as a special case both~\cite[Theorem~2.1]{Tul} and~\cite[Theorem~2]{SCh} in which
+the cases $\Phi=\rA_\ell$, $\ell\geq 4$, $\Phi=\rE_\ell$, $\ell=6,7,8$ were studied, respectively.
 The special cases $\Phi=\rA_3$ and $\Phi=\rD_\ell$, $\ell\geq 4$ of \cref{tm:lg-principle} are new and have not been known before.
+
+As a yet another motivation for ??? we mention that a symplectic counterpart of~\cref{lg-principle} was demonstrated by
+the first-named author $\Phi=\rC_\ell$ starting from $\ell\geq 3$.
 
@@
              \St(n,\,R_a[X],\,XR_a[X]) \ar@{-->}[ru]_-{T} \ar@{^{(}->}[r] & \St(n, R_a[X])} \label{eq:diagram} \end{equation}
-Here $n\geq5$, $a$ is arbitrary non-nilpotent element of $R$ and $\lambda_a^*$ is the morphism induced by the morphism $\lambda_a\colon R \to R_a$ of principal localisation (i.\,e.
-localisation by the powers of $a$).
+Here $n\geq5$, $a$ denotes an arbitrary non-nilpotent element of $R$ and $\lambda_a^*$ is the morphism of Steinberg groups induced by the morphism 
+$\lambda_a\colon R \to R_a$ of localisation by the powers of $a$.
 Notice that $XR_a[X]$ is a splitting ideal for both $R_a[X]$ and $R \ltimes XR_a[X]$.
-It is clear that the image of $T$ is contained in the image of the top arrow, therefore this implies that the relative Steinberg groups in the left-hand side of the diagram are isomoprhic.
+It is clear that the image of $T$ is contained in the image of the top arrow, therefore the relative Steinberg groups in the left-hand side of the diagram are isomoprhic.
 %This $T$ is an inverse to a map induced by localisation, so that constructing $\mathrm T$ may be treated
@@
 
-%\printbibliography
+\printbibliography
 

### 2016-05-11 paper.tex
Small changes

@@
 The {\it elementary group} $\E(\Phi, R)$ is defined as the subgroup of $\GG(\Phi, R)$ generated by elementary root unipotents $t_\alpha(\xi)$, $\xi\in R$, $\alpha\in \Phi$.
-By definition, the Steinberg group $\St(\Phi, R)$ is presented by generators $x_\alpha(\xi)$, which model the unipotents $t_\alpha(\xi)$, subjected to Steinberg relations (see~\cref{sec:prelim}). 
-There is a natural map $\phi\colon\St(\Phi, R)\twoheadrightarrow \GG(\Phi, R)$ sending $x_\alpha(\xi)$ to $t_\alpha(\xi)$ whose image equals $\E(\Phi, R)$.
+By definition, the Steinberg group $\St(\Phi, R)$ is presented by generators $x_\alpha(\xi)$, which model the unipotents $t_\alpha(\xi)$, and Steinberg relations (see~\cref{sec:prelim}). 
+Thus, there is a well-defined map $\phi\colon\St(\Phi, R)\twoheadrightarrow \GG(\Phi, R)$ sending $x_\alpha(\xi)$ to $t_\alpha(\xi)$ whose image is $\E(\Phi, R)$.
 
@@
 It is a classical theorem of M.~Kervaire and R.~Steinberg that the stable Steinberg group $\St(R)$ is the universal central extension of $\E(R)$ for arbitrary $R$, see \cite[Theorem~III.5.5]{Kbook}.
-The unstable analogue of the ``universality'' part of this theorem was proved by M.~Stein and W.~van~der~Kallen for $\Phi$ of rank $\geq 5$ (or even $\geq 4$ for $\Phi$ of type $\rA_\ell, \rB_\ell, \rC_\ell$, see \cite{St1, KaS})
-However, until recently, the analogue of the ``centrality'' part was only known for $\Phi=\rA_\ell$, $\ell\geq 3$, see~\cite[Corollary~2]{vdK} and for other classical $\Phi$ ``in the stable range'',
-i.\,e. when the dimension of $R$ is suffiently small in comparison with the rank of $\Phi$, see~\cite[Corollary~3.4]{St78}.
+The unstable analogue of the ``universality'' part of this theorem was obtained by M.~Stein and W.~van~der~Kallen for $\Phi$ of rank $\ell \geq 5$ (or even $\ell \geq 4$ for $\Phi$ of type $\rA_\ell, \rB_\ell, \rC_\ell$, see \cite{St1, KaS})
+However, until recently, the analogue of the ``centrality'' part was only known in the case of a general $R$ for $\Phi=\rA_\ell$, $\ell\geq 3$ see~\cite[Corollary~2]{vdK}.
+The best result for other classical $\Phi$ was that the centrality holds ``in the stable range'',
+i.\,e. when the dimension of $R$ is suffiently small as compared to the rank of $\Phi$, see~\cite[Corollary~3.4]{St78}.
 
@@
 In turn, the key result of this paper is the following theorem.
-\begin{tm}\label{tm:centrality}  Let $R$ be an arbitrary commutative ring and $\ell\geq 4$ then 
-the group $\Kt(\rD_\ell, R)$ is a central subgroup of $\St(\rD_\ell, R)$. \end{tm}
+\begin{tm}[``Centrality of $\Kt$''] \label{tm:centrality}  Let $R$ be an arbitrary commutative ring.
+Then for $\ell\geq 4$ the group $\Kt(\rD_\ell, R)$ is a central subgroup of $\St(\rD_\ell, R)$. \end{tm}
 
-The above theorem is a corollary of the following local-global principle (cf. with the proof of~\cite[Theorem~1]{SCh}).
-\begin{tm}\label{tm:lg-principle} Let $\Phi$ be an irreducible simply-laced root system of rank $\geq 3$ and $R$ be arbitrary commutative ring.
+We claim that \cref{tm:centrality} is a corollary of $\Kt$-analogue of Quillen's local-global principle,
+very much in the same fashion as the normality theorem for the elementary subgroup is a corollary of Quillen's local-global principle for $\Ko$.
+The proof of this claim can be found in \cite{SCh}
+For the proof of this claim we refer the reader to the proof of \cite[Theorem~1]{SCh} which works in our situation verbatim.
+%The above theorem is a corollary of the following local-global principle (cf. with the proof of~\cite[Theorem~1]{SCh}).
+\begin{tm}[``Quillen's LG-principle for $\Kt$''] \label{tm:lg-principle} 
+Let $\Phi$ be an irreducible simply-laced root system of rank $\geq 3$ and $R$ be arbitrary commutative ring.
 Then an element $g\in\St(\Phi,\,R[X])$ satisfying $g(0)=1\in\St(\Phi,\,R)$ is trivial in $\St(\Phi,\,R[X])$
-if and only if the images $g_M\in\St(\Phi,\,R_M[X])$ of $g$ under localisation morphisms $R\to R_M$ are trivial for all maximal ideals $M\trianglelefteq R$. \end{tm}
+if and only if the images $\lambda^*(g)\in\St(\Phi,\,R_M[X])$ of $g$ under localisation maps $\lambda_M\colonR\to R_M$ are trivial for all maximal ideals $M\trianglelefteq R$. \end{tm}
+The proof for the assertion that \cref{tm:lg-principle} follows from \cref{tm:centrality} is a verbatim repetion of the proof of \cite[Theorem~1]{SCh}.
 

### 2016-05-11 paper.tex
Minor changes

@@
 
-It is a classical theorem of M.~Kervaire and R.~Steinberg that the stable Steinberg group $\St(R)$ is the universal central extension of $\E(R)$ for arbitrary $R$, see \cite[Theorem~III.5.5]{Kbook}.
-The unstable analogue of the ``universality'' part of this theorem was obtained by M.~Stein and W.~van~der~Kallen for $\Phi$ of rank $\ell \geq 5$ (or even $\ell \geq 4$ for $\Phi$ of type $\rA_\ell, \rB_\ell, \rC_\ell$, see \cite{St1, KaS})
-However, until recently, the analogue of the ``centrality'' part was only known in the case of a general $R$ for $\Phi=\rA_\ell$, $\ell\geq 3$ see~\cite[Corollary~2]{vdK}.
-The best result for other classical $\Phi$ was that the centrality holds ``in the stable range'',
+It is a classical theorem of M.~Kervaire and R.~Steinberg that the stable Steinberg group $\St(R)$ is the universal central extension of $\E(R)$, see \cite[Theorem~III.5.5]{Kbook}.
+The unstable analogue of the ``universality'' part of this theorem is known since 1970's from the works of M.~Stein and W.~van~der~Kallen for $\Phi$ with rank $\ell \geq 5$ (or even $\ell \geq 4$ for $\Phi=\rA_\ell, \rB_\ell, \rC_\ell$), see \cite{St1, KaS}.
+However, until recently, the analogue of the ``centrality'' part was only known in the special case $\Phi=\rA_\ell$, $\ell\geq 3$ see~\cite[Corollary~2]{vdK}.
+The best known result for other classical $\Phi$ was that the centrality holds ``in the stable range'',
 i.\,e. when the dimension of $R$ is suffiently small as compared to the rank of $\Phi$, see~\cite[Corollary~3.4]{St78}.
@@
 
-We claim that \cref{tm:centrality} is a corollary of $\Kt$-analogue of Quillen's local-global principle,
+Centrality of $\Kt$ is a corollary of the following variant of Quillen's local-global principle,
 very much in the same fashion as the normality theorem for the elementary subgroup is a corollary of Quillen's local-global principle for $\Ko$.
-The proof of this claim can be found in \cite{SCh}
-For the proof of this claim we refer the reader to the proof of \cite[Theorem~1]{SCh} which works in our situation verbatim.
-%The above theorem is a corollary of the following local-global principle (cf. with the proof of~\cite[Theorem~1]{SCh}).
 \begin{tm}[``Quillen's LG-principle for $\Kt$''] \label{tm:lg-principle} 
@@
 Then an element $g\in\St(\Phi,\,R[X])$ satisfying $g(0)=1\in\St(\Phi,\,R)$ is trivial in $\St(\Phi,\,R[X])$
-if and only if the images $\lambda^*(g)\in\St(\Phi,\,R_M[X])$ of $g$ under localisation maps $\lambda_M\colonR\to R_M$ are trivial for all maximal ideals $M\trianglelefteq R$. \end{tm}
-The proof for the assertion that \cref{tm:lg-principle} follows from \cref{tm:centrality} is a verbatim repetion of the proof of \cite[Theorem~1]{SCh}.
+if and only if the images $\lambda_M^*(g)\in\St(\Phi,\,R_M[X])$ of $g$ under localisation maps $\lambda_M\colonR\to R_M$ are trivial for all maximal ideals $M\trianglelefteq R$. \end{tm}
+For the proof of the claim that \cref{tm:lg-principle} follows from \cref{tm:centrality} we refer the reader to the proof of Theorem~1 in \cite{SCh} which works verbatim in our case.
 
-\cref{tm:lg-principle} includes as a special case both~\cite[Theorem~2.1]{Tul} and~\cite[Theorem~2]{SCh} in which
-the cases $\Phi=\rA_\ell$, $\ell\geq 4$, $\Phi=\rE_\ell$, $\ell=6,7,8$ were studied, respectively.
-The special cases $\Phi=\rA_3$ and $\Phi=\rD_\ell$, $\ell\geq 4$ of \cref{tm:lg-principle} are new and have not been known before.
+The assertion of \cref{tm:lg-principle} was known previously in the following two situations:
+\begin{itemize}
+ \item in the case $\Phi=\rA_\ell$, $\ell\geq 4$ it was proved by Tulenbaev, the proof see~\cite[Theorem~2.1]{Tul}
+ \item $\Phi=\rE_\ell$, $\ell=6,7,8$ and the second-named author
+\end{itemize}
+Thus, the special cases $\Phi=\rA_3$ and $\Phi=\rD_\ell$, $\ell\geq 4$ of \cref{tm:lg-principle} are new and have not been known before.
+We also notice that a symplectic counterpart of~\cref{lg-principle} was demonstrated recently by the first-named author.
 
-As a yet another motivation for ??? we mention that a symplectic counterpart of~\cref{lg-principle} was demonstrated by
-the first-named author $\Phi=\rC_\ell$ starting from $\ell\geq 3$.
+On the other hand, the special case 
+includes as a special case both and~\cite[Theorem~2]{SCh} in which
+the cases were studied, respectively.
+
+As a yet another motivation for ??? we mention that
 

### 2016-05-11 paper.tex
More fixes

@@
 
-Centrality of $\Kt$ is a corollary of the following variant of Quillen's local-global principle,
-very much in the same fashion as the normality theorem for the elementary subgroup is a corollary of Quillen's local-global principle for $\Ko$.
+Centrality of $\Kt$ follows the following the following analogue of Quillen's local-global principle,
+very much in the same fashion as the normality theorem for the elementary subgroup follows from Quillen's local-global principle for $\Ko$, cf.~\cite[Theorem~3.1]{Basu05}.
 \begin{tm}[``Quillen's LG-principle for $\Kt$''] \label{tm:lg-principle} 
@@
 Then an element $g\in\St(\Phi,\,R[X])$ satisfying $g(0)=1\in\St(\Phi,\,R)$ is trivial in $\St(\Phi,\,R[X])$
-if and only if the images $\lambda_M^*(g)\in\St(\Phi,\,R_M[X])$ of $g$ under localisation maps $\lambda_M\colonR\to R_M$ are trivial for all maximal ideals $M\trianglelefteq R$. \end{tm}
-For the proof of the claim that \cref{tm:lg-principle} follows from \cref{tm:centrality} we refer the reader to the proof of Theorem~1 in \cite{SCh} which works verbatim in our case.
+if and only if the images $\lambda_M^*(g)\in\St(\Phi,\,R_M[X])$ of $g$ under localisation maps $\lambda_M\colon R\to R_M$ are trivial for all maximal ideals $M\trianglelefteq R$. \end{tm}
+For the proof of the claim that \cref{tm:lg-principle} follows from \cref{tm:centrality} we refer the reader to the proof of Theorem~1 in \cite{SCh} (which works verbatim in our situation).
 
-The assertion of \cref{tm:lg-principle} was known previously in the following two situations:
+\cref{tm:lg-principle} was known previously in the following two special cases.
 \begin{itemize}
- \item in the case $\Phi=\rA_\ell$, $\ell\geq 4$ it was proved by Tulenbaev, the proof see~\cite[Theorem~2.1]{Tul}
- \item $\Phi=\rE_\ell$, $\ell=6,7,8$ and the second-named author
+ \item In the case $\Phi=\rA_\ell$, $\ell\geq 4$ it was proved by Tulenbaev, see~\cite[Theorem~2.1]{Tul}. 
+ \item In the case $\Phi=\rE_\ell$, $\ell=6,7,8$ it was obtained in~\cite{SCh} by the second-named author.
 \end{itemize}
 Thus, the special cases $\Phi=\rA_3$ and $\Phi=\rD_\ell$, $\ell\geq 4$ of \cref{tm:lg-principle} are new and have not been known before.
-We also notice that a symplectic counterpart of~\cref{lg-principle} was demonstrated recently by the first-named author.
 
-On the other hand, the special case 
-includes as a special case both and~\cite[Theorem~2]{SCh} in which
-the cases were studied, respectively.
+Notice that the first-named author has recently established the local-global principle for $\Kt(\rC_\ell, R)$ under the assumption $\ell\geq 3$.
+The main shortcoming of Tulenbaev's proof is that it left the case $\Phi=\rA_3$ unsettled.
 
-As a yet another motivation for ??? we mention that
-
-There are known counterexamples to centrality of $\Kt$ in rank $2$ (see~\cite{W}).
-This shows that our assumption on the rank of $\Phi$ in \cref{tm:lg-principle} is strict.
+Since there are known counterexamples to centrality of $\Kt$ in the rank $2$ case (see~\cite{W}), our assumption on the rank of $\Phi$ in \cref{tm:lg-principle} can not be weakened.
 

### 2016-05-12 paper.tex
Minor fixes

@@
 It is a classical theorem of M.~Kervaire and R.~Steinberg that the stable Steinberg group $\St(R)$ is the universal central extension of $\E(R)$, see \cite[Theorem~III.5.5]{Kbook}.
-The unstable analogue of the ``universality'' part of this theorem is known since 1970's from the works of M.~Stein and W.~van~der~Kallen for $\Phi$ with rank $\ell \geq 5$ (or even $\ell \geq 4$ for $\Phi=\rA_\ell, \rB_\ell, \rC_\ell$), see \cite{St1, KaS}.
+The unstable analogue of the ``universality'' part of this theorem has been known since 1970's for $\Phi$ with of $\ell \geq 5$ (or even $\ell \geq 4$ for $\Phi=\rA_\ell, \rB_\ell, \rC_\ell$), see \cite{St1, KaS}.
 However, until recently, the analogue of the ``centrality'' part was only known in the special case $\Phi=\rA_\ell$, $\ell\geq 3$ see~\cite[Corollary~2]{vdK}.
@@
 
-Centrality of $\Kt$ follows the following the following analogue of Quillen's local-global principle,
-very much in the same fashion as the normality theorem for the elementary subgroup follows from Quillen's local-global principle for $\Ko$, cf.~\cite[Theorem~3.1]{Basu05}.
+Centrality of $\Kt$ is a corollary of the following analogue of Quillen's local-global principle,
+very much in the same fashion as the normality theorem for the elementary subgroup is a corollary of the local-global principle for $\Ko$, cf.~\cite[Theorem~3.1]{Basu05}.
 \begin{tm}[``Quillen's LG-principle for $\Kt$''] \label{tm:lg-principle} 
@@
 if and only if the images $\lambda_M^*(g)\in\St(\Phi,\,R_M[X])$ of $g$ under localisation maps $\lambda_M\colon R\to R_M$ are trivial for all maximal ideals $M\trianglelefteq R$. \end{tm}
-For the proof of the claim that \cref{tm:lg-principle} follows from \cref{tm:centrality} we refer the reader to the proof of Theorem~1 in \cite{SCh} (which works verbatim in our situation).
+For the proof of the claim that \cref{tm:lg-principle} follows from \cref{tm:centrality} we refer the reader to \cite{SCh} (cf. with the proof of Theorem~1 ibid.).
 
-\cref{tm:lg-principle} was known previously in the following two special cases.
-\begin{itemize}
- \item In the case $\Phi=\rA_\ell$, $\ell\geq 4$ it was proved by Tulenbaev, see~\cite[Theorem~2.1]{Tul}. 
- \item In the case $\Phi=\rE_\ell$, $\ell=6,7,8$ it was obtained in~\cite{SCh} by the second-named author.
-\end{itemize}
-Thus, the special cases $\Phi=\rA_3$ and $\Phi=\rD_\ell$, $\ell\geq 4$ of \cref{tm:lg-principle} are new and have not been known before.
-
-Notice that the first-named author has recently established the local-global principle for $\Kt(\rC_\ell, R)$ under the assumption $\ell\geq 3$.
-The main shortcoming of Tulenbaev's proof is that it left the case $\Phi=\rA_3$ unsettled.
-
-Since there are known counterexamples to centrality of $\Kt$ in the rank $2$ case (see~\cite{W}), our assumption on the rank of $\Phi$ in \cref{tm:lg-principle} can not be weakened.
-
-Compare \cref{tm:lg-principle} with the local-global principle for $\Ko$ which states that an element of the congruence subgroup $g\in \GG(\Phi,\,R[X], XR[X])$ is elementary
-(i.\,e. lies in $\E(\Phi, R[X])$) if and only if $g_M=1\in\E(\Phi,\,R_M)$ for all maximal ideals $M \trianglelefteq R$.
-
-Our proof of \cref{tm:lg-principle} is similar to that of \cite[Theorem~1]{SCh}.
-Using the same patching technique we reduce the problem to the case $\Phi=\rA_3$.
-Then, using a new presentation of the relative Steinberg group $\St(4, R, I)$ we reprove Tulenbaev's key lemma (cf. \cite[Lemma~2.3]{Tul}) in the rank $3$ case.
+In the special case $\Phi=\rA_\ell$, $\ell\geq 4$ the assertion of \cref{tm:lg-principle} was obtained by Tulenbaev, see~\cite[Theorem~2.1]{Tul}.
+Despite the fact that the key ingredient in Tulenbaev's proof (``another presentation'' of the Steinberg group) is available for $\Phi=\rA_3$, Tulenbaev's proof does not work in this case for technical reasons.
+On the other hand, in~\cite{SCh} the second-named author developed a patching technique which allowed him to deduce \cref{tm:lg-principle} from Tulenbaev's result in another special case $\Phi=\rE_\ell$, $\ell=6,7,8$.
+Thus, \cref{tm:lg-principle} contains two cases that have not been previously known: $\Phi=\rA_3$ and $\Phi=\rD_\ell$, $\ell\geq 4$.
+We also note that recently the first-named author has obtained an analogue of \cref{tm:lg-principle} for $\Kt(\rC_\ell, R)$ under the assumption $\ell\geq 3$.
 
 The rest of the paper is organised as follows. 
-In \cref{sec:yap} we describe a new symmetric presentation for the relative Steinberg group of rank $3$.
-This presentation is then used in~\cref{sec:lgp} to establish the particular case $\Phi=\rA_3$ of \cref{tm:lg-principle}.
+In \cref{sec:patching} we explain how \cref{tm:lg-principle} can be reduced to its own special case $\Phi=\rA_3$ by means of the patching technique of~\cite{SCh}.
+Next, in \cref{sec:yap} we describe a new ``transpose-symmetric'' presentation for the relative linear Steinberg group. 
+Finally, we use this presentation in~\cref{sec:lgp} where we prove \cref{tm:lg-principle} in the case $\Phi=\rA_3$.
 %It mimics the standart vector representation of $\SL(n,\,R)$, therefore in the first section we use representations and corresponding vector notation. 
-Finally, in \cref{sec:patching} we derive our principal results from this special case and the amalgamation theorem for relative Steinberg groups from~\cite{SCh}.
+%Finally, in \cref{sec:patching} we derive our principal results from this special case and the amalgamation theorem for relative Steinberg groups from~\cite{SCh}.
 %There we switch to the root notation.
@@
 
-\section{Yet another presentation for the relative Steinberg group.} \label{sec:yap}
+\section{Main reduction} \label{sec:patching}
 The key ingredient in Tulenbaev's proof of the local-global principle is the construction of the homomorphism $T$ which fits into the following commutative diagram.
@@
 %of $\mathrm K_2(\mathrm D_l,\,R)$ we need such a map for $n=4$ (i.e., for the group of type $\mathrm A_3$).
+
+%Since there are known counterexamples to centrality of $\Kt$ and, thus, to \cref{tm:lg-principle} for $\Phi$ of rank $2$ (see~\cite{W}), 
+%this gives a complete answer to the question for which $\ell$ the local-global principle holds for $\Kt(\rC_\ell, R)$.
+
+%The main idea of our proof of~\cref{tm:lg-principle} is to first settle the case $\Phi=\rA_3$ and then derive the other cases from it using the patching technique of~\cite{SCh}.
+
+%Compare \cref{tm:lg-principle} with the local-global principle for $\Ko$ which states that an element of the congruence subgroup $g\in \GG(\Phi,\,R[X], XR[X])$ is elementary
+%(i.\,e. lies in $\E(\Phi, R[X])$) if and only if $\lambda_M^*(g)=1\in\E(\Phi,\,R_M[X])$ for all maximal ideals $M \trianglelefteq R$.
+
+\section{Yet another presentation for the relative Steinberg group.} \label{sec:yap}
 

### 2016-05-12 paper.tex
Minor fixes

@@
 \DeclareRobustCommand{\VAN}[2]{#1}
+\newcommand{\eval}[4]{ev_{\scriptstyle \left[\frac{#2[#1] \rightarrow #3}{#1 \mapsto #4}\right]}}
+\newcommand{\ev}[3]{\eval{t}{#1}{#2}{#3}}
 
@@
 if and only if the images $\lambda_M^*(g)\in\St(\Phi,\,R_M[X])$ of $g$ under localisation maps $\lambda_M\colon R\to R_M$ are trivial for all maximal ideals $M\trianglelefteq R$. \end{tm}
-For the proof of the claim that \cref{tm:lg-principle} follows from \cref{tm:centrality} we refer the reader to \cite{SCh} (cf. with the proof of Theorem~1 ibid.).
 
@@
 The rest of the paper is organised as follows. 
-In \cref{sec:patching} we explain how \cref{tm:lg-principle} can be reduced to its own special case $\Phi=\rA_3$ by means of the patching technique of~\cite{SCh}.
+After introducing the preliminaries we explain in \cref{sec:patching} how the patching technique of~\cite{SCh} allows one to reduce \cref{tm:lg-principle} to the special case $\Phi=\rA_3$.
 Next, in \cref{sec:yap} we describe a new ``transpose-symmetric'' presentation for the relative linear Steinberg group.
-Finally, we use this presentation in~\cref{sec:lgp} where we prove \cref{tm:lg-principle} in the case $\Phi=\rA_3$.
+Finally, this presentation is used in~\cref{sec:lgp} to prove \cref{tm:lg-principle} in the case $\Phi=\rA_3$.
 %It mimics the standart vector representation of $\SL(n,\,R)$, therefore in the first section we use representations and corresponding vector notation. 
@@
 $$\xymatrix{0\ar@<0.1ex>[r]^{}&I\ar@<0.1ex>[r]^{}&R\ar@<0.5ex>[r]^{\pi}&R/I\ar@<0.5ex>[l]^{\sigma}\ar@<0.1ex>[r]^{}&0}$$
-For a splitting ideal $I\trianglelefteq R$ the \emph{relative Steinberg group} $\St(n,\,R,\,I) = \St(\rA_{n-1}, R, I)$ can be defined as the kernel $\Ker\big(\St(n,\,R)\epi\St(n,\,R/I)\big)$.
+For a splitting ideal $I\trianglelefteq R$ the \emph{relative Steinberg group} $\St(\Phi, R, I)$ can be defined as the kernel $\Ker\big(\St(\Phi,\,R)\epi\St(\Phi,\,R/I)\big)$.
 
@@
 \section{Main reduction} \label{sec:patching}
-The key ingredient in Tulenbaev's proof of the local-global principle is the construction of the homomorphism $T$ which fits into the following commutative diagram.
+First of all, we remind the reader the way how \cref{tm:lg-principle} is proved in~\cite{Tul,SCh}.
+
+\begin{df}
+We say that the Steinberg group functor $\St(\Phi, -)$ satisfies {\it Tulenbaev lifting property} if for any ring $R$ and any non-nilpotent element $a \in R$
+there exists a map $T$ which fits into the following commutative diagram.
 \numberwithin{equation}{section}
-\begin{equation} \xymatrix{\St(n,\,R\ltimes XR_a[X],\,XR_a[X]) \ar@{^{(}->}[r] \ar[d]_-{\lambda_a^*} & \St(n, R \ltimes XR_a[X]) \ar[d]_-{\lambda_a^*} \\
-             \St(n,\,R_a[X],\,XR_a[X]) \ar@{-->}[ru]_-{T} \ar@{^{(}->}[r] & \St(n, R_a[X])} \label{eq:diagram} \end{equation}
-Here $n\geq5$, $a$ denotes an arbitrary non-nilpotent element of $R$ and $\lambda_a^*$ is the morphism of Steinberg groups induced by the morphism 
-$\lambda_a\colon R \to R_a$ of localisation by the powers of $a$.
+\setcounter{equation}{1}
+\begin{equation} \xymatrix{\St(\Phi,\,R\ltimes XR_a[X],\,XR_a[X]) \ar@{^{(}->}[r] \ar[d]_-{\lambda_a^*} & \St(\Phi, R \ltimes XR_a[X]) \ar[d]_-{\lambda_a^*} \\
+                           \St(\Phi,\,R_a[X],\,XR_a[X]) \ar@{-->}[ru]_-{T} \ar@{^{(}->}[r] & \St(\Phi, R_a[X])} \label{eq:diagram} \end{equation}
+Here $\lambda_a^*$ denotes the morphism of Steinberg groups induced by the morphism $\lambda_a\colon R \to R_a$ of localisation by the powers of $a$.                           
 Notice that $XR_a[X]$ is a splitting ideal for both $R_a[X]$ and $R \ltimes XR_a[X]$.
-It is clear that the image of $T$ is contained in the image of the top arrow, therefore the relative Steinberg groups in the left-hand side of the diagram are isomoprhic.
+\end{df}
+It is clear that the image of $T$ is contained in the image of the top arrow, therefore, Tulenbaev lifting property implies that the relative Steinberg groups in the left-hand side of the diagram are isomoprhic.
+
+We claim that the main results of the paper follow from Tulenbaev's lifting property.
+\begin{prop} Consider the following statements.
+\begin{enumerate}
+ \item The Steinberg group functor $\St(\Phi, -)$ satisfies Tulenbaev lifting property;
+ \item A dilation principle holds for $\St(\Phi, -)$, i.\,e. if $g\in\St(\Phi, A[X], XA[X])$ is such that $\lambda_a^*(h) = 1 \in \St(\Phi, R_a[X])$ then
+       for sufficiently large $n$ one has $ev_{X = a^n Y}^*(h) = 1 \in \St(\Phi, A[Y])$, where $ev_{X=a^n Y}$ denotes the unique $R$-algebra morphism $R[X]\to R[Y]$ sending $X$ to $a^nY$;
+ \item A local global principle for $\Kt$ holds for $\St(\Phi, -)$;
+ \item Centrality of $\Kt$ holds for $\St(\Phi, -)$.
+\end{enumerate}
+Then for any irreducible $\Phi$ of rank $\geq 2$ there are implications $a) \implies b) \implies c) \implies d)$. \end{prop}
+\begin{proof} The specified implications are contained in the proofs of Lemma~15, Theorem~2 and Theorem~1 of \cite{SCh}, respectively. \end{proof}
+
+We now discuss how Tulenbaev's lifting property is proved.
+
 %This $T$ is an inverse to a map induced by localisation, so that constructing $\mathrm T$ may be treated
@@
 Now we turn to the main result of this paper, namely, we construct for $n\geq 4$ the map $$T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X]),$$ that fits into the diagram \eqref{eq:diagram}.
-The local-global principle for the Steinberg group and centrality of $\mathrm K_2$ will formally follow from the existence of this map, see~\cite[Lemmas~15--16, and the proof of Theorem~2]{SCh}.
+BLAH-BLAH-BLAH
 

### 2016-05-12 paper.tex
Minor fixes

@@
 \DeclareRobustCommand{\VAN}[2]{#1}
-\newcommand{\eval}[4]{ev_{\scriptstyle \left[\frac{#2[#1] \rightarrow #3}{#1 \mapsto #4}\right]}}
-\newcommand{\ev}[3]{\eval{t}{#1}{#2}{#3}}
+\newcommand{\catname}[1]{{\normalfont\textbf{#1}}}
 
@@
 By definition, the Steinberg group $\St(\Phi, R)$ is presented by generators $x_\alpha(\xi)$, which model the unipotents $t_\alpha(\xi)$, and Steinberg relations (see~\cref{sec:prelim}). 
-Thus, there is a well-defined map $\phi\colon\St(\Phi, R)\twoheadrightarrow \GG(\Phi, R)$ sending $x_\alpha(\xi)$ to $t_\alpha(\xi)$ whose image is $\E(\Phi, R)$.
+Thus, there is a well-defined map $\phi\colon\St(\Phi, R)\to \GG(\Phi, R)$ sending $x_\alpha(\xi)$ to $t_\alpha(\xi)$ whose image is $\E(\Phi, R)$.
 
@@
 \section{Main reduction} \label{sec:patching}
-First of all, we remind the reader the way how \cref{tm:lg-principle} is proved in~\cite{Tul,SCh}.
+First of all, we recall how \cref{tm:lg-principle} is proved in~\cite{Tul,SCh}.
 
@@
 We claim that the main results of the paper follow from Tulenbaev's lifting property.
-\begin{prop} Consider the following statements.
+\begin{prop} Consider the following statements:
 \begin{enumerate}
- \item The Steinberg group functor $\St(\Phi, -)$ satisfies Tulenbaev lifting property;
- \item A dilation principle holds for $\St(\Phi, -)$, i.\,e. if $g\in\St(\Phi, A[X], XA[X])$ is such that $\lambda_a^*(h) = 1 \in \St(\Phi, R_a[X])$ then
+ \item the Steinberg group functor $\St(\Phi, -)$ satisfies lifting property~\eqref{eq:diagram};
+ \item a dilation principle holds for $\St(\Phi, -)$, i.\,e. if $g\in\St(\Phi, A[X], XA[X])$ is such that $\lambda_a^*(h) = 1 \in \St(\Phi, R_a[X])$ then
        for sufficiently large $n$ one has $ev_{X = a^n Y}^*(h) = 1 \in \St(\Phi, A[Y])$, where $ev_{X=a^n Y}$ denotes the unique $R$-algebra morphism $R[X]\to R[Y]$ sending $X$ to $a^nY$;
- \item A local global principle for $\Kt$ holds for $\St(\Phi, -)$;
- \item Centrality of $\Kt$ holds for $\St(\Phi, -)$.
+ \item a local global principle for $\Kt$ holds for $\St(\Phi, -)$;
+ \item centrality of $\Kt$ holds for $\St(\Phi, -)$.
 \end{enumerate}
@@
 
-We now discuss how Tulenbaev's lifting property is proved.
+In order to check the lifting property~\eqref{eq:diagram} one needs to have some description of the relative Steinberg group $\St(\Phi, R, I)$ by means of generators and relations.
+In~\cite{Tul} another presentation was used for this purpose. We recall the details of this presentation in the next section.
+On the other hand, in~\cite{SCh} the second-named author used an amalgamation theorem for the relative Steinberg group on which we now focus our attention.
+
+For a simply laced root system $\Phi$ we denote by $\catname{Subsys}(\Phi)$ the category of root subsystems of $\Phi$.
+Its objects are all root subsystems $\Psi\subseteq \Phi$ and its morphisms are in one-to-one correspondence with inclusions of the form $\Psi_1\subseteq \Psi_2$.
+
+We denote by $\mathcal{G}_{1,n}$ the full subcategory of $\catname{Subsys}(\Phi)$ whose objects are exactly root subsystems of type $\rA_1$ or $\rA_n$. 
+It is easy to see that $\mathcal{G}_{1,n}$ is a directed bipartite graph whose only nonidentical morphisms are inclusions of the form $\{\alpha, -\alpha\} \subseteq \Psi \cong \rA_3$, $\Psi \subseteq \Phi$.
+Now we able to formulate the amalgamation theorem~\cite[Theorem~9]{SCh}.
+\begin{tm*} \label{tm:relPres} The group $\St(\Phi, R, I)$ is isomorphic to $G:=\varinjlim_{\mathcal{G}_{1,3}}\St(-, R, I)$ as an abstract group. \end{tm*}
 

### 2016-05-12 paper.tex
Many fixes

@@
 Recall that to each reduced irreducible root system $\Phi$ and a commutative ring $R$ one can associate a split simple group $\GG(\Phi, R)$ called a \emph{Chevalley group}.
-The {\it elementary group} $\E(\Phi, R)$ is defined as the subgroup of $\GG(\Phi, R)$ generated by elementary root unipotents $t_\alpha(\xi)$, $\xi\in R$, $\alpha\in \Phi$.
+The {\it elementary group} $\E(\Phi, R)$ is defined as the subgroup of $\GG(\Phi, R)$ generated by elementary root unipotents $t_\alpha(\xi)$, $\xi\in R$, $\alpha\in \Phi$, see~\cite{Ta, St78}.
 By definition, the Steinberg group $\St(\Phi, R)$ is presented by generators $x_\alpha(\xi)$, which model the unipotents $t_\alpha(\xi)$, and Steinberg relations (see~\cref{sec:prelim}). 
@@
 All commutators are left-normed, i.\,e. $[x,\,y]=xyx\inv y\inv$. 
+We denote by $R^n$ the free $R$-module with basis $e_1,\ldots,e_n$ and by $\Um(n,\,R)$ the subset of unimodular columns $v\in R^n$ 
+whose entries generate $R$ as an ideal.
 
@@
 
-We denote by $R^n$ the free $R$-module with basis $e_1,\ldots,e_n$ and by $\Um(n,\,R)$ the subset of unimodular columns $v\in R^n$ 
-whose entries generate $R$ as an ideal.
-
-As usual, $\E(n, R)=\E(\rA_{n-1}, R)$ denotes the elementary group, i.\,e. the subgroup of the general linear group $\GL(n, R)$ generated by transvections
-$t_{ij}(r)=1+r \cdot e_{ij}$, $1\leq i\neq j\leq n$, $r\in R$,
-where 1 stands for the identity matrix and $e_{ij}$ for the matrix unit.
-
-The Steinberg group $\St(n, R) = \St(\rA_{n-1}, R)$ is the group defined by generators
-$x_{ij}(r)$, $1\leq i\neq j\leq n$, $r\in R\}$ and relations
+First of all, recall that for a simply laced root system $\Phi$ of rank $\geq 2$ the Steinberg group $\St(\Phi, R)$ 
+is defined by generators $x_\alpha(r)$, $\alpha\in\Phi$, $r\in R$ and the following relations:
+\begin{align}
+ x_\alpha(r) x_\alpha(s) & = x_\alpha(r+s) & \nonumber \\
+ [x_\alpha(r),  x_\beta(s)] & = x_{\alpha+\beta}(N_{\alpha,\beta} rs) &\ \alpha,\beta\in \Phi,\ \alpha+\beta\in\Phi \nonumber \\
+ [x_\alpha(r),  x_\beta(s)] & = 1 &\ \alpha,\beta\in \Phi,\ \alpha+\beta\not\in\Phi \nonumber
+\end{align}
+Here $N_{\alpha,\beta}$ are the structure constants of $\Phi$ which are equal to $\pm 1$.
+In the case $\Phi=\rA_\ell$ we use a more common notation for root unipotents: $x_{ij}(r)$, $1\leq i\neq j\leq n$, $r\in R$,
 \setcounter{equation}{0}
@@
 \begin{align}
-&x_{ij}(r)x_{ij}(s)=x_{ij}(r+s), \label{add0}\\
-&[x_{ij}(r),\,x_{hk}(s)]=1,\text{ for }h\neq j,\ k\neq i, \label{ccf1}\\
-&[x_{ij}(r),\,x_{jk}(s)]=x_{ik}(rs) \label{ccf2}.
+x_{ij}(r)x_{ij}(s)      & = x_{ij}(r+s),& \label{add0}\\
+[x_{ij}(r),\,x_{hk}(s)] & = 1,& \text{ for }h\neq j,\ k\neq i, \label{ccf1}\\
+[x_{ij}(r),\,x_{jk}(s)] & = x_{ik}(rs)& \label{ccf2}.
 \end{align}
-The natural projection $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ sends $x_{ij}(r)$ to $t_{ij}(r)$.
+We denote by $\E(n, R)=\E(\rA_{n-1}, R)$ the elementary subgroup of $\SL(n, R)$, i.\,e.
+the subgroup generated by elementary transvections $t_{ij}(r)=1+r \cdot e_{ij}$, $1\leq i\neq j\leq n$, $r\in R$.
+Here $1$ denotes the identity matrix and $e_{ij}$ is the standard matrix unit. The natural projection $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ sends $x_{ij}(r)$ to $t_{ij}(r)$.
 
@@
 
-For a general $I$ the relative Steinberg group $\St(\Phi, R, I)$ is no more a subgroup of $\St(\Phi, R)$ and should be defined as a central extension of the above kernel.
+For arbitrary $I$ the relative Steinberg group $\St(\Phi, R, I)$ is no more a subgroup of $\St(\Phi, R)$ and should be defined as a central extension of the above kernel.
 For the purposes of the present text it suffices to consider only relative Steinberg groups corresponding to splitting ideals.
@@
 
-\section{Main reduction} \label{sec:patching}
-First of all, we recall how \cref{tm:lg-principle} is proved in~\cite{Tul,SCh}.
+\section{Reduction to the case \texorpdfstring{$\rA_3$}{A3}} \label{sec:patching}
+First, we make the following definition inspired by Lemmas~2.3,~3.2 of~\cite{Tul}.
 
-\begin{df}
+\begin{df} \label{df:tlp}
 We say that the Steinberg group functor $\St(\Phi, -)$ satisfies {\it Tulenbaev lifting property} if for any ring $R$ and any non-nilpotent element $a \in R$
-there exists a map $T$ which fits into the following commutative diagram.
+there exists a map $T_\Phi$ which fits into the following commutative diagram.
 \numberwithin{equation}{section}
@@
 \begin{equation} \xymatrix{\St(\Phi,\,R\ltimes XR_a[X],\,XR_a[X]) \ar@{^{(}->}[r] \ar[d]_-{\lambda_a^*} & \St(\Phi, R \ltimes XR_a[X]) \ar[d]_-{\lambda_a^*} \\
-                           \St(\Phi,\,R_a[X],\,XR_a[X]) \ar@{-->}[ru]_-{T} \ar@{^{(}->}[r] & \St(\Phi, R_a[X])} \label{eq:diagram} \end{equation}
+                           \St(\Phi,\,R_a[X],\,XR_a[X]) \ar@{-->}[ru]_-{T_\Phi} \ar@{^{(}->}[r] & \St(\Phi, R_a[X])} \label{eq:diagram} \end{equation}
 Here $\lambda_a^*$ denotes the morphism of Steinberg groups induced by the morphism $\lambda_a\colon R \to R_a$ of localisation by the powers of $a$.                           
@@
 \end{df}
-It is clear that the image of $T$ is contained in the image of the top arrow, therefore, Tulenbaev lifting property implies that the relative Steinberg groups in the left-hand side of the diagram are isomoprhic.
+It is clear that the image of $T_\Phi$ is contained in the image of the top arrow, therefore, Tulenbaev lifting property implies that the relative Steinberg groups in the left-hand side of the diagram are isomoprhic.
 
-We claim that the main results of the paper follow from Tulenbaev's lifting property.
+We claim that the main results of this paper follow from Tulenbaev's lifting property.
 \begin{prop} Consider the following statements:
@@
        for sufficiently large $n$ one has $ev_{X = a^n Y}^*(h) = 1 \in \St(\Phi, A[Y])$, where $ev_{X=a^n Y}$ denotes the unique $R$-algebra morphism $R[X]\to R[Y]$ sending $X$ to $a^nY$;
- \item a local global principle for $\Kt$ holds for $\St(\Phi, -)$;
- \item centrality of $\Kt$ holds for $\St(\Phi, -)$.
+ \item Quillen's local global principle for $\Kt$ holds for $\St(\Phi, -)$;
+ \item the centrality of $\Kt$ holds for $\St(\Phi, -)$.
 \end{enumerate}
@@
 
-In order to check the lifting property~\eqref{eq:diagram} one needs to have some description of the relative Steinberg group $\St(\Phi, R, I)$ by means of generators and relations.
-In~\cite{Tul} another presentation was used for this purpose. We recall the details of this presentation in the next section.
-On the other hand, in~\cite{SCh} the second-named author used an amalgamation theorem for the relative Steinberg group on which we now focus our attention.
+In order to construct the arrow $T_\Phi$ fitting in the diagram~\eqref{eq:diagram} one needs to have some direct description of the relative Steinberg group $\St(\Phi, R, I)$.
+For example, in~\cite{Tul} Tulenbaev uses a variant of of W.~van~der~Kallen's ``another presentation'' for this purpose. The details of this approach are outlined in the next section.
+On the other hand, in~\cite{SCh} the second-named author obtained a theorem which asserts that the relative Steinberg group $\St(\Phi, R, I)$ can be presented as an amalgamated product of
+several copies of relative Steinberg groups of smaller rank.
 
+To formulate this theorem we will need several technical definitions.
 For a simply laced root system $\Phi$ we denote by $\catname{Subsys}(\Phi)$ the category of root subsystems of $\Phi$.
 Its objects are all root subsystems $\Psi\subseteq \Phi$ and its morphisms are in one-to-one correspondence with inclusions of the form $\Psi_1\subseteq \Psi_2$.
+It is clear that the relative Steinberg group can be turned into a functor $\St(-, R, I)\colon \catname{Subsys}(\Phi) \rightarrow\catname{Groups}.$
 
-We denote by $\mathcal{G}_{1,n}$ the full subcategory of $\catname{Subsys}(\Phi)$ whose objects are exactly root subsystems of type $\rA_1$ or $\rA_n$. 
-It is easy to see that $\mathcal{G}_{1,n}$ is a directed bipartite graph whose only nonidentical morphisms are inclusions of the form $\{\alpha, -\alpha\} \subseteq \Psi \cong \rA_3$, $\Psi \subseteq \Phi$.
-Now we able to formulate the amalgamation theorem~\cite[Theorem~9]{SCh}.
-\begin{tm*} \label{tm:relPres} The group $\St(\Phi, R, I)$ is isomorphic to $G:=\varinjlim_{\mathcal{G}_{1,3}}\St(-, R, I)$ as an abstract group. \end{tm*}
+We denote by $\mathcal{G}_{1,n}$ the full subcategory of $\catname{Subsys}(\Phi)$ whose objects are root subsystems $\Psi\subseteq \Phi$ having type $\rA_1$ or $\rA_n$. 
+It is easy to see that $\mathcal{G}_{1,n}$ is a directed bipartite graph whose only nonidentical morphisms are inclusions of the form $i_{\alpha, \Psi}\colon \{\alpha, -\alpha\} \subseteq \Psi \cong \rA_3$, $\Psi \subseteq \Phi$.
+\begin{tm*} \label{tm:relPres} For a simply laced irreducible root system $\Phi$ of rank $\geq 3$
+the group $\St(\Phi, R, I)$ is isomorphic as an abstract group to $\varinjlim_{\mathcal{G}_{1,3}}\St(-, R, I)$. \end{tm*}
+\begin{proof} See~\cite[Theorem~9]{SCh} \end{proof}
+
+The above theorem allows one to construct the arrow $T_\Phi$ by means of the universal property of colimits.
+More precisely, one needs to construct the maps $T_{\Psi}$ for subsystems $\Psi\subseteq\Phi$ of type $\rA_3$ and then check that
+relations $T_\Psi \circ i_{\alpha, \Psi} = T_{\Psi'} \circ i_{\alpha, \Psi'}$ hold for all $\Psi$, $\Psi'$ of type $\rA_3$ containing a common root $\alpha$
+(here $i_{\alpha, \Psi}$ denotes the obvious morphism $\St(\{\alpha, -\alpha\}, R, I) \to \St(\Psi, R, I)$).
+The latter check is relatively formal and, essentially, has already been made in~\cite{SCh} 
+(see the proof of Lemma~14 and notice that everywhere in it $\rA_4$'s can be replaced with $\rA_3$'s).
+On the other hand, constructing $T_\Psi$ for $\Psi=\rA_3$ is not at all obvious and will be done in the section to follow.
+
+Summing up the above discussion, we have shown that both \cref{tm:centrality} and \cref{tm:lg-principle} follow from Tulenbaev's lifting property in the special case $\Phi=\rA_3$.
 
@@
 For a splitting ideal $I$ and $n\geq 4$ the group $\St(n,\,R,\,I)$ is isomorphic to the group defined by generators
-$$\{X(u,\,v)\mid u\in\E(n,\,R)e_1,\ v\in I^n,\ u^tv=0\}$$ and the following set of relations
+$$\{X(u,\,v)\mid u\in\E(n,\,R)e_1,\ v\in I^n,\ u^tv=0\}$$ and the following set of relations:
 \setcounter{equation}{0}
@@
 After applying additivity relations \eqref{add2}, \eqref{add3} and moving the factor $X(e_i, -\xi' e_j)$ to the left hand side of the formula by means of relation \eqref{conj2}
-one gets the following expression
+one gets the following expression:
 $$(X(e_j, \eta'e_k) \cdot X(e_i, (\xi' \eta' + \pi(\xi)\eta' + \pi(\eta)\xi')e_k \cdot X(e_j, -\eta'e_k),\ x_{ik}(\pi(\xi\eta)).$$
@@
 On the other hand, $\kappa$ is surjective by Lemma~\ref{allyouneedisf}\,$(\mathrm a)$.
-Thus, we have the following result.
+Thus, we have demonstrated the following result.
 
@@
 
-\section{The local-global principle for $\Kt$.} \label{sec:lgp}
+\section{The local-global principle for \texorpdfstring{$\Kt$}{K2}}\label{sec:lgp}
 %At this point we have demonstrated for $n\geq4$ and a splitting ideal $I$ that $\St^*(n,\,R,\,I)$ and $\St(n,\,R,\,I)$ are isomorphic.
 Now we turn to the main result of this paper, namely, we construct for $n\geq 4$ the map $$T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X]),$$ that fits into the diagram \eqref{eq:diagram}.
-BLAH-BLAH-BLAH
 

### 2016-05-13 paper.tex
Fixed many typos

@@
 It is a classical theorem of M.~Kervaire and R.~Steinberg that the stable Steinberg group $\St(R)$ is the universal central extension of $\E(R)$, see \cite[Theorem~III.5.5]{Kbook}.
-The unstable analogue of the ``universality'' part of this theorem has been known since 1970's for $\Phi$ with of $\ell \geq 5$ (or even $\ell \geq 4$ for $\Phi=\rA_\ell, \rB_\ell, \rC_\ell$), see \cite{St1, KaS}.
+The unstable analogue of the ``universality'' part of this theorem has been known since 1970's for $\Phi$ with rank $\ell \geq 5$ (or even $\ell \geq 4$ for $\Phi=\rA_\ell, \rB_\ell, \rC_\ell$), see \cite{St1, KaS}.
 However, until recently, the analogue of the ``centrality'' part was only known in the special case $\Phi=\rA_\ell$, $\ell\geq 3$ see~\cite[Corollary~2]{vdK}.
@@
 
-Now consider the case $j=h$, $i\neq k$
+Now consider the case $j=h$, $i\neq k$.
 By~\cite[3.12]{vdK} one has $$g\,x(u,\,u_{ij}ac_{ij})g\inv=x(\phi(g)u,\,\phi(g)^*u_{ij}ac_{ij}).$$
@@
 \label{yproperties}
-For $u$, $u'$, $w$ and $v\in B^n$, such that $u$ and $u'$ have decomposition as in above definition, $w^tv=0$, $a$, $b\in I(v)$, $c\in B$, $g\in\St(n,\,B)$ holds
+For $u$, $u'$, $w$ and $v\in B^n$, such that $u$ and $u'$ have decomposition as in the above definition, $w^tv=0$, $a$, $b\in I(v)$, $c\in B$, $g\in\St(n,\,B)$ one has
 \begin{enumerate}

### 2016-05-15 paper.tex
Fixes after 1st part of discussion

@@
 \newcommand{\E}{{\mathrm{E}}}
-\newcommand{\GG}{{\mathrm{G}}}
+\newcommand{\GG}{{\mathrm{G}_{sc}}}
 \newcommand{\Um}{\mathop{\mathrm{Um}}\nolimits}
@@
 \date {\today}
-\thanks{Authors of the present paper acknowledge the financial support from Russian Science Foundation grant 14-11-00297}
+\thanks{The authors of the present paper acknowledge the financial support from Russian Science Foundation grant 14-11-00297}
 
@@
 
-\begin{abstract} We give a short uniform proof of centrality of $\mathrm K_2(\Phi, R)$ for all simply-laced root systems $\Phi$ of rank $\geq 3$.
+\begin{abstract} We give a short uniform proof of centrality of $\Kt(\Phi, R)$ for all simply-laced root systems $\Phi$ of rank $\geq 3$.
 \end{abstract}
@@
 
-Recall that to each reduced irreducible root system $\Phi$ and a commutative ring $R$ one can associate a split simple group $\GG(\Phi, R)$ called a \emph{Chevalley group}.
+Recall that to each reduced irreducible root system $\Phi$ and a commutative ring $R$ one can associate a split simple simply-connected group $\GG(\Phi, R)$ called a \emph{Chevalley group}.
 The {\it elementary group} $\E(\Phi, R)$ is defined as the subgroup of $\GG(\Phi, R)$ generated by elementary root unipotents $t_\alpha(\xi)$, $\xi\in R$, $\alpha\in \Phi$, see~\cite{Ta, St78}.
@@
 It is a classical theorem of M.~Kervaire and R.~Steinberg that the stable Steinberg group $\St(R)$ is the universal central extension of $\E(R)$, see \cite[Theorem~III.5.5]{Kbook}.
-The unstable analogue of the ``universality'' part of this theorem has been known since 1970's for $\Phi$ with rank $\ell \geq 5$ (or even $\ell \geq 4$ for $\Phi=\rA_\ell, \rB_\ell, \rC_\ell$), see \cite{St1, KaS}.
+The unstable analogue of the ``universality'' part of this theorem has been known since 1970's for $\Phi$ of rank $\ell \geq 5$ (or even $\ell \geq 4$ for $\Phi=\rA_\ell, \rB_\ell, \rC_\ell$), see \cite{St1, KaS}.
 However, until recently, the analogue of the ``centrality'' part was only known in the special case $\Phi=\rA_\ell$, $\ell\geq 3$ see~\cite[Corollary~2]{vdK}.
@@
 Thus, \cref{tm:lg-principle} contains two cases that have not been previously known: $\Phi=\rA_3$ and $\Phi=\rD_\ell$, $\ell\geq 4$.
-We also note that recently the first-named author has obtained an analogue of \cref{tm:lg-principle} for $\Kt(\rC_\ell, R)$ under the assumption $\ell\geq 3$.
+We also note that recently the first-named author has obtained an analogue of \cref{tm:lg-principle} for $\Kt(\rC_\ell, R)$ under the assumption $\ell\geq 3$, see~\cite{Lav2}.
 
-The rest of the paper is organised as follows. 
+The paper is organised as follows. 
 After introducing the preliminaries we explain in \cref{sec:patching} how the patching technique of~\cite{SCh} allows one to reduce \cref{tm:lg-principle} to the special case $\Phi=\rA_3$.
@@
 All commutators are left-normed, i.\,e. $[x,\,y]=xyx\inv y\inv$. 
-We denote by $R^n$ the free $R$-module with basis $e_1,\ldots,e_n$ and by $\Um(n,\,R)$ the subset of unimodular columns $v\in R^n$ 
-whose entries generate $R$ as an ideal.
+We denote by $R^n$ the free $R$-module with a basis $e_1,\ldots,e_n$ and by $\Um(n,\,R)$ the subset of unimodular columns $v\in R^n$, i.\,e. 
+columns whose entries generate $R$ as an ideal.
 
@@
 \begin{align}
- x_\alpha(r) x_\alpha(s) & = x_\alpha(r+s) & \nonumber \\
- [x_\alpha(r),  x_\beta(s)] & = x_{\alpha+\beta}(N_{\alpha,\beta} rs) &\ \alpha,\beta\in \Phi,\ \alpha+\beta\in\Phi \nonumber \\
- [x_\alpha(r),  x_\beta(s)] & = 1 &\ \alpha,\beta\in \Phi,\ \alpha+\beta\not\in\Phi \nonumber
+ x_\alpha(r) x_\alpha(s) & = x_\alpha(r+s), & \nonumber \\
+ [x_\alpha(r),  x_\beta(s)] & = x_{\alpha+\beta}(N_{\alpha,\beta} rs), &\ \alpha,\beta\in \Phi,\ \alpha+\beta\in\Phi, \nonumber \\
+ [x_\alpha(r),  x_\beta(s)] & = 1, &\ \alpha,\beta\in \Phi,\ \alpha+\beta\not\in\Phi. \nonumber
 \end{align}
@@
 [x_{ij}(r),\,x_{hk}(s)] & = 1,& \text{ for }h\neq j,\ k\neq i, \label{ccf1}\\
-[x_{ij}(r),\,x_{jk}(s)] & = x_{ik}(rs)& \label{ccf2}.
+[x_{ij}(r),\,x_{jk}(s)] & = x_{ik}(rs).& \label{ccf2}
 \end{align}
-We denote by $\E(n, R)=\E(\rA_{n-1}, R)$ the elementary subgroup of $\SL(n, R)$, i.\,e.
-the subgroup generated by elementary transvections $t_{ij}(r)=1+r \cdot e_{ij}$, $1\leq i\neq j\leq n$, $r\in R$.
+In the case $\Phi=\rA_\ell$ the elementary root unipotents $t_\alpha(r)$ are exactly the elementary transvections $t_{ij}(r)=1+r \cdot e_{ij}$, $1\leq i\neq j\leq n$, $r\in R$
+and the elementary subgroup $\E(\rA_{n-1}, R)$ is also denoted by $\E(n, R)$.
 Here $1$ denotes the identity matrix and $e_{ij}$ is the standard matrix unit. The natural projection $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ sends $x_{ij}(r)$ to $t_{ij}(r)$.
@@
                            \St(\Phi,\,R_a[X],\,XR_a[X]) \ar@{-->}[ru]_-{T_\Phi} \ar@{^{(}->}[r] & \St(\Phi, R_a[X])} \label{eq:diagram} \end{equation}
-Here $\lambda_a^*$ denotes the morphism of Steinberg groups induced by the morphism $\lambda_a\colon R \to R_a$ of localisation by the powers of $a$.                           
+Here $R\ltimes XR_a[X]$ denotes the semidirect product of the ring $R$ and the $R$-algebra $XR_a[X]$ (see~e.\,g.~\cite[Definition~3.2]{SCh}), $\lambda_a^*$ is the morphism of Steinberg groups induced by the morphism $\lambda_a\colon R \to R_a$ of localisation by the powers of $a$.
 Notice that $XR_a[X]$ is a splitting ideal for both $R_a[X]$ and $R \ltimes XR_a[X]$.
@@
 We claim that the main results of this paper follow from Tulenbaev's lifting property.
-\begin{prop} Consider the following statements:
+\begin{prop} For any irreducible $\Phi$ of rank $\geq 2$ there are implications $a) \implies b) \implies c) \implies d)$.
 \begin{enumerate}
  \item the Steinberg group functor $\St(\Phi, -)$ satisfies lifting property~\eqref{eq:diagram};
- \item a dilation principle holds for $\St(\Phi, -)$, i.\,e. if $g\in\St(\Phi, A[X], XA[X])$ is such that $\lambda_a^*(h) = 1 \in \St(\Phi, R_a[X])$ then
+ \item a dilation principle holds for $\St(\Phi, -)$, i.\,e. if $g\in\St(\Phi, A[X], XA[X])$ is such that $\lambda_a^*(g) = 1 \in \St(\Phi, R_a[X])$ then
        for sufficiently large $n$ one has $ev_{X = a^n Y}^*(h) = 1 \in \St(\Phi, A[Y])$, where $ev_{X=a^n Y}$ denotes the unique $R$-algebra morphism $R[X]\to R[Y]$ sending $X$ to $a^nY$;
@@
  \item the centrality of $\Kt$ holds for $\St(\Phi, -)$.
-\end{enumerate}
-Then for any irreducible $\Phi$ of rank $\geq 2$ there are implications $a) \implies b) \implies c) \implies d)$. \end{prop}
+\end{enumerate} \end{prop}
 \begin{proof} The specified implications are contained in the proofs of Lemma~15, Theorem~2 and Theorem~1 of \cite{SCh}, respectively. \end{proof}
@@
 To formulate this theorem we will need several technical definitions.
-For a simply laced root system $\Phi$ we denote by $\catname{Subsys}(\Phi)$ the category of root subsystems of $\Phi$.
+For a simply laced root system $\Phi$ we denote by $\catname{Subsys}(\Phi)$ the category of (not necessarily irreducible) root subsystems of $\Phi$.
 Its objects are all root subsystems $\Psi\subseteq \Phi$ and its morphisms are in one-to-one correspondence with inclusions of the form $\Psi_1\subseteq \Psi_2$.
-It is clear that the relative Steinberg group can be turned into a functor $\St(-, R, I)\colon \catname{Subsys}(\Phi) \rightarrow\catname{Groups}.$
+It is clear that the relative Steinberg group can be turned into a functor $\St(-, R, I)\colon \catname{Subsys}(\Phi) \rightarrow\catname{Groups},$ cf.~\cite[Lemma~6]{SCh}.
 
 We denote by $\mathcal{G}_{1,n}$ the full subcategory of $\catname{Subsys}(\Phi)$ whose objects are root subsystems $\Psi\subseteq \Phi$ having type $\rA_1$ or $\rA_n$. 
-It is easy to see that $\mathcal{G}_{1,n}$ is a directed bipartite graph whose only nonidentical morphisms are inclusions of the form $i_{\alpha, \Psi}\colon \{\alpha, -\alpha\} \subseteq \Psi \cong \rA_3$, $\Psi \subseteq \Phi$.
+It is easy to see that $\mathcal{G}_{1,n}$ is a directed bipartite graph whose only nonidentical morphisms are inclusions of the form $i_{\alpha, \Psi}\colon \{\alpha, -\alpha\} \subseteq \Psi \cong \rA_n$, for $\Psi \subseteq \Phi$.
+The following result has been proved in~\cite{SCh}, see~Theorem~9.
 \begin{tm*} \label{tm:relPres} For a simply laced irreducible root system $\Phi$ of rank $\geq 3$
 the group $\St(\Phi, R, I)$ is isomorphic as an abstract group to $\varinjlim_{\mathcal{G}_{1,3}}\St(-, R, I)$. \end{tm*}
-\begin{proof} See~\cite[Theorem~9]{SCh} \end{proof}
+%\begin{proof} See~\cite[Theorem~9]{SCh} \end{proof}
 

### 2016-05-15 paper.tex
Fixes from 2nd part of our discussion

@@
 All commutators are left-normed, i.\,e. $[x,\,y]=xyx\inv y\inv$. 
-We denote by $R^n$ the free $R$-module with a basis $e_1,\ldots,e_n$ and by $\Um(n,\,R)$ the subset of unimodular columns $v\in R^n$, i.\,e. 
+We denote by $R^n$ the free right $R$-module with a basis $e_1,\ldots,e_n$ and by $\Um(n,\,R)$ the subset of unimodular columns $v\in R^n$, i.\,e. 
 columns whose entries generate $R$ as an ideal.
@@
 
-Define the map $\psi$ by $\psi(x_{ij}(\xi)) = (X(e_i, (\xi - \pi(\xi)e_j),\ x_{ij}(\pi(\xi)))$. 
+Define the map $\psi$ by $\psi(x_{ij}(\xi)) = (X(e_i, (\xi - e_j\pi(\xi)),\ x_{ij}(\pi(\xi)))$. 
 We have to check that $\psi$ preserves relations \eqref{add0}--\eqref{ccf2}.
@@
 For $\xi\in R$ set $\xi' = \xi - \pi(\xi)$.
-Specializing $a = X(e_i, \xi' e_j)$, $b = x_{ij}(\pi(\xi))$, $c = X(e_j, \eta'e_k)$, $d = x_{jk}(\pi(\eta))$ and using the definition of the conjugation action 
+Specializing $a = X(e_i,  e_j\xi')$, $b = x_{ij}(\pi(\xi))$, $c = X(e_j, e_k\eta')$, $d = x_{jk}(\pi(\eta))$ and using the definition of the conjugation action 
 one computes the commutator $[\psi(x_{ij}(\xi), \psi(x_{jk}(\eta)]$ as follows:
 \setcounter{equation}{2}
-\begin{equation} \left(X(e_i, \xi' e_j) \cdot X(e_j + \pi(\xi)e_i, \eta'e_k) \cdot X(e_i, \pi(\eta)\xi' e_k - \xi' e_j) \cdot X(e_j, -\eta'e_k),\ x_{ik}(\pi(\xi\eta))\right).
+\begin{equation} \left(X(e_i,  e_j\xi') \cdot X(e_j + e_i\pi(\xi), e_k\eta') \cdot X(e_i,  e_k\pi(\eta)\xi' -  e_j\xi') \cdot X(e_j, -e_k\eta'),\ x_{ik}(\pi(\xi\eta))\right).
 \label{eq:proofS3}\end{equation}
 \setcounter{lm}{3}
-After applying additivity relations \eqref{add2}, \eqref{add3} and moving the factor $X(e_i, -\xi' e_j)$ to the left hand side of the formula by means of relation \eqref{conj2}
+After applying additivity relations \eqref{add2}, \eqref{add3} and moving the factor $X(e_i, - e_j\xi')$ to the left hand side of the formula by means of relation \eqref{conj2}
 one gets the following expression:
-$$(X(e_j, \eta'e_k) \cdot X(e_i, (\xi' \eta' + \pi(\xi)\eta' + \pi(\eta)\xi')e_k \cdot X(e_j, -\eta'e_k),\ x_{ik}(\pi(\xi\eta)).$$
+$$\left(X(e_j, e_k\eta') \cdot X(e_i, e_k(\xi' \eta' + \pi(\xi)\eta' + \pi(\eta)\xi')) \cdot X(e_j, -e_k\eta'),\ x_{ik}(\pi(\xi\eta))\right).$$
 Since $\xi'\eta' + \pi(\xi)\eta' + \pi(\eta)\xi' = \xi\eta - \pi(\xi\eta)$ the above expression clearly simplifies to $\psi(x_{ik}(\xi\eta))$, as claimed.
@@
 
-It remains to check that the map $\varphi$ given by $\varphi\left((X(u, v), 1)\right) = X(u, v),$ $\varphi\left((1, x_{ij}(\xi))\right) = X(e_i, \sigma(\xi)e_j)$
+It remains to check that the map $\varphi$ given by $\varphi\left((X(u, v), 1)\right) = X(u, v),$ $\varphi\left((1, x_{ij}(\xi))\right) = X(e_i, e_j\sigma(\xi))$
 is well-defined and inverse to $\psi$.
@@
 Denote by $\phi\colon\St^*(n,\,R,\,I)\rightarrow\E(n,\,R)$ the natural map sending $F(u,\,v)\mapsto t(u,\,v)$ and $S(u,\,v)\mapsto t(u,\,v)$.
-Then the following facts are true.
+Then the following facts hold:
 \begin{enumerate}
@@
 Applying relations \eqref{add5}, \eqref{coinc} we get
-$$S(u,\,v)=\prod\limits_{k\neq1}S(Ne_k\tilde u_k,\,N^*e_1)=\prod\limits_{k\neq1}F(Ne_k,\,N^*e_1\tilde u_k)$$
+$$S(u',\,v')=\prod\limits_{k\neq1}S(Ne_k\tilde u_k,\,N^*e_1)=\prod\limits_{k\neq1}F(Ne_k,\,N^*e_1\tilde u_k)$$
 and, thus, obtain $(\mathrm{a})$. Obviously, $(\mathrm{b})$ follows from $(\mathrm{a})$. 
@@
 \begin{df} For $u\in R^n$, $v\in\E(n,\,R)e_1$, $u^tv=0$, consider the set $\overline Y(u,\,v)\subseteq\St(n,\,R)$
- consisiting of all elements $y\in\St(n,\,R)$ that admit a decomposition $y=\prod x(w^k,\,v)$, 
- where $\sum u^k=u$ and $u^k= (e_pv_q-e_qv_p)c^k$ for some $c^k\in R$, $1\leq p\neq q\leq n$. \end{df}
+ consisiting of all elements $y\in\St(n,\,R)$ that admit a decomposition $y=\prod x(u^k,\,v)$, 
+ where $\sum u^k=u$ and $u^k= (e_pv_q-e_qv_p)c_k$ for some $c_k\in R$, $1\leq p\neq q\leq n$. \end{df}
 
@@
 We will prove a somewhat more general result. Let $B$ be a commutative unital ring.
-We call an ideal $I$ of $B$ \emph{uniquely $r$-divisible} if for every $m\in I$ there exists only one $m'\in I$ such that $rm' = m$ (we denote such $m'$ by $\frac{m}{r}$).
+We call an ideal $I$ of $B$ \emph{uniquely $r$-divisible} if for every $m\in I$ there exists a unique $m'\in I$ such that $rm' = m$ (we denote such $m'$ by $\frac{m}{r}$).
 Clearly, $I$ is uniquely $r$-divisible if and only if the restriction of the morphism of principal localisation $\lambda_r\colon R \to R_r$ to $I$ is an isomorphism.
@@
 $X_{u,v}(1) = X(u, v)$).
-The key feature of this definition is that the assumption $u \in\Um(n, B)$ is replaced with a weaker condition $a \in I(u)$ (this is equivalent to saying that $u$ becomes unimodular after localisation in $a$).
+The key feature of this definition is that the assumption $u \in\Um(n, B)$ is replaced with a weaker condition $a \in I(u)$ (this is equivalent to saying that $u$ becomes unimodular after localisation by the powers of $a$).
 %The idea is the following. Say $a$ is not a zero divisor, then $ua^m\in B$ for some $m$ and we will construct some element ``$X(ua^m,\,va^{-m})$''.
@@
 \end{df}
+Notice that Tulenbaev uses different notation for van der Kallen elements, e.\,g. he writes $X_{u,v}$ instead of $X(u,\,v)$ and $X(u,\,v)$ instead of $x(u,\,v)$. 
+We stick to van der Kallen's notation.
+
 Tulenbaev shows that the factors $x(u,\,v_ka)$, $1\leq k\leq N$ commute, see~\cite[Lemma~1.1\,e)]{Tul}.
@@
 \end{rk}
-
-Notice that Tulenbaev uses different notation for van der Kallen elements, e.\,g. he writes $X_{u,v}$ instead of $X(u,\,v)$ and $X(u,\,v)$ instead of $x(u,\,v)$. 
-We stick to van der Kallen's notation.
 
@@
 $$x(\phi(g)u,\,\phi(g)^* u_{ij} ac_{ij})=x\left(u',\,u'_{ij}c_{ij}a\right)\cdot x\left(u',\,u'_{ki} rc_{ij}a\right).$$
+Since $u_{ij} = - u_{ji}$, $c_{ij}= - c_{ji}$ the case $i=h$, $j\neq k$ formally follows from the previous one.
+
 Decomposing in this fashion each factor $g\,x(u,u_{ij}ac_{ij})g^{-1}$ for which $\phi(g)^*u_{ij}ac_{ij}$ does not have two zero coordinates, 
  we arrive at a product satisfying the requirements of the definition of $X_{\phi(g)u,\phi(g)^*wb}(a)$.
-
- Since $u_{ij} = - u_{ji}$, $c_{ij}= - c_{ji}$ the case $i=h$, $j\neq k$ formally follows from the one just considered. \end{proof}
+ \end{proof}
 
@@
 Set $Y_{u,v}(a)=\prod_{k=1}^Mx(u_ka,\,v)$. 
-Similarly to \cref{df:TulX} this definition does not depend neither on the order of factors nor on the choice of decomposition for $u$.
+Similarly to \ref{df:TulX} one can check that this definition does not depend neither on the order of factors nor on the choice of decomposition for $u$.
 \end{df}
@@
 \begin{lm}\label{x=y}
-Let $u$, $v$, $x$, $y$ be elements of $B^n$ and $b,r\in B$ be such that $u^t v = 0$, $x^ty=b$, $x^tv=0$, $u^ty=0$ and $b\in I(u)\cap I(v)$.
+Let $u$, $v$, $x$, $y$ be elements of $B^n$ and $b\in I(u)\cap I(v)$, $r\in B$ be such that $u^t v = 0$, $x^ty=b$, $x^tv=0$, $u^ty=0$, $x^tu = 0$, $y^tv=0$.
 Then one has $X_{u,vb^4r}(b)=Y_{ub^4r,v}(b).$
@@
 We can also assume that $m$ is so large that $a^{2m}\in I(\tilde{u})\cap I(\tilde{v})$ and there exist $\tilde{x}$, $\tilde{y}$ such that the following equations hold:
-$$\lambda_a(\tilde{x})=Me_3a^m,\ \lambda_a(\tilde{y})=M^*e_3a^m\text{ and }\tilde{x}^t\tilde{y}=a^{2m},\ \tilde{x}^t\tilde{v} = 0,\ \tilde{u}^t\tilde{y} =0.$$
+$$\lambda_a(\tilde{x})=Me_3a^m,\ \lambda_a(\tilde{y})=M^*e_3a^m\text{ and }\tilde{x}^t\tilde{y}=a^{2m},\ \tilde{x}^t\tilde{v} = 0,\ \tilde{u}^t\tilde{y} =0,\ \tilde{x}^t\tilde{u} = 0,\ \tilde{y}^t\tilde{v}=0.$$
 To obtain~\eqref{eq:last} it remains to apply \cref{x=y} taking $b=a^{2m}$, $r=c/a^{12m}$.

### 2016-05-17 paper.tex
Fixed Vavilov comments

@@
 \DeclareFieldFormat[article, inproceedings, inbook, thesis]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
+\DeclareFieldFormat{postnote}{#1}
 \addbibresource{paper.bib}
@@
 \date {\today}
-\thanks{The authors of the present paper acknowledge the financial support from Russian Science Foundation grant 14-11-00297}
+\thanks{The authors of the present paper acknowledge the financial support of the Russian Science Foundation grant 14-11-00297}
 
@@
 \section*{Introduction}
-The aim of this paper is to establish Quillen's local-global principle and the centrality of even orthogonal $\Kt$ for arbitrary commutative ring $R$.
+The aim of this paper is to establish Quillen's local-global principle and the centrality of even orthogonal $\Kt$ for an arbitrary commutative ring $R$.
 
@@
 
-By a theorem of Taddei (see~\cite{Ta}) the elementary group $\E(\Phi, R)$ is a normal subgroup of $\GG(\Phi, R)$ if $\Phi$ has rank at least $2$.
+By a theorem of Taddei (see~\cite{Ta}) the elementary group $\E(\Phi, R)$ is a normal subgroup of $\GG(\Phi, R)$ when $\Phi$ has rank at least $2$.
 Thus, similarly to the definition of algebraic $\mathrm{SK}_1$ and $\Kt$-functors, one can define the groups $\Ko(\Phi, R)$, $\Kt(\Phi, R)$ as the cokernel and kernel of $\phi$:
@@
 The unstable analogue of the ``universality'' part of this theorem has been known since 1970's for $\Phi$ of rank $\ell \geq 5$ (or even $\ell \geq 4$ for $\Phi=\rA_\ell, \rB_\ell, \rC_\ell$), see \cite{St1, KaS}.
-However, until recently, the analogue of the ``centrality'' part was only known in the special case $\Phi=\rA_\ell$, $\ell\geq 3$ see~\cite[Corollary~2]{vdK}.
+However, until recently, the analogue of the ``centrality'' part was only known in the special case $\Phi=\rA_\ell$, $\ell\geq 3$, see~\cite[Corollary~2]{vdK}.
 The best known result for other classical $\Phi$ was that the centrality holds ``in the stable range'',
@@
 
-Recently the authors of this paper have established the centrality of $\Kt(\rC_\ell, R)$ ($\ell\geq 3$) and $\Kt(\rE_\ell, R)$ ($\ell=6,7,8$) for arbitrary commutative ring $R$, see \cite{Lav, SCh}.
+Recently the authors of this paper have established the centrality of $\Kt(\rC_\ell, R)$ ($\ell\geq 3$) and $\Kt(\rE_\ell, R)$ ($\ell=6,7,8$) for an arbitrary commutative ring $R$, see \cite{Lav, SCh}.
 In turn, the key result of this paper is the following theorem.
@@
 \begin{tm}[``Quillen's LG-principle for $\Kt$''] \label{tm:lg-principle} 
-Let $\Phi$ be an irreducible simply-laced root system of rank $\geq 3$ and $R$ be arbitrary commutative ring.
+Let $\Phi$ be an irreducible simply-laced root system of rank $\geq 3$ and $R$ be a commutative ring.
 Then an element $g\in\St(\Phi,\,R[X])$ satisfying $g(0)=1\in\St(\Phi,\,R)$ is trivial in $\St(\Phi,\,R[X])$
@@
 
-In the special case $\Phi=\rA_\ell$, $\ell\geq 4$ the assertion of \cref{tm:lg-principle} was obtained by Tulenbaev, see~\cite[Theorem~2.1]{Tul}.
+In the special case $\Phi=\rA_\ell$, $\ell\geq 4$, the assertion of \cref{tm:lg-principle} was obtained by Tulenbaev, see~\cite[Theorem~2.1]{Tul}.
 Despite the fact that the key ingredient in Tulenbaev's proof (``another presentation'' of the Steinberg group) is available for $\Phi=\rA_3$, Tulenbaev's proof does not work in this case for technical reasons.
@@
 Thus, \cref{tm:lg-principle} contains two cases that have not been previously known: $\Phi=\rA_3$ and $\Phi=\rD_\ell$, $\ell\geq 4$.
+In rank $2$ there are known counterxamples to centrality of $\Kt$, which shows that our assumption on the rank of $\Phi$ in \cref{tm:lg-principle} is the best possible, see~\cite{W}.
 We also note that recently the first-named author has obtained an analogue of \cref{tm:lg-principle} for $\Kt(\rC_\ell, R)$ under the assumption $\ell\geq 3$, see~\cite{Lav2}.
@@
 We denote by $R^n$ the free right $R$-module with a basis $e_1,\ldots,e_n$ and by $\Um(n,\,R)$ the subset of unimodular columns $v\in R^n$, i.\,e. 
-columns whose entries generate $R$ as an ideal.
+columns whose components generate $R$ as an ideal.
 
@@
  x_\alpha(r) x_\alpha(s) & = x_\alpha(r+s), & \nonumber \\
- [x_\alpha(r),  x_\beta(s)] & = x_{\alpha+\beta}(N_{\alpha,\beta} rs), &\ \alpha,\beta\in \Phi,\ \alpha+\beta\in\Phi, \nonumber \\
+ [x_\alpha(r),  x_\beta(s)] & = x_{\alpha+\beta}(N_{\alpha,\beta}\cdot rs), &\ \alpha,\beta\in \Phi,\ \alpha+\beta\in\Phi, \nonumber \\
  [x_\alpha(r),  x_\beta(s)] & = 1, &\ \alpha,\beta\in \Phi,\ \alpha+\beta\not\in\Phi. \nonumber
@@
 Here $N_{\alpha,\beta}$ are the structure constants of $\Phi$ which are equal to $\pm 1$.
-In the case $\Phi=\rA_\ell$ we use a more common notation for root unipotents: $x_{ij}(r)$, $1\leq i\neq j\leq n$, $r\in R$,
+We use more a more familiar notation for root unipotents in the case $\Phi=\rA_\ell$:
+$x_{ij}(r),\ 1\leq i\neq j\leq n,\ r\in R,$
 \setcounter{equation}{0}
@@
 \end{align}
-In the case $\Phi=\rA_\ell$ the elementary root unipotents $t_\alpha(r)$ are exactly the elementary transvections $t_{ij}(r)=1+r \cdot e_{ij}$, $1\leq i\neq j\leq n$, $r\in R$
-and the elementary subgroup $\E(\rA_{n-1}, R)$ is also denoted by $\E(n, R)$.
-Here $1$ denotes the identity matrix and $e_{ij}$ is the standard matrix unit. The natural projection $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ sends $x_{ij}(r)$ to $t_{ij}(r)$.
+In this situation the elementary root unipotents coincide with elementary transvections $t_{ij}(r)=1+r \cdot e_{ij}$, $1\leq i\neq j\leq n$, $r\in R$
+and the elementary subgroup $\E(\rA_{n-1}, R)$ is denoted by $\E(n, R)$.
+Here $1$ denotes the identity matrix and $e_{ij}$ ientriess the standard matrix unit. 
+The natural projection $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ sends $x_{ij}(r)$ to $t_{ij}(r)$.
 
-In \cite{Sus} Suslin showed for $n\geq 3$ that the elementary group $\E(n, R)$ coincides with the subgroup of $\GL(n,\,R)$ generated by matrices
+In \cite{Sus} Suslin showed that for $n\geq 3$ the elementary group $\E(n, R)$ coincides with the subgroup of $\GL(n,\,R)$ generated by matrices
 of the form $t(u,\,v)=1+uv^t$ where $u\in\Um(n,\,R)$, $v\in R^n$ and $u^tv=0$. Here $u^t$ stands for the transpose of $u$.
-This result clearly implies that $\E(n,\,R)$ is normal inside $\GL(n,\,R)$.
-Afterwards, W.~van~der~Kallen developed Suslin's ideas and showed for $n\geq4$ that the Steinberg group $\St(n,\,R)$ is isomorphic to the group presented by generators
-$$\{X(u,\,v)\mid u\in\Um(n,\,R),\ v\in R^n,\ u^tv=0\}$$ and the following list of relations (see~\cite[Theorem~1]{vdK}):
+This result clearly implies that $\E(n,\,R)$ is normal in $\GL(n,\,R)$.
+Developing Suslin's ideas, W.~van~der~Kallen showed that for $n\geq4$ the Steinberg group $\St(n,\,R)$ is isomorphic to the group with the following presentation by generators
+$$\{X(u,\,v)\mid u\in\Um(n,\,R),\ v\in R^n,\ u^tv=0\}$$ and relations:
 \setcounter{equation}{0} \renewcommand{\theequation}{K\arabic{equation}}
@@
 %Our notation for the generators of $\St(n, R)$ differs from van der Kallen's, e.\,g.
-Notice that we parametrize elements $X(u, v)$ with two columns rather than with one column and one row as it is done in~\cite{vdK}.
+Notice that we parametrize elements $X(u, v)$ by two columns rather than by a column and a row as it is done in~\cite{vdK}.
 Our generator $X(u,v)$ corresponds to van der Kallen's generator $X(u, v^t)$.
 
-Recall that an ideal $I\trianglelefteq R$ is called a \emph{splitting ideal} if the canonical projection $R \twoheadrightarrow R/I$ splits as a unital ring morphism, i.\,e. one has $\pi\sigma=1$.
+Recall that an ideal $I\trianglelefteq R$ is called a \emph{splitting ideal} if the canonical projection $R \twoheadrightarrow R/I$ splits as a unital ring morphism, i.\,e. one has $\pi\sigma=1$:
 $$\xymatrix{0\ar@<0.1ex>[r]^{}&I\ar@<0.1ex>[r]^{}&R\ar@<0.5ex>[r]^{\pi}&R/I\ar@<0.5ex>[l]^{\sigma}\ar@<0.1ex>[r]^{}&0}$$
@@
 
-For arbitrary $I$ the relative Steinberg group $\St(\Phi, R, I)$ is no more a subgroup of $\St(\Phi, R)$ and should be defined as a central extension of the above kernel.
+In the case of an arbitrary $I$ the relative Steinberg group $\St(\Phi, R, I)$ does not have to be a subgroup of $\St(\Phi, R)$ and should be defined as a central extension of the above kernel.
 For the purposes of the present text it suffices to consider only relative Steinberg groups corresponding to splitting ideals.
@@
                            \St(\Phi,\,R_a[X],\,XR_a[X]) \ar@{-->}[ru]_-{T_\Phi} \ar@{^{(}->}[r] & \St(\Phi, R_a[X])} \label{eq:diagram} \end{equation}
-Here $R\ltimes XR_a[X]$ denotes the semidirect product of the ring $R$ and the $R$-algebra $XR_a[X]$ (see~e.\,g.~\cite[Definition~3.2]{SCh}), $\lambda_a^*$ is the morphism of Steinberg groups induced by the morphism $\lambda_a\colon R \to R_a$ of localisation by the powers of $a$.
+Here, $R\ltimes XR_a[X]$ denotes the semidirect product of the ring $R$ and the $R$-algebra $XR_a[X]$ (see~e.\,g.~\cite[Definition~3.2]{SCh}), $\lambda_a^*$ is the morphism of Steinberg groups induced by the morphism $\lambda_a\colon R \to R_a$ of localisation by the powers of $a$.
 Notice that $XR_a[X]$ is a splitting ideal for both $R_a[X]$ and $R \ltimes XR_a[X]$.
@@
 (see the proof of Lemma~14 and notice that everywhere in it $\rA_4$'s can be replaced with $\rA_3$'s).
-On the other hand, constructing $T_\Psi$ for $\Psi=\rA_3$ is not at all obvious and will be done in the section to follow.
+On the other hand, constructing $T_\Psi$ for $\Psi=\rA_3$ is not at all obvious and will be done in the following sections.
 
@@
 \end{prop}
-Here $\Um_{n\times2}(R)$ denotes the set of $n\times2$ \emph{unimodular matrices}, i.\,e.
+Here, $\Um_{n\times2}(R)$ denotes the set of $n\times2$ \emph{unimodular matrices}, i.\,e.
 matrices $M$ such that there exists a $2\times n$ matrix $N$ satisfying $NM=\begin{pmatrix}1&0\\0&1\end{pmatrix}$.
@@
 $$\left(X(e_j, e_k\eta') \cdot X(e_i, e_k(\xi' \eta' + \pi(\xi)\eta' + \pi(\eta)\xi')) \cdot X(e_j, -e_k\eta'),\ x_{ik}(\pi(\xi\eta))\right).$$
-Since $\xi'\eta' + \pi(\xi)\eta' + \pi(\eta)\xi' = \xi\eta - \pi(\xi\eta)$ the above expression clearly simplifies to $\psi(x_{ik}(\xi\eta))$, as claimed.
+Since $\xi'\eta' + \pi(\xi)\eta' + \pi(\eta)\xi' = \xi\eta - \pi(\xi\eta),$ the above expression simplifies to $\psi(x_{ik}(\xi\eta))$, as claimed.
 Verification of the fact that $\psi$ preserves relations \eqref{add0}, \eqref{ccf1} is similar to the above computation but is easier.
@@
 
-Both ``another presentations'' of van der Kallen and Tulenbaev are given in terms of generators parametrised by pairs of vectors,
- where the first one is ``good'' in some sense  (i.\,e. unimodular or a column of an elementary matrix) while the second one is arbitrary.
-It is easy to formulate the additivity property in the second argument for these generators (cf. \eqref{add1}, \eqref{add2}),
-while it is not so easy when it comes to the additivity in the first argument (cf. \eqref{add3}).
+Both ``another presentation'' of van der Kallen and that of Tulenbaev are given in terms of generators parametrised by pairs of vectors,
+ where the first one is ``nice'' in some sense i.\,e. unimodular, a column of an elementary matrix or the like, while the second one is arbitrary.
+It is easy to formulate the additivity property in the second argument for these generators, cf.~\eqref{add1}, \eqref{add2},
+while it is not so easy when it comes to the additivity in the first argument, cf. \eqref{add3}.
 %Such presentations allowed them to formulate easily an additivity by the second argument, but one has to write something similar to T3 instead of additivity by the first one.
@@
 The main problem with this recipe is that the assumption $n\geq5$ is essential to check that the relation~\eqref{add3} holds.
+It is not possible to choose arbitrary orthogonal vectors $u$, $v$ as parameters for the generators, since in this situation it is not even known that $t(u,\,v)\in\E(n,\,R)$.
 
-It is not possible to choose arbitrary orthogonal vectors $u$, $v$ as parameters for the generators because in this situation it is not even known that $t(u,\,v)\in\E(n,\,R)$, see~\cite{Rao}.
-
-To generalise Tulenbaev's results for $n=4$ we use a more symmetric presentation with two types of generators: 
-$F(u,\,v)$ with $u$ good and $v$ arbitrary and $S(u,\,v)$ with $u$ arbitrary and $v$ good.
+To generalise Tulenbaev's results to $n=4$ we use a more symmetric presentation with two types of generators: 
+$F(u,\,v)$ with $u$ nice and $v$ arbitrary and $S(u,\,v)$ with $u$ arbitrary and $v$ nice.
 The generators $F(u,\,v)$ are additive in the second component, while $S(u,\,v)$ are additive in the first one.
-When $u$ and $v$ are both good we require that these two generators coincide.
+When $u$ and $v$ are both nice we require that these two generators coincide.
 More formally, we make the following definition.
@@
 \end{multline*}
-subject to relations
+subject to the relations
 \setcounter{equation}{0}
@@
 Notice that we only described how a generator $F(u, v)$ acts via conjugation on another generator $F(u',v')$ and have omitted three similar relations involving generators $S(u,v)$ of the second type.
-The reason for this is the following lemma which asserts that the ``missing'' relations will follow automatically from \eqref{add4}--\eqref{coinc}.
+The reason for this is the following lemma asserting that the ``missing'' relations automatically follow from \eqref{add4}--\eqref{coinc}.
 \begin{lm}
@@
 Denote by $\phi\colon\St^*(n,\,R,\,I)\rightarrow\E(n,\,R)$ the natural map sending $F(u,\,v)\mapsto t(u,\,v)$ and $S(u,\,v)\mapsto t(u,\,v)$.
-Then the following facts hold:
+Then the following holds:
 \begin{enumerate}
@@
 By \eqref{add4} we have $$F(u,\,v)=\prod\limits_{k\neq1}F(Me_1,\,M^*e_k\tilde v_k)$$
-where $\tilde v_k$ stands for $k$-th coordinate of $\tilde v=\sum e_i\tilde v_i$.
+where $\tilde v_k$ stands for the $k$-th coordinate of $\tilde v=\sum e_i\tilde v_i$.
 Applying relations \eqref{add5}, \eqref{coinc} we get
 $$S(u',\,v')=\prod\limits_{k\neq1}S(Ne_k\tilde u_k,\,N^*e_1)=\prod\limits_{k\neq1}F(Ne_k,\,N^*e_1\tilde u_k)$$
-and, thus, obtain $(\mathrm{a})$. Obviously, $(\mathrm{b})$ follows from $(\mathrm{a})$. 
+which implies $(\mathrm{a})$. Obviously, $(\mathrm{b})$ follows from $(\mathrm{a})$. 
 To prove $(\mathrm{c})$ it suffices to show that
 $$F(u,\,v)S(u',\,v')F(u,\,v)\inv=S(t(u,\,v)u',\,t(u,\,v)^*v').$$
-For $S(u',\,v')=\prod_{k\neq 1} F(Ne_k,\,N^*e_1\tilde u_k)$ we have
+Indeed, for $S(u',\,v')=\prod_{k\neq 1} F(Ne_k,\,N^*e_1\tilde u_k)$ we have
 \begin{multline*}
@@
 
-Our next goal is to show for a splitting ideal $I\trianglelefteq R$ that the group $\St^*(n,\,R,\,I)$ is isomorphic to $\St(n,\,R,\,I)=\Ker\big(\St(n,\,R)\epi\St(n,\,R/I)\big)$.
-With this end we construct two mutually inverse homomorphisms
+Our next goal is to show that for a splitting ideal $I\trianglelefteq R$ the group $\St^*(n,\,R,\,I)$ is isomorphic to $\St(n,\,R,\,I)=\Ker\big(\St(n,\,R)\epi\St(n,\,R/I)\big)$.
+With this end, we construct two mutually inverse homomorphisms
 $$\xymatrix{\St^*(n,\,R,\,I)\ar@<0.5ex>[r]^{\iota}&\St(n,\,R,\,I)\ar@<0.5ex>[l]^{\kappa}.}$$
-
 In order to construct the arrow $\kappa$ we use the presentation from \cref{prop:TulPres}.
@@
 In view of \cref{rk:T123'} it suffices to check that $F(u,v)$ satisfy the relations \eqref{add2}, \eqref{conj2}, \eqref{add3'}.
-The validity of relations \eqref{add2}, \eqref{conj2} is obvious while \eqref{add3'} follows from \eqref{add5} and \eqref{coinc}, indeed:
+The validity of relations \eqref{add2}, \eqref{conj2} is obvious, while \eqref{add3'} follows from \eqref{add5} and \eqref{coinc}. Indeed,
 $$ F(e_i, rae_k) F(e_j, ae_k) = S(rae_i, e_k) S(ae_j, e_k) = S(a(re_i+e_j), e_k) = F(e_ir+e_j, ae_k). \qedhere $$
 
-As for the map $\iota$, we firsty define it as a homomorphism to the absolute group.
+As for the map $\iota$, we first define it as a homomorphism to the absolute group. % which does not rely on the assumption that $I$ is splitting.
 Then we prove that the image of $\iota$ is contained in $\St(n, R, I)$.
 %$$\xymatrix{\St^*(n,\,R,\,I)\ar@<0.0ex>[r]^{\iota}&\St(n,\,R).}$$
-Clearly, $\iota$ should map the elements $F(u,\,v)$ to van der Kallen's generators $X(u,\,v)$.
-We should find the images for the elements $S(u,\,v)$ as well.
+Clearly, $\iota$ the elements $F(u,\,v)$ should go to van der Kallen's generators $X(u,\,v)$.
+But now we should find the images for the elements $S(u,\,v)$ as well.
 First of all, recall that van der Kallen in~\cite[3.8--3.10]{vdK} constructs the following elements:
@@
 \begin{equation} (w^t\cdot v)\cdot u = \sum_{p<q}u_{pq},\text{ where }u_{pq} = (e_pv_q - e_qv_p)\cdot  (u_pw_q - u_qw_p)\in{}\!R^n, \label{eq:canonical}\end{equation}
-therefore $\overline Y(u,\,v)$ is not empty (cf.~\cite[3.1--3.2]{vdK}).
+therefore $\overline Y(u,\,v)$ is not empty, cf.~\cite[3.1--3.2]{vdK}.
 Obviously, for $x\in\overline Y(u,\,v)$ and $y\in\overline Y(w,\,v)$ one has $xy\in\overline Y(u+w,\,v)$.
 
-Repeating~\cite[3.14--3.15]{vdK} verbatim one shows the following.
+Repeating~\cite[3.14--3.15]{vdK} verbatim one can show the following.
 \begin{lm} For $g\in\St(n,\,R)$ one has
@@
 We denote the only element of $\overline Y(u,\,v)$ by $Y(u,\,v)$. 
-Now we can finish the definition of $\iota$ by requiring that $\iota(S(u,\,v)) = Y(u,\,v)$ for $S(u,\,v)\in\St^*(n,\,R,\,I)$. 
-To show that the map $\iota$ is well-defined we should check that elements $X(u,\,v)$ and $Y(u,\,v)$ satisfy relations \eqref{add4}--\eqref{coinc} 
-(with $F$'s and $S$'s replaced with $X$'s and $Y$'s).
-Only the relation \eqref{coinc} is not immediately obvious.
-\begin{lm} \label{lm:XY} For $(u,\,v^t)=(Me_1,\,e_2^tM\inv)$, $M\in\E(n,\,R)$, $a\in I$ one has $X(u,\,va)=Y(ua,\,v)$. \end{lm}
+Now, we can finish the definition of $\iota$ by requiring that $\iota(S(u,\,v)) = Y(u,\,v)$ for $S(u,\,v)\in\St^*(n,\,R,\,I)$. 
+To show that the map $\iota$ is well-defined we should check that elements $X(u,\,v)$ and $Y(u,\,v)$ satisfy relations \eqref{add4}--\eqref{coinc},
+with $F$'s and $S$'s replaced with $X$'s and $Y$'s.
+Here, only the relation \eqref{coinc} is not immediately obvious.
+\begin{lm} \label{lm:XY} For $(u,\,v^t)=(Me_1,\,e_2^tM\inv)$, $M\in\E(n,\,R)$, $a\in I$, one has $X(u,\,va)=Y(ua,\,v)$. \end{lm}
 \begin{proof}
@@
 %At this point we have demonstrated for $n\geq4$ and a splitting ideal $I$ that $\St^*(n,\,R,\,I)$ and $\St(n,\,R,\,I)$ are isomorphic.
-Now we turn to the main result of this paper, namely, we construct for $n\geq 4$ the map $$T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X]),$$ that fits into the diagram \eqref{eq:diagram}.
+Now we turn to the main result of this paper, namely, for $n\geq 4$ we construct the map $$T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X]),$$ that fits into the diagram \eqref{eq:diagram}.
 
 We will prove a somewhat more general result. Let $B$ be a commutative unital ring.
-We call an ideal $I$ of $B$ \emph{uniquely $r$-divisible} if for every $m\in I$ there exists a unique $m'\in I$ such that $rm' = m$ (we denote such $m'$ by $\frac{m}{r}$).
-Clearly, $I$ is uniquely $r$-divisible if and only if the restriction of the morphism of principal localisation $\lambda_r\colon R \to R_r$ to $I$ is an isomorphism.
+We call an ideal $I$ of $B$ \emph{uniquely $r$-divisible} if for every $m\in I$ there exists a unique $m'\in I$ such that $rm' = m$.
+In the sequel we denote such an $m'$ by $\frac{m}{r}$.
+Clearly, $I$ is uniquely $r$-divisible if and only if the restriction of the principal localisation morphism $\lambda_r\colon R \to R_r$ to $I$ is an isomorphism.
 
 \begin{tm} \label{a3map} Let $B$ be a ring, $a\in B$ and let $I$ be an ideal of $B$ that is uniquely $a$-divisible.
-Then for $n\geq 4$ there exists a map $T\colon\St^*(n,\,B_a,\,I)\rightarrow\St(n,\,B)$ which makes the following diagram commute.
+Then for $n\geq 4$ there exists a map $T\colon\St^*(n,\,B_a,\,I)\rightarrow\St(n,\,B)$ that makes the following diagram commute:
 \begin{equation} \xymatrix{ \St^*(n,\,B,\,I)\ar@<-0.0ex>[rr]^{\iota}\ar@<-0.0ex>[d]_{\lambda_{a}^*} && \St(n,\,B)\ar@<-0.0ex>[d]^{\lambda_{a}^*}\\
@@
 
-For a vector $u\in R^n$ we denote by $I(u)$ the ideal generated by the entries of $u\in R^n$, i.\,e. $I(u)=\sum\limits_{k=1}^nu_kR$.
-To prove \cref{a3map} we follow the approach of Tulenbaev and construct yet another family of elements $X_{u,v}(a)\in \St(n,\,B)$, $a\in B$ which contains van der Kallen's generators $X(u, v)$ as a subfamily (i.\,e.
-$X_{u,v}(1) = X(u, v)$).
-The key feature of this definition is that the assumption $u \in\Um(n, B)$ is replaced with a weaker condition $a \in I(u)$ (this is equivalent to saying that $u$ becomes unimodular after localisation by the powers of $a$).
+For a vector $u\in R^n$ we denote by $I(u)$ the ideal generated by the components of $u\in R^n$, i.\,e. $I(u)=\sum\limits_{k=1}^nu_kR$.
+To prove \cref{a3map} we follow the approach of Tulenbaev and construct yet another family of elements $X_{u,v}(a)\in \St(n,\,B)$, $a\in B$ which contains van der Kallen's generators $X(u, v)$ as a subfamily, i.\,e.
+$X_{u,v}(1) = X(u, v)$.
+The key feature of this definition is that the assumption $u \in\Um(n, B)$ is replaced by a weaker condition $a \in I(u)$ equivalent to imposing that $u$ becomes unimodular after localisation by the powers of $a$.
 %The idea is the following. Say $a$ is not a zero divisor, then $ua^m\in B$ for some $m$ and we will construct some element ``$X(ua^m,\,va^{-m})$''.
@@
 \begin{df} \label{df:TulX}
-For $u \in R^n$ we denote by $D(u)$ the set consisting of all $v\in B^n$ decomposing into a sum $v=\sum_{k=1}^Nv_k$ where $v_1,\ldots,v_N\in B^n$ are such that $u^tv_k=0$ and each $v_k$ has at least two zero coordinates.
-Now for $a\in I(u)$ and $v \in D(u)$ set $X_{u,v}(a) = \prod\limits_{k=1}^Nx(u,\,v_ka)$.
+For $u \in R^n$ we denote by $D(u)$ the set consisting of all $v\in B^n$ decomposing into a sum $v=\sum_{k=1}^Nv_k$, where $v_1,\ldots,v_N\in B^n$ are such that $u^tv_k=0$ and each $v_k$ has at least two zero coordinates.
+Now, for $a\in I(u)$ and $v \in D(u)$ set $X_{u,v}(a) = \prod\limits_{k=1}^Nx(u,\,v_ka)$.
 \end{df}
@@
 
-Tulenbaev shows that the factors $x(u,\,v_ka)$, $1\leq k\leq N$ commute, see~\cite[Lemma~1.1\,e)]{Tul}.
+Tulenbaev shows that the factors $x(u,\,v_ka)$, $1\leq k\leq N$, commute, see~\cite[Lemma~1.1\,e)]{Tul}.
 He also shows that if $v$ admits another decomposition $v=\sum_{j=1}^Mv'_j$ satisfying the assumptions of \cref{df:TulX} then one has
@@
 \begin{rk} \label{rk:ID}
-From the canonical decomposition~\eqref{eq:canonical} it follows that $vb\in D(u)$ for any $b\in I(u)$ and $v$ such that $v^tu=0$.
+It follows from the canonical decomposition~\eqref{eq:canonical} that $vb\in D(u)$ for any $b\in I(u)$ and $v$ such that $v^tu=0$.
 In particular, if $I$ is uniquely $a$-divisible and $a^k\in I(u)$, then every $v\in I^n$ satisfying $v^tu=0$ is contained in $D(u)$.
@@
 \begin{lm} \label{xproperties}
-For $u$, $w\in B^n$, $v, v' \in D(u)$ such that $u^tw=0$, for $a$, $b\in I(u)$, $c\in B$, $g\in\St(n,\,B)$ the following are true:
+For $u$, $w\in B^n$, $v, v' \in D(u)$ such that $u^tw=0$, for $a$, $b\in I(u)$, $c\in B$, $g\in\St(n,\,B)$ the following holds:
 \begin{enumerate}
@@
 The assertion of $(\mathrm d)$ is proven in~\cite[Lemma~1.3\,b)]{Tul} under the assumption $n\geq5$. 
-Afterwards Tulenbaev remarks that the assertion remains true for $n=4$. % We will give a detailed proof of this fact.
+Tulenbaev remarks that the assertion remains true for $n=4$. % We will give a detailed proof of this fact.
 Indeed, take $z\in B^n$ such that $z^tu=b$ and write the canonical decomposition \eqref{eq:canonical}:
 $$(z^tu)w=\sum_{i<j}u_{ij} c_{ij}, \text{ where } u_{ij}=e_iu_j-e_ju_i,\text{ and }c_{ij}=w_iz_j-w_jz_i.$$
-Each $u_{ij} c_{ij}$ is orthogonal to $u$ and, because of the assumption $n\geq4$, has at least two zero coordinates.
+Each $u_{ij} c_{ij}$ is orthogonal to $u$ and, since $n\geq4$, it has at least two zero components.
 Thus, $X_{u,wb}(a)=\prod_{i<j}x(u,\, u_{ij} ac_{ij})$. 
-It is enough to prove the assertion of $(\mathrm d)$ in the special case $g=x_{hk}(r)$.
-If $h\neq i,j$ or $\{h,k\}=\{i,j\}$ the vector $\phi(g)^*u_{ij}ac_{ij}$ still has two zero coordinates.
+It suffices to prove the assertion of $(\mathrm d)$ in the special case $g=x_{hk}(r)$.
+If $h\neq i,j$ or $\{h,k\}=\{i,j\}$ the vector $\phi(g)^*u_{ij}ac_{ij}$ still has two zero components.
 
-Now consider the case $j=h$, $i\neq k$.
+Now, consider the case $j=h$, $i\neq k$.
 By~\cite[3.12]{vdK} one has $$g\,x(u,\,u_{ij}ac_{ij})g\inv=x(\phi(g)u,\,\phi(g)^*u_{ij}ac_{ij}).$$
@@
 $\phi(g)^*u_{ij} = t_{kj}(-r) \cdot u_{ij} = e_iu_j - e_ju_i + e_kru_i =u'_{ij}+u'_{ki}r,$ 
-we obtain from~\cite[3.11]{vdK} that
+from~\cite[3.11]{vdK} we obtain that
 $$x(\phi(g)u,\,\phi(g)^* u_{ij} ac_{ij})=x\left(u',\,u'_{ij}c_{ij}a\right)\cdot x\left(u',\,u'_{ki} rc_{ij}a\right).$$
@@
 
-Decomposing in this fashion each factor $g\,x(u,u_{ij}ac_{ij})g^{-1}$ for which $\phi(g)^*u_{ij}ac_{ij}$ does not have two zero coordinates, 
+Decomposing in this fashion each factor $g\,x(u,u_{ij}ac_{ij})g^{-1}$ for which $\phi(g)^*u_{ij}ac_{ij}$ does not have two zero components, 
  we arrive at a product satisfying the requirements of the definition of $X_{\phi(g)u,\phi(g)^*wb}(a)$.
@@
 \begin{df} \label{df:TulY}
-Let $v\in B^n$, $a\in I(v)$, and $u \in D(v)$, i.\,e. $u = \sum\limits_{i=1}^M u_i$ for some $u_k$ having two zero components such that $v^tu_k=0$.
+Let $v\in B^n$, $a\in I(v)$, and $u \in D(v)$, i.\,e. $u = \sum\limits_{i=1}^M u_i$ for some $u_k$ such that $v^tu_k=0$ and each $u_k$ has two zero components.
 Set $Y_{u,v}(a)=\prod_{k=1}^Mx(u_ka,\,v)$. 
-Similarly to \ref{df:TulX} one can check that this definition does not depend neither on the order of factors nor on the choice of decomposition for $u$.
+Similarly to \ref{df:TulX} one can check that this definition does not depend either on the order of factors or on the choice of decomposition for $u$.
 \end{df}
@@
 
-Finally, it remains to show that for a ``good'' pair $(u,\,v)$ the elements $X$ and $Y$ coincide.
+Finally, it remains to show that for a ``nice'' pair $(u,\,v)$ the elements $X$ and $Y$ coincide.
 \begin{lm}\label{x=y}
@@
 
-Now, we are ready to construct the desired map $T\colon\St(n,\,B_a,\,I)\rightarrow\St(n,\,B).$
+Now, we are all set to construct the desired map $T\colon\St(n,\,B_a,\,I)\rightarrow\St(n,\,B).$
 
@@
 $$ \lambda_a(\tilde{w})=wa^m,\ \lambda_a(\tilde{u})=ua^m\text{ and moreover }\tilde u^tv=0\text{ and }\tilde w^t\tilde u=a^{2m}.$$
-It is clear that $a^{2m}\in I(\tilde u)$, moreover by~\cref{rk:ID} we have $v/a^{3m} \in D(\tilde u)$, therefore we are allowed to set $T(F(u,\,v))=X_{\tilde u,v/a^{3m}}(a^{2m})$.
+It is clear that $a^{2m}\in I(\tilde u)$, moreover by~\cref{rk:ID} we have $v/a^{3m} \in D(\tilde u)$, therefore we can set $T(F(u,\,v))=X_{\tilde u,v/a^{3m}}(a^{2m})$.
 
@@
 
-It remains to check for $u = Me_1$, $v=M^*e_2$ and $c\in I$ that 
+It remains to check that for $u = Me_1$, $v=M^*e_2$ and $c\in I$ one has
 \begin{equation}T(F(u, cv)) = X_{\tilde u,\,\tilde v c/a^{4m}}(a^{2m}) = Y_{\tilde uc/a^{4m},\, \tilde v}(a^{2m}) = T(S(uc, v)). \label{eq:last}\end{equation}
 Here $\tilde u, \tilde v \in B^n$ are liftings of $u$ and $v$ such that $\lambda_a(\tilde u)= ua^m$, $\lambda_a(\tilde v)= va^m$ and $\tilde u^t \tilde v = 0$.
-We can also assume that $m$ is so large that $a^{2m}\in I(\tilde{u})\cap I(\tilde{v})$ and there exist $\tilde{x}$, $\tilde{y}$ such that the following equations hold:
+We can also assume that $m$ is large enough to ensure that $a^{2m}\in I(\tilde{u})\cap I(\tilde{v})$ and there exist $\tilde{x}$, $\tilde{y}$ such that the following equations hold:
 $$\lambda_a(\tilde{x})=Me_3a^m,\ \lambda_a(\tilde{y})=M^*e_3a^m\text{ and }\tilde{x}^t\tilde{y}=a^{2m},\ \tilde{x}^t\tilde{v} = 0,\ \tilde{u}^t\tilde{y} =0,\ \tilde{x}^t\tilde{u} = 0,\ \tilde{y}^t\tilde{v}=0.$$
-To obtain~\eqref{eq:last} it remains to apply \cref{x=y} taking $b=a^{2m}$, $r=c/a^{12m}$.
+To obtain~\eqref{eq:last} it remains to apply \cref{x=y} (with $b=a^{2m}$, $r=c/a^{12m}$).
 Thus, the map $T$ is well-defined.

### 2016-05-24 paper.tex
Purged commented lines

@@
 
-%\begin{thebibliography}{99}
-%\bibitem{Lav2} A.~Lavrenov, A local--global principle for symplectic $\mathrm K_2$, {\it to appear}.
-%\bibitem{Rao} *Statement of Ravi Rao's hypothesis
-%\bibitem{Swa1} *Swan's relative Steinberg group 1
-%\bibitem{Swa2} *Swan's relative Steinberg group 2
-%\bibitem{Swa3} *Swan's relative Steinberg group 3
-%\bibitem{Tul0} *Tulenbaev's paper on almost commutative rings (cite somewhere)
-%\end{thebibliography}
-
 \section*{Introduction}
@@
 Finally, this presentation is used in~\cref{sec:lgp} to prove \cref{tm:lg-principle} in the case $\Phi=\rA_3$.
-%It mimics the standart vector representation of $\SL(n,\,R)$, therefore in the first section we use representations and corresponding vector notation. 
-%Finally, in \cref{sec:patching} we derive our principal results from this special case and the amalgamation theorem for relative Steinberg groups from~\cite{SCh}.
-%There we switch to the root notation.
 
@@
 columns whose components generate $R$ as an ideal.
-
-%Tulenbaev used {\it another presentation} for a relative Steinberg group to prove a local--global
-%principle for a linear Steinberg group~\cite{Tul}. 
-%This relative another presentation was inspired by the {\it absolute} one of van der Kallen~\cite{vdK}. 
-%However, Tulenbaev's presentation can only be used for $\St(l+1,\,R)=\St(\mathrm A_l,\,R)$, $l\geq4$.
-
-%Tulenbaev's result can be applied to the subsystems of type $\mathrm A_4$ inside $\mathrm E_l$ and ``glued'' 
-% to get a local--global principle for Steinberg groups of type $\mathrm E_l$~\cite{SCh}. 
-%To use this glueing method for groups of type $\mathrm D_l$ as well one has to work with subsystems 
-%of type $\mathrm A_3$ instead, and thus extend Tulenbaev's result to the case of $\mathrm A_3$.
-
-%Recently, the local--global principle was obtained for Steinberg groups of type $\mathrm C_l$ starting from rank 3~\cite{Lav2}. 
-%That is another motivation to consider the linear Steinberg group in rank 3.
 
@@
 This presentation clearly implies that $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ is a central extension.
-%Our notation for the generators of $\St(n, R)$ differs from van der Kallen's, e.\,g.
 Notice that we parametrize elements $X(u, v)$ by two columns rather than by a column and a row as it is done in~\cite{vdK}.
@@
 
-%This $T$ is an inverse to a map induced by localisation, so that constructing $\mathrm T$ may be treated
-%as a proof of excision property for Steinberg group in this very particular situation.
-
-%To prove the local--global principle for Steinberg groups of type $\mathrm D_l$ and centrality 
-%of $\mathrm K_2(\mathrm D_l,\,R)$ we need such a map for $n=4$ (i.e., for the group of type $\mathrm A_3$).
-
-%Since there are known counterexamples to centrality of $\Kt$ and, thus, to \cref{tm:lg-principle} for $\Phi$ of rank $2$ (see~\cite{W}), 
-%this gives a complete answer to the question for which $\ell$ the local-global principle holds for $\Kt(\rC_\ell, R)$.
-
-%The main idea of our proof of~\cref{tm:lg-principle} is to first settle the case $\Phi=\rA_3$ and then derive the other cases from it using the patching technique of~\cite{SCh}.
-
-%Compare \cref{tm:lg-principle} with the local-global principle for $\Ko$ which states that an element of the congruence subgroup $g\in \GG(\Phi,\,R[X], XR[X])$ is elementary
-%(i.\,e. lies in $\E(\Phi, R[X])$) if and only if $\lambda_M^*(g)=1\in\E(\Phi,\,R_M[X])$ for all maximal ideals $M \trianglelefteq R$.
-
 \section{Yet another presentation for the relative Steinberg group.} \label{sec:yap}
@@
 In order to construct the arrow $T$ Tulenbaev uses the following presentation for the relative Steinberg group, see~\cite[Proposition~1.6]{Tul}. 
-%Assume that $I\trianglelefteq R$ such that a short exact sequence
-%\renewcommand{\theequation}{$\dagger$}
 \setcounter{lm}{1}
@@
 while it is not so easy when it comes to the additivity in the first argument, cf. \eqref{add3}.
-%Such presentations allowed them to formulate easily an additivity by the second argument, but one has to write something similar to T3 instead of additivity by the first one.
 
@@
  For a splitting ideal $I \trianglelefteq R$ and $n\geq 4$ the groups $\St^*(n,\,R,\,I)$ and $\St(n,\,R, I)$ are isomorphic.
-% there exists a well-defined homomorphism $$\iota\colon\St^*(n,\,R,\,I)\rightarrow\St(n,\,R, I) \subseteq \St(n, R)$$ 
-% satisfying the equalities $\iota (F(u,\,v)) = X(u,\,v)$ and $\iota (S(u,\,v)) = Y(u,\,v)$. 
 \end{prop}
-%\begin{proof}
-%We already know that $\iota$ is well-defined. It suffices to check that the image of $\iota$ is contained in $\St(n,\,R,I)$.
-%Denote the canonical projection $R\epi R/I$ by $\rho$.
-%Clearly, the induced group morphism $\rho^*\colon\St(n,\,R)\rightarrow\St(n,\,R/I)$ sends $X(u,\,v)$ to $X(\rho(u),\,\rho(v))$ and $Y(u,\,v)$ to $Y(\rho(u),\,\rho(v))$. 
-%Observe that $\E(n,\,R)\epi\E(n,\,R/I)$ is surjective, therefore for $x\in\E(n,\,R)e_1$ one has $\rho(x)\in\E(n,\,R/I)e_1$. 
-%, as required. \end{proof}
-
-\begin{comment}
-We constructed $\iota$ for an arbitrary $I\trianglelefteq R$. For $I$ a splitting ideal we construct an inverse homomorphism
-$$
-\kappa\colon\St(n,\,R,\,I)\rightarrow\St^*(n,\,R,\,I).
-$$
-With this end we recall a presentation of $\St(n,\,R,\,I)$ as a group with action of $\St(n,\,R)$.
-For a splitting ideal such a presentation was firstly obtained by Swan~\cite{Swa1,Swa2,Swa3}, and for an arbitrary $I$ by Keune~\cite{Keu} and Loday~\cite{Lod}.
-
-For a group $G$ acting on a group $H$ from the left denote by $\!\,^gh$ the image of $h\in H$ under homomorphism corresponding by $g\in G$.
-
-Let $I\trianglelefteq R$ be a splitting ideal then $\St(n,\,R,\,I)$ can be presented as a group with action of $\St(n,\,R)$ with the set of (relative) generators
-$$
-\{y_{ij}(a)\mid a\in I,\ 1\leq i\neq j\leq n\}
-$$
-subject to relations
-\setcounter{equation}{0}
-\renewcommand{\theequation}{KL\arabic{equation}}
-\begin{align}
-&y_{ij}(a)y_{ij}(b)=y_{ij}(a+b),\\
-&\!\,^{x_{ij}(r)}y_{hk}(b)=y_{hk}(b),\text{ for }h\neq j,\ k\neq i,\\
-&\!\,^{x_{ij}(r)}y_{jk}(b)\cdot y_{jk}(-b)=y_{ik}(rb),\\
-&y_{ij}(a)\cdot\,^{x_{jk}(s)}y_{ij}(-a)=y_{ik}(as),\\
-&\!\,^{x_{hk}(a)}\big(\!\,^gy_{ij}(b)\big)=y_{hk}(a)\cdot\,^gy_{ij}(b)\cdot y_{hk}(-a)\,\text{ for }a\in I,\ g\in\St(n,\,R).
-\end{align}
-
-In other words, $\St(n,\,R,\,I)$ is isomorphic to a quotient group of a free group $F$ on the set of generators 
-$$\St(n,\,R)\times\{y_{ij}(a)\mid a\in I,\ 1\leq i\neq j\leq n\}$$
-(the natural action of $\St(n,\,R)$ on $F$ is given by $\!\,^f(g,\,y)=(fg,\,y)$) modulo the normal equivariant subgroup generated by KL1--KL5 (where $y_{ij}(a)$ stands for $(1,\,y_{ij}(a))$.
-Keune in Loday consider only stable Steinberg group $\St(R)=\varinjlim\St(n,\,R)$.
-This presentation for unstable group firstly appeared in~\cite{SCh} in the context of Chevalley groups.
-Observe that the definition of the relative Steinberg group in~\cite[Def.~3.3]{SCh} differs from ours but remark after this definition and~\cite[Lem.~8]{SCh} immediantly imply that for a splitting ideal $I\trianglelefteq R$ it coincides with the one given in the present paper.
-The existance of the presentation is proven in~\cite[Prop.~6]{SCh}.
-Relation~5 in~\cite[Prop.~6]{SCh} joins relations KL3 and KL4, and relations~2 and 3 follow from KL4 and KL5 with the use of KL6.
-
-One could probably wonder why Tulenbaev needs his own presentation for $\St(n,\,R,\,I)$ and does not use the one of Keune--Loday.
-The reason is the following.
-To construct a map from Keune--Loday group one should firstly define an action of the absolute Steinberg group on the target group, in our context, the action of $\St(n,\,B_a)$ on $\St(n,\,B,\,I)$, what is probably possible, but seems to be much harder, then giving another presentation (in particular, one should define $\!\,^{x_{ij}(r/a^m)}y_{ji}(c)$).
-
-Now, to construct
-$
-\kappa\colon\St(n,\,R,\,I)\rightarrow\St^*(n,\,R,\,I)
-$
-we need to define an action of $\St(n,\,R)$ on $\St^*(n,\,R,\,I)$ and find elements $y^*_{ij}(a)\in\St^*(n,\,R,\,I)$ subject to KL1--KL5.
-To define a action of the absolute group we use van der Kallen's another presentaion for it.
-For $u\in\Um(n,\,R)$, $v\in R^n$, $u^tv=0$ define
-$
-\alpha(u,\,v)\colon\St^*(n,\,R,\,I)\rightarrow\St^*(n,\,R,\,I)
-$
-by $\alpha(u,\,v)\big(F(u',\,v')\big)=F(t(u,\,v)u',\,t(u,\,v)^*v')$, and $\alpha(u,\,v)\big(S(u',\,v')\big)=S(t(u,\,v)u',\,t(u,\,v)^*v')$.
-Obviously, the images of the generators satisfy R1--R4, so that $\alpha(u,\,v)$ is a well-defined automorphism.
-Also, $\alpha$'s themselves clearly satisfy K1--K2, thus $X(u,\,v)\mapsto\alpha(u,\,v)$ is a well-defined action of $\St(n,\,R)$ on $\St^*(n,\,R,\,I)$.
-
-Next, define $y_{ij}^*(a)=F(e_i,\,e_ja)$, $a\in I$. These elements obviously satisfy KL1, KL2 and KL5. Check KL3:
-\begin{multline*}
-\!\,^{x_{ij}(r)}y^*_{jk}(b)=F(t_{ij}(r)e_j,\,t_{ji}(-r)e_kb)=F(e_ir+e_j,\,e_kb)=\\
-=S(e_irb+e_jb,\,e_k)=S(e_irb,\,e_k)S(e_jb,\,e_k)=F(e_i,\,e_krb)F(e_j,\,e_kb).
-\end{multline*} 
-KL4 is similar. Finally, we have a well-defined map
-$$
-\kappa\colon\St(n,\,R,\,I)\rightarrow\St^*(n,\,R,\,I)
-$$
-sending $y_{ij}(a)$ to $y^*_{ij}(a)$. 
-\end{comment}
 
 \section{The local-global principle for \texorpdfstring{$\Kt$}{K2}}\label{sec:lgp}
-%At this point we have demonstrated for $n\geq4$ and a splitting ideal $I$ that $\St^*(n,\,R,\,I)$ and $\St(n,\,R,\,I)$ are isomorphic.
 Now we turn to the main result of this paper, namely, for $n\geq 4$ we construct the map $$T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X]),$$ that fits into the diagram \eqref{eq:diagram}.
@@
 The key feature of this definition is that the assumption $u \in\Um(n, B)$ is replaced by a weaker condition $a \in I(u)$ equivalent to imposing that $u$ becomes unimodular after localisation by the powers of $a$.
-%The idea is the following. Say $a$ is not a zero divisor, then $ua^m\in B$ for some $m$ and we will construct some element ``$X(ua^m,\,va^{-m})$''.
-%One can not garantee that $ua^m\in\E(n,\,B)e_1a^k$, however, the ideal generated by entries of $ua^m$ contains some power of $a$ .
-%More formally, we have the following definition.
-%Then, we need generators parametrised by pairs $(u,\,v)$ with $u^tv=0$, $v\in I$, $a^m\in\mathrm I(u)$ for some $m\in\mathbb N$. Such generators are defined in~\cite{Tul}.
 

### 2016-05-24 paper.tex
Somehow managed to avoid discussion about Steinberg groups of rank 1

@@
        for sufficiently large $n$ one has $ev_{X = a^n Y}^*(h) = 1 \in \St(\Phi, A[Y])$, where $ev_{X=a^n Y}$ denotes the unique $R$-algebra morphism $R[X]\to R[Y]$ sending $X$ to $a^nY$;
- \item Quillen's local global principle for $\Kt$ holds for $\St(\Phi, -)$;
- \item the centrality of $\Kt$ holds for $\St(\Phi, -)$.
+ \item the assertion of \cref{tm:lg-principle} holds for $\St(\Phi, -)$;
+ \item $\Kt(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$.
 \end{enumerate} \end{prop}
@@
 
-To formulate this theorem we will need several technical definitions.
-For a simply laced root system $\Phi$ we denote by $\catname{Subsys}(\Phi)$ the category of (not necessarily irreducible) root subsystems of $\Phi$.
-Its objects are all root subsystems $\Psi\subseteq \Phi$ and its morphisms are in one-to-one correspondence with inclusions of the form $\Psi_1\subseteq \Psi_2$.
-It is clear that the relative Steinberg group can be turned into a functor $\St(-, R, I)\colon \catname{Subsys}(\Phi) \rightarrow\catname{Groups},$ cf.~\cite[Lemma~6]{SCh}.
+To formulate this theorem we will need one more definition.
+For $s\in I$, $r\in R$ and $\alpha\in \Phi$ we set $z_\alpha(s, r) := x_\alpha(s)^{x_{-\alpha}(r)} \in \St(\Phi, R, I)$.
+If the rank of $\Phi$ is at least $2$ then $\St(\Phi, R, I)$ is generated by the set consisting of all elements $z_\alpha(s,r)$, see~\cite[Lemma~5]{SCh}.
 
-We denote by $\mathcal{G}_{1,n}$ the full subcategory of $\catname{Subsys}(\Phi)$ whose objects are root subsystems $\Psi\subseteq \Phi$ having type $\rA_1$ or $\rA_n$. 
-It is easy to see that $\mathcal{G}_{1,n}$ is a directed bipartite graph whose only nonidentical morphisms are inclusions of the form $i_{\alpha, \Psi}\colon \{\alpha, -\alpha\} \subseteq \Psi \cong \rA_n$, for $\Psi \subseteq \Phi$.
-The following result has been proved in~\cite{SCh}, see~Theorem~9.
-\begin{tm*} \label{tm:relPres} For a simply laced irreducible root system $\Phi$ of rank $\geq 3$
-the group $\St(\Phi, R, I)$ is isomorphic as an abstract group to $\varinjlim_{\mathcal{G}_{1,3}}\St(-, R, I)$. \end{tm*}
-%\begin{proof} See~\cite[Theorem~9]{SCh} \end{proof}
+Now denote by $G_0$ the free product of Steinberg groups $\St(\Psi, R, I)$ where $\Psi$ varies over all root subsystems of $\Phi$ which have type $\rA_3$.
+Denote by $z_\alpha^\Psi(s,r)$ the image of $z_\alpha(s,r)\in\St(\Psi, R, I)$ under the canonical embedding $\St(\Psi, R, I) \hookrightarrow G_0$.
+Now let $G$ be the quotient of $G_0$ modulo all relations of the form $z_\alpha^{\Psi_1}(s, r) = z_\alpha^{\Psi_2}(s, r)$, where $\alpha\in\Psi_1\cap\Psi_2$, $s\in I$, $r\in I$ 
+and both $\Psi_1$ and $\Psi_2$ have type $\rA_3$.
+The following result has been proved in~\cite{SCh}, see~Theorem~9 combined with Remark~3.16.
+\begin{tm*} \label{tm:relPres} For a simply laced irreducible root system $\Phi$ of rank $\geq 3$ the canonical map $G \rightarrow \St(\Phi, R, I)$ is an isomorphism of groups.
+\end{tm*}
 
 The above theorem allows one to construct the arrow $T_\Phi$ by means of the universal property of colimits.
-More precisely, one needs to construct the maps $T_{\Psi}$ for subsystems $\Psi\subseteq\Phi$ of type $\rA_3$ and then check that
-relations $T_\Psi \circ i_{\alpha, \Psi} = T_{\Psi'} \circ i_{\alpha, \Psi'}$ hold for all $\Psi$, $\Psi'$ of type $\rA_3$ containing a common root $\alpha$
-(here $i_{\alpha, \Psi}$ denotes the obvious morphism $\St(\{\alpha, -\alpha\}, R, I) \to \St(\Psi, R, I)$).
-The latter check is relatively formal and, essentially, has already been made in~\cite{SCh} 
-(see the proof of Lemma~14 and notice that everywhere in it $\rA_4$'s can be replaced with $\rA_3$'s).
-On the other hand, constructing $T_\Psi$ for $\Psi=\rA_3$ is not at all obvious and will be done in the following sections.
+More precisely, one needs to construct the maps $T_{\Psi}$ for all subsystems $\Psi\subseteq\Phi$ of type $\rA_3$ and then check that
+relations $T_{\Psi_1}(z_\alpha^{\Psi_1}(s,r)) = T_{\Psi_2}(z_\alpha^{\Psi_2}(s,r))$ hold for all $\Psi_1$, $\Psi_2$ of type $\rA_3$ containing a common root $\alpha$.
+If in the latter statement one replaces $\rA_3$'s with $\rA_4$'s then such a check has already been made in~\cite{SCh}, see Lemma~14.
+It is easy to see that the argument of Lemma~14 works verbatim in our situation (one only has to replace all references to Lemma~3 in its proof with references to Lemma~2).
+On the other hand, the probem of existence of $T_\Psi$ for $\Psi$ of type $\rA_3$ is not easy and will be solved in the following sections of the paper.
 

### 2016-05-25 paper.tex
Written honest proof of the remark in the beginning of section 2

@@
 For a splitting ideal $I\trianglelefteq R$ the \emph{relative Steinberg group} $\St(\Phi, R, I)$ can be defined as the kernel $\Ker\big(\St(\Phi,\,R)\epi\St(\Phi,\,R/I)\big)$.
+Applying the functor $\St(\Phi, -)$ to $\pi$ and $\sigma$ we get that $\St(\Phi, R) = \St(\Phi, R, I) \rtimes \St(\Phi, R/I)$.
 
@@
 \setcounter{equation}{1}
-\begin{equation} \xymatrix{\St(\Phi,\,R\ltimes XR_a[X],\,XR_a[X]) \ar@{^{(}->}[r] \ar[d]_-{\lambda_a^*} & \St(\Phi, R \ltimes XR_a[X]) \ar[d]_-{\lambda_a^*} \\
+\begin{equation} \xymatrix{\St(\Phi,\,R\ltimes XR_a[X],\,XR_a[X]) \ar@{^{(}->}[r] \ar[d] & \St(\Phi, R \ltimes XR_a[X]) \ar[d]_-{\lambda_a^*} \\
                            \St(\Phi,\,R_a[X],\,XR_a[X]) \ar@{-->}[ru]_-{T_\Phi} \ar@{^{(}->}[r] & \St(\Phi, R_a[X])} \label{eq:diagram} \end{equation}
-Here, $R\ltimes XR_a[X]$ denotes the semidirect product of the ring $R$ and the $R$-algebra $XR_a[X]$ (see~e.\,g.~\cite[Definition~3.2]{SCh}), $\lambda_a^*$ is the morphism of Steinberg groups induced by the morphism $\lambda_a\colon R \to R_a$ of localisation by the powers of $a$.
+Here, $R\ltimes XR_a[X]$ denotes the semidirect product of the ring $R$ and the $R$-algebra $XR_a[X]$ 
+(see~e.\,g.~\cite[Definition~3.2]{SCh}), $\lambda_a^*$ is the morphism of Steinberg groups induced by the morphism $\lambda_a\colon R \to R_a$ of localisation by the powers of $a$ and 
+the left arrow is the restriction of $\lambda_a^*$ to the first factor in the decomposition $\St(\Phi, R \ltimes XR_a[X]) \cong \St(\Phi, R\ltimes XR_a[X], XR_a[X]) \rtimes \St(\Phi, R)$.
 Notice that $XR_a[X]$ is a splitting ideal for both $R_a[X]$ and $R \ltimes XR_a[X]$.
 \end{df}
-It is clear that the image of $T_\Phi$ is contained in the image of the top arrow, therefore, Tulenbaev lifting property implies that the relative Steinberg groups in the left-hand side of the diagram are isomoprhic.
+In fact, one can show that Tulenbaev lifting property implies that the relative Steinberg groups in the left-hand side of the diagram are isomorphic.
+To see this, notice that the commutativity of the top (resp. bottom) triangle implies that left arrow is injective (resp. surjective).
 

### 2016-05-25 paper.tex
Fixed all Andrei's remarks

@@
 Applying the functor $\St(\Phi, -)$ to $\pi$ and $\sigma$ we get that $\St(\Phi, R) = \St(\Phi, R, I) \rtimes \St(\Phi, R/I)$.
+Here the group $\St(\Phi, R/I)$ acts on $\St(\Phi, R, I)$ by conjugation via the splitting map, i.\,e. $(g, h) (g',h') = (g {}^{\sigma^*(h)}g', hh')$.
 
@@
 
-Summing up the above discussion, we have shown that both \cref{tm:centrality} and \cref{tm:lg-principle} follow from Tulenbaev's lifting property in the special case $\Phi=\rA_3$.
+Summing up the above discussion, we have shown that both \cref{tm:centrality} and \cref{tm:lg-principle} follow from the special case $\Phi=\rA_3$ of Tulenbaev's lifting property.
 
 \section{Yet another presentation for the relative Steinberg group.} \label{sec:yap}
-
-In order to construct the arrow $T$ Tulenbaev uses the following presentation for the relative Steinberg group, see~\cite[Proposition~1.6]{Tul}. 
+In order to construct the arrow $T$ Tulenbaev uses a variant of ``another presentation'' for the relative Steinberg group, cf.~\cite[Proposition~1.6]{Tul}. 
 \setcounter{lm}{1}
@@
 \end{align}
-Moreover, the group $\St(n, R)$ decomposes into the semidirect product $\St(n,\,R, I)\rtimes \St(n,\,R/I)$.
+Moreover, one can replace the last family of relations in the definition of $\St(n, R, I)$ with the following smaller family:
+\setcounter{equation}{2} \renewcommand{\theequation}{T\arabic{equation}'}
+\begin{equation} X(e_ir+e_j,\,e_k)=X(e_i,\,rae_k)X(e_j,\,ae_k)\,\text{ for }r\in R,\ a\in I\text{ and } i,j,k\text{ distinct}. \label{add3'} \end{equation} 
 \end{prop}
-Here, $\Um_{n\times2}(R)$ denotes the set of $n\times2$ \emph{unimodular matrices}, i.\,e.
-matrices $M$ such that there exists a $2\times n$ matrix $N$ satisfying $NM=\begin{pmatrix}1&0\\0&1\end{pmatrix}$.
-In the definition of the semidirect product the group $\St(n, R/I)$ acts on $\St(n, R, I)$ by conjugation via the splitting map, i.\,e.
-${}^g X(u,\,v) = X(\phi(\sigma(g))u, \phi(\sigma(g))^*v)$ for $g \in \St(n, R/I)$.
+In the statement of the third relation we denote by $\Um_{n\times2}(R)$ the set of $n\times2$ \emph{unimodular matrices},
+i.\,e. matrices $M$ such that there exists a $2\times n$ matrix $N$ satisfying $NM=\left(\begin{smallmatrix}1&0\\0&1\end{smallmatrix}\right)$.
 
-\begin{proof} For the sake of completeness we present below a more detailed version of Tulenbaev's proof.
-Tulenbaev constructs a pair of mutually inverse maps
+\begin{proof} 
+Since the statement of our proposition contains one more claim which is not contained in~\cite[Proposition~1.6]{Tul}, we reproduce below a more detailed version of the original proof of Tulenbaev.
+The idea is to construct a pair of mutually inverse maps (as before, $\St(n, R/I)$ acts on $\St(n,R,I)$ by conjugation):
 $$\xymatrix{ \St(n, R, I) \rtimes \St(n, R/I) \ar@<0.6ex>[r]^-\varphi &  \ar[l]^-\psi \St(n, R).}$$
 
-Define the map $\psi$ by $\psi(x_{ij}(\xi)) = (X(e_i, (\xi - e_j\pi(\xi)),\ x_{ij}(\pi(\xi)))$. 
+We define the map $\psi$ by $\psi(x_{ij}(\xi)) = (X(e_i, (\xi - e_j\pi(\xi)),\ x_{ij}(\pi(\xi)))$. 
 We have to check that $\psi$ preserves relations \eqref{add0}--\eqref{ccf2}.
@@
 \setcounter{lm}{3}
-After applying additivity relations \eqref{add2}, \eqref{add3} and moving the factor $X(e_i, - e_j\xi')$ to the left hand side of the formula by means of relation \eqref{conj2}
+After applying additivity relations \eqref{add2}, \eqref{add3'} and moving the factor $X(e_i, - e_j\xi')$ to the left hand side of the formula by means of relation \eqref{conj2}
 one gets the following expression:
@@
 Verification of the fact that $\psi$ preserves relations \eqref{add0}, \eqref{ccf1} is similar to the above computation but is easier.
-In particular, one does not need to use relation~\eqref{add3}.
+In particular, one does not need to use the relation~\eqref{add3'}.
 
-It remains to check that the map $\varphi$ given by $\varphi\left((X(u, v), 1)\right) = X(u, v),$ $\varphi\left((1, x_{ij}(\xi))\right) = X(e_i, e_j\sigma(\xi))$
-is well-defined and inverse to $\psi$.
+Now define the map $\varphi$ by $\varphi\left((X(u, v), 1)\right) = X(u, v),$ $u\in E(n, R)e_1$, $v\in I^n$, $\varphi\left((1, x_{ij}(\xi))\right) = X(e_i, e_j\sigma(\xi))$.
+It is clear that $\varphi$ preserves the relations \eqref{add2}--\eqref{conj2}.
+The relation~\eqref{add3} follows from~\eqref{add1}--\ref{conj1}, see~\cite[(1.3)]{Tul}, thus, the map $\varphi$ is well-defined.
+it is easy to check that $\varphi\psi=1$ therefore $\psi$ is injective.
+To see that $\psi$ is surjective it remains to notice that the elements $(X(u,v), 1)$, $u\in \E(n, R)e_1$, $v\in I^n$ lie in the image of $\psi$.
 \end{proof}
-
-\begin{rk} \label{rk:T123'} Notice that from the proof of the above proposition it follows that one could replace the family of relations \eqref{add3}
-in the definition of $\St(n, R, I)$ with the following smaller family:
-\setcounter{equation}{2} \renewcommand{\theequation}{T\arabic{equation}'}
-\begin{equation} X(e_ir+e_j,\,e_k)=X(e_i,\,rae_k)X(e_j,\,ae_k)\,\text{ for }r\in R,\ a\in I\text{ and } i,j,k\text{ distinct}. \label{add3'} \end{equation} 
-This follows from the fact that only this smaller family of relations was actually used in the construction of the map $\psi$
-(more precisely, it was used to simplify the second factor of~\eqref{eq:proofS3}). \end{rk}
 
@@
 amounts to choosing certain elements in the group $\St(n,\,R\ltimes XR_a[X])$ and proving that these elements satisfy relations \eqref{add2}--\eqref{add3}, see~\cite[Lemmas~1.2 and~1.3\,c)]{Tul}.
-The main problem with this recipe is that the assumption $n\geq5$ is essential to check that the relation~\eqref{add3} holds.
-It is not possible to choose arbitrary orthogonal vectors $u$, $v$ as parameters for the generators, since in this situation it is not even known that $t(u,\,v)\in\E(n,\,R)$.
+The main problem with this recipe is that the assumption $n\geq5$ is essential for the verification of the fact that relations~\eqref{add3} (or even~\eqref{add3'}) hold.
+%It is not possible to choose arbitrary orthogonal vectors $u$, $v$ as parameters for the generators, since in this situation it is not even known that $t(u,\,v)\in\E(n,\,R)$.
 
@@
 We set $$\kappa(X(u,v)) = F(u,v),\ u\in \E(n, R)e_1,\ v\in I^n.$$ 
-In view of \cref{rk:T123'} it suffices to check that $F(u,v)$ satisfy the relations \eqref{add2}, \eqref{conj2}, \eqref{add3'}.
+It suffices to check that $F(u,v)$ satisfy the relations \eqref{add2}, \eqref{conj2}, \eqref{add3'}.
 The validity of relations \eqref{add2}, \eqref{conj2} is obvious, while \eqref{add3'} follows from \eqref{add5} and \eqref{coinc}. Indeed,
@@
 For a vector $u\in R^n$ we denote by $I(u)$ the ideal generated by the components of $u\in R^n$, i.\,e. $I(u)=\sum\limits_{k=1}^nu_kR$.
-To prove \cref{a3map} we follow the approach of Tulenbaev and construct yet another family of elements $X_{u,v}(a)\in \St(n,\,B)$, $a\in B$ which contains van der Kallen's generators $X(u, v)$ as a subfamily, i.\,e.
+To prove \cref{a3map} we follow the approach of Tulenbaev and construct certain family of elements $X_{u,v}(a)\in \St(n,\,B)$, $a\in B$ which contains van der Kallen's generators $X(u, v)$ as a subfamily, i.\,e.
 $X_{u,v}(1) = X(u, v)$.

### 2016-06-01 paper.tex
Andrei's fixes

@@
 \usepackage[utf8]{inputenc}
-\usepackage[backend=biber, citestyle=numeric-comp, natbib=true, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
+\usepackage[backend=bibtex, citestyle=numeric-comp, natbib=true, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
 \usepackage[activate={true,nocompatibility}]{microtype}
@@
 \begin{tm}[``Centrality of $\Kt$''] \label{tm:centrality}  Let $R$ be an arbitrary commutative ring.
-Then for $\ell\geq 4$ the group $\Kt(\rD_\ell, R)$ is a central subgroup of $\St(\rD_\ell, R)$. \end{tm}
+Then, for $\ell\geq 4$ the group $\Kt(\rD_\ell, R)$ is a central subgroup of $\St(\rD_\ell, R)$. \end{tm}
 
@@
 All commutators are left-normed, i.\,e. $[x,\,y]=xyx\inv y\inv$. 
-We denote by $R^n$ the free right $R$-module with a basis $e_1,\ldots,e_n$ and by $\Um(n,\,R)$ the subset of unimodular columns $v\in R^n$, i.\,e. 
+We denote by $R^n$ the free right $R$-module with a basis $e_1,\ldots,e_n$ and by $\Um(n,\,R)$ the set of unimodular columns $v\in R^n$, i.\,e. 
 columns whose components generate $R$ as an ideal.
@@
 Here $N_{\alpha,\beta}$ are the structure constants of $\Phi$ which are equal to $\pm 1$.
-We use more a more familiar notation for root unipotents in the case $\Phi=\rA_\ell$:
+We use a more familiar notation for root unipotents in the case $\Phi=\rA_\ell$:
 $x_{ij}(r),\ 1\leq i\neq j\leq n,\ r\in R,$
@@
 and the elementary subgroup $\E(\rA_{n-1}, R)$ is denoted by $\E(n, R)$.
-Here $1$ denotes the identity matrix and $e_{ij}$ ientriess the standard matrix unit. 
+Here $1$ denotes the identity matrix and $e_{ij}$ is the standard matrix unit. 
 The natural projection $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ sends $x_{ij}(r)$ to $t_{ij}(r)$.
@@
 This result clearly implies that $\E(n,\,R)$ is normal in $\GL(n,\,R)$.
-Developing Suslin's ideas, W.~van~der~Kallen showed that for $n\geq4$ the Steinberg group $\St(n,\,R)$ is isomorphic to the group with the following presentation by generators
+Developing Suslin's ideas, van~der~Kallen showed that for $n\geq4$ the Steinberg group $\St(n,\,R)$ is isomorphic to the group with the following presentation by generators
 $$\{X(u,\,v)\mid u\in\Um(n,\,R),\ v\in R^n,\ u^tv=0\}$$ and relations:
@@
 
-In the case of an arbitrary $I$ the relative Steinberg group $\St(\Phi, R, I)$ does not have to be a subgroup of $\St(\Phi, R)$ and should be defined as a central extension of the above kernel.
+In the case of an arbitrary $I$ the relative Steinberg group $\St(\Phi, R, I)$ is not a subgroup of $\St(\Phi, R)$ and should be defined as a central extension of the above kernel.
 For the purposes of the present text it suffices to consider only relative Steinberg groups corresponding to splitting ideals.
@@
 We claim that the main results of this paper follow from Tulenbaev's lifting property.
-\begin{prop} For any irreducible $\Phi$ of rank $\geq 2$ there are implications $a) \implies b) \implies c) \implies d)$.
+\begin{prop} For any irreducible $\Phi$ of rank $\geq 2$ hold implications $a) \implies b) \implies c) \implies d)$.
 \begin{enumerate}
@@
  \item a dilation principle holds for $\St(\Phi, -)$, i.\,e. if $g\in\St(\Phi, A[X], XA[X])$ is such that $\lambda_a^*(g) = 1 \in \St(\Phi, R_a[X])$ then
-       for sufficiently large $n$ one has $ev_{X = a^n Y}^*(h) = 1 \in \St(\Phi, A[Y])$, where $ev_{X=a^n Y}$ denotes the unique $R$-algebra morphism $R[X]\to R[Y]$ sending $X$ to $a^nY$;
+       for a sufficiently large $n$ one has $ev_{X = a^n Y}^*(h) = 1 \in \St(\Phi, A[Y])$, where $ev_{X=a^n Y}$ denotes the unique $R$-algebra morphism $R[X]\to R[Y]$ sending $X$ to $a^nY$;
  \item the assertion of \cref{tm:lg-principle} holds for $\St(\Phi, -)$;
@@
 
-Now denote by $G_0$ the free product of Steinberg groups $\St(\Psi, R, I)$ where $\Psi$ varies over all root subsystems of $\Phi$ which have type $\rA_3$.
+Now, denote by $G_0$ the free product of Steinberg groups $\St(\Psi, R, I)$ where $\Psi$ varies over all root subsystems of $\Phi$ which have type $\rA_3$.
 Denote by $z_\alpha^\Psi(s,r)$ the image of $z_\alpha(s,r)\in\St(\Psi, R, I)$ under the canonical embedding $\St(\Psi, R, I) \hookrightarrow G_0$.
@@
 %$$\xymatrix{\St^*(n,\,R,\,I)\ar@<0.0ex>[r]^{\iota}&\St(n,\,R).}$$
-Clearly, $\iota$ the elements $F(u,\,v)$ should go to van der Kallen's generators $X(u,\,v)$.
+Clearly, the elements $F(u,\,v)$ should go to van der Kallen's generators $X(u,\,v)$.
 But now we should find the images for the elements $S(u,\,v)$ as well.
@@
 \begin{prop} \label{lm:map-iota}
- For a splitting ideal $I \trianglelefteq R$ and $n\geq 4$ the groups $\St^*(n,\,R,\,I)$ and $\St(n,\,R, I)$ are isomorphic.
+ For a splitting ideal $I \trianglelefteq R$ and $n\geq 4$ the groups $\St^*(n,\,R,\,I)$ and $\St(n,\,R,\,I)$ are isomorphic.
 \end{prop}
@@
 Set $Y_{u,v}(a)=\prod_{k=1}^Mx(u_ka,\,v)$. 
-Similarly to \ref{df:TulX} one can check that this definition does not depend either on the order of factors or on the choice of decomposition for $u$.
+Similarly to \ref{df:TulX} one can check that this definition does depend neither on the order of factors nor on the choice of decomposition for $u$.
 \end{df}

### 2016-06-01 paper.tex
Purged unnecessary things in preamble

@@
 
-\newlist{thmlist}{enumerate}{1} \setlist[thmlist]{label=(\roman{thmlisti}), ref=\thethm.(\roman{thmlisti}),noitemsep} \Crefname{thmlisti}{Theorem}{Theorems}
-\newlist{lemlist}{enumerate}{1} \setlist[lemlist]{label=(\roman{lemlisti}), ref=\thelemma.(\roman{lemlisti}),noitemsep} \Crefname{lemlisti}{Lemma}{Lemmas}
-
 \theoremstyle{plain} \declaretheorem[name=Theorem, Refname={Theorem,Theorems}]{tm} \Crefname{tm}{Theorem}{Theorems}
@@
 \theoremstyle{remark} \newtheorem{rk}[lm]{Remark} \Crefname{rk}{Remark}{Remarks}
-\newtheorem*{mtm}{Main Theorem}
-\newtheorem*{atm}{Another Presentation}
-\newlist{lmlist}{enumerate}{1} \setlist[lmlist]{label={\rm(\roman{lmlisti})}, ref=\thelm.(\roman{lmlisti}),noitemsep} \Crefname{lmlisti}{Lemma}{Lemmas}
 
@@
 \newcommand{\rG}{\mathsf{G}}
-\DeclareRobustCommand{\VAN}[2]{#1}
-\newcommand{\catname}[1]{{\normalfont\textbf{#1}}}
-
-\renewcommand{\labelenumi}{\theenumi{\rm)}}
-\renewcommand{\theenumi}{\alph{enumi}}
-
-\newcommand\restr[2]{{\left.\kern-\nulldelimiterspace #1 \vphantom{\big|}\right|_{#2}}}
-\newcommand*\MapsTo{\xrightarrow[\raisebox{0.25 em}{\smash{\ensuremath{\sim}}}]{}}
 

### 2016-09-14 paper.tex
Fixed compilation at arXiv
Fixed referee comments + written equation T3' equivariantly

--- 2016-05-25 paper.tex
@@
 &X(u,\,v)X(u,\,w)=X(u,\,v+w), \label{add1} \\
-&X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(v,\,u)\inv v'). \label{conj1}
+&X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(u,\,v)^* v'). \label{conj1}
 \end{align}
-This presentation clearly implies that $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ is a central extension.
+In the above formula $t(v,\,u)^*$ denotes the corresponding contragradient matrix, i.\,e. $t(v,\,u)^* = t(v,\,u)\inv = t(v,\,-u)$.
+We employ the same notation for contragradient matrices below, i.\,e. for $M\in\E(n,R)$ we set $M^* = (M^t)\inv$.
+
+The above presentation clearly implies that $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ is a central extension.
 Notice that we parametrize elements $X(u, v)$ by two columns rather than by a column and a row as it is done in~\cite{vdK}.
@@
 In order to construct the arrow $T_\Phi$ fitting in the diagram~\eqref{eq:diagram} one needs to have some direct description of the relative Steinberg group $\St(\Phi, R, I)$.
-For example, in~\cite{Tul} Tulenbaev uses a variant of of W.~van~der~Kallen's ``another presentation'' for this purpose. The details of this approach are outlined in the next section.
+For example, in~\cite{Tul} Tulenbaev uses a variant of W.~van~der~Kallen's ``another presentation'' for this purpose. The details of this approach are outlined in the next section.
 On the other hand, in~\cite{SCh} the second-named author obtained a theorem which asserts that the relative Steinberg group $\St(\Phi, R, I)$ can be presented as an amalgamated product of
@@
 \setcounter{equation}{2} \renewcommand{\theequation}{T\arabic{equation}'}
-\begin{equation} X(e_ir+e_j,\,e_k)=X(e_i,\,rae_k)X(e_j,\,ae_k)\,\text{ for }r\in R,\ a\in I\text{ and } i,j,k\text{ distinct}. \label{add3'} \end{equation} 
+\begin{equation} X(Me_1r+Me_2,\,M^*e_3a)=X(Me_1,\,M^*e_3ar)X(Me_2,\,M^*e_3a)\, \label{add3'} \end{equation} 
+for $r\in R$, $a\in I$ and $M\in E(n, R)$.
 \end{prop}
 In the statement of the third relation we denote by $\Um_{n\times2}(R)$ the set of $n\times2$ \emph{unimodular matrices},
-i.\,e. matrices $M$ such that there exists a $2\times n$ matrix $N$ satisfying $NM=\left(\begin{smallmatrix}1&0\\0&1\end{smallmatrix}\right)$.
+i.\,e. matrices $m$ such that there exists a $2\times n$ matrix $m'$ satisfying $m'm=\left(\begin{smallmatrix}1&0\\0&1\end{smallmatrix}\right)$.
 
@@
 Let $F(u,\,v)$ be an arbitrary generator of the first type and let $M\in\E(n,\,R)$ be such that $F(u,\,v)=F(Me_1,\,M^*\tilde v)$. 
-Here we denote by $M^*$ the contragradient matrix, $M^*=(M\inv)^t$. 
+%As before, we denote by $M^*$ the contragradient matrix, $M^*=(M\inv)^t$.
 By \eqref{add4} we have $$F(u,\,v)=\prod\limits_{k\neq1}F(Me_1,\,M^*e_k\tilde v_k)$$
@@
 The validity of relations \eqref{add2}, \eqref{conj2} is obvious, while \eqref{add3'} follows from \eqref{add5} and \eqref{coinc}. Indeed,
-$$ F(e_i, rae_k) F(e_j, ae_k) = S(rae_i, e_k) S(ae_j, e_k) = S(a(re_i+e_j), e_k) = F(e_ir+e_j, ae_k). \qedhere $$
-
+\begin{multline} F(me_1, m^*e_3ar) F(me_2, m^*e_3a) = S(me_1ar, m^*e_3) S(me_2a, m^*e_3) = \\ = S(m(e_1r+e_2)a, m^*e_3) = F(me_1r+me_2, m^*e_3a). \qedhere \end{multline}
+%TODO: Why the last equality holds? This seems plausible but I'd like to have some precise phrase.
 As for the map $\iota$, we first define it as a homomorphism to the absolute group. % which does not rely on the assumption that $I$ is splitting.

### 2016-09-14 paper.tex

--- 2016-06-01 paper.tex
@@
 \documentclass[11pt]{amsart}
-\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, enumitem, mathtools, xfrac, nameref, thmtools, hyperref}
+\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, enumitem, mathtools, xfrac, microtype, nameref, thmtools, hyperref, cleveref}
 \usepackage[utf8]{inputenc}
 \usepackage[backend=bibtex, citestyle=numeric-comp, natbib=true, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
-\usepackage[activate={true,nocompatibility}]{microtype}
-\usepackage[capitalize]{cleveref}
 \usepackage[english]{babel} 
@@
 Set $Y_{u,v}(a)=\prod_{k=1}^Mx(u_ka,\,v)$. 
-Similarly to \ref{df:TulX} one can check that this definition does depend neither on the order of factors nor on the choice of decomposition for $u$.
+Similarly to \ref{df:TulX} one can check that this definition does not depend either on the order of factors or on the choice of a decomposition for $u$.
 \end{df}

### 2016-09-22 paper.tex
Fixed wrong items in theorems
Minor fixes

@@
 \theoremstyle{remark} \newtheorem{rk}[lm]{Remark} \Crefname{rk}{Remark}{Remarks}
+
+\renewcommand{\labelenumi}{\theenumi{\rm)}}
+\renewcommand{\theenumi}{\alph{enumi}}
 
@@
 Since the statement of our proposition contains one more claim which is not contained in~\cite[Proposition~1.6]{Tul}, we reproduce below a more detailed version of the original proof of Tulenbaev.
-The idea is to construct a pair of mutually inverse maps (as before, $\St(n, R/I)$ acts on $\St(n,R,I)$ by conjugation):
-$$\xymatrix{ \St(n, R, I) \rtimes \St(n, R/I) \ar@<0.6ex>[r]^-\varphi &  \ar[l]^-\psi \St(n, R).}$$
-
+For a time being denote by $G$ the group defined by T1, T2, T3'.
+We write $\pi(\xi)$ for the image of $\xi\in R$ in the quotient ring and assume that $R/I$ is embedded into $R$.
+The idea is to construct a pair of mutually inverse maps:
+$$\xymatrix{G\rtimes \St(n, R/I) \ar@<0.6ex>[r]^-\varphi &  \ar[l]^-\psi \St(n, R)}$$
+where $\St(n, R/I)$ acts on $G$ via $$\,^{X(u,\,v)}X(u',v')=X(t(u,\,v)u',\,t(u,\,v)^*v').$$
 We define the map $\psi$ by $\psi(x_{ij}(\xi)) = (X(e_i, (\xi - e_j\pi(\xi)),\ x_{ij}(\pi(\xi)))$. 
@@
 The validity of relations \eqref{add2}, \eqref{conj2} is obvious, while \eqref{add3'} follows from \eqref{add5} and \eqref{coinc}. Indeed,
-\begin{multline} F(me_1, m^*e_3ar) F(me_2, m^*e_3a) = S(me_1ar, m^*e_3) S(me_2a, m^*e_3) = \\ = S(m(e_1r+e_2)a, m^*e_3) = F(me_1r+me_2, m^*e_3a). \qedhere \end{multline}
+\begin{multline} F(Me_1, M^*e_3ar) F(Me_2, M^*e_3a) = S(Me_1ar, M^*e_3) S(Me_2a, M^*e_3) = \\ = S(M(e_1r+e_2)a, M^*e_3) = F(Me_1r+Me_2, M^*e_3a). \qedhere \end{multline}
 %TODO: Why the last equality holds? This seems plausible but I'd like to have some precise phrase.

### 2016-10-14 paper.tex
Fixed minor bugs discovered after publication is complete

@@
  [x_\alpha(r),  x_\beta(s)] & = x_{\alpha+\beta}(N_{\alpha,\beta}\cdot rs), &\ \alpha,\beta\in \Phi,\ \alpha+\beta\in\Phi, \nonumber \\
- [x_\alpha(r),  x_\beta(s)] & = 1, &\ \alpha,\beta\in \Phi,\ \alpha+\beta\not\in\Phi. \nonumber
+ [x_\alpha(r),  x_\beta(s)] & = 1, &\ \alpha,\beta\in \Phi,\ \alpha \perp \beta. \nonumber
 \end{align}
@@
 We claim that the main results of this paper follow from Tulenbaev's lifting property.
-\begin{prop} For any irreducible $\Phi$ of rank $\geq 2$ hold implications $a) \implies b) \implies c) \implies d)$.
+\begin{prop} For any irreducible $\Phi$ of rank $\geq 2$ hold implications \[a) \implies b) \implies c) \implies d).\]
 \begin{enumerate}
- \item the Steinberg group functor $\St(\Phi, -)$ satisfies lifting property~\eqref{eq:diagram};
- \item a dilation principle holds for $\St(\Phi, -)$, i.\,e. if $g\in\St(\Phi, A[X], XA[X])$ is such that $\lambda_a^*(g) = 1 \in \St(\Phi, R_a[X])$ then
+ \item The Steinberg group functor $\St(\Phi, -)$ satisfies lifting property~\eqref{eq:diagram};
+ \item A dilation principle holds for $\St(\Phi, -)$, i.\,e. if $g\in\St(\Phi, A[X], XA[X])$ is such that $\lambda_a^*(g) = 1 \in \St(\Phi, R_a[X])$ then
        for a sufficiently large $n$ one has $ev_{X = a^n Y}^*(h) = 1 \in \St(\Phi, A[Y])$, where $ev_{X=a^n Y}$ denotes the unique $R$-algebra morphism $R[X]\to R[Y]$ sending $X$ to $a^nY$;
- \item the assertion of \cref{tm:lg-principle} holds for $\St(\Phi, -)$;
+ \item The assertion of \cref{tm:lg-principle} holds for $\St(\Phi, -)$;
  \item $\Kt(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$.

### 2016-12-28 paper.tex
Minor
Fixed more types
Fixed arXiv compilation

@@
 \usepackage[utf8]{inputenc}
-\usepackage[backend=bibtex, citestyle=numeric-comp, natbib=true, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
+\usepackage[backend=bibtex, citestyle=numeric-comp, natbib=true, sortlocale=en_US, url=true, doi=true, eprint=true, maxbibnames=4]{biblatex}            
 \usepackage[english]{babel} 
@@
 %Bibliography
-\renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
-\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{http://dx.doi.org/\thefield{doi}}{#1}}}
-\DeclareFieldFormat{title}{\usebibmacro{string+doi}{\mkbibemph{#1}}}
-\DeclareFieldFormat[article, inproceedings, inbook, thesis]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
-\DeclareFieldFormat{postnote}{#1}
+%\renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
+%\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{http://dx.doi.org/\thefield{doi}}{#1}}}
+%\DeclareFieldFormat{title}{\usebibmacro{string+doi}{\mkbibemph{#1}}}
+%\DeclareFieldFormat[article, inproceedings, inbook, thesis]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
+%\DeclareFieldFormat{postnote}{#1}
 \addbibresource{paper.bib}
@@
 \newcommand{\E}{{\mathrm{E}}}
-\newcommand{\GG}{{\mathrm{G}_{sc}}}
+\newcommand{\GG}{{\mathrm{G}_{\mathrm{sc}}}}
 \newcommand{\Um}{\mathop{\mathrm{Um}}\nolimits}
@@
  [x_\alpha(r),  x_\beta(s)] & = x_{\alpha+\beta}(N_{\alpha,\beta}\cdot rs), &\ \alpha,\beta\in \Phi,\ \alpha+\beta\in\Phi, \nonumber \\
- [x_\alpha(r),  x_\beta(s)] & = 1, &\ \alpha,\beta\in \Phi,\ \alpha \perp \beta. \nonumber
+ [x_\alpha(r),  x_\beta(s)] & = 1, &\ \alpha,\beta\in \Phi,\ \alpha+\beta \not \in \Phi \cup \{0\}. \nonumber
 \end{align}
@@
 \end{align}
-In the above formula $t(v,\,u)^*$ denotes the corresponding contragradient matrix, i.\,e. $t(v,\,u)^* = t(v,\,u)\inv = t(v,\,-u)$.
+In the above formula $t(u,\,v)^*$ denotes the corresponding contragradient matrix, i.\,e. $t(u,\,v)^* = t(v,\,u)\inv = t(v,\,-u)$.
 We employ the same notation for contragradient matrices below, i.\,e. for $M\in\E(n,R)$ we set $M^* = (M^t)\inv$.
@@
 $$\xymatrix{\St^*(n,\,R,\,I)\ar@<0.5ex>[r]^{\iota}&\St(n,\,R,\,I)\ar@<0.5ex>[l]^{\kappa}.}$$
-In order to construct the arrow $\kappa$ we use the presentation from \cref{prop:TulPres}.
+In order to construct the arrow $\kappa$ we use the presentation from Proposition~\ref{prop:TulPres}.
 We set $$\kappa(X(u,v)) = F(u,v),\ u\in \E(n, R)e_1,\ v\in I^n.$$ 
@@
 Tulenbaev shows that the factors $x(u,\,v_ka)$, $1\leq k\leq N$, commute, see~\cite[Lemma~1.1\,e)]{Tul}.
-He also shows that if $v$ admits another decomposition $v=\sum_{j=1}^Mv'_j$ satisfying the assumptions of \cref{df:TulX} then one has
+He also shows that if $v$ admits another decomposition $v=\sum_{j=1}^Mv'_j$ satisfying the assumptions of Definition~\ref{df:TulX} then one has
 $\prod_{k=1}^Nx(u,\,v_ka)=\prod_{j=1}^Mx(u,\,v'_ja)$, see the discussion following \cite[Lemma~1.1]{Tul}.
@@
 Finally, it remains to show that for a ``nice'' pair $(u,\,v)$ the elements $X$ and $Y$ coincide.
-\begin{lm}\label{x=y}
+\begin{lm}\label{xeqy}
 Let $u$, $v$, $x$, $y$ be elements of $B^n$ and $b\in I(u)\cap I(v)$, $r\in B$ be such that $u^t v = 0$, $x^ty=b$, $x^tv=0$, $u^ty=0$, $x^tu = 0$, $y^tv=0$.
@@
 
-The first two assertions of \cref{xproperties} guarantee that this definition does not depend on the choice of $m$ and the liftings $\tilde u$ and $\tilde w$.
+The first two assertions of Lemma~\ref{xproperties} guarantee that this definition does not depend on the choice of $m$ and the liftings $\tilde u$ and $\tilde w$.
 Similarly, we can define $T(S(u,\,v))=Y_{u/a^{3m},\tilde v}(a^{2m})$.
@@
 $$\lambda_a(\tilde{x})=Me_3a^m,\ \lambda_a(\tilde{y})=M^*e_3a^m\text{ and }\tilde{x}^t\tilde{y}=a^{2m},\ \tilde{x}^t\tilde{v} = 0,\ \tilde{u}^t\tilde{y} =0,\ \tilde{x}^t\tilde{u} = 0,\ \tilde{y}^t\tilde{v}=0.$$
-To obtain~\eqref{eq:last} it remains to apply \cref{x=y} (with $b=a^{2m}$, $r=c/a^{12m}$).
+To obtain~\eqref{eq:last} it remains to apply Lemma~\ref{xeqy} (with $b=a^{2m}$, $r=c/a^{12m}$).
 Thus, the map $T$ is well-defined.
